### 2025-04-19 draft.tex
Initial commit

\documentclass[12pt,twoside,a4paper]{report}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{enumerate}
\usepackage[vmargin=2.5cm, hmargin=2.5cm]{geometry}
\usepackage{hyperref}
\usepackage{fontspec}
\usepackage{unicode-math}
\usepackage{stackengine}
\usepackage{minitoc}
\usepackage{amsthm}

\setmainfont{Linux Libertine O}
\setsansfont{Linux Biolinum O}

\setlength{\parindent}{0em}
\addtolength{\parskip}{1ex}

\usepackage[backend=biber,style=ieee]{biblatex}
\addbibresource{ref.bib}

\theoremstyle{definition}
\newtheorem*{definition*}{Definition}

\newcounter{motivation}
\renewcommand{\themotivation}{\Roman{motivation}}

\newcommand{\motivation}[1]{%
    \refstepcounter{motivation}%
    \vspace{1.5em}%
    \noindent\textbf{Motivation \themotivation.  #1}
    \par
    \expandafter\edef\csname savedmotivation\themotivation\endcsname{%
        \noexpand\noindent\noexpand\textbf{Motivation \themotivation. #1}\noexpand\par
    }%
}

\begin{document}

\dominitoc

\title{Using functor categories to generate intermediate code with Agda}
\author{Jack Gao}
\date{\today}
\maketitle

\tableofcontents
\newpage

\chapter{Introduction}
    \minitoc
    An Algol-like language is a typed lambda calculus with store. In this dissertation, the source language is an Algol-like language with the following primitive types:
    \begin{itemize}
        \item 
            \textbf{comm}: the commands
        \item 
            \textbf{intexp}: the integer expressions
        \item 
            \textbf{intacc}: the integer acceptors
        \item 
            \textbf{intvar}: the integer variables
    \end{itemize}
    and the set $\Theta$ of types is defined as follows:
    \[ \Theta := \textbf{comm} \mid \textbf{intexp} \mid \textbf{intacc} \mid \textbf{intvar} \mid \Theta \to \Theta \]

    [Considering adding an example of Algol-like language here]

    The target language is an assembly-style intermediate language for a stack machine. It is defined with four stack-descriptor-indexed families of non-terminals: 
    \begin{itemize}
        \item 
            $\langle\text{L}_{sd}\rangle$: lefthand sides
        \item 
            $\langle\text{S}_{sd}\rangle$: Simple righthand sides
        \item
            $\langle\text{R}_{sd}\rangle$: righthand sides
        \item
            $\langle\text{I}_{sd}\rangle$: instruction sequences
    \end{itemize}

    The grammer of the target language is specified in Chapter 3.

    This dissertation presents an implementation of a compiler from the source language to the target language with Agda \cite{Agda}. This implementation is based on the work of Reynolds \cite{Reynolds}, who presented a denotational semantics of Algol-like languages in the form of a presheaf category over stack descriptors. The compiler is implemented as a functor from the source language to the target language. The implementation is verified with Agda's type system, which ensures that the generated code is well-typed and adheres to the semantics of both the source and target languages. This implementation proves and refines Reynolds' work, providing a practical example of how to use functor categories to generate intermediate code.

    \section{Motivation and related work}
        The denotational semantics of Algol-like languages can be structured as a presheaf category over stack descriptors, which has been shown by Reynolds \cite{essence} and Oles \cite{Oles_1} \cite{Oles_2}. By interpreting the source language into this category, where objects of the category represent instruction sequences parameterised by stack layouts, the semantic model directly yields a compiler. The mathematical structure of the compiler has been specified by Reynolds in his paper ``Using Functor Categories to Generate Intermediate Code'' \cite{Reynolds}.

        This project is motivated and guided by the following:

        \motivation{Implementation of the compiler}
        Reynolds concluded that he did not have a proper dependently typed programming language in hand, so his compiler remained a partial function theoretically. We aim to provide a computer implementation of this theoretical framework in a dependently typed programming language.

        \motivation{Formal verification of the compiler}
        The terms in Reynolds' work are also written by hand. Terms are complicated and error-prone, and it is difficult to verify the correctness of the terms. We aim to provide a formalisation of the terms in a proof assistant to verify the correctness of the terms.

        \motivation{Trend of verified compilers}
        The rise of verified compilers including CompCert \cite{CompCert}, CakeML \cite{CakeML} reflects a broader trend toward trustworthy systems, where correctness proofs replace testing for critical guarantees. Like Lean 4 \cite{Lean4}, we leverage dependent types to internalise the verification of correctness of terms.

    \section{Language choice: Agda's advantages}
        Agda \cite{Agda} is a dependently typed programming language and proof assistant. Agda captures the source language's intrinsic sytax with indexed families, which contains only well-typed terms. Therefore, it focuses on the correct programs and rules out the ill-typed nonsensical inputs.

        (Example of Agda)

        Dependently typed languages provide a natural framework for expressing functor categories is proven both theoretically and practically. There have been dependent-type-theoretic model of categories \cite{Dybjer}, and it has been shown that functor categories arise naturally as dependent function types \cite{Jacobs}. A formalisation of Category Theory, including Cartesian Closed Categories, functors and presheaves has been developed in Agda by Hu and Caratte \cite{Cat_Agda}. Other proof assistants, such as Isabelle/Hol, does not have a dependently typed language structure, and thus cannot express the functor categories as naturally as Agda.

        [Do I need a table for comparing other proof assistants and Agda?]

    \section{Contributions}
        Addressed the two motivations presented in 1.1 and contributed to the following:
        \begin{quote}
            \savedmotivationI
            We implemented the compiler from the source language to the target language in Agda.

            \savedmotivationII
            We formalised the terms in the source language and target language in Agda, and proved that the compiler is a functor from the source language to the target language.

            \savedmotivationIII
            This implementation follows the trend of verified compilers, and provides a practical example of how to use functor categories to generate intermediate code.
        \end{quote}

\chapter{Preparation}
    \minitoc

    \section{Starting Point}
    Prior to this project, I had no experience with Agda. Although I was aware of the open-source online tutorial \textit{Programming Language Foundations in Agda} (PLFA) \cite{plfa}, my preparation was limited to setting up the Agda environment on my laptop by following the ``Front Matter'' section of the tutorial.

    I did not have any other experience with compiler beyond Part IB Compiler Construction Course. I had no prior exposure to category theory and type theory before the Part II lectures.

    \section{Category theory background}
        Category 
        \subsection{Category}
        \begin{definition*}[Category]
            A category $\mathcal{C}$ is specified by the following:
            \begin{itemize}
                \item 
                    a collection of objects $\textbf{obj}(\mathcal{C})$, whose elements are called $\mathcal{C}$-objects;
                \item 
                    for each $X, Y \in \textbf{obj}(\mathcal{C})$, a collection of morphisms $\mathcal{C}{(X,Y)}$, whose elements are called $\mathcal{C}$-morphisms from $X$ to $Y$;
                \item 
                    for each $X \in \textbf{obj}(\mathcal{C})$, an element $\textbf{id}_X \in \mathcal{C}{(X,X)}$ called the identity morphism on $X$;
                \item 
                    for each $X, Y, Z \in \textbf{obj}(\mathcal{C})$, a function 
                    \[\begin{aligned}
                        \mathcal{C}{(X,Y)} \times \mathcal{C}{(Y,Z)} &\to \mathcal{C}{(X,Z)} \\
                        (f,g) &\mapsto g \circ f
                    \end{aligned}\]
                    called the composition of morphisms;
            \end{itemize}
            satisfying the following properties:
            \begin{itemize}
                \item 
                    \textbf{(Unit Law)}
                    for all $X, Y \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$, we have:
                    \begin{equation} \label{law: unit}
                        \textbf{id}_Y \circ f = f = f \circ \textbf{id}_X
                    \end{equation}
                \item
                    \textbf{(Associativity Law)}
                    for all $X, Y, Z, W \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$, $g \in \mathcal{C}{(Y,Z)}$, $h \in \mathcal{C}{(Z,W)}$, we have:
                    \begin{equation} \label{law: associativity}
                        h \circ (g \circ f) = (h \circ g) \circ f
                    \end{equation}
            \end{itemize}

            [Considering adding different notations for morphisms, composition, identity morphisms, etc.]
            [Considering adding a diagram for the definition of category]
            [Considering adding examples of categories]

        \end{definition*}

        \subsection{Functor}
        \begin{definition*}[Functor]
            A functor $F$ from a category $\mathcal{C}$ to a category $\mathcal{D}$ is specified by the following:
            \begin{itemize}
                \item 
                    a function 
                    \[\begin{aligned}
                        \textbf{obj}(\mathcal{C}) &\to \textbf{obj}(\mathcal{D}) \\
                        X &\mapsto F(X)
                    \end{aligned}\]

                \item 
                    for each $X, Y \in \textbf{obj}(\mathcal{C})$, a function 
                    \[\begin{aligned}
                        \mathcal{C}{(X,Y)} &\to \mathcal{D}{(F(X),F(Y))} \\
                        f &\mapsto F(f)
                    \end{aligned}\]
            \end{itemize}
            satisfying the following properties:
            \begin{itemize}
                \item 
                    for all $X, Y \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$, we have:
                    \begin{equation} \label{law: functor_id}
                        F(\textbf{id}_X) = \textbf{id}_{F(X)}
                    \end{equation}
                \item
                    for all $X, Y, Z \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$, $g \in \mathcal{C}{(Y,Z)}$, we have:
                    \begin{equation} \label{law: functor_comp}
                        F(g \circ f) = F(g) \circ F(f)
                    \end{equation}
            \end{itemize}
        \end{definition*}
        [Considering adding examples of functors: e.g. free functor, forgetful functor, etc.]

        \subsection{Natural transformation}
        Before introducing the definition of natural transformation, we need to get familiar with the notation of commutative diagrams.

        \subsection{Presheaf}

        \subsection{Functor category}

        \subsection{Cartesian closed category}

        \subsection{Yoneda lemma}

        \subsection{Functor categories}

    \section{Agda}

    \section{Requirement Analysis}

    \section{Tools Used}
    Completing the project is an iterative process. I used Git \cite{git} for version control, and work had been synchronised with a GitHub \cite{github} repository for backup.

    For the development environment, I tried both Emacs \cite{emacs} and Visual Studio Code \cite{vscode} with an agda-mode extension \cite{agda_mode} on Windows Subsystem for Linux with Ubuntu \cite{wsl_ubuntu} 22.04 LTS. I am more familiar with the snippet and syntax highlighting features of Visual Studio Code, so I used it for most of the development.

    The interactive development of Agda with holes and type checking is very useful for debugging.

    Code from the PLFA tutorial and Agda standard library \cite{agda_std} were used as references.

    \begin{enumerate}
        \item 
            Tools used:
            git version control

            have tried emacs
            vscode interactive 
    \end{enumerate}

    \printbibliography
\end{document}

### 2025-04-19 src/compiler.lagda.tex
Initial commit

\documentclass{article}
\usepackage{agda}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathabx}

\usepackage{unicode-math}
\setmathfont{XITS Math}

\usepackage{newunicodechar}
\newunicodechar{≤}{\ensuremath{\leq}}
\newunicodechar{≡}{\ensuremath{\equiv}}
\newunicodechar{∸}{\ensuremath{\dotdiv}}
\newunicodechar{∀}{\ensuremath{\forall}}
\newunicodechar{→}{\ensuremath{\rightarrow}}
\newunicodechar{ℕ}{\ensuremath{\mathbb{N}}}
\newunicodechar{ℤ}{\ensuremath{\mathbb{Z}}}

\begin{document}
\begin{code}
module compiler where

open import source
open import target
open import lib

infixr 1 _⇒ₛ_ 
infixl 2 _×_

-- Product and projection function
data _×_ (A B : Set) : Set where
    _,_ : A → B → A × B

π₁ : ∀ {A B} → A × B → A
π₁ (a , _) = a

π₂ : ∀ {A B} → A × B → B
π₂ (_ , b) = b

--  Type Interpretation
Compl : SD → Set
Compl sd = I sd

_×ₛ_ : (SD → Set) → (SD → Set) → SD → Set
(P ×ₛ Q) sd = P sd × Q sd

_⇒ₛ_ : (SD → Set) → (SD → Set) → SD → Set
(P ⇒ₛ Q) sd = ∀{sd'} → (sd ≤ₛ sd') → P sd' → Q sd'

Intcompl : SD → Set
Intcompl = R ⇒ₛ Compl

⟦_⟧ty : Type → SD → Set
⟦ comm ⟧ty = Compl ⇒ₛ Compl
⟦ intexp ⟧ty = Intcompl ⇒ₛ Compl
⟦ intacc ⟧ty = Compl ⇒ₛ Intcompl
⟦ intvar ⟧ty = ⟦ intexp ⟧ty ×ₛ ⟦ intacc ⟧ty
⟦ θ₁ ⇒ θ₂ ⟧ty = ⟦ θ₁ ⟧ty ⇒ₛ ⟦ θ₂ ⟧ty

-- Unit type for empty context
data ∅ : Set where
    unit : ∅

-- Context Interpretation
⟦_⟧ctx : Context → SD → Set
⟦ · ⟧ctx _ = ∅
⟦ Γ , A ⟧ctx sd = ⟦ Γ ⟧ctx sd × ⟦ A ⟧ty sd

get-var : ∀ {Γ A sd} → A ∈ Γ → ⟦ Γ ⟧ctx sd → ⟦ A ⟧ty sd
get-var Z     (_ , a) = a
get-var (S x) (γ , _) = get-var x γ

-- get-num : ∀ {Γ} → (e : Γ ⊢ source.ℕ) → target.ℕ
-- get-num Zero = target.zero
-- get-num (Suc m) = target.suc (get-num m)

fmap-⇒ : ∀ {P Q sd sd'} → (P ⇒ₛ Q) sd → sd ≤ₛ sd' → (P ⇒ₛ Q) sd'
fmap-⇒ θ p p' x = θ (≤ₛ-trans p p') x

fmap-Compl : ∀ {sd sd'} → Compl sd → sd ≤ₛ sd' → Compl sd'
fmap-Compl {sd} c (<-f f<f') = popto sd (<-f f<f') c
fmap-Compl {⟨ _ , d ⟩} {⟨ _ , d' ⟩} c (≤-d d≤d') = adjustdisp_dec (≤→Fin (-→≤ {d'} {≤→Fin d≤d'}) ) (sub I {!   !} c)

-- fmap-× : ∀ {P Q sd sd'} → (P ×ₛ Q) sd → sd ≤ₛ sd' → (P ×ₛ Q) sd'

fmap-A : ∀ {A sd sd'} → ⟦ A ⟧ty sd → sd ≤ₛ sd' → ⟦ A ⟧ty sd'
fmap-A {comm} c p i = {!   !}
fmap-A {intexp} = {!   !}
fmap-A {intacc} = {!   !}
fmap-A {intvar} = {!   !}
fmap-A {A ⇒ B} = fmap-⇒ {⟦ A ⟧ty} {⟦ B ⟧ty}

fmap-Γ : ∀ {Γ sd sd'} → ⟦ Γ ⟧ctx sd → sd ≤ₛ sd' → ⟦ Γ ⟧ctx sd'
fmap-Γ {·} unit _ = unit
fmap-Γ {Γ , A} (γ , a) p = fmap-Γ γ p , fmap-A {A} a p

⟦_⟧ : ∀ {Γ A} → (e : Γ ⊢ A) → (sd : SD) → ⟦ Γ ⟧ctx sd → ⟦ A ⟧ty sd
⟦ Var x ⟧ _ γ = get-var x γ
⟦ Lambda f ⟧ sd γ {sd' = sd'} p a = ⟦ f ⟧ sd' (fmap-Γ γ p , a) 
⟦ App f e ⟧ sd γ = ⟦ f ⟧ sd γ (≤-d ≤-refl) (⟦ e ⟧ sd γ)
⟦ Skip ⟧ _ _ _ γ = γ
⟦ Seq c₁ c₂ ⟧ sd γ sd' p = ⟦ c₁ ⟧ sd γ sd' (⟦ c₂ ⟧ sd γ sd' p)
⟦ Lit i ⟧ _ _ _ κ = κ ≤ₛ-refl (r-s (s-lit i))
⟦ Neg e ⟧ sd γ p κ = {!   !} 
⟦ Plus e e₁ ⟧ _ γ = {!   !} 
\end{code}
\end{document}

### 2025-04-19 draft.tex
more definitions added

@@
 \setsansfont{Linux Biolinum O}
+
+\graphicspath{{./fig/}}
 
@@
         \begin{definition*}[Category]
-            A category $\mathcal{C}$ is specified by the following:
+            A \emph{category} $\mathcal{C}$ is specified by the following:
             \begin{itemize}
@@
                 \item 
-                    \textbf{(Unit Law)}
+                    \textbf{(Unit Laws)}
                     for all $X, Y \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$, we have:
@@
             [Considering adding different notations for morphisms, composition, identity morphisms, etc.]
+
             [Considering adding a diagram for the definition of category]
+
             [Considering adding examples of categories]
@@
 
+        Before other definitions, we need to get familiar with the notation of commutative diagrams.
+        \subsubsection{Commutative diagrams}
+        A \emph{diagram} in a category $\mathcal{C}$ is a directed graph whose vertices are $\mathcal{C}$-objects and whose edges are $\mathcal{C}$-morphisms.
+
+        A diagram is \emph{commutative} (or \emph{commutes}) if any two finite paths in the graph between any two vertices $X$ and $Y$ in the diagram determine the equal morphism $f \in \mathcal{C}{(X,Y)}$ under the composition of morphisms.
+
+        \begin{figure}[htb!]
+            \centering
+            \begin{minipage}{0.3\textwidth}
+                \centering
+                \includegraphics[width=0.8\textwidth]{2_2_1_unit_laws.pdf}
+                \caption{Commutative diagram for Unit Laws}
+                \label{fig: unit_laws}
+            \end{minipage} \hspace{0.2\textwidth}
+            \begin{minipage}{0.3\textwidth}
+                \centering
+                \includegraphics[width=0.8\textwidth]{2_2_1_associativity_law.pdf}
+                \caption{Commutative diagram for Associativity Law}
+                \label{fig: associativity_law}
+            \end{minipage}
+        \end{figure}
+
+        As examples of commutative diagrams, Figure \ref{fig: associativity_law} and Figure \ref{fig: unit_laws} are commutative diagrams for the unit laws and associativity law respectively.
+
+        \subsection{Cartesian closed category}
         \subsection{Functor}
         \begin{definition*}[Functor]
-            A functor $F$ from a category $\mathcal{C}$ to a category $\mathcal{D}$ is specified by the following:
+            Given two categories $\mathcal{C}$ and $\mathcal{D}$, a \emph{functor} $F: \mathcal{C} \to \mathcal{D}$ is specified by:
             \begin{itemize}
@@
         \subsection{Natural transformation}
-        Before introducing the definition of natural transformation, we need to get familiar with the notation of commutative diagrams.
+        \begin{definition*}[Natural transformation]
+
+            Given two categories $\mathcal{C}$ and $\mathcal{D}$, and two functors $F,G: \mathcal{C} \to \mathcal{D}$, a \emph{natural transformation} $\theta : F \to G$ is a family of morphisms $\theta_X \in \mathcal{D}{(F(X),G(X))}$ for each $X \in \textbf{obj}(\mathcal{C})$ such that for all $X, Y \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$, the following diagram
+            \begin{equation}
+                \vcenter{\hbox{\includegraphics[width=0.3\textwidth]{2_2_3_natural_transformation.pdf}}}
+                \label{cd: natural_transformation}
+            \end{equation}
+
+            commutes in $\mathcal{D}$, i.e. the following equation holds:
+            \begin{equation} \label{law: natural_transformation}
+                G(f) \circ \theta_X = \theta_Y \circ F(f)
+            \end{equation}
+
+        \end{definition*}
+        [Considering adding examples of natural transformations]
+
+        \subsection{Functor category}
+        \begin{definition*}[Functor category]
+            Given two categories $\mathcal{C}$ and $\mathcal{D}$, the \emph{functor category} $\mathcal{D}^{\mathcal{C}}$ is the category satisfying the following:
+            \begin{itemize}
+                \item 
+                    the objects of $\mathcal{D}^{\mathcal{C}}$ are all functors $\mathcal{C} \to \mathcal{D}$;
+                \item 
+                    given two functors $F,G: \mathcal{C} \to \mathcal{D}$, the morphisms from $F$ to $G$ in $\mathcal{D}^{\mathcal{C}}$ are all natural transformations $\theta : F \to G$;
+                \item
+                    composition and identity morphisms in $\mathcal{D}^{\mathcal{C}}$ are defined as follows:
+                    \begin{itemize}
+                        \item 
+                            the identity morphism $\textbf{id}_F$ on $F$ is defined as $\theta_X = \textbf{id}_{F(X)}$ for all $X \in \textbf{obj}(\mathcal{C})$;
+                        \item
+                            the composition of two natural transformations $\theta : F \to G$ and $\phi : G \to H$ is defined as $(\phi \circ \theta)_X = \phi_X \circ \theta_X$ for all $X \in \textbf{obj}(\mathcal{C})$.
+                    \end{itemize}
+            \end{itemize}
+        \end{definition*}
+
+        \subsection{Yoneda lemma}
+        \begin{definition*}[Yoneda functor]
+            Given a category $\mathcal{C}$, the \emph{Yoneda functor} $y: \mathcal{C} \to \mathcal{C}^{\mathcal{C}^{op}}$ is defined as follows:
+            \begin{itemize}
+                \item 
+                    for each $X \in \textbf{obj}(\mathcal{C})$, $y(X)$ is the functor $y(X): \mathcal{C}^{op} \to \textbf{Set}$ defined as:
+                    \[ y(X)(Y) = \mathcal{C}{(Y,X)} \]
+                    for all $Y \in \textbf{obj}(\mathcal{C})$;
+                \item
+                    for each $X, Y \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$, $y(f)$ is the natural transformation $y(f): y(X) \to y(Y)$ defined as:
+                    \[ y(f)_Y = f \circ - : y(X)(Y) \to y(Y)(Y) \]
+                    for all $Y \in \textbf{obj}(\mathcal{C})$.
+                    In other words, $y(f)_Y$ is the function that takes an element $g \in y(X)(Y) = \mathcal{C}{(Y,X)}$ and returns the element $f \circ g \in y(Y)(Y) = \mathcal{C}{(Y,Y)}$.
+                    The function $y(f)_Y$ is a morphism in $\mathcal{C}^{\mathcal{C}^{op}}$ from $y(X)(Y)$ to $y(Y)(Y)$.
+                    In other words, $y(f)_Y$ is a morphism in $\mathcal{C}^{\mathcal{C}^{op}}$ from the functor $y(X)$ to the functor $y(Y)$.
+                    The morphism $y(f)_Y$ is defined for all $Y \in \textbf{obj}(\mathcal{C})$.
+                    In other words, $y(f)$ is a natural transformation from the functor $y(X)$ to the functor $y(Y)$.
+            \end{itemize}
+        \end{definition*}
+
+        \begin{definition*}[Yoneda lemma]
+            Given a category $\mathcal{C}$, the \emph{Yoneda lemma} states that for any functor $F: \mathcal{C} \to \textbf{Set}$, there is a natural isomorphism:
+            \[ \begin{aligned}
+                \textbf{Nat}(y(X),F) &\cong F(X) \\
+                \theta &\mapsto \theta_X
+            \end{aligned} \]
+            for all $X \in \textbf{obj}(\mathcal{C})$, where $\textbf{Nat}(y(X),F)$ is the set of natural transformations from the functor $y(X)$ to the functor $F$.
+        \end{definition*}
 
         \subsection{Presheaf}
+        \begin{definition*}[Presheaf]
+            Given a category $\mathcal{C}$, a \emph{presheaf} on $\mathcal{C}$ is a functor $F: \mathcal{C}^{op} \to \textbf{Set}$.
+            A presheaf is a contravariant functor, which means that it reverses the direction of morphisms.
+            In other words, a presheaf is a functor that takes objects in $\mathcal{C}$ and assigns them sets, and takes morphisms in $\mathcal{C}$ and assigns them functions between the corresponding sets.
+            The presheaf $F$ is defined as follows:
+            \begin{itemize}
+                \item 
+                    for each $X \in \textbf{obj}(\mathcal{C})$, $F(X)$ is a set;
+                \item
+                    for each $X, Y \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$, $F(f)$ is a function $F(Y) \to F(X)$.
+                    In other words, $F(f)$ is a function that takes an element $g \in F(Y)$ and returns the element $f \circ g \in F(X)$.
+                    The function $F(f)$ is a morphism in $\mathcal{C}^{op}$ from $F(Y)$ to $F(X)$.
+                    In other words, $F(f)$ is a morphism in $\mathcal{C}^{op}$ from the functor $F(Y)$ to the functor $F(X)$.
+                    The morphism $F(f)$ is defined for all $X, Y \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$.
+                    In other words, $F(f)$ is a natural transformation from the functor $F(Y)$ to the functor $F(X)$.
+            \end{itemize}
+        \end{definition*}
 
-        \subsection{Functor category}
-
-        \subsection{Cartesian closed category}
-
-        \subsection{Yoneda lemma}
-
-        \subsection{Functor categories}
+        \subsection{Cartesian closed structure in presheaf categories}
 
     \section{Agda}
+        \subsection{Standard library}
+
+        \subsection{Dependent Types}
+
+        \subsection{Curry-Howard Correspondence}
+
+        \subsection{Equality}
+
+        \subsection{Proof Example}
+
+        \subsection{Interactive programming with holes}
 
@@
 
-    The interactive development of Agda with holes and type checking is very useful for debugging.
-
     Code from the PLFA tutorial and Agda standard library \cite{agda_std} were used as references.
 
-    \begin{enumerate}
-        \item 
-            Tools used:
-            git version control
+\chapter{Implementation}
 
-            have tried emacs
-            vscode interactive 
-    \end{enumerate}
+\chapter{Evaluation}
+
+\chapter{Conclusion}
 
     \printbibliography
+
 \end{document}

### 2025-04-20 draft.tex
definition almost completed; agda introduction added; files restructured

@@
 \usepackage{amsthm}
+\usepackage{listings}
 
@@
 
-\graphicspath{{./fig/}}
+\graphicspath{{./fig/category_theory/}}
 
@@
 
-        Before other definitions, we need to get familiar with the notation of commutative diagrams.
+            \subsubsection{Opposite category}
+            The idea of opposite category is that if we have a category $\mathcal{C}$, we can reverse the direction of all morphisms in $\mathcal{C}$ to obtain a new category $\mathcal{C}^{\textbf{op}}$.
+
+            \begin{definition*}[Opposite category]
+                Given a category $\mathcal{C}$, its \emph{opposite category} $\mathcal{C}^{\textbf{op}}$ is specified by:
+                \begin{itemize}
+                    \item 
+                        the objects of $\mathcal{C}^{\textbf{op}}$ are the same as those of $\mathcal{C}$;
+                    \item 
+                        for each $X, Y \in \textbf{obj}(\mathcal{C})$, the morphisms from $X$ to $Y$ in $\mathcal{C}^{\textbf{op}}$ are the morphisms from $Y$ to $X$ in $\mathcal{C}$;
+                    \item 
+                        the identity morphism on $X$ in $\mathcal{C}^{\textbf{op}}$ is the identity morphism on $X$ in $\mathcal{C}$;
+                    \item 
+                        the composition of morphisms in $\mathcal{C}^{\textbf{op}}$ is defined as the composition of morphisms in $\mathcal{C}$.
+                \end{itemize}
+            \end{definition*}
+
+                % \paragraph{The principle of duality}
+                % Whenever one defines a concept or proves a theorem in category theory $\mathcal{C}$, one can obtain another concept or theorem in the opposite category $\mathcal{C}^{\textbf{op}}$, called the \emph{dual} of the original concept or theorem, by reversing all arrows in the original concept or theorem.
+
+            The notation of commutative diagram is widely used in category theory as a convenient visual representation of the relationships between objects and morphisms in a category.
             \subsubsection{Commutative diagrams}
@@
                     \centering
-                \includegraphics[width=0.8\textwidth]{2_2_1_unit_laws.pdf}
+                    \includegraphics[width=0.8\textwidth]{unit_laws.pdf}
                     \caption{Commutative diagram for Unit Laws}
@@
                     \centering
-                \includegraphics[width=0.8\textwidth]{2_2_1_associativity_law.pdf}
+                    \includegraphics[width=0.8\textwidth]{associativity_law.pdf}
                     \caption{Commutative diagram for Associativity Law}
@@
 
+        \subsection{Isomorphism}
+        \begin{definition*}[Isomorphism]
+            Given a category $\mathcal{C}$, a $C$-morphism $f : X \to Y$ is called an \emph{isomorphism} if there exists a $C$-morphism $g : Y \to X$ such that the following diagram commutes:
+            \begin{equation}
+                \vcenter{\hbox{\includegraphics[width=0.3\textwidth]{isomorphism.pdf}}}
+                \label{cd: isomorphism}
+            \end{equation}
+            In other words, $f$ is an isomorphism if there exists a morphism $g$ such that $g \circ f = \textbf{id}_X$ and $f \circ g = \textbf{id}_Y$.
+
+            The morphism $g$ is uniquely determined by $f$ and is called the \emph{inverse} of $f$, denoted as $f^{-1}$.
+
+            Given two objects $X$ and $Y$ in a category $\mathcal{C}$, if there exists an isomorphism from $X$ to $Y$, we say that $X$ and $Y$ are \emph{isomorphic} in $\mathcal{C}$ and write $X \cong Y$.
+
+        \end{definition*}
+        [Considering adding examples of isomorphism]
+
+        \subsection{Terminal object}
+        \begin{definition*}[Terminal object]
+            Given a category $\mathcal{C}$, an object $T \in \textbf{obj}(\mathcal{C})$ is called a \emph{terminal object} if for all $X \in \textbf{obj}(\mathcal{C})$, there exists a unique \textbf{C}-morphism $f : X \to T$.
+        \end{definition*}
+        [Considering adding examples of terminal object]
+
+        Terminal objects are unique up to isomorphism. In other words, we have
+        \begin{itemize}
+            \item 
+                if $T$ and $T'$ are both terminal objects in $\mathcal{C}$, then there exists a unique isomorphism $f : T \to T'$.
+            \item
+                if $T$ is a terminal object in $\mathcal{C}$ and $T \cong T'$, then $T'$ is also a terminal object in $\mathcal{C}$.
+        \end{itemize}
+
+        % \subsection{Initial object}
+        % \begin{definition*}[Initial object]
+        %     Given a category $\mathcal{C}$, an object $I \in \textbf{obj}(\mathcal{C})$ is called an \emph{initial object} if for all $X \in \textbf{obj}(\mathcal{C})$, there exists a unique \textbf{C}-morphism $f : I \to X$.
+        % \end{definition*}
+        % Initial object is dual to terminal object. By the principle of duality, initial objects are unique up to isomorphism. In other words, we have
+        % \begin{itemize}
+        %     \item 
+        %         if $I$ and $I'$ are both initial objects in $\mathcal{C}$, then there exists a unique isomorphism $f : I \to I'$.
+        %     \item
+        %         if $I$ is an initial object in $\mathcal{C}$ and $I \cong I'$, then $I'$ is also an initial object in $\mathcal{C}$.
+        % \end{itemize}
+
+        \subsection{Binary product}
+        \begin{definition*}[Binary product]
+            Given a category $\mathcal{C}$, the \emph{binary product} of two objects $X$ and $Y$ in $\mathcal{C}$ is specified by
+            \begin{itemize}
+                \item a $\mathcal{C}$-object $X \times Y$;
+                \item two $\mathcal{C}$-morphisms $\pi_1 : X \times Y \to X$ and $\pi_2 : X \times Y \to Y$ called the \emph{projections} of $X \times Y$;
+            \end{itemize}
+            such that for all $Z \in \textbf{obj}(\mathcal{C})$ and morphisms $f : Z \to X$ and $g : Z \to Y$, there exists a unique morphism $u : Z \to X \times Y$ such that the following diagram commutes in $\mathcal{C}$:
+            \begin{equation}
+                \vcenter{\hbox{\includegraphics[width=0.4\textwidth]{binary_product.pdf}}}
+                \label{cd: binary_product}
+            \end{equation}
+            The unique morphism $u$ is written as 
+            \[ \langle x, y \rangle : Z \to X \times Y \]
+            where $x = \pi_1 \circ u$ and $y = \pi_2 \circ u$.
+        \end{definition*}
+        It can be shown that the binary product is unique up to (unique) isomorphism.
+
+        \subsection{Exponential}
+        \begin{definition*}[Exponential]
+            Given a category $\mathcal{C}$ with binary products, the \emph{exponential} of two objects $X$ and $Y$ in $\mathcal{C}$ is specified by
+            \begin{itemize}
+                \item a $\mathcal{C}$-object $X \Rightarrow Y$;
+                \item a $\mathcal{C}$-morphism $\textbf{app} : (X \Rightarrow Y) \times X \to Y$ called the \emph{application} of $X \Rightarrow Y$;
+            \end{itemize}
+            such that for all $Z \in \textbf{obj}(\mathcal{C})$ and morphisms $f : Z \times X \to Y$, there exists a unique morphism $u : Z \to X \Rightarrow Y$ such that the following diagram commutes in $\mathcal{C}$:
+            \begin{equation}
+                \vcenter{\hbox{\includegraphics[width=0.4\textwidth]{exponential.pdf}}}
+                \label{cd: exponential}
+            \end{equation}
+            We write $\textbf{cur} f$ for the unique morphism $u$ such that $f = \textbf{app} \circ (\textbf{cur} f \times \textbf{id}_X)$, 
+            where $\textbf{cur} f$ is called the \emph{currying} of $f$.
+        \end{definition*}
+        It can be shown that the exponential is unique up to (unique) isomorphism.
+
         \subsection{Cartesian closed category}
+        \begin{definition*}[Cartesian closed category]
+            A category $\mathcal{C}$ is called a \emph{Cartesian closed category} (ccc) if it has a terminal object, binary products and exponentials of any two objects.
+        \end{definition*}
+
         \subsection{Functor}
@@
             \begin{equation}
-                \vcenter{\hbox{\includegraphics[width=0.3\textwidth]{2_2_3_natural_transformation.pdf}}}
+                \vcenter{\hbox{\includegraphics[width=0.3\textwidth]{natural_transformation.pdf}}}
                 \label{cd: natural_transformation}
@@
     \section{Agda}
-        \subsection{Standard library}
+        \subsection{Basic datatypes and pattern matching}
+        We will go through a simple example in PLFA \cite{plfa} to illustrate the basic datatypes and pattern matching in Agda.
 
@@
 
-        \subsection{Curry-Howard Correspondence}
+        \subsection{Curry-Howard-Lambek correspondence}
 
-        \subsection{Equality}
+        \subsection{Equality, congruence and substitution}
 
-        \subsection{Proof Example}
+        % \subsection{Proof Example}
+
+        \subsection{Standard library}
 
         \subsection{Interactive programming with holes}
+        A feature of Agda is that it allows us to write programs with holes interatively.
+A hole is a placeholder for a term that we have not yet defined.
+By leaving holes in place of undefined terms, we can write programs that are incomplete but still type-check, and Agda's type checker will guide completion of the program: the context window displays inferred types of the holes, available variables and candidate terms with their types.
+Holes also supports case split and refinement, which means we can fill in a hole partially and split it into smaller holes.
+
+        [Considering adding examples of holes and case split, see https://plfa.github.io/Naturals/]
+
+        In my implementation, I used holes to write the terms in the compiler.
+The complex terms are incrementally filled and verified by interatively refining partial implementations, reducing post-hoc debugging and ensuring robustness.
 

### 2025-04-23 draft.tex
introduction and preparation almost complete

@@
 \usepackage{listings}
+\usepackage{xcolor}
+\usepackage{xeCJK}
 
@@
 \setsansfont{Linux Biolinum O}
+\setCJKmainfont{Noto Serif CJK JP}
 
-\graphicspath{{./fig/category_theory/}}
+\graphicspath{{./fig/category_theory/}{./fig/agda/lagda/latex/}}
 
@@
 \newtheorem*{definition*}{Definition}
+
+\theoremstyle{definition}
+\newtheorem*{theorem*}{Theorem}
 
@@
 }
+
+\newcommand{\secref}[1]{\S\ref{#1}}
+
+\definecolor{mediumblue}{HTML}{0000CD}
+\definecolor{green}{HTML}{008B00}
+\newcommand{\mb}[1]{\textcolor{mediumblue}{#1}}
+\newcommand{\gn}[1]{\textcolor{green}{#1}}
+
+\newcommand{\bN}{\mathbb{N}}
+
+\newcommand{\yo}{\mathord{\text{\kern0.03em \scalebox{0.8}{よ}\kern0.03em}}}
 
@@
 
-    The grammer of the target language is specified in Chapter 3.
+    The grammer of the target language is specified in Chapter 3. [Add exact section/subsection here]
 
@@
 
-    \section{Motivation and related work}
+    \section{Motivation and related work} \label{sec: motivation}
         The denotational semantics of Algol-like languages can be structured as a presheaf category over stack descriptors, which has been shown by Reynolds \cite{essence} and Oles \cite{Oles_1} \cite{Oles_2}.
@@
 
-        (Example of Agda)
-
         Dependently typed languages provide a natural framework for expressing functor categories is proven both theoretically and practically.
 There have been dependent-type-theoretic model of categories \cite{Dybjer}, and it has been shown that functor categories arise naturally as dependent function types \cite{Jacobs}.
-A formalisation of Category Theory, including Cartesian Closed Categories, functors and presheaves has been developed in Agda by Hu and Caratte \cite{Cat_Agda}.
+A formalisation of Category Theory, including cartesian closed categories, functors and presheaves has been developed in Agda by Hu and Caratte \cite{Cat_Agda}.
 Other proof assistants, such as Isabelle/Hol, does not have a dependently typed language structure, and thus cannot express the functor categories as naturally as Agda.
+Agda also provides an interactive environment for writing and verifying programs, which will be further discussed in \secref{subsec: holes}.
 
@@
     \section{Contributions}
-        Addressed the two motivations presented in 1.1 and contributed to the following:
+        Addressed the three motivations presented in \secref{sec: motivation} and contributed to the following:
         \begin{quote}
@@
 
-    \section{Category theory background}
-        Category 
+    \section{Category theory background} \label{sec: cat}
+        Category theory provides a high-level abstraction from which we can reason about the structure of mathematical objects and their relationships.
+It provides us a ``bird's eye view'' of the mathematics which enable us to spot patterns that are difficult to see in the details.
+\cite{basic_cat} More specifically, it provides a ``purer'' view of functions that is not derived from sets.
+\cite{scott-lambda} Compared to set theory which is ``element-oriented'', category theory is ``function-oriented'' and ``morphism-oriented''.
+We understand structures not via elements but by how they transform into each other.
+
+        Notation in category theory is similar to that in set theory and type theory.
+For example, $A, B, \dots$ are used to denote objects, sets, or types, and arrows are used to denote morphisms or functions (e.g.\ $A \to B$).
+There is a deeper connection between category theory and type theory.
+Curry-Howard correspondence \cite{curry-howard} states that there is a correspondence between logic and type theory, where propositions correspond to types and proofs correspond to terms.
+This correspondence was later extended by Joachim Lambek, who showed that cartesian closed categories provide a natural semantic setting for the simply typed lambda calculus.
+\cite{lambek} Under this perspective, types become objects in a category, and programs correspond to morphisms.
+We will further explore this connection in \secref{subsec: curry-howard-lambek}.
+
+        The following is a brief introduction to the basic concepts of category theory, which is based on the work of Leinster \cite{basic_cat}, 
+        Riehl \cite{cat_context}, and the lecture notes of Part II Category Theory by Andrew Pitts and Marcelo Fiore \cite{cat_lecture_notes}.
+
         \subsection{Category}
@@
                 \item 
-                    for each $X, Y \in \textbf{obj}(\mathcal{C})$, a collection of morphisms $\mathcal{C}{(X,Y)}$, whose elements are called $\mathcal{C}$-morphisms from $X$ to $Y$;
+                    for each $X, Y \in \textbf{obj}(\mathcal{C})$, a collection of morphisms $\mathcal{C}{(X,Y)}$, whose elements are called $\mathcal{C}$-morphisms from $X$ to $Y$ (e.g.\ $f : X \to Y$);
                 \item 
@@
             \end{itemize}
+        \end{definition*}
 
-            [Considering adding different notations for morphisms, composition, identity morphisms, etc.]
-
-            [Considering adding a diagram for the definition of category]
-
-            [Considering adding examples of categories]
-
-        \end{definition*}
+        An example of category is the category of sets, denoted as $\mathcal{Set}$, specifed by:
+        \begin{itemize}
+            \item 
+                the objects of $\mathcal{Set}$ are a fixed universe of sets;
+            \item
+                for each $X, Y \in \textbf{obj}(\mathcal{Set})$, the morphisms from $X$ to $Y$ in $\mathcal{Set}$ are the functions from $X$ to $Y$;
+            \item
+                the identity morphism on $X$ in $\mathcal{Set}$ is the identity function on $X$;
+            \item
+                the composition of morphisms in $\mathcal{Set}$ is defined as the composition of functions.
+        \end{itemize}
+        Associativity law and unit laws are satisfied in $\mathcal{Set}$, since the composition of functions is associative and the identity function compose with any function is the function itself.
 
@@
         \end{definition*}
+
         [Considering adding examples of isomorphism]
@@
         \end{definition*}
+
         [Considering adding examples of functors: e.g. free functor, forgetful functor, etc.]
@@
         \end{definition*}
+
         [Considering adding examples of natural transformations]
@@
 
-        \subsection{Yoneda lemma}
-        \begin{definition*}[Yoneda functor]
-            Given a category $\mathcal{C}$, the \emph{Yoneda functor} $y: \mathcal{C} \to \mathcal{C}^{\mathcal{C}^{op}}$ is defined as follows:
-            \begin{itemize}
-                \item 
-                    for each $X \in \textbf{obj}(\mathcal{C})$, $y(X)$ is the functor $y(X): \mathcal{C}^{op} \to \textbf{Set}$ defined as:
-                    \[ y(X)(Y) = \mathcal{C}{(Y,X)} \]
-                    for all $Y \in \textbf{obj}(\mathcal{C})$;
-                \item
-                    for each $X, Y \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$, $y(f)$ is the natural transformation $y(f): y(X) \to y(Y)$ defined as:
-                    \[ y(f)_Y = f \circ - : y(X)(Y) \to y(Y)(Y) \]
-                    for all $Y \in \textbf{obj}(\mathcal{C})$.
-                    In other words, $y(f)_Y$ is the function that takes an element $g \in y(X)(Y) = \mathcal{C}{(Y,X)}$ and returns the element $f \circ g \in y(Y)(Y) = \mathcal{C}{(Y,Y)}$.
-                    The function $y(f)_Y$ is a morphism in $\mathcal{C}^{\mathcal{C}^{op}}$ from $y(X)(Y)$ to $y(Y)(Y)$.
-                    In other words, $y(f)_Y$ is a morphism in $\mathcal{C}^{\mathcal{C}^{op}}$ from the functor $y(X)$ to the functor $y(Y)$.
-                    The morphism $y(f)_Y$ is defined for all $Y \in \textbf{obj}(\mathcal{C})$.
-                    In other words, $y(f)$ is a natural transformation from the functor $y(X)$ to the functor $y(Y)$.
-            \end{itemize}
-        \end{definition*}
-
-        \begin{definition*}[Yoneda lemma]
-            Given a category $\mathcal{C}$, the \emph{Yoneda lemma} states that for any functor $F: \mathcal{C} \to \textbf{Set}$, there is a natural isomorphism:
-            \[ \begin{aligned}
-                \textbf{Nat}(y(X),F) &\cong F(X) \\
-                \theta &\mapsto \theta_X
-            \end{aligned} \]
-            for all $X \in \textbf{obj}(\mathcal{C})$, where $\textbf{Nat}(y(X),F)$ is the set of natural transformations from the functor $y(X)$ to the functor $F$.
-        \end{definition*}
-
-        \subsection{Presheaf}
+        \subsection{Presheaf category}
         \begin{definition*}[Presheaf]
-            Given a category $\mathcal{C}$, a \emph{presheaf} on $\mathcal{C}$ is a functor $F: \mathcal{C}^{op} \to \textbf{Set}$.
+            Given a category $\mathcal{C}$, a \emph{presheaf} on $\mathcal{C}$ is a functor $F: \mathcal{C}^{\textbf{op}} \to \textbf{Set}$.
             A presheaf is a contravariant functor, which means that it reverses the direction of morphisms.
@@
                     for each $X, Y \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$, $F(f)$ is a function $F(Y) \to F(X)$.
-                    In other words, $F(f)$ is a function that takes an element $g \in F(Y)$ and returns the element $f \circ g \in F(X)$.
-                    The function $F(f)$ is a morphism in $\mathcal{C}^{op}$ from $F(Y)$ to $F(X)$.
-                    In other words, $F(f)$ is a morphism in $\mathcal{C}^{op}$ from the functor $F(Y)$ to the functor $F(X)$.
-                    The morphism $F(f)$ is defined for all $X, Y \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$.
-                    In other words, $F(f)$ is a natural transformation from the functor $F(Y)$ to the functor $F(X)$.
             \end{itemize}
@@
 
+        \begin{definition*}[Presheaf category]
+            Given a category $\mathcal{C}$, the \emph{presheaf category} $\mathcal{P}(\mathcal{C})$ is the functor category $\mathcal{Set}^{\mathcal{C}^{\textbf{op}}}$.
+            \begin{itemize}
+                \item 
+                    the objects of $\mathcal{P}(\mathcal{C})$ are all presheaves on $\mathcal{C}$;
+                \item
+                    given two presheaves $F,G: \mathcal{C}^{\textbf{op}} \to \mathcal{Set}$, the morphisms from $F$ to $G$ in $\mathcal{P}(\mathcal{C})$ are all natural transformations $\theta : F \to G$.
+            \end{itemize}
+        \end{definition*}
+
+        \subsection{Yoneda lemma}
+        \begin{definition*}[Yoneda functor]
+            Given a category $\mathcal{C}$, the \emph{Yoneda functor} $\yo: \mathcal{C} \to \mathcal{Set}^{\mathcal{C}^{\textbf{op}}}$ is defined as follows:
+            \begin{itemize}
+                \item 
+                    for each $X \in \textbf{obj}(\mathcal{C})$, $\yo(X)$ is the functor $y(X) : \mathcal{C}^{\textbf{op}} \to \mathcal{Set}$ defined as:
+                    \begin{equation} \label{eq: yoneda_element}
+                        \yo(X)(Y) = \mathcal{C}{(Y,X)}
+                    \end{equation}
+                    for all $Y \in \textbf{obj}(\mathcal{C})$;
+                \item
+                    for each $X, Y \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$, $\yo(f)$ is the morphism $\yo(X) \to \yo(Y)$ defined a natural transformation whose component at any given $Z \in \mathcal{C}^{\textbf{op}}$ is given by:
+                    \begin{equation} \label{eq: yoneda_morphism}
+                        \begin{aligned}
+                            (\yo(f))_Z : \mathcal{C}{(Z,Y)} &\to \mathcal{C}{(Z,X)} \\
+                            g &\mapsto g \circ f
+                        \end{aligned}
+                    \end{equation}
+                    for all $Z \in \textbf{obj}(\mathcal{C})$.
+                \end{itemize}
+
+        \end{definition*}
+
+        \begin{theorem*}[Yoneda lemma]
+            Given a category $\mathcal{C}$, the \emph{Yoneda lemma} states that for each object $X \in \textbf{obj}(\mathcal{C})$ and any functor $F: \mathcal{C} \to \textbf{Set}$, there is a natural isomorphism:
+            \begin{equation} \label{eq: yoneda_lemma}
+                \mathcal{Set}^{\mathcal{C}^{\textbf{op}}}(\yo(X), F) \cong F(X)
+            \end{equation}
+        \end{theorem*}
+
         \subsection{Cartesian closed structure in presheaf categories}
+        \begin{theorem*}[Cartesian closed structure in presheaf categories]
+            Given a small category $\mathcal{C}$, the presheaf category $\mathcal{Set}^{\mathcal{C}^{\textbf{op}}}$ is a Cartesian closed category.
+            \begin{itemize}
+                \item 
+                    The terminal object in $\mathcal{Set}^{\mathcal{C}^{\textbf{op}}}$ is the constant functor $\mathbf{1} : \mathcal{C}^{\textbf{op}} \to \mathcal{Set}$, given by 
+                    \begin{equation}
+                        \begin{cases}
+                            \mathbf{1}(X) = \{\ast\} & \text{for all } X \in \textbf{obj}(\mathcal{C}) \\
+                            \mathbf{1}(f) = \textbf{id}_{\{\ast\}} & \text{for all } f \in \mathcal{C}{(X,Y)}
+                        \end{cases}
+                    \end{equation}
+
+                \item
+                    The binary product in $\mathcal{Set}^{\mathcal{C}^{\textbf{op}}}$ is given by the product of functors, which is defined as follows:
+                    \begin{equation}
+                        \begin{aligned}
+                            (F \times G)(X) &= F(X) \times G(X) \\
+                            (F \times G)(f) &= F(f) \times G(f)
+                        \end{aligned}
+                    \end{equation}
+
+                \item
+                    The exponential in $\mathcal{Set}^{\mathcal{C}^{\textbf{op}}}$ is given by the Yoneda lemma,
+                    \begin{equation}
+                        \begin{aligned}
+                            G^{F}(X) &= \mathcal{Set}^{\mathcal{C}^{\textbf{op}}}(\yo(X) \times F, G) \\
+                            G^{F}(f)(\theta) &= \theta \circ (\yo(f) \times \textbf{id}_F) \quad \text{for all } \theta \in \mathcal{Set}^{\mathcal{C}^{\textbf{op}}}(\yo(Y) \times F, G)
+                        \end{aligned}
+                    \end{equation}
+            \end{itemize}
+        \end{theorem*}
 
@@
 
+        \[\includegraphics[width=\textwidth]{example.pdf}\]
+
+        Here we define a datatype $\mb{\bN}$ for natural numebers.
+$\mb{\bN}$ itself has a type $\mb{\mathsf{Set}}$, which is the type of all small types.
+The natural number is defined as a recursive datatype with two constructors: $\gn{\mathsf{zero}}$ and $\gn{\mathsf{suc}}$, where
+        $\gn{\mathsf{zero}}$ is the base case and $\gn{\mathsf{suc}}$ is the inductive case.
+The $\gn{\mathsf{zero}}$ constructor has type $\mb{\bN}$, and the $\gn{\mathsf{suc}}$ constructor has type $\mb{\bN \to \bN}$.
+
+        In order to define the plus function $\mb{\_+\_}$, we use pattern matching to match the input argument with the constructors of the datatype.
+The first case is the base case, where we match the input argument with $\gn{\mathsf{zero}}$.
+In this case, we return the second argument.
+The second case is the inductive case, where we match the input argument with $\gn{\mathsf{suc}}$.
+In this case, we return $\gn{\mathsf{suc}}$ applied to the result of adding one to the second argument.
+
         \subsection{Dependent Types}
+        A dependent type is a type that depends on a value. In terms of type judgement, simple types are in form of
+        \[ x_1 : T_1, x_2 : T_2, \dots, x_n : T_n \vdash t(x_1, \dots, x_n) : T \]
+        In contrast, dependent types are in form of
+        \[ x_1 : T_1, x_2 : T_2, \dots, x_n : T_n \vdash t(x_1, \dots, x_n) : T(x_1, \dots, x_n) \]
+        or more generally
+        \[ x_1 : T_1, x_2 : T_2(x_1), \dots, x_n : T_n(x_1, \dots, x_{n-1}) \vdash t(x_1, \dots, x_n) : T(x_1, \dots, x_n) \]
 
-        \subsection{Curry-Howard-Lambek correspondence}
+        A classical example of dependent types in Agda is the type of vectors, which are lists with a length.
+
+        \[\includegraphics[width=\textwidth]{vector.pdf}\]
+
+        Here we define a datatype $\mb{\mathsf{Vec}}$ for vectors.
+The type of vectors is dependent on the length of the vector.
+With dependent types, we can encode properties directly into types and ensure that they are satisfied at compile time.
+
+        \subsection{Curry-Howard-Lambek correspondence} \label{subsec: curry-howard-lambek}
+        As introduced in \secref{sec: cat}, Curry-Howard correspondence states that there is a correspondence between logic and type theory, and Lambek extended this correspondence to show that cartesian closed categories provide a natural semantic setting for the simply typed lambda calculus.
+They can be summarised as follows:
+        \begin{table}[htb!]
+            \centering
+            \begin{tabular}{|c|c|c|}
+                \hline
+                \textbf{Logic} & \textbf{Type theory} & \textbf{Category theory} \\
+                \hline
+                Proposition & Type & Object \\
+                Proof & Term & Morphism \\
+                Falsity & Empty type & Initial object \\
+                Truth & Unit type & Terminal object \\
+                Implication & Function type & Exponential object \\
+                Conjunction & Product type & Product \\
+                Disjunction & Sum type & Coproduct \\
+                Universal quantification & Dependent product type &  \\
+                Existential quantification & Dependent sum type &  \\
+                \hline
+            \end{tabular}
+            \caption{Curry-Howard-Lambek correspondence}
+            \label{tab: curry-howard-lambek}
+        \end{table}
 
         \subsection{Equality, congruence and substitution}
+        Equality here refers to the propositional equality. In Agda it is defined as
+        \[\includegraphics[width=\textwidth]{equality.pdf}\]
+        With equality as a type, whenever we want to prove that two terms are equal, we need to provide a witness of the equality.
+For example if we want to prove $x \equiv y$, we write out a term of type $\mb{\mathsf{x = y}}$, and then give its definition, which constructs a proof of the equality.
+A simple proof that directly uses the definition of equality is as follows:
+        \[\includegraphics[width=\textwidth]{sym_trans.pdf}\]
+        Here we are able to prove the symmetry and transitivity of equality by using the definition of equality. Those two properties are very useful for later proofs.
 
-        % \subsection{Proof Example}
+        We can also have more complex proof with congruence and substitution, which can also be directly derived from the definition of equality as follows:
+        \[\includegraphics[width=\textwidth]{cong_subst.pdf}\]
+        Congruence is a property of equality that states that if two terms are equal, then they can be substituted for each other in any context.
+Substitution is a property where we can get a new proof by replacing a term in a proof with another term that is equal to it.
+
+        Here is a simple example of how congruence can be used in a proof:
+        \[\includegraphics[width=\textwidth]{cong_example.pdf}\]
+
+        In this example, we want to prove that $\gn{\mathsf{zero}}$ is the right identity of the plus function. We do an inductive proof by pattern matching on the first argument of the plus function.
+
+        In the base case, we have $\gn{\mathsf{zero}} \mb{{}+{}} \gn{\mathsf{zero}} \equiv \gn{\mathsf{zero}}$, which is trivially true by the definition of the plus function (zero is defined to be the left identity of the plus function).
+
+        In the inductive case, we need to show $\gn{\mathsf{suc}}\ n \mb{{}+{}} \gn{\mathsf{zero}} \equiv \gn{\mathsf{suc}}\ n$.
+We can use the definition of the plus function to rewrite the left-hand side as $\gn{\mathsf{suc}}\ (n \mb{{}+{}} \gn{\mathsf{zero}})$.
+By the inductive hypothesis, we know that $n \mb{{}+{}} \gn{\mathsf{zero}} \equiv n$, so we can substitute $n$ for $n \mb{{}+{}} \gn{\mathsf{zero}}$ in the right-hand side by congruence, and we are done.
+
+        \subsection{Proof Example}
+        [decide exact example here]
 
         \subsection{Standard library}
+        The Agda standard library \cite{agda_std} is a collection of modules that provide a wide range of useful functions and types.
+It includes modules for basic data types, such as natural numbers, lists, and vectors.
+In my implementation, however, I defined most of the basic data types and functions from scratch for the following two reasons:
+        \begin{itemize}
+            \item
+                I wanted to have a better understanding of the basic data types and functions, so I decided to implement them from scratch.
+            \item
+                I need a particular representation of minus operation that ensures the input is always valid. This is further explained in [to add]
+        \end{itemize}
 
-        \subsection{Interactive programming with holes}
+        With standard library, we can use actual numbers $1, 2, 3, \dots$ instead of calling the constructor $\gn{\mathsf{suc}}$ multiple times.
+This is a convenient feature for testing.
+Agda provides a way to link self-defined functions to the standard library with a BUILTIN programa.
+This allows me to use a convenient syntax for numbers, while still using the self-defined functions in the implementation.
+
+        \subsection{Interactive programming with holes} \label{subsec: holes}
         A feature of Agda is that it allows us to write programs with holes interatively.
@@
     \section{Requirement Analysis}
+    To complete a compiler in Agda we need to implement the following components:
+    \begin{itemize}
+        \item 
+            A file source.agda that record the syntax of the source language.
+
+        \item
+            A file target.agda that record the syntax of the target language.
+
+        \item
+            A file compiler.agda that uses source.agda and target.agda as modules, and write functions whose input is a term in the source language and output is a term in the target language.
+    \end{itemize}
+    The success criteria of the project is that the compiler can compile a term in the source language to a term in the target language, and the output term is well-typed in the target language.
 
@@
     Code from the PLFA tutorial and Agda standard library \cite{agda_std} were used as references.
+
+    \section{Summary}
+    \begin{itemize}
+        \item 
+        requirement Analysis
+
+        \item
+        tools and engineering approach
+
+    \end{itemize}
 

### 2025-04-23 draft.tex
programa example added; citation adjusted

@@
 \definecolor{green}{HTML}{008B00}
+\definecolor{orange}{HTML}{CD6600}
+
 \newcommand{\mb}[1]{\textcolor{mediumblue}{#1}}
 \newcommand{\gn}[1]{\textcolor{green}{#1}}
+\newcommand{\og}[1]{\textcolor{orange}{#1}}
 
@@
 
-    This dissertation presents an implementation of a compiler from the source language to the target language with Agda \cite{Agda}.
-This implementation is based on the work of Reynolds \cite{Reynolds}, who presented a denotational semantics of Algol-like languages in the form of a presheaf category over stack descriptors.
+    This dissertation presents an implementation of a compiler from the source language to the target language with Agda~\cite{Agda}.
+This implementation is based on the work of Reynolds~\cite{Reynolds}, who presented a denotational semantics of Algol-like languages in the form of a presheaf category over stack descriptors.
 The compiler is implemented as a functor from the source language to the target language.
@@
     \section{Motivation and related work} \label{sec: motivation}
-        The denotational semantics of Algol-like languages can be structured as a presheaf category over stack descriptors, which has been shown by Reynolds \cite{essence} and Oles \cite{Oles_1} \cite{Oles_2}.
+        The denotational semantics of Algol-like languages can be structured as a presheaf category over stack descriptors, which has been shown by Reynolds~\cite{essence} and Oles~\cite{Oles_1}~\cite{Oles_2}.
 By interpreting the source language into this category, where objects of the category represent instruction sequences parameterised by stack layouts, the semantic model directly yields a compiler.
-The mathematical structure of the compiler has been specified by Reynolds in his paper ``Using Functor Categories to Generate Intermediate Code'' \cite{Reynolds}.
+The mathematical structure of the compiler has been specified by Reynolds in his paper ``Using Functor Categories to Generate Intermediate Code''~\cite{Reynolds}.
 
@@
         \motivation{Trend of verified compilers}
-        The rise of verified compilers including CompCert \cite{CompCert}, CakeML \cite{CakeML} reflects a broader trend toward trustworthy systems, where correctness proofs replace testing for critical guarantees.
-Like Lean 4 \cite{Lean4}, we leverage dependent types to internalise the verification of correctness of terms.
+        The rise of verified compilers including CompCert~\cite{CompCert}, CakeML~\cite{CakeML} reflects a broader trend toward trustworthy systems, where correctness proofs replace testing for critical guarantees.
+Like Lean 4~\cite{Lean4}, we leverage dependent types to internalise the verification of correctness of terms.
 
     \section{Language choice: Agda's advantages}
-        Agda \cite{Agda} is a dependently typed programming language and proof assistant.
+        Agda~\cite{Agda} is a dependently typed programming language and proof assistant.
 Agda captures the source language's intrinsic sytax with indexed families, which contains only well-typed terms.
@@
         Dependently typed languages provide a natural framework for expressing functor categories is proven both theoretically and practically.
-There have been dependent-type-theoretic model of categories \cite{Dybjer}, and it has been shown that functor categories arise naturally as dependent function types \cite{Jacobs}.
-A formalisation of Category Theory, including cartesian closed categories, functors and presheaves has been developed in Agda by Hu and Caratte \cite{Cat_Agda}.
+There have been dependent-type-theoretic model of categories~\cite{Dybjer}, and it has been shown that functor categories arise naturally as dependent function types~\cite{Jacobs}.
+A formalisation of Category Theory, including cartesian closed categories, functors and presheaves has been developed in Agda by Hu and Caratte~\cite{Cat_Agda}.
 Other proof assistants, such as Isabelle/Hol, does not have a dependently typed language structure, and thus cannot express the functor categories as naturally as Agda.
@@
     Prior to this project, I had no experience with Agda.
-Although I was aware of the open-source online tutorial \textit{Programming Language Foundations in Agda} (PLFA) \cite{plfa}, my preparation was limited to setting up the Agda environment on my laptop by following the ``Front Matter'' section of the tutorial.
+Although I was aware of the open-source online tutorial \textit{Programming Language Foundations in Agda} (PLFA)~\cite{plfa}, my preparation was limited to setting up the Agda environment on my laptop by following the ``Front Matter'' section of the tutorial.
 
@@
         Category theory provides a high-level abstraction from which we can reason about the structure of mathematical objects and their relationships.
-It provides us a ``bird's eye view'' of the mathematics which enable us to spot patterns that are difficult to see in the details.
-\cite{basic_cat} More specifically, it provides a ``purer'' view of functions that is not derived from sets.
-\cite{scott-lambda} Compared to set theory which is ``element-oriented'', category theory is ``function-oriented'' and ``morphism-oriented''.
+It provides us a ``bird's eye view'' of the mathematics which enable us to spot patterns that are difficult to see in the details~\cite{basic_cat}.
+More specifically, it provides a ``purer'' view of functions that is not derived from sets~\cite{scott-lambda}.
+Compared to set theory which is ``element-oriented'', category theory is ``function-oriented'' and ``morphism-oriented''.
 We understand structures not via elements but by how they transform into each other.
@@
 There is a deeper connection between category theory and type theory.
-Curry-Howard correspondence \cite{curry-howard} states that there is a correspondence between logic and type theory, where propositions correspond to types and proofs correspond to terms.
-This correspondence was later extended by Joachim Lambek, who showed that cartesian closed categories provide a natural semantic setting for the simply typed lambda calculus.
-\cite{lambek} Under this perspective, types become objects in a category, and programs correspond to morphisms.
+Curry-Howard correspondence~\cite{curry-howard} states that there is a correspondence between logic and type theory, where propositions correspond to types and proofs correspond to terms.
+This correspondence was later extended by Joachim Lambek, who showed that cartesian closed categories provide a natural semantic setting for the simply typed lambda calculus~\cite{lambek}.
+Under this perspective, types become objects in a category, and programs correspond to morphisms.
 We will further explore this connection in \secref{subsec: curry-howard-lambek}.
 
-        The following is a brief introduction to the basic concepts of category theory, which is based on the work of Leinster \cite{basic_cat}, 
-        Riehl \cite{cat_context}, and the lecture notes of Part II Category Theory by Andrew Pitts and Marcelo Fiore \cite{cat_lecture_notes}.
+        The following is a brief introduction to the basic concepts of category theory, which is based on the work of Leinster~\cite{basic_cat}, 
+        Riehl~\cite{cat_context}, and the lecture notes of Part II Category Theory by Andrew Pitts and Marcelo Fiore~\cite{cat_lecture_notes}.
 
@@
         \subsection{Basic datatypes and pattern matching}
-        We will go through a simple example in PLFA \cite{plfa} to illustrate the basic datatypes and pattern matching in Agda.
+        We will go through a simple example in PLFA~\cite{plfa} to illustrate the basic datatypes and pattern matching in Agda.
 
-        \[\includegraphics[width=\textwidth]{example.pdf}\]
+        \[\includegraphics[width=\textwidth]{natural_plus.pdf}\]
 
@@
         \subsection{Standard library}
-        The Agda standard library \cite{agda_std} is a collection of modules that provide a wide range of useful functions and types.
+        The Agda standard library~\cite{agda_std} is a collection of modules that provide a wide range of useful functions and types.
 It includes modules for basic data types, such as natural numbers, lists, and vectors.
@@
 This is a convenient feature for testing.
-Agda provides a way to link self-defined functions to the standard library with a BUILTIN programa.
+Agda provides a way to link self-defined functions to the standard library with a \og{\textsf{BUILTIN}} programa.
 This allows me to use a convenient syntax for numbers, while still using the self-defined functions in the implementation.
+        \[\includegraphics[width=\textwidth]{natural_programma.pdf}\]
+        Note that in agda we can use unicode characters for terms, which makes the code more readable. For example, here we simply name the term \mb{1+1$\equiv$2}.
 
@@
     \section{Tools Used}
-    Completing the project is an iterative process. I used Git \cite{git} for version control, and work had been synchronised with a GitHub \cite{github} repository for backup.
+    Completing the project is an iterative process. I used Git~\cite{git} for version control, and work had been synchronised with a GitHub~\cite{github} repository for backup.
 
-    For the development environment, I tried both Emacs \cite{emacs} and Visual Studio Code \cite{vscode} with an agda-mode extension \cite{agda_mode} on Windows Subsystem for Linux with Ubuntu \cite{wsl_ubuntu} 22.04 LTS.
+    For the development environment, I tried both Emacs~\cite{emacs} and Visual Studio Code~\cite{vscode} with an agda-mode extension~\cite{agda_mode} on Windows Subsystem for Linux with Ubuntu~\cite{wsl_ubuntu} 22.04 LTS.
 I am more familiar with the snippet and syntax highlighting features of Visual Studio Code, so I used it for most of the development.
 
-    Code from the PLFA tutorial and Agda standard library \cite{agda_std} were used as references.
+    Code from the PLFA tutorial and Agda standard library~\cite{agda_std} were used as references.
 

### 2025-05-01 draft.tex
implementation and evaluation structure

@@
 \usepackage{xeCJK}
+\usepackage{dirtree}
+\usepackage{float}
+\usepackage{pdfpages}
+\usepackage{atbegshi}
 
@@
 
-\graphicspath{{./fig/category_theory/}{./fig/agda/lagda/latex/}}
+\graphicspath{{./fig/category_theory/}{./fig/agda/lagda/latex/}{./fig/implementation/}{./proposal/}{./code/}}
 
@@
 \theoremstyle{definition}
-\newtheorem*{definition*}{Definition}
+\newtheorem{definition}{Definition}
 
 \theoremstyle{definition}
-\newtheorem*{theorem*}{Theorem}
+\newtheorem{theorem}{Theorem}
+
+\theoremstyle{definition}
+\newtheorem{example}{Example}
+
+\theoremstyle{definition}
+\newtheorem{prf}{Proof}
 
@@
 \newcommand{\secref}[1]{\S\ref{#1}}
+\newcommand{\chapref}[1]{\ref{#1}}
 
@@
 
+\newcommand{\bracket}[1]{\left\langle #1 \right\rangle}
+
 \begin{document}
@@
 
-\title{Using functor categories to generate intermediate code with Agda}
-\author{Jack Gao}
-\date{\today}
-\maketitle
+\begin{titlepage}
+    \begin{flushright}
+        \textbf{\Large Jack Gao}
+    \end{flushright}
+
+    \vspace{12em}
+
+    \begin{center}
+        \textbf{\huge Using functor categories to generate intermediate code with Agda}
+        \vspace{3em}
+
+        {\Large Computer Science Tripos - Part II Dissertation}
+        \vspace{1em}
+
+        {\Large Homerton College}
+        \vspace{1em}
+
+        {\large \today}
+    \end{center}
+\end{titlepage}
+
+\begin{titlepage}
+    \vspace*{5em}
+    \textbf{\LARGE Declaration of Originality}
+    \vspace{2em}
+
+    I, the candidate for Part II of the Computer Science Tripos with Blind Grading Number 2330G, hereby declare that this report and the work described in it are my own work, unaided except as may be specified below, and that the report does not contain material that has already been used to any substantial extent for a comparable purpose.
+In preparation of this report, I adhered to the Department of Computer Science and Technology AI Policy.
+I am content for my report to be made available to the students and staff of the University.
+    \vspace{1em}
+
+    Date: \today
+\end{titlepage}
+
+\begin{titlepage}
+    \vspace*{5em}
+    \textbf{\LARGE Proforma}
+    \vspace{2em}
+
+    \begin{tabular}{ll}
+        \textbf{Candidate Number:} & 2330G \\
+        \textbf{Title of Project:} & Using functor categories to generate intermediate code with Agda \\
+        \textbf{Examination} & Computer Science Tripos - Part II - 2025 \\
+        \textbf{Word-Count:} & [wordcount] \\
+        \textbf{Code line count:} & [linecount] \\
+        \textbf{Project Originator:} & Yulong Huang \\
+        \textbf{Project Supervisor:} & Yulong Huang and Yufeng Li \\
+    \end{tabular}
+
+    \vspace{2em}
+    \textbf{\Large Original Aims of the Project}
+    \vspace{1em}
+
+    \vspace{2em}
+    \textbf{\Large Work Completed}
+    \vspace{1em}
+
+    \vspace{2em}
+    \textbf{\Large Special Difficulties}
+    \vspace{1em}
+\end{titlepage}
 
@@
     \minitoc
-    An Algol-like language is a typed lambda calculus with store. In this dissertation, the source language is an Algol-like language with the following primitive types:
-    \begin{itemize}
-        \item 
-            \textbf{comm}: the commands
-        \item 
-            \textbf{intexp}: the integer expressions
-        \item 
-            \textbf{intacc}: the integer acceptors
-        \item 
-            \textbf{intvar}: the integer variables
-    \end{itemize}
-    and the set $\Theta$ of types is defined as follows:
-    \[ \Theta := \textbf{comm} \mid \textbf{intexp} \mid \textbf{intacc} \mid \textbf{intvar} \mid \Theta \to \Theta \]
+    Programming languages act as a bridge between human thought and machine execution.
+They exist in two complementary realms: the human realm, where intent is expressed through abstractions like variables and functions, and the machine realm, where low-level instructions are executed on hardware.
 
-    [Considering adding an example of Algol-like language here]
+    Denotational semantics is related to the human realms.
+It provides a theoretical framework for defining the meaning of programming languages by interpreting them into mathematical objects.
+By formalising the denotational semantics of a programming language, we ensure that its abstraction align with human intuition.
 
-    The target language is an assembly-style intermediate language for a stack machine. It is defined with four stack-descriptor-indexed families of non-terminals: 
-    \begin{itemize}
-        \item 
-            $\langle\text{L}_{sd}\rangle$: lefthand sides
-        \item 
-            $\langle\text{S}_{sd}\rangle$: Simple righthand sides
-        \item
-            $\langle\text{R}_{sd}\rangle$: righthand sides
-        \item
-            $\langle\text{I}_{sd}\rangle$: instruction sequences
-    \end{itemize}
+    Compilers are related to the machine realms.
+They are programs that translate high-level code into executable instructions, resolving abstractions into concrete operations like memory allocation and register management.
+Compilers are essential for turning human-written code into physical computation.
 
-    The grammer of the target language is specified in Chapter 3. [Add exact section/subsection here]
+    This project explores how the two process can be deeply connected by demonstrating how denotational semantics can directly generate a compiler.
+Simple Typed Lambda Calculus (STLC) is a well-studied programming language that serves as a foundation for many modern languages.
+It has denotational semantics in cartesian closed categories, shown by Lambek~\cite{lambek}.
+As a ccc, presheaf categories over store locations can be used to model STLC with stores, as shown by by Reynolds~\cite{essence} and Oles~\cite{Oles_1}~\cite{Oles_2}.
+Instead, Reynolds~\cite{Reynolds} presented a denotational semantics of STLC with stores in the form of a presheaf category over compiler states.
+By interpresting the source language into the presheaf category over stack descriptors, where objects of the category represent instruction sequences parameterised by stack layouts, the semantic model directly yields a compiler.
 
-    This dissertation presents an implementation of a compiler from the source language to the target language with Agda~\cite{Agda}.
-This implementation is based on the work of Reynolds~\cite{Reynolds}, who presented a denotational semantics of Algol-like languages in the form of a presheaf category over stack descriptors.
-The compiler is implemented as a functor from the source language to the target language.
+    I implement this compiler for STLC with stores in a dependently typed programming language, Agda~\cite{Agda}.
+The compiler is a functor (structure-preserving map) from the source language's semantic domain to the target language's instruction set.
 The implementation is verified with Agda's type system, which ensures that the generated code is well-typed and adheres to the semantics of both the source and target languages.
-This implementation proves and refines Reynolds' work, providing a practical example of how to use functor categories to generate intermediate code.
 
-    \section{Motivation and related work} \label{sec: motivation}
-        The denotational semantics of Algol-like languages can be structured as a presheaf category over stack descriptors, which has been shown by Reynolds~\cite{essence} and Oles~\cite{Oles_1}~\cite{Oles_2}.
-By interpreting the source language into this category, where objects of the category represent instruction sequences parameterised by stack layouts, the semantic model directly yields a compiler.
-The mathematical structure of the compiler has been specified by Reynolds in his paper ``Using Functor Categories to Generate Intermediate Code''~\cite{Reynolds}.
+    This work both validates and refines Reynolds' theory, offering a concrete example of how category-theoretic semantics can generate intermediate code.
+The project also serves as a practical demonstration of the power of dependently typed programming languages can mechanise the link between theory and practice.
 
+    \section{Motivation} \label{sec: motivation}
         This project is motivated and guided by the following:
@@
         \motivation{Implementation of the compiler}
-        Reynolds concluded that he did not have a proper dependently typed programming language in hand, so his compiler remained a partial function theoretically.
-We aim to provide a computer implementation of this theoretical framework in a dependently typed programming language.
+        Reynolds concluded that he did not have a proper dependently typed programming language in hand, so his compiler remained a partial function.
+I aim to provide a computer implementation of this theoretical framework in a dependently typed programming language.
 
         \motivation{Formal verification of the compiler}
-        The terms in Reynolds' work are also written by hand.
-Terms are complicated and error-prone, and it is difficult to verify the correctness of the terms.
-We aim to provide a formalisation of the terms in a proof assistant to verify the correctness of the terms.
+        Reynolds' work presented detailed definitions of denotational semantics of STLC with stores, which are complicated and error-prone.
+The rise of verified compilers including CompCert~\cite{CompCert}, CakeML~\cite{CakeML} reflects a broader trend toward trustworthy systems, where correctness proofs replace testing for critical guarantees.
+I aim to provide a formalisation of the definition in a proof assistant to verify the correctness of the given denotational semantics.
 
-        \motivation{Trend of verified compilers}
-        The rise of verified compilers including CompCert~\cite{CompCert}, CakeML~\cite{CakeML} reflects a broader trend toward trustworthy systems, where correctness proofs replace testing for critical guarantees.
+        % \motivation{Trend of verified compilers}
+        % The rise of verified compilers including CompCert~\cite{CompCert}, CakeML~\cite{CakeML} reflects a broader trend toward trustworthy systems, where correctness proofs replace testing for critical guarantees.
 Like Lean 4~\cite{Lean4}, we leverage dependent types to internalise the verification of correctness of terms.
@@
 Other proof assistants, such as Isabelle/Hol, does not have a dependently typed language structure, and thus cannot express the functor categories as naturally as Agda.
+
+        Compared to other dependently typed languages, Agda is more balanced in terms of programming and proving.
+Its \og{\textsf{with}}-abstraction and \og{\textsf{rewrite}} construction allow for a more flexible and powerful way to define and manipulate terms.
+The \og{\textsf{with}}-abstraction allows us to inspect intermediate values in a term, which gives a refined view of a function's argument.
+The \og{\textsf{rewrite}} construction allows us to define new terms by expanding existing terms, which avoids rewriting proofs of similar structures.
+
         Agda also provides an interactive environment for writing and verifying programs, which will be further discussed in \secref{subsec: holes}.
-
-        [Do I need a table for comparing other proof assistants and Agda?]
 
@@
             \savedmotivationI
-            We implemented the compiler from the source language to the target language in Agda.
+            I implemented the compiler from the source language to the target language in Agda.
 
             \savedmotivationII
-            We formalised the terms in the source language and target language in Agda, and proved that the compiler is a functor from the source language to the target language.
+            I formalised the terms in the source language and target language in Agda, and proved that the compiler is a functor from the source language to the target language.
 
-            \savedmotivationIII
-            This implementation follows the trend of verified compilers, and provides a practical example of how to use functor categories to generate intermediate code.
+            % \savedmotivationIII
+            % This implementation follows the trend of verified compilers, and provides a practical example of how to use functor categories to generate intermediate code.
         \end{quote}
@@
     \minitoc
+
+    For implementing the compiler, I need to understand the theoretical background of presheaves and functor categories that are used as the denotational semantics of the source language, and I need to understand Agda's dependent types to correctly express the dependent function space of presheaf exponentials.
+This chapter begins with my starting point and an introduction to category theory, followed by a brief overview of the dependently typed programming language Agda, and requirements analysis of the compiler.
 
@@
 
-    \section{Category theory background} \label{sec: cat}
+    \section{Category theory} \label{sec: cat}
         Category theory provides a high-level abstraction from which we can reason about the structure of mathematical objects and their relationships.
@@
 For example, $A, B, \dots$ are used to denote objects, sets, or types, and arrows are used to denote morphisms or functions (e.g.\ $A \to B$).
-There is a deeper connection between category theory and type theory.
-Curry-Howard correspondence~\cite{curry-howard} states that there is a correspondence between logic and type theory, where propositions correspond to types and proofs correspond to terms.
-This correspondence was later extended by Joachim Lambek, who showed that cartesian closed categories provide a natural semantic setting for the simply typed lambda calculus~\cite{lambek}.
-Under this perspective, types become objects in a category, and programs correspond to morphisms.
-We will further explore this connection in \secref{subsec: curry-howard-lambek}.
+There is a deeper connection between category theory and type theory, which will
+        be discussed in \secref{subsec: curry-howard-lambek}.
 
@@
         \subsection{Category}
-        \begin{definition*}[Category]
+        \begin{definition}[Category]
             A \emph{category} $\mathcal{C}$ is specified by the following:
@@
             \end{itemize}
-        \end{definition*}
+        \end{definition}
 
+        \begin{example}[$\mathcal{Set}$]
             An example of category is the category of sets, denoted as $\mathcal{Set}$, specifed by:
@@
                 \item
-                for each $X, Y \in \textbf{obj}(\mathcal{Set})$, the morphisms from $X$ to $Y$ in $\mathcal{Set}$ are the functions from $X$ to $Y$;
+                    for each $X, Y \in \textbf{obj}(\mathcal{Set})$, the morphisms from $X \to Y$ in $\mathcal{Set}$ are the functions $X \to Y$;
                 \item
@@
             Associativity law and unit laws are satisfied in $\mathcal{Set}$, since the composition of functions is associative and the identity function compose with any function is the function itself.
+        \end{example}
+
+        \begin{example}[$\mathcal{Poset}$]
+            Another example of category is the category of posets, denoted as $\mathcal{Poset}$, specified by:
+            \begin{itemize}
+                \item 
+                    the objects of $\mathcal{Poset}$ are a fixed universe of posets, which is a set $P$ with a binary relation $\subseteq$ that is 
+                    \begin{itemize}
+                        \item reflexive: $\forall x \in P, x \subseteq x$;
+                        \item transitive: $\forall x, y, z \in P, x \subseteq y \land y \subseteq z \implies x \subseteq z$;
+                        \item antisymmetric: $\forall x, y \in P, x \subseteq y \land y \subseteq x \implies x = y$.
+                    \end{itemize}
+                \item
+                    for each $X, Y \in \textbf{obj}(\mathcal{Poset})$, the morphisms from $X$ to $Y$ in $\mathcal{Poset}$ are the monotone (order-preserving) functions from $X$ to $Y$;
+                \item
+                    the identity morphism on $X$ in $\mathcal{Poset}$ is the identity function on $X$;
+                \item
+                    the composition of morphisms in $\mathcal{Poset}$ is defined as the composition of functions.
+            \end{itemize}
+            Associativity law and unit laws are satisfied in $\mathcal{Poset}$, since the set of monotone functions contains identity functions and is closed under composition.
+
+            $\mathcal{Poset}$ is used later for stack descriptors in the denotational semantics of the source language.
+        \end{example}
 
@@
 
-            \begin{definition*}[Opposite category]
+            \begin{definition}[Opposite category]
                 Given a category $\mathcal{C}$, its \emph{opposite category} $\mathcal{C}^{\textbf{op}}$ is specified by:
@@
                 \end{itemize}
-            \end{definition*}
+            \end{definition}
 
@@
 
-            \begin{figure}[htb!]
+            \begin{figure}[H]
                 \centering
@@
         \subsection{Isomorphism}
-        \begin{definition*}[Isomorphism]
+        \begin{definition}[Isomorphism]
             Given a category $\mathcal{C}$, a $C$-morphism $f : X \to Y$ is called an \emph{isomorphism} if there exists a $C$-morphism $g : Y \to X$ such that the following diagram commutes:
@@
 
-        \end{definition*}
+        \end{definition}
 
-        [Considering adding examples of isomorphism]
-
-        \subsection{Terminal object}
-        \begin{definition*}[Terminal object]
+        \subsection{Cartesian closed category}
+            \subsubsection{Terminal object}
+            \begin{definition}[Terminal object]
                 Given a category $\mathcal{C}$, an object $T \in \textbf{obj}(\mathcal{C})$ is called a \emph{terminal object} if for all $X \in \textbf{obj}(\mathcal{C})$, there exists a unique \textbf{C}-morphism $f : X \to T$.
-        \end{definition*}
-        [Considering adding examples of terminal object]
-
+            \end{definition}
             Terminal objects are unique up to isomorphism. In other words, we have
@@
             \end{itemize}
+            \begin{example}[Terminal object in $\mathcal{Set}$]
+                $\mathcal{Set}$ has a terminal object $\{\ast\}$, which is an arbitrary singleton set containing a single element $\ast$.
 
-        % \subsection{Initial object}
-        % \begin{definition*}[Initial object]
-        %     Given a category $\mathcal{C}$, an object $I \in \textbf{obj}(\mathcal{C})$ is called an \emph{initial object} if for all $X \in \textbf{obj}(\mathcal{C})$, there exists a unique \textbf{C}-morphism $f : I \to X$.
-        % \end{definition*}
-        % Initial object is dual to terminal object. By the principle of duality, initial objects are unique up to isomorphism. In other words, we have
-        % \begin{itemize}
-        %     \item 
-        %         if $I$ and $I'$ are both initial objects in $\mathcal{C}$, then there exists a unique isomorphism $f : I \to I'$.
-        %     \item
-        %         if $I$ is an initial object in $\mathcal{C}$ and $I \cong I'$, then $I'$ is also an initial object in $\mathcal{C}$.
-        % \end{itemize}
+                For any set $X$, there exists a unique function $f : X \to \{\ast\}$ that maps every element of $X$ to the single element $\ast$ in $\{\ast\}$.
 
-        \subsection{Binary product}
-        \begin{definition*}[Binary product]
+                There is a unique isomorphism $f : \{\ast\} \to \{\cdot\}$ for any two singleton sets $\{\ast\}$ and $\{\cdot\}$, which is $f(\ast) = \cdot$.
+            \end{example}
+
+            \subsubsection{Binary product}
+            \begin{definition}[Binary product]
                 Given a category $\mathcal{C}$, the \emph{binary product} of two objects $X$ and $Y$ in $\mathcal{C}$ is specified by
@@
                 The unique morphism $u$ is written as 
-            \[ \langle x, y \rangle : Z \to X \times Y \]
-            where $x = \pi_1 \circ u$ and $y = \pi_2 \circ u$.
-        \end{definition*}
+                \[ \bracket{ f, g } : Z \to X \times Y \]
+                where $f = \pi_1 \circ u$ and $g = \pi_2 \circ u$.
+            \end{definition}
             It can be shown that the binary product is unique up to (unique) isomorphism.
 
-        \subsection{Exponential}
-        \begin{definition*}[Exponential]
+            \begin{example}[Binary product in $\mathcal{Set}$]
+                The binary product of two sets $X$ and $Y$ in $\mathcal{Set}$ is the Cartesian product $X \times Y = \{(x,y) \mid x \in X \land y \in Y\}$, where $(x,y)$ are ordered pairs.
+
+                We have the following projections:
+                \begin{itemize}
+                    \item 
+                        $\pi_1 : X \times Y \to X$ is defined as $\pi_1(x,y) = x$ for all $(x,y) \in X \times Y$;
+                    \item
+                        $\pi_2 : X \times Y \to Y$ is defined as $\pi_2(x,y) = y$ for all $(x,y) \in X \times Y$.
+                \end{itemize}
+
+                For any set $Z$, for any functions $f : Z \to X$ and $g : Z \to Y$, the unique morphism $u : Z \to X \times Y$ is defined as:
+                \[u(z) = (f(z), g(z)) \text{ for all $z \in Z$.}\]
+            \end{example}
+
+            \subsubsection{Exponential}
+            \begin{definition}[Exponential]
                 Given a category $\mathcal{C}$ with binary products, the \emph{exponential} of two objects $X$ and $Y$ in $\mathcal{C}$ is specified by
@@
                 where $\textbf{cur} f$ is called the \emph{currying} of $f$.
-        \end{definition*}
+            \end{definition}
             It can be shown that the exponential is unique up to (unique) isomorphism.
 
-        \subsection{Cartesian closed category}
-        \begin{definition*}[Cartesian closed category]
+            \begin{example}[Exponential in $\mathcal{Set}$]
+                The exponential of two sets $X$ and $Y$ in $\mathcal{Set}$ is the set of all functions from $X$ to $Y$.
+
+                Function application gives the morphism $\textbf{app} : (X \Rightarrow Y) \times X \to Y$ as $\textbf{app}(f,x) = f(x)$ for all $f \in X \Rightarrow Y$ and $x \in X$.
+
+                The currying operation transform a function $f : Z \times X \to Y$ into a function $\textbf{cur} f : Z \to (X \Rightarrow Y)$, which is defined as $\textbf{cur} f(z) = \lambda x.f(z,x)$ for all $z \in Z$ and $x \in X$.
+
+            \end{example}
+
+        \begin{definition}[Cartesian closed category]
             A category $\mathcal{C}$ is called a \emph{Cartesian closed category} (ccc) if it has a terminal object, binary products and exponentials of any two objects.
-        \end{definition*}
+        \end{definition}
 
         \subsection{Functor}
-        \begin{definition*}[Functor]
+        \begin{definition}[Functor]
             Given two categories $\mathcal{C}$ and $\mathcal{D}$, a \emph{functor} $F: \mathcal{C} \to \mathcal{D}$ is specified by:
@@
                 \item 
-                    for all $X, Y \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$, we have:
-                    \begin{equation} \label{law: functor_id}
-                        F(\textbf{id}_X) = \textbf{id}_{F(X)}
-                    \end{equation}
+                    for all $X, Y \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$, we have: $ F(\textbf{id}_X) = \textbf{id}_{F(X)}$
                 \item
-                    for all $X, Y, Z \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$, $g \in \mathcal{C}{(Y,Z)}$, we have:
-                    \begin{equation} \label{law: functor_comp}
-                        F(g \circ f) = F(g) \circ F(f)
-                    \end{equation}
+                    for all $X, Y, Z \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$, $g \in \mathcal{C}{(Y,Z)}$, we have: $F(g \circ f) = F(g) \circ F(f)$
             \end{itemize}
-        \end{definition*}
-
-        [Considering adding examples of functors: e.g. free functor, forgetful functor, etc.]
+        \end{definition}
 
         \subsection{Natural transformation}
-        \begin{definition*}[Natural transformation]
+        \begin{definition}[Natural transformation]
 
@@
 
-            commutes in $\mathcal{D}$, i.e. the following equation holds:
-            \begin{equation} \label{law: natural_transformation}
-                G(f) \circ \theta_X = \theta_Y \circ F(f)
-            \end{equation}
+            commutes in $\mathcal{D}$, i.e. $G(f) \circ \theta_X = \theta_Y \circ F(f)$
 
-        \end{definition*}
-
-        [Considering adding examples of natural transformations]
+        \end{definition}
 
         \subsection{Functor category}
-        \begin{definition*}[Functor category]
+        \begin{definition}[Functor category]
             Given two categories $\mathcal{C}$ and $\mathcal{D}$, the \emph{functor category} $\mathcal{D}^{\mathcal{C}}$ is the category satisfying the following:
@@
             \end{itemize}
-        \end{definition*}
+        \end{definition}
 
         \subsection{Presheaf category}
-        \begin{definition*}[Presheaf]
+        \begin{definition}[Presheaf]
             Given a category $\mathcal{C}$, a \emph{presheaf} on $\mathcal{C}$ is a functor $F: \mathcal{C}^{\textbf{op}} \to \textbf{Set}$.
@@
             \end{itemize}
-        \end{definition*}
+        \end{definition}
 
-        \begin{definition*}[Presheaf category]
-            Given a category $\mathcal{C}$, the \emph{presheaf category} $\mathcal{P}(\mathcal{C})$ is the functor category $\mathcal{Set}^{\mathcal{C}^{\textbf{op}}}$.
+        \begin{definition}[Presheaf category]
+            Given a category $\mathcal{C}$, the \emph{presheaf category} $\hat{\mathcal{C}}$ is the is the functor category $\mathcal{Set}^{\mathcal{C}^{\textbf{op}}}$, which explicitly contains the following:
             \begin{itemize}
                 \item 
-                    the objects of $\mathcal{P}(\mathcal{C})$ are all presheaves on $\mathcal{C}$;
+                    the objects of $\hat{\mathcal{C}}$ are all presheaves on $\mathcal{C}$;
                 \item
-                    given two presheaves $F,G: \mathcal{C}^{\textbf{op}} \to \mathcal{Set}$, the morphisms from $F$ to $G$ in $\mathcal{P}(\mathcal{C})$ are all natural transformations $\theta : F \to G$.
+                    given two presheaves $F,G: \mathcal{C}^{\textbf{op}} \to \mathcal{Set}$, the morphisms from $F$ to $G$ in $\hat{\mathcal{C}}$ are all natural transformations $\theta : F \to G$.
             \end{itemize}
-        \end{definition*}
+        \end{definition}
 
         \subsection{Yoneda lemma}
-        \begin{definition*}[Yoneda functor]
-            Given a category $\mathcal{C}$, the \emph{Yoneda functor} $\yo: \mathcal{C} \to \mathcal{Set}^{\mathcal{C}^{\textbf{op}}}$ is defined as follows:
+        \begin{definition}[Yoneda functor]
+            Given a category $\mathcal{C}$, the \emph{Yoneda functor} $\yo: \mathcal{C} \to \hat{\mathcal{C}}$ is defined as follows:
             \begin{itemize}
                 \item 
-                    for each $X \in \textbf{obj}(\mathcal{C})$, $\yo(X)$ is the functor $y(X) : \mathcal{C}^{\textbf{op}} \to \mathcal{Set}$ defined as:
+                    for each $X \in \textbf{obj}(\mathcal{C})$, $\yo(X)$ is the functor $\mathcal{C}^{\textbf{op}} \to \mathcal{Set}$ defined as:
                     \begin{equation} \label{eq: yoneda_element}
@@
 
-        \end{definition*}
+        \end{definition}
 
-        \begin{theorem*}[Yoneda lemma]
+        \begin{theorem}[Yoneda lemma]
             Given a category $\mathcal{C}$, the \emph{Yoneda lemma} states that for each object $X \in \textbf{obj}(\mathcal{C})$ and any functor $F: \mathcal{C} \to \textbf{Set}$, there is a natural isomorphism:
             \begin{equation} \label{eq: yoneda_lemma}
-                \mathcal{Set}^{\mathcal{C}^{\textbf{op}}}(\yo(X), F) \cong F(X)
+                {\hat{\mathcal{C}}}(\yo(X), F) \cong F(X)
             \end{equation}
-        \end{theorem*}
+        \end{theorem}
 
         \subsection{Cartesian closed structure in presheaf categories}
-        \begin{theorem*}[Cartesian closed structure in presheaf categories]
-            Given a small category $\mathcal{C}$, the presheaf category $\mathcal{Set}^{\mathcal{C}^{\textbf{op}}}$ is a Cartesian closed category.
+        \begin{prf}[Cartesian closed structure in presheaf categories]
+            Given a small category $\mathcal{C}$, the presheaf category $\hat{\mathcal{C}}$ is a Cartesian closed category.
             \begin{itemize}
                 \item 
-                    The terminal object in $\mathcal{Set}^{\mathcal{C}^{\textbf{op}}}$ is the constant functor $\mathbf{1} : \mathcal{C}^{\textbf{op}} \to \mathcal{Set}$, given by 
+                    The terminal object in $\hat{\mathcal{C}}$ is the constant functor $\mathbf{1} : \mathcal{C}^{\textbf{op}} \to \mathcal{Set}$, given by 
                     \begin{equation}
@@
                 \item
-                    The binary product in $\mathcal{Set}^{\mathcal{C}^{\textbf{op}}}$ is given by the product of functors, which is defined as follows:
+                    The binary product in $\hat{\mathcal{C}}$ is given by the product of functors, which is defined as follows:
                     \begin{equation}
@@
                 \item
-                    The exponential in $\mathcal{Set}^{\mathcal{C}^{\textbf{op}}}$ is given by the Yoneda lemma,
+                    The exponential in $\hat{\mathcal{C}}$ is derived from the Yoneda lemma,
                     \begin{equation}
                         \begin{aligned}
-                            G^{F}(X) &= \mathcal{Set}^{\mathcal{C}^{\textbf{op}}}(\yo(X) \times F, G) \\
-                            G^{F}(f)(\theta) &= \theta \circ (\yo(f) \times \textbf{id}_F) \quad \text{for all } \theta \in \mathcal{Set}^{\mathcal{C}^{\textbf{op}}}(\yo(Y) \times F, G)
+                            G^{F}(X) &= \hat{\mathcal{C}}(\yo(X) \times F, G) \\
+                            G^{F}(f)(\theta) &= \theta \circ (\yo(f) \times \textbf{id}_F) \quad \text{for all } \theta \in \hat{\mathcal{C}}(\yo(Y) \times F, G)
                         \end{aligned}
@@
             \end{itemize}
-        \end{theorem*}
+        \end{prf}
 
@@
         \subsection{Curry-Howard-Lambek correspondence} \label{subsec: curry-howard-lambek}
-        As introduced in \secref{sec: cat}, Curry-Howard correspondence states that there is a correspondence between logic and type theory, and Lambek extended this correspondence to show that cartesian closed categories provide a natural semantic setting for the simply typed lambda calculus.
-They can be summarised as follows:
-        \begin{table}[htb!]
+        Curry-Howard correspondence~\cite{curry-howard} establishes an isomorphism between logic and type theory, where propositions correspond to types and proofs correspond to terms.
+This correspondence forms the foundation of functional programming languages that can be used to implement proofs.
+Building upon this, Joachim Lambek showed that cartesian closed categories provide a natural semantic setting for the simply typed lambda calculus (STLC)~\cite{lambek}.
+The Curry-Howard-Lambek correspondence can be summarized as follows:
+        \begin{table}[H]
             \centering
@@
                 Truth & Unit type & Terminal object \\
-                Implication & Function type & Exponential object \\
+                Implication & Function type & Exponential \\
                 Conjunction & Product type & Product \\
                 Disjunction & Sum type & Coproduct \\
-                Universal quantification & Dependent product type &  \\
-                Existential quantification & Dependent sum type &  \\
+                % Universal quantification & Dependent product type &  \\
+                % Existential quantification & Dependent sum type &  \\
                 \hline
@@
 
-        \subsection{Proof Example}
-        [decide exact example here]
+        % \subsection{With and Rewrite}
 
@@
 
-    \section{Tools Used}
+\chapter{Implementation} \label{chap: implementation}
+    \minitoc
+    This chapter details the implementation of the compiler in Agda.
+Starting with a brief overview of the tools used, it then describes the directory structure and file dependencies.
+Then it discusses the
+    followed by the implementation of the source language, the target language, and finally the compiler.
+
+    \section{Tools used}
+    The project is implemented in Agda 2.7.0.1, which is the latest stable version at the time of writing.
+
     Completing the project is an iterative process. I used Git~\cite{git} for version control, and work had been synchronised with a GitHub~\cite{github} repository for backup.
@@
 
-    Code from the PLFA tutorial and Agda standard library~\cite{agda_std} were used as references.
+    Code from the PLFA tutorial and Agda standard library~\cite{agda_std} were used as references for implementation of the source language and the customised library.
+Apart from that, the code is written from scratch.
 
-    \section{Summary}
+    \section{Repository Overview}
+        \subsection{Directory structure}
+        The repository contains two independent implementations of the compiler, organised as follows:
+        \dirtree{%
+            .1 ..
+            .2 fin.
+            .3 lib.agda.
+            .3 source.agda.
+            .3 target.agda.
+            .3 compiler.agda.
+            .2 proof.
+            .3 lib.agda.
+            .3 source.agda.
+            .3 target.agda.
+            .3 compiler.agda.
+        }
+
+        \subsection{File dependencies and descriptions}
+        The dependency graph for each implementation is identical as follows:
+        \begin{figure}[H]
+            \centering
+            \includegraphics[width=0.6\textwidth]{dependencies.pdf}
+            \caption{Dependency graph for the compiler}
+            \label{fig: dependencies}
+        \end{figure}
+
+        \begin{table}[H]
+            \centering
+            \begin{tabular}{l l l}
+                \hline
+                \textbf{File} & \textbf{Description}\\
+                \hline
+                lib.agda & Shared utilities (e.g. natural numbers and operations, equality, etc.) \\
+                source.agda & Source language syntax \\
+                target.agda & Target language (stack machine) instructions \\
+                compiler.agda & Compiler functor \\
+                \hline
+            \end{tabular}
+            \caption{File descriptions}
+            \label{tab: file_descriptions}
+        \end{table}
+
+    \section{Source Language}
+    A Simply Typed Lambda Calculus (STLC) is a typed lambda calculus with only one type constructor ($\to$) that builds function types.
+
+        \subsection{Types}
+        In this dissertation, the source language is an STLC with the following primitive types:
         \begin{itemize}
             \item 
-        requirement Analysis
+                \textbf{comm}: the commands
+            \item 
+                \textbf{intexp}: the integer expressions
+            \item 
+                \textbf{intacc}: the integer acceptors
+            \item 
+                \textbf{intvar}: the integer variables
+        \end{itemize}
+        and the set $\Theta$ of types is defined as follows:
+        \[ \Theta := \textbf{comm} \mid \textbf{intexp} \mid \textbf{intacc} \mid \textbf{intvar} \mid \Theta \to \Theta \]
 
-        \item
-        tools and engineering approach
+        which corresponds with the following agda implementation:
+        \[\includegraphics[width=\textwidth]{/source/types.pdf}\]
 
+        \subsection{Contexts, variables and the lookup judgement}
+        We define the context as a finite list of types.
+When we are looking up a variable, the type of the variable is either on the top of the context or in the tail of the context.
+The context and the lookup judgement are defined as follows:
+        \[\includegraphics[width=\textwidth]{/source/contexts.pdf}\]
+
+        \subsection{Terms and the typing judgement}
+        The terms and the typing judgement are described in the following rules:
+        \begin{itemize}
+            \item For any variable we have 
+                \[\includegraphics{source_terms_var.pdf}\]
+            \item For lambda abstraction we have
+                \[\includegraphics{source_terms_lambda.pdf}\]
+            \item For command we have
+                \[\includegraphics{source_terms_comm.pdf}\]
+            \item For integer expression we have
+                \[\includegraphics{source_terms_intexp.pdf}\]
         \end{itemize}
 
-\chapter{Implementation}
+        The corresponding Agda implementation is as follows:
+        \[\includegraphics[width=\textwidth]{/source/terms.pdf}\]
+
+    \section{Target Language}
+    The target language is an assembly-style intermediate language for a stack machine. It is defined with four stack-descriptor-indexed families of non-terminals: 
+    \begin{itemize}
+        \item 
+            $\bracket{\text{L}_{sd}}$: lefthand sides
+        \item 
+            $\bracket{\text{S}_{sd}}$: Simple righthand sides
+        \item
+            $\bracket{\text{R}_{sd}}$: righthand sides
+        \item
+            $\bracket{\text{I}_{sd}}$: instruction sequences
+    \end{itemize}
+
+    Here the stack descriptor $sd$ is defined as a pair of natural numbers $(f, d)$, where $f$ is the frame number and $d$ is the displacement.
+The stack descriptor is used to keep track of the current frame and the displacement of the stack.
+The stack descriptor is used to access the stack in the target language.
+
+    The order of the stack descriptor is defined as follows:
+    \[\bracket{f, d} \leq \bracket{f', d'} \Leftrightarrow f < f' \lor (f = f' \land d \leq d')\]
+
+    We also define addition and subtraction of stack descriptors as follows:
+    \[\bracket{f, d} \pm n = \bracket{f, d \pm n} \text{ for } n \in \mathbb{N}\]
+
+    \subsection{Grammar}
+    The grammar of the target language is defined as follows:
+    \[\begin{aligned}
+        \bracket{\text{L}_{sd}} ::={}& sd^v \\
+                        &\mid \textsf{sbrs}  \\
+        \bracket{\text{S}_{sd}} ::={}& \bracket{\text{L}_{sd}} \\
+                        &\mid \textsf{lit} \bracket{\text{integer}} \\
+        \bracket{\text{R}_{sd}} ::={}& \bracket{\text{S}_{sd}} \\
+                        &\mid \bracket{ \text{unary operator} } \bracket{ \text{S}_{sd}}\\
+                        &\mid \bracket{\text{S}_{sd}} \bracket{\text{binary operator}} \bracket{ \text{S}_{sd} } \\
+        \bracket{\text{I}_{sd}} ::={}& \textsf{stop} \\
+                        &\mid \bracket{\text{L}_{sd+\delta}} \gets \bracket{\text{R}_{sd}}[\delta] \text{ ; } \bracket{\text{I}_{sd+\delta}} \\
+                        &\mid \textsf{if } \bracket{\text{S}_{sd}} \bracket{\text{relational operator}} \bracket{\text{S}_{sd}}[\delta] \textsf{ then } \bracket{\text{I}_{sd+\delta}} \textsf{ else } \bracket{\text{I}_{sd+\delta}} \\
+                        &\mid \textsf{adjustdisp} [\delta] \text{ ; } \bracket{\text{I}_{sd+\delta}} \\
+                        &\mid \textsf{popto } sd' \text{ ; } \bracket{\text{I}_{sd'}} \text{ when } sd' \leq sd \\
+    \end{aligned}\]
+
+    Here the intended meaning of $\delta$ is the displacement of the stack descriptor, which can be either positive or negative.
+To make a rigorous definition, we define $\delta$ as a natural number, and treat the positive and negative displacements as two different instructions, using addition and subtraction of stack descriptors respectively.
+
+    For negative displacements, we need to make sure that the the subtraction is valid, i.e.
+the displacement is less than or equal to the current stack descriptor.
+Here we need a rigorous definition of the subtraction of natural numbers.
+There are two different ways to define the subtraction: using an extra proof or using the dependent type fin.
+
+    \section{Customised Library}
+
+    \section{Compiler}
 
 \chapter{Evaluation}
+    \minitoc
+    Chapter~\chapref{chap: implementation} describes the implementation of the source language, the target language and the compiler in Agda.
+This chapter evaluates the implementation with a demonstrative example in Agda, and discusses the success criteria of the project.
+    \section{A demonstrative example in Agda}
+
+    \section{Success criteria}
 
 \chapter{Conclusion}
+    \minitoc
+    \section{Results}
+
+    \section{Overview}
+
+    \section{Lessons learned}
+
+    % \section{Future work}
 
@@
 
+\appendix
+
+\cleardoublepage
+\let\cleardoublepage\clearpage
+\pagestyle{empty}
+\pagenumbering{gobble}
+\includepdf[pages=-, fitpaper=true, pagecommand={}]{final_proposal.pdf}
+\AtBeginShipoutNext{\AtBeginShipoutDiscard}
 \end{document}

### 2025-05-01 fig/implementation/dependencies.tex
implementation and evaluation structure

\documentclass[border=0mm]{standalone}
\usepackage{fontspec}
\usepackage{unicode-math}
\usepackage{tikz}
\usetikzlibrary{arrows.meta, positioning}
\setmainfont{Linux Libertine O}
\setsansfont{Linux Biolinum O}

\begin{document}
	\begin{tikzpicture}[
		node distance=1cm and 1cm,
		every node/.style={draw, rounded corners=2pt, minimum width=2.5cm, minimum height=1cm, align=center},
		arrow/.style={-{Latex}, thick}
	]

		% Nodes
		\node (lib) {lib.agda};
		\node[below left=of lib] (source) {source.agda};
		\node[below right=of lib] (target) {target.agda};
		\node[below left=of target] (compiler) {compiler.agda};

		% Arrows
		\draw[arrow] (lib) -- (source);
		\draw[arrow] (lib) -- (target);
		\draw[arrow] (source) -- (compiler);
		\draw[arrow] (target) -- (compiler);
		\draw[arrow] (lib) -- (compiler);

	\end{tikzpicture}
\end{document}

### 2025-05-01 src/compiler.lagda.tex
implementation and evaluation structure

@@
 \documentclass{article}
+
+\usepackage[active,tightpage]{preview}
+\PreviewEnvironment{prev}
+\setlength\PreviewBorder{0pt}
+
 \usepackage{agda}
@@
 \newunicodechar{ℤ}{\ensuremath{\mathbb{Z}}}
+\newunicodechar{δ}{\ensuremath{\delta}}
+\newunicodechar{∈}{\ensuremath{\in}}
+\newunicodechar{⊢}{\ensuremath{\vdash}}
+\newunicodechar{⇒}{\ensuremath{\Rightarrow}}
+\newunicodechar{⟶}{\ensuremath{\longrightarrow}}
+\newunicodechar{ₛ}{\ensuremath{\textsubscript{s}}}
+\newunicodechar{ᵛ}{\ensuremath{\textsuperscript{v}}}
 
 \begin{document}
+\begin{prev}
 \begin{code}
@@
 get-var : ∀ {Γ A sd} → A ∈ Γ → ⟦ Γ ⟧ctx sd → ⟦ A ⟧ty sd
-get-var Z     (_ , a) = a
-get-var (S x) (γ , _) = get-var x γ
+get-var Zero     (_ , a) = a
+get-var (Suc x) (γ , _) = get-var x γ
 
--- get-num : ∀ {Γ} → (e : Γ ⊢ source.ℕ) → target.ℕ
--- get-num Zero = target.zero
--- get-num (Suc m) = target.suc (get-num m)
-
+-- Functorality
 fmap-⇒ : ∀ {P Q sd sd'} → (P ⇒ₛ Q) sd → sd ≤ₛ sd' → (P ⇒ₛ Q) sd'
@@
 fmap-Compl {sd} c (<-f f<f') = popto sd (<-f f<f') c
-fmap-Compl {⟨ _ , d ⟩} {⟨ _ , d' ⟩} c (≤-d d≤d') = adjustdisp_dec (≤→Fin (-→≤ {d'} {≤→Fin d≤d'}) ) (sub I {!   !} c)
+fmap-Compl {⟨ f , d ⟩} {⟨ f , d' ⟩} c (≤-d d≤d') = 
+    adjustdisp-dec ((d' - d) d≤d') (-→≤ d≤d') 
+        (sub I (-ₛ≡ 
+            {n = (d' - d) d≤d'} 
+                (n-[n-m]≡m d≤d')) c)
 
--- fmap-× : ∀ {P Q sd sd'} → (P ×ₛ Q) sd → sd ≤ₛ sd' → (P ×ₛ Q) sd'
+fmap-L : ∀ {sd sd'} → L sd → sd ≤ₛ sd' → L sd'
+fmap-L (l-var sdᵛ sdᵛ≤ₛsd) sd≤ₛsd' = l-var sdᵛ (≤ₛ-trans sdᵛ≤ₛsd sd≤ₛsd')
+fmap-L (l-sbrs) _ = l-sbrs
+
+fmap-S : ∀ {sd sd'} → S sd → sd ≤ₛ sd' → S sd'
+fmap-S (s-l l) sd≤ₛsd' = s-l (fmap-L l sd≤ₛsd')
+fmap-S (s-lit lit) _ = s-lit lit
 
 fmap-A : ∀ {A sd sd'} → ⟦ A ⟧ty sd → sd ≤ₛ sd' → ⟦ A ⟧ty sd'
-fmap-A {comm} c p i = {!   !}
-fmap-A {intexp} = {!   !}
-fmap-A {intacc} = {!   !}
-fmap-A {intvar} = {!   !}
+fmap-A {comm}  = fmap-⇒ {Compl} {Compl}
+fmap-A {intexp} = fmap-⇒ {Intcompl} {Compl}
+fmap-A {intacc} = fmap-⇒ {Compl} {Intcompl}
+fmap-A {intvar} ( e , a ) sd≤ₛsd' = ( fmap-A {intexp} e sd≤ₛsd' , fmap-A {intacc} a sd≤ₛsd' )
 fmap-A {A ⇒ B} = fmap-⇒ {⟦ A ⟧ty} {⟦ B ⟧ty}
@@
 fmap-Γ {Γ , A} (γ , a) p = fmap-Γ γ p , fmap-A {A} a p
+
+sd≤ₛsd'→sd≤ₛsd'-ₛ[d'-[suc-d]] : ∀ {sd sd'} → sd ≤ₛ sd' → (δ₁≤δ₂ : suc (SD.d sd) ≤ SD.d sd') → sd ≤ₛ ((sd' -ₛ ((SD.d sd' - (suc (SD.d sd))) δ₁≤δ₂)) (-→≤ δ₁≤δ₂))
+sd≤ₛsd'→sd≤ₛsd'-ₛ[d'-[suc-d]] {⟨ f , _ ⟩} {⟨ f' , _ ⟩} (<-f f<f') _ = <-f f<f'
+sd≤ₛsd'→sd≤ₛsd'-ₛ[d'-[suc-d]] {⟨ f , d ⟩} {⟨ f , d' ⟩} (≤-d d≤d') δ₁≤δ₂ = ≤-d (suc-d≤d'→d≤d'-[d'-[suc-d]] δ₁≤δ₂)
+
+assign : (sd : SD) → (sd' : SD) → (S ⇒ₛ Compl) sd → sd ≤ₛ sd' → R sd' → I sd'
+assign ⟨ f , d ⟩ ⟨ f' , d' ⟩ β sd≤ₛsd' r with (≤-compare {suc d} {d'})
+... | leq δ₁≤δ₂ = assign-dec ((d' - (suc d)) δ₁≤δ₂) 
+                    (-→≤ δ₁≤δ₂) (l-var ⟨ f , d ⟩ (sd≤ₛsd'→sd≤ₛsd'-ₛ[d'-[suc-d]] sd≤ₛsd' δ₁≤δ₂)) r 
+                    (β ((sd≤ₛsd'→sd≤ₛsd'-ₛ[d'-[suc-d]] sd≤ₛsd' δ₁≤δ₂)) 
+                        (s-l (l-var ⟨ f , d ⟩ ((sd≤ₛsd'→sd≤ₛsd'-ₛ[d'-[suc-d]] sd≤ₛsd' δ₁≤δ₂)))))
+
+... | geq δ₂≤δ₁ = assign-inc (((suc d) - d') δ₂≤δ₁) 
+                    (l-var ⟨ f , d ⟩ (≤ₛ-trans sd≤ₛsd' +ₛ→≤ₛ)) r 
+                    (β ((≤ₛ-trans sd≤ₛsd' +ₛ→≤ₛ)) 
+                        (s-l (l-var ⟨ f , d ⟩ ((≤ₛ-trans sd≤ₛsd' +ₛ→≤ₛ)))))
+
+use-temp : ∀ {sd sd'} → (S ⇒ₛ Compl) sd → sd ≤ₛ sd' → R sd' → I sd'
+use-temp β sd≤ₛsd' (r-s s) = β sd≤ₛsd' s
+use-temp {sd} {sd'} β sd≤ₛsd' (r-unary uop s) = 
+    assign sd sd' β sd≤ₛsd' (r-unary uop s)
+use-temp {sd} {sd'} β sd≤ₛsd' (r-binary s₁ bop s₂) = 
+    assign sd sd' β sd≤ₛsd' (r-binary s₁ bop s₂)
 
@@
 ⟦ Lit i ⟧ _ _ _ κ = κ ≤ₛ-refl (r-s (s-lit i))
-⟦ Neg e ⟧ sd γ p κ = {!   !} 
-⟦ Plus e e₁ ⟧ _ γ = {!   !} 
+⟦ Neg e ⟧ sd γ p κ = ⟦ e ⟧ sd γ p (use-temp λ p s → κ p (r-unary UNeg s))    
+⟦ Plus e₁ e₂ ⟧ sd γ p κ = ⟦ e₁ ⟧ sd γ p (use-temp (λ p' s₁ → ⟦ e₂ ⟧ sd γ (≤ₛ-trans p p') (use-temp (λ p'' s₂ →  κ (≤ₛ-trans p' p'') (r-binary (fmap-S s₁ p'') BPlus s₂)))))
 \end{code}
+\end{prev}
 \end{document}

### 2025-05-06 draft.tex
two methods compared

@@
 \usepackage{amssymb}
+\usepackage{mathabx}
 \usepackage{graphicx}
@@
 \definecolor{orange}{HTML}{CD6600}
+\definecolor{darkpink}{HTML}{EE1289}
 
@@
 \newcommand{\og}[1]{\textcolor{orange}{#1}}
+\newcommand{\dpink}[1]{\textcolor{darkpink}{#1}}
 
@@
 
-\newcommand{\bracket}[1]{\left\langle #1 \right\rangle}
+\newcommand{\bracket}[1]{\left\{ #1 \right\}}
+\newcommand{\ang}[1]{\left\langle #1 \right\rangle}
+
+\newcommand{\frontmatter}{
+  \pagenumbering{roman}
+}
+
+\newcommand{\mainmatter}{
+  \cleardoublepage
+  \pagenumbering{arabic}
+  \setcounter{page}{1}
+}
 
@@
 
+\frontmatter
 \tableofcontents
@@
 
+\mainmatter
 \chapter{Introduction}
@@
 
-        \[\includegraphics[width=\textwidth]{natural_plus.pdf}\]
+        \[\includegraphics[scale=1.2]{natural_plus.pdf}\]
 
@@
 
-        \[\includegraphics[width=\textwidth]{vector.pdf}\]
+        \[\includegraphics[scale=1.2]{vector.pdf}\]
 
@@
 Building upon this, Joachim Lambek showed that cartesian closed categories provide a natural semantic setting for the simply typed lambda calculus (STLC)~\cite{lambek}.
-The Curry-Howard-Lambek correspondence can be summarized as follows:
+The Curry-Howard-Lambek correspondence can be summarised as follows:
         \begin{table}[H]
@@
 
-        \subsection{Equality, congruence and substitution}
+        \subsection{Equality, congruence and substitution}\label{subsec: equality}
         Equality here refers to the propositional equality. In Agda it is defined as
-        \[\includegraphics[width=\textwidth]{equality.pdf}\]
+        \[\includegraphics[scale=1.2]{equality.pdf}\]
         With equality as a type, whenever we want to prove that two terms are equal, we need to provide a witness of the equality.
@@
 A simple proof that directly uses the definition of equality is as follows:
-        \[\includegraphics[width=\textwidth]{sym_trans.pdf}\]
+        \[\includegraphics[scale=1.2]{sym_trans.pdf}\]
         Here we are able to prove the symmetry and transitivity of equality by using the definition of equality. Those two properties are very useful for later proofs.
@@
         We can also have more complex proof with congruence and substitution, which can also be directly derived from the definition of equality as follows:
-        \[\includegraphics[width=\textwidth]{cong_subst.pdf}\]
+        \[\includegraphics[scale=1.2]{cong_subst.pdf}\]
         Congruence is a property of equality that states that if two terms are equal, then they can be substituted for each other in any context.
@@
         Here is a simple example of how congruence can be used in a proof:
-        \[\includegraphics[width=\textwidth]{cong_example.pdf}\]
+        \[\includegraphics[scale=1.2]{cong_example.pdf}\]
 
@@
 
+        \subsubsection{Builtin pragma} \label{subsubsec: builtin_pragma}
         With standard library, we can use actual numbers $1, 2, 3, \dots$ instead of calling the constructor $\gn{\mathsf{suc}}$ multiple times.
 This is a convenient feature for testing.
-Agda provides a way to link self-defined functions to the standard library with a \og{\textsf{BUILTIN}} programa.
+Agda provides a way to link self-defined functions to the standard library with a \og{\textsf{BUILTIN}} pragma.
 This allows me to use a convenient syntax for numbers, while still using the self-defined functions in the implementation.
-        \[\includegraphics[width=\textwidth]{natural_programma.pdf}\]
+        \[\includegraphics[scale=1.2]{natural_pragma.pdf}\]
         Note that in agda we can use unicode characters for terms, which makes the code more readable. For example, here we simply name the term \mb{1+1$\equiv$2}.
@@
 
-        [Considering adding examples of holes and case split, see https://plfa.github.io/Naturals/]
-
         In my implementation, I used holes to write the terms in the compiler.
@@
 Starting with a brief overview of the tools used, it then describes the directory structure and file dependencies.
-Then it discusses the
-    followed by the implementation of the source language, the target language, and finally the compiler.
+Then it discusses the specification of the source language, and the target language, which lead us to the problem of implementing a rigorous natural number subtraction and two different approaches.
+We will further see the difference between the two approaches and how they affect the implementation of the customised library and the implementation of the compiler.
 
@@
     \section{Source Language}
-    A Simply Typed Lambda Calculus (STLC) is a typed lambda calculus with only one type constructor ($\to$) that builds function types.
+    A simply typed lambda calculus (STLC) is a typed lambda calculus with only one type constructor ($\to$) that builds function types.
 
@@
             \item 
-                \textbf{comm}: the commands
-            \item 
-                \textbf{intexp}: the integer expressions
-            \item 
-                \textbf{intacc}: the integer acceptors
-            \item 
-                \textbf{intvar}: the integer variables
+                \textsf{comm}: the commands
+            \item 
+                \textsf{intexp}: the integer expressions
+            \item 
+                \textsf{intacc}: the integer acceptors
+            \item 
+                \textsf{intvar}: the integer variables
         \end{itemize}
         and the set $\Theta$ of types is defined as follows:
-        \[ \Theta := \textbf{comm} \mid \textbf{intexp} \mid \textbf{intacc} \mid \textbf{intvar} \mid \Theta \to \Theta \]
-
+        \[ \Theta := \textsf{comm} \mid \textsf{intexp} \mid \textsf{intacc} \mid \textsf{intvar} \mid \Theta \to \Theta \]
         which corresponds with the following agda implementation:
-        \[\includegraphics[width=\textwidth]{/source/types.pdf}\]
+        \[\includegraphics[scale=1.2]{/source/types.pdf}\]
+
+        \subsubsection{Subtypes}
+        We use the preorder $A \leq: B$ to denote the subtype relation $A$ is a subtype of $B$, as it has the following properties:
+        \begin{itemize}
+            \item 
+                reflexivity: $A \leq: A$;
+            \item 
+                transitivity: if $A \leq: B$ and $B \leq: C$, then $A \leq: C$.
+        \end{itemize}
+
+        The source language has the following subtype relations:
+        \[ \textsf{intvar} \leq: \textsf{intexp} \qquad \textsf{intvar} \leq: \textsf{intacc} \]
+        and for function types we have the contravariant subtyping:
+        \[ A' \leq: A \land B \leq: B' \Rightarrow A \to B \leq: A' \to B' \]
+
+        it is defined in Agda as follows:
+        \[\includegraphics[scale=1.2]{/source/subtype.pdf}\]
 
@@
 The context and the lookup judgement are defined as follows:
-        \[\includegraphics[width=\textwidth]{/source/contexts.pdf}\]
+        \[\includegraphics[scale=1.2]{/source/contexts.pdf}\]
 
@@
                 \[\includegraphics{source_terms_var.pdf}\]
+            \item For subtyping we have
+                \[\includegraphics{source_terms_subtype.pdf}\]
             \item For lambda abstraction we have
@@
 
-        The corresponding Agda implementation is as follows:
-        \[\includegraphics[width=\textwidth]{/source/terms.pdf}\]
+        The corresponding Agda implementation is as follows, note that the Agda implementation does not include the name of the terms, but the names are included in the latex implementation for clarity:
+        \[\includegraphics[scale=1.2]{/source/terms.pdf}\]
+
+        Here the definition of the integers is defined in the customised library, which is defined in [section ref].
+
+        \subsection{Operational Semantics}
+        The operational semantics of the source language is defined with renaming, substitution and reduction rules.
+However, since the compiler itself does not require the operational semantics, the implementation is included in the appendix [link to appendix].
+Operational semantics can be used to verify the correctness of the compiler in the future, but it is beyond the scope of this dissertation.
 
@@
         \item 
-            $\bracket{\text{L}_{sd}}$: lefthand sides
-        \item 
-            $\bracket{\text{S}_{sd}}$: Simple righthand sides
-        \item
-            $\bracket{\text{R}_{sd}}$: righthand sides
-        \item
-            $\bracket{\text{I}_{sd}}$: instruction sequences
-    \end{itemize}
-
-    Here the stack descriptor $sd$ is defined as a pair of natural numbers $(f, d)$, where $f$ is the frame number and $d$ is the displacement.
-The stack descriptor is used to keep track of the current frame and the displacement of the stack.
-The stack descriptor is used to access the stack in the target language.
-
-    The order of the stack descriptor is defined as follows:
-    \[\bracket{f, d} \leq \bracket{f', d'} \Leftrightarrow f < f' \lor (f = f' \land d \leq d')\]
-
-    We also define addition and subtraction of stack descriptors as follows:
-    \[\bracket{f, d} \pm n = \bracket{f, d \pm n} \text{ for } n \in \mathbb{N}\]
+            $\bracket{\textsf{L}_{sd}}$: lefthand sides
+        \item 
+            $\bracket{\textsf{S}_{sd}}$: simple righthand sides
+        \item
+            $\bracket{\textsf{R}_{sd}}$: righthand sides
+        \item
+            $\bracket{\textsf{I}_{sd}}$: instruction sequences
+    \end{itemize}
+
+    \subsection{Stack descriptor}
+    The stack descriptor $sd$ is defined as a pair of natural numbers $\ang{f, d}$, where $f$ is the frame number and $d$ is the displacement.
+
+    It is defined in Agda as follows:
+    \[\includegraphics[scale=1.2]{/target/stack_descriptor.pdf}\]
+    This requires the definition of natural numbers, which is defined in \secref{subsec: natural_numbers}.
+
+    For a stack descriptor $sd$, we can use \dpink{SD.f} $sd$ to access the frame number and \dpink{SD.d} $sd$ to access the displacement.
+
+    \subsubsection{Order}
+    The stack descriptor is ordered lexicographically with $\leq_s$ as follows:
+    \[\ang{f, d} \leq_s \ang{f', d'} \Leftrightarrow f < f' \lor (f = f' \land d \leq d')\]
+
+    It is defined in Agda as follows:
+    \[\includegraphics[scale=1.2]{/target/stack_descriptor_order.pdf}\]
+    This requires the definition of the order of natural numbers, which is defined in \secref{subsec: order}.
+
+    \subsubsection{Addition and subtraction of stack descriptors}
+    We define addition and subtraction of stack descriptors as follows:
+    \[\ang{f, d} \pm_s n = \ang{f, d \pm n} \text{ for } n \in \mathbb{N}\]
+    Addition of stack displacement is defined in Agda as follows:
+    \[\includegraphics[scale=1.2]{/target/stack_descriptor_add.pdf}\]
+    For subtraction, we need to make sure that the subtraction is valid, i.e.
+the subtracted displacement is less than or equal to the displacement of the current stack descriptor.
+Here we need a rigorous definition of the subtraction of natural numbers, which is defined in \secref{subsec: subtraction}
+
+    \subsubsection{Properties of order and addition}
+    We can use reflexivity and transitivity of the order $<$ and $\leq$ to prove that the order of stack descriptors $\leq_s$ is a preorder. The proof is as follows:
+    \begin{itemize}
+        \item 
+            Reflexivity: $sd \leq_s sd$ is trivially true since $f = f$ and $d \leq d$.
+        \item
+            Transitivity: if $\ang{f, d} \leq_s \ang{f', d'}$ and $\ang{f', d'} \leq_s \ang{f'', d''}$, we do the following case split:
+            \begin{itemize}
+                \item 
+                    if $f < f'$, $f' = f''$ and $d \leq d'$, then $f < f''$; 
+                \item 
+                    if $f < f'$ and $f' < f''$, then $f < f''$ by transitivity of $<$;
+                \item
+                    if $f = f'$, $d \leq d'$ and $f' < f''$, then $f < f''$;
+                \item
+                    if $f = f'$, $d \leq d'$, $f' = f''$ and $d' \leq d''$, then $f = f''$ and $d \leq d''$ by transitivity of $\leq$.
+\footnote{Note that the properties of $=$ is not required in as in the Agda definition of $\leq_s$, we directly define $f'$ to be $f$ instead of defining a equivalence relation, thus equivalence can be checked directly via type checking.}
+            \end{itemize}
+    \end{itemize}
+    The proof is defined in Agda as follows:
+    \[\includegraphics[scale=1.2]{/target/stack_descriptor_order_proof.pdf}\]
+
+    When a natural number is added to a stack descriptor, it is guaranteed that the new stack descriptor is not less than the old stack descriptor.
+This can be proved directly using the same properties of integer addition.
+The proof is defined in Agda as follows:
+    \[\includegraphics[scale=1.2]{/target/stack_descriptor_add_proof.pdf}\]
+
+    Proof above requires the proof of the properties of natural numbers, which is defined in [section ref].
 
     \subsection{Grammar}
-    The grammar of the target language is defined as follows:
+    The grammar of the target language is defined as follows, given the current stack descriptor $sd = \ang{f, d}$, and new stack descriptor $sd' = \ang{f', d'}$:
     \[\begin{aligned}
-        \bracket{\text{L}_{sd}} ::={}& sd^v \\
-                        &\mid \textsf{sbrs}  \\
-        \bracket{\text{S}_{sd}} ::={}& \bracket{\text{L}_{sd}} \\
-                        &\mid \textsf{lit} \bracket{\text{integer}} \\
-        \bracket{\text{R}_{sd}} ::={}& \bracket{\text{S}_{sd}} \\
-                        &\mid \bracket{ \text{unary operator} } \bracket{ \text{S}_{sd}}\\
-                        &\mid \bracket{\text{S}_{sd}} \bracket{\text{binary operator}} \bracket{ \text{S}_{sd} } \\
-        \bracket{\text{I}_{sd}} ::={}& \textsf{stop} \\
-                        &\mid \bracket{\text{L}_{sd+\delta}} \gets \bracket{\text{R}_{sd}}[\delta] \text{ ; } \bracket{\text{I}_{sd+\delta}} \\
-                        &\mid \textsf{if } \bracket{\text{S}_{sd}} \bracket{\text{relational operator}} \bracket{\text{S}_{sd}}[\delta] \textsf{ then } \bracket{\text{I}_{sd+\delta}} \textsf{ else } \bracket{\text{I}_{sd+\delta}} \\
-                        &\mid \textsf{adjustdisp} [\delta] \text{ ; } \bracket{\text{I}_{sd+\delta}} \\
-                        &\mid \textsf{popto } sd' \text{ ; } \bracket{\text{I}_{sd'}} \text{ when } sd' \leq sd \\
+        \bracket{\textsf{L}_{sd}} ::={}& sd^v \quad \text{when } sd^v \leq_s sd \\
+                        &\mid \texttt{sbrs}  \\
+        \bracket{\textsf{S}_{sd}} ::={}& \bracket{\textsf{L}_{sd}} \\
+                        &\mid \texttt{lit} \bracket{\text{integer}} \\
+        \bracket{\textsf{R}_{sd}} ::={}& \bracket{\textsf{S}_{sd}} \\
+                        &\mid \bracket{ \text{unary operator} } \bracket{ \textsf{S}_{sd}}\\
+                        &\mid \bracket{\textsf{S}_{sd}} \bracket{\textsf{binary operator}} \bracket{ \textsf{S}_{sd} } \\
+        \bracket{\textsf{I}_{sd}} ::={}& \texttt{stop} \\
+                        &\left.
+                        \begin{aligned}
+                        &\mid \bracket{\textsf{L}_{sd+\delta}} \gets \bracket{\textsf{R}_{sd}}[\delta] \text{ ; } \bracket{\textsf{I}_{sd+\delta}} \\
+                        &\mid \texttt{if } \bracket{\textsf{S}_{sd}} \bracket{\text{relational operator}} \bracket{\textsf{S}_{sd}}[\delta] \\
+                        & \hphantom{\mid {}} \texttt{ then } \bracket{\textsf{I}_{sd+\delta}} \texttt{ else } \bracket{\textsf{I}_{sd+\delta}} \\
+                        &\mid \texttt{adjustdisp} [\delta] \text{ ; } \bracket{\textsf{I}_{sd+\delta}} \\
+                        \end{aligned}
+                        \quad \right\} \text{if } d + \delta \geq 0  \\
+                        &{}\mid \texttt{popto } sd' \text{ ; } \bracket{\textsf{I}_{sd'}} \quad \text{when } sd' \leq_s sd \\
     \end{aligned}\]
 
-    Here the intended meaning of $\delta$ is the displacement of the stack descriptor, which can be either positive or negative.
+    \subsubsection{Operators}
+    The operators are defined as follows:
+    \[\begin{aligned}
+        \textsf{unary operator} &\in \{\texttt{UNeg}\} \\
+        \textsf{binary operator} &\in \{\texttt{BPlus}, \texttt{BMinus}, \texttt{BTimes}\} \\
+        \textsf{relational operator} &\in \{\texttt{RLeq}, \texttt{RLt}\}
+    \end{aligned}\]
+
+    The operators are defined in Agda as follows:
+    \[\includegraphics[scale=1.2]{/target/operators.pdf}\]
+
+    \subsubsection{Lefthand sides, simple righthand sides and righthand sides}
+    The lefthand sides, simple righthand sides and righthand sides are straightforward, and they are defined as follows in Agda:
+    \[\includegraphics[scale=1.2]{/target/leftrighthand_sides.pdf}\]
+
+    \subsubsection{Instruction sequences}
+    In the instruction sequences, $\delta$ as a displacement can be either positive or negative.
 To make a rigorous definition, we define $\delta$ as a natural number, and treat the positive and negative displacements as two different instructions, using addition and subtraction of stack descriptors respectively.
-
-    For negative displacements, we need to make sure that the the subtraction is valid, i.e.
-the displacement is less than or equal to the current stack descriptor.
-Here we need a rigorous definition of the subtraction of natural numbers.
-There are two different ways to define the subtraction: using an extra proof or using the dependent type fin.
+Since the definition of negative displacement involves the rigorous definition of subtraction, we will discuss the subtraction of natural numbers and correpsonding implementation in \secref{subsec: subtraction}.
+The definition (except for the negative displacement) in Agda is as follows:
+    \[\includegraphics[scale=1.2]{/target/instruction_inc.pdf}\]
 
     \section{Customised Library}
+    The customised library is a collection of types and functions centered around natural numbers, their operations and properties.
+
+    \subsection{Natural numbers, integers and addition} \label{subsec: natural_numbers}
+    The definition of natural numbers, integers and addition is standard, and it is defined as follows:
+    \[\includegraphics[scale=1.2]{/lib/natural.pdf}\]
+    The use of \og{\textsf{BUILTIN}} is specifed in \secref{subsubsec: builtin_pragma}.
+
+    \subsection{Equality, congruence and substitution}
+    The definition of equality, congruence and substitution is similar to the one in \secref{subsec: equality}.\footnote{The definition of equality and related properties in the custom library differ slightly by using an indexed $\mb{\mathsf{Set}}$, which provides a more general formulation.
+See Appendex [corresponding link].}
+
+    \subsection{Order of natural numbers} \label{subsec: order}
+    The order of natural numbers we defined include $\leq$ and $<$, which are defined standardly as follows:
+    \[\includegraphics[scale=1.2]{/lib/order.pdf}\]
+
+    \subsection{Properties of order and addition}
+    \subsubsection{Transitivity and reflexivity}
+    The transitivity and reflexivity of the order $<$ and $\leq$ are defined as follows:
+    \[\includegraphics[scale=1.2]{/lib/order_proof.pdf}\]
+
+    \subsubsection{Implication of order}
+    We know that $\forall m, n \in \bN$, if $m < n$, then we have $m + 1 \leq n$ and $m \leq n$. This is defined in Agda as follows:
+    \[\includegraphics[scale=1.2]{/lib/order_implication.pdf}\]
+
+    \subsubsection{Totality of order}
+    It is useful to case split the order of natural numbers, i.e.
+for any $m, n \in \bN$, we have $m \leq n$ or $n \leq m$.
+This is defined in Agda by defining either case as an instance of the \mb{\textsf{Total}} type, and then showing that for any $m, n \in \bN$, we can construct a \mb{\textsf{Total}} type by case-split and \og{\textsf{with}}-construct.
+The proof is as follows:
+    \[\includegraphics[scale=1.2]{/lib/order_totality.pdf}\]
+
+    \subsubsection{Other properties}
+    We can show that when a number $n$ is added to a natural number $m$, the result is greater than or equal to $m$. This is defined in Agda as follows:
+    \[\includegraphics[scale=1.2]{/lib/order_add.pdf}\]
+
+    \subsection{Subtraction} \label{subsec: subtraction}
+    In the standard library~\cite{agda_std}, the subtraction of natural numbers is defined as follows:\footnote{The definition in the standard library directly uses symbol $\mathsf{-}$, but here for clarity we use $\mathsf{\dotdiv}$ instead.}
+    \[\includegraphics[scale=1.2]{minus.pdf}\]
+    Mathematically we have $ n \dotdiv m = \max(0, n - m)$.
+This definition is valid and ensures that the result is a natural number.
+However, there are two problems with this definition for our implementation:
+    \begin{itemize}
+        \item 
+            The definition of subtraction is not rigorous.
+Input $n$ should be guaranteed not to be less than $m$, and at any point in the program if there is a subtraction where $n < m$, the program should fail to type check instead of making $0$ type check with it.
+        \item
+            We lose many numerical properties of natural numbers.
+For example, $n \dotdiv m + m = n$ or $n \dotdiv (n \dotdiv m) = m$ are not guaranteed to hold if we allow $n < m$.
+Those properties are very useful for the implementation of the compiler.
+    \end{itemize}
+    We need a more rigorous definition of subtraction that ensures the result is a natural number and preserves the numerical properties.
+The key is to have a proof that the first argument is greater than or equal to the second argument.
+There are two approaches to achieve this:
+
+    \subsubsection{Explicit proof-passing approach}
+    A straightforward approach is directly include a third argument in the subtraction function, which is a proof that the first argument is greater than or equal to the second argument.
+The definition in Agda is as follows:
+    \[\includegraphics[scale=1.2]{/lib/proof/minus.pdf}\]
+
+    The corresponding implementation for subtraction of stack descriptors carries along the proof as follows:
+    \[\includegraphics[scale=1.2]{/target/proof/stack_descriptor_minus.pdf}\]
+
+    In the implementation of instruction sequences, we need to carry along the proof as well. The implementation in Agda is as follows:
+    \[\includegraphics[scale=1.2]{/target/proof/instruction_dec.pdf}\]
+
+    \subsubsection{\textsf{Fin}-based approach}
+    Instead of include the proof directly, we can define the type of the subtrahend as a type that depends on the minuend, where the type encodes the proof.
+There is a standard library in Agda on finite sets, where a type $\mb{\mathsf{Fin}}$ is defined as a type that depends on a natural number $n$, where $\mb{\mathsf{Fin}}\ n$ can be seen as the set of natural numbers less than $n$.
+The definition is as follows:
+    \[\includegraphics[scale=1.2]{/lib/fin/fin.pdf}\]
+
+    An intuitive explanation of the definition of $\mb{\mathsf{Fin}}$ is as follows:
+    \begin{itemize}
+        \item Base case: when $n = 0$, there is no element less than $0$, so we do not have any constructor that gives us an element of type $\mb{\mathsf{Fin}}\ 0$. 
+        \item Inductive case: 
+        \begin{figure}[H]
+            \centering
+            \includegraphics[width=0.35\textwidth]{fin_inductive.pdf}
+            \caption{Inductive case of $\mb{\mathsf{Fin}}$}
+            \label{fig: fin_inductive}
+        \end{figure}
+    \end{itemize}
+
+    For subtraction, we only need to change the type of the subtrahend to $\mb{\mathsf{Fin}}\ (\gn{\mathsf{suc}}\ n)$ compared to the implementation of addition. The definition in Agda is as follows:
+    \[\includegraphics[scale=1.2]{/lib/fin/minus.pdf}\]
+
+    The corresponding implementation for subtraction of stack descriptors and instruction sequences only requires a change of the type of the subtrahend as follows:
+    \[\includegraphics[scale=1.2]{/target/fin/instruction_dec.pdf}\]
+
+    \subsubsection{Comparison of the two approaches}
+    The straightforward approach explicitly carries proofs in the type system, which is more transparent but verbose.
+The fin approach intially appears to be more elegant, as it encapsulates bounds check within a refined type.
+However, this elegance is superficial: constructing a term of type $\mb{\mathsf{Fin}}\ n$ still requires the same underlying proof of boundedness, shifting complexity to auxiliary conversions.
+
+    To prove a property with the fin approach, we need the following auxiliary function:
+    \[\includegraphics[scale=1.2]{/lib/fin/toFin.pdf}\]
+
+    Here is a comparison of the two approaches representing the property $\mathsf{suc}\ (n - m) \equiv \mathsf{suc}\ n - m$:
+    \begin{figure}[H]
+        \centering
+        \includegraphics[scale=1.2]{/lib/proof/minus-suc.pdf}
+        \includegraphics[scale=1.2]{/lib/fin/minus-suc.pdf}
+        \caption{Comparison of explicit vs. \textsf{Fin}-based approaches}
+        \label{fig: fin_comparison}
+    \end{figure}
+    It is clear that the explicit proof-passing approach is more straightforward and easier to understand.
+The fin-based approach requires additional auxiliary functions and conversions, which makes the code more complex and harder to read.
+
+    Although the project completed both approaches, the following implementation of the compiler uses the explicit proof-passing approach due to its simplicity and clarity.
+
+    \subsection{More properties of natural numbers}
 

### 2025-05-06 src/compiler.lagda.tex
two methods compared

@@
 \newunicodechar{δ}{\ensuremath{\delta}}
+\newunicodechar{λ}{\ensuremath{\lambda}}
 \newunicodechar{∈}{\ensuremath{\in}}
@@
 \newunicodechar{ᵛ}{\ensuremath{\textsuperscript{v}}}
+\newunicodechar{ʳ}{\ensuremath{\textsuperscript{r}}}
+\newunicodechar{₁}{\ensuremath{\textsubscript{1}}}
+\newunicodechar{₂}{\ensuremath{\textsubscript{2}}}
+\newunicodechar{⟨}{\ensuremath{\langle}}
+\newunicodechar{⟩}{\ensuremath{\rangle}}
+\newunicodechar{–}{\ensuremath{-}}
 
@@
 
-get-var : ∀ {Γ A sd} → A ∈ Γ → ⟦ Γ ⟧ctx sd → ⟦ A ⟧ty sd
-get-var Zero     (_ , a) = a
-get-var (Suc x) (γ , _) = get-var x γ
+⟦_⟧var : ∀ {Γ A sd} → A ∈ Γ → ⟦ Γ ⟧ctx sd → ⟦ A ⟧ty sd
+⟦ Zero ⟧var (_ , a) = a
+⟦ Suc B∈Γ ⟧var (γ , _) =  ⟦ B∈Γ ⟧var γ
+
+⟦_⟧sub : ∀ {A B sd} → A ≤: B → ⟦ A ⟧ty sd → ⟦ B ⟧ty sd
+⟦ ≤:-refl ⟧sub a = a
+⟦ ≤:-trans A≤:A' A'≤:A'' ⟧sub a = ⟦ A'≤:A'' ⟧sub (⟦ A≤:A' ⟧sub a)
+⟦ ≤:-fn A≤:A' B'≤:B ⟧sub a = λ sd≤ₛsd' a' → ⟦ B'≤:B ⟧sub (a sd≤ₛsd' (⟦ A≤:A' ⟧sub a'))
+⟦ var-≤:-exp ⟧sub (exp , acc) = exp
+⟦ var-≤:-acc ⟧sub (exp , acc) = acc
 
@@
     adjustdisp-dec ((d' - d) d≤d') (-→≤ d≤d') 
-        (sub I (-ₛ≡ 
-            {n = (d' - d) d≤d'} 
-                (n-[n-m]≡m d≤d')) c)
+        (I-sub {n = (d' - d) d≤d'} (n-[n-m]≡m d≤d') c)
+        -- (sub I (-ₛ≡ 
+        --     {n = (d' - d) d≤d'} 
+        --         (n-[n-m]≡m d≤d')) c)
 
@@
 
+new-intvar : ∀ sd → ⟦ intvar ⟧ty sd
+new-intvar sd = ( e , a )
+    where
+        sd' : SD
+        e : ⟦ intexp ⟧ty sd
+        e sd≤ₛsd' β = β ≤ₛ-refl (r-s (s-l (l-var sd sd≤ₛsd')))
+        a : ⟦ intacc ⟧ty sd
+        a sd≤ₛsd' κ (≤-d {d = d'} {d' = d''} d'≤d'') r = {!   !}
+        -- a {sd' = sd'} sd≤ₛsd' κ (≤-d {d = d'} {d' = d''} d'≤d'') r = assign-dec ((d'' - d') d'≤d'') (-→≤ d'≤d'') 
+        --     (l-var sd' (≤-d (m≡n,p≤n→p≤m (n-[n-m]≡m d'≤d'') ≤-refl))) r (I-sub {n = (d'' - d') d'≤d''} ((n-[n-m]≡m d'≤d'')) κ)
+
 assign : (sd : SD) → (sd' : SD) → (S ⇒ₛ Compl) sd → sd ≤ₛ sd' → R sd' → I sd'
@@
 ⟦_⟧ : ∀ {Γ A} → (e : Γ ⊢ A) → (sd : SD) → ⟦ Γ ⟧ctx sd → ⟦ A ⟧ty sd
-⟦ Var x ⟧ _ γ = get-var x γ
-⟦ Lambda f ⟧ sd γ {sd' = sd'} p a = ⟦ f ⟧ sd' (fmap-Γ γ p , a) 
+⟦ Var A∈Γ ⟧ sd γ = ⟦ A∈Γ ⟧var γ
+⟦ Sub Γ⊢A A≤:B ⟧ sd γ = ⟦ A≤:B ⟧sub (⟦ Γ⊢A ⟧ sd γ)
+⟦ Lambda f ⟧ sd γ {sd' = sd'} sd≤ₛsd' a = ⟦ f ⟧ sd' (fmap-Γ γ sd≤ₛsd' , a) 
 ⟦ App f e ⟧ sd γ = ⟦ f ⟧ sd γ (≤-d ≤-refl) (⟦ e ⟧ sd γ)
-⟦ Skip ⟧ _ _ _ γ = γ
-⟦ Seq c₁ c₂ ⟧ sd γ sd' p = ⟦ c₁ ⟧ sd γ sd' (⟦ c₂ ⟧ sd γ sd' p)
+⟦ Skip ⟧ sd γ sd≤ₛsd' κ = κ
+⟦ Seq c₁ c₂ ⟧ sd γ sd≤ₛsd' κ = ⟦ c₁ ⟧ sd γ sd≤ₛsd' (⟦ c₂ ⟧ sd γ sd≤ₛsd' κ)
+⟦ NewVar c ⟧ sd γ {sd' = sd'} sd≤ₛsd' κ = assign-inc 1 (l-var sd' (≤-d +→≤)) (r-s (s-lit (pos 0))) (⟦ c ⟧ (sd' +ₛ 1) (fmap-Γ (( fmap-Γ γ sd≤ₛsd' , new-intvar sd)) (+ₛ→≤ₛ {sd'} {1})) ≤ₛ-refl (adjustdisp-dec 1 +→≤ʳ (sub I (-ₛ≡ {d' = SD.d sd' + 1} {n = 1} (n+m-m≡n {m = 1})) κ)))
+⟦ Assign a e ⟧ sd γ sd≤ₛsd' κ = ⟦ e ⟧ sd γ sd≤ₛsd' (⟦ a ⟧ sd γ sd≤ₛsd' κ)
 ⟦ Lit i ⟧ _ _ _ κ = κ ≤ₛ-refl (r-s (s-lit i))
-⟦ Neg e ⟧ sd γ p κ = ⟦ e ⟧ sd γ p (use-temp λ p s → κ p (r-unary UNeg s))    
+⟦ Neg e ⟧ sd γ sd≤ₛsd' κ = ⟦ e ⟧ sd γ sd≤ₛsd' (use-temp λ sd≤ₛsd' s → κ sd≤ₛsd' (r-unary UNeg s))    
 ⟦ Plus e₁ e₂ ⟧ sd γ p κ = ⟦ e₁ ⟧ sd γ p (use-temp (λ p' s₁ → ⟦ e₂ ⟧ sd γ (≤ₛ-trans p p') (use-temp (λ p'' s₂ →  κ (≤ₛ-trans p' p'') (r-binary (fmap-S s₁ p'') BPlus s₂))))) 

### 2025-05-06 src/fin/compiler.lagda.tex
two methods compared

--- 2025-05-01 src/compiler.lagda.tex
@@
 fmap-Compl {⟨ f , d ⟩} {⟨ f , d' ⟩} c (≤-d d≤d') = 
-    adjustdisp-dec ((d' - d) d≤d') (-→≤ d≤d') 
-        (sub I (-ₛ≡ 
-            {n = (d' - d) d≤d'} 
-                (n-[n-m]≡m d≤d')) c)
+    adjustdisp-dec (≤→Fin (-→≤ {d'} {≤→Fin d≤d'}) ) (sub I ((-ₛ≡ {n = ≤→Fin (-→≤ {d'} {≤→Fin d≤d'})} (n-[n-m]≡m d≤d'))) c)
 
@@
 fmap-L (l-var sdᵛ sdᵛ≤ₛsd) sd≤ₛsd' = l-var sdᵛ (≤ₛ-trans sdᵛ≤ₛsd sd≤ₛsd') 
-fmap-L (l-sbrs) _ = l-sbrs
+fmap-L l-sbrs _ = l-sbrs
 
 fmap-S : ∀ {sd sd'} → S sd → sd ≤ₛ sd' → S sd'
-fmap-S (s-l l) sd≤ₛsd' = s-l (fmap-L l sd≤ₛsd')
+fmap-S (s-l l) p = s-l (fmap-L l p)
 fmap-S (s-lit lit) _ = s-lit lit
@@
 fmap-A {intacc} = fmap-⇒ {Compl} {Intcompl}
-fmap-A {intvar} ( e , a ) sd≤ₛsd' = ( fmap-A {intexp} e sd≤ₛsd' , fmap-A {intacc} a sd≤ₛsd' )
+fmap-A {intvar} ( e , a ) p = ( fmap-A {intexp} e p , fmap-A {intacc} a p )
 fmap-A {A ⇒ B} = fmap-⇒ {⟦ A ⟧ty} {⟦ B ⟧ty}
@@
 
-sd≤ₛsd'→sd≤ₛsd'-ₛ[d'-[suc-d]] : ∀ {sd sd'} → sd ≤ₛ sd' → (δ₁≤δ₂ : suc (SD.d sd) ≤ SD.d sd') → sd ≤ₛ ((sd' -ₛ ((SD.d sd' - (suc (SD.d sd))) δ₁≤δ₂)) (-→≤ δ₁≤δ₂))
-sd≤ₛsd'→sd≤ₛsd'-ₛ[d'-[suc-d]] {⟨ f , _ ⟩} {⟨ f' , _ ⟩} (<-f f<f') _ = <-f f<f'
+-- assign : (δ₁ : ℕ) → (δ₂ : ℕ) → (sd : SD) → (S ⇒ₛ Compl) sd → (sd' : SD) → sd ≤ₛ sd' → (δ₂ ≤ SD.d sd') → R sd' → I sd'
+-- assign δ₁ δ₂ sd β sd' sd≤ₛsd' δ₂≤d' r with (≤-compare {δ₁} {δ₂})
+-- ... | leq δ₁≤δ₂ = assign-dec (≤→Fin (≤-trans (-→≤ {δ₂} {≤→Fin δ₁≤δ₂}) δ₂≤d')) {!   !} r (β {!   !} {!   !})
+-- ... | geq δ₂≤δ₁ = assign-inc (δ₁ - (≤→Fin δ₂≤δ₁)) (l-var sd (≤ₛ-trans sd≤ₛsd' +ₛ→≤ₛ)) r (β (≤ₛ-trans sd≤ₛsd' +ₛ→≤ₛ) ((s-l (l-var sd (≤ₛ-trans sd≤ₛsd' +ₛ→≤ₛ)))))
+
+sd≤ₛsd'→sd≤ₛsd'-ₛ[d'-[suc-d]] : ∀ {sd sd'} → sd ≤ₛ sd' → (δ₁≤δ₂ : suc (SD.d sd) ≤ SD.d sd') → sd ≤ₛ (sd' -ₛ ≤→Fin (-→≤ {SD.d sd'} {≤→Fin δ₁≤δ₂})) 
+sd≤ₛsd'→sd≤ₛsd'-ₛ[d'-[suc-d]] {⟨ f , d ⟩} {⟨ f' , d' ⟩} (<-f f<f') _ = <-f f<f'
 sd≤ₛsd'→sd≤ₛsd'-ₛ[d'-[suc-d]] {⟨ f , d ⟩} {⟨ f , d' ⟩} (≤-d d≤d') δ₁≤δ₂ = ≤-d (suc-d≤d'→d≤d'-[d'-[suc-d]] δ₁≤δ₂)
@@
 assign ⟨ f , d ⟩ ⟨ f' , d' ⟩ β sd≤ₛsd' r with (≤-compare {suc d} {d'})
-... | leq δ₁≤δ₂ = assign-dec ((d' - (suc d)) δ₁≤δ₂) 
-                    (-→≤ δ₁≤δ₂) (l-var ⟨ f , d ⟩ (sd≤ₛsd'→sd≤ₛsd'-ₛ[d'-[suc-d]] sd≤ₛsd' δ₁≤δ₂)) r 
-                    (β ((sd≤ₛsd'→sd≤ₛsd'-ₛ[d'-[suc-d]] sd≤ₛsd' δ₁≤δ₂)) 
-                        (s-l (l-var ⟨ f , d ⟩ ((sd≤ₛsd'→sd≤ₛsd'-ₛ[d'-[suc-d]] sd≤ₛsd' δ₁≤δ₂)))))
+...
+| leq δ₁≤δ₂ = assign-dec (≤→Fin (-→≤ {d'} {≤→Fin δ₁≤δ₂})) (l-var ⟨ f , d ⟩ (sd≤ₛsd'→sd≤ₛsd'-ₛ[d'-[suc-d]] sd≤ₛsd' δ₁≤δ₂)) r (β (sd≤ₛsd'→sd≤ₛsd'-ₛ[d'-[suc-d]] sd≤ₛsd' δ₁≤δ₂) (s-l (l-var ⟨ f , d ⟩ (sd≤ₛsd'→sd≤ₛsd'-ₛ[d'-[suc-d]] sd≤ₛsd' δ₁≤δ₂))))
+... | geq δ₂≤δ₁ = assign-inc ((suc d) - (≤→Fin δ₂≤δ₁)) (l-var ⟨ f , d ⟩ (≤ₛ-trans sd≤ₛsd' +ₛ→≤ₛ)) r (β (≤ₛ-trans sd≤ₛsd' +ₛ→≤ₛ) (s-l (l-var ⟨ f , d ⟩ (≤ₛ-trans sd≤ₛsd' +ₛ→≤ₛ))))
 
-... | geq δ₂≤δ₁ = assign-inc (((suc d) - d') δ₂≤δ₁) 
-                    (l-var ⟨ f , d ⟩ (≤ₛ-trans sd≤ₛsd' +ₛ→≤ₛ)) r 
-                    (β ((≤ₛ-trans sd≤ₛsd' +ₛ→≤ₛ)) 
-                        (s-l (l-var ⟨ f , d ⟩ ((≤ₛ-trans sd≤ₛsd' +ₛ→≤ₛ)))))
+-- doubted
+
+-- use-temp : ∀ {sd sd'} → (β : (S ⇒ₛ Compl) sd) → sd ≤ₛ sd' → (r : R sd') → I sd'
+-- use-temp β sd≤ₛsd' (r-s s) = β sd≤ₛsd' s
+-- use-temp {sd} {sd'} β sd≤ₛsd' (r-unary uop s) = assign (SD.d sd + 1) (SD.d sd') sd β sd' sd≤ₛsd' ≤-refl (r-unary uop s)
+-- use-temp {sd} {sd'} β sd≤ₛsd' (r-binary s₁ bop s₂) = assign (SD.d sd + 1) (SD.d sd') sd β sd' sd≤ₛsd' ≤-refl (r-binary s₁ bop s₂)
 
@@
 use-temp β sd≤ₛsd' (r-s s) = β sd≤ₛsd' s
-use-temp {sd} {sd'} β sd≤ₛsd' (r-unary uop s) = 
-    assign sd sd' β sd≤ₛsd' (r-unary uop s)
-use-temp {sd} {sd'} β sd≤ₛsd' (r-binary s₁ bop s₂) = 
-    assign sd sd' β sd≤ₛsd' (r-binary s₁ bop s₂)
+use-temp {sd} {sd'} β sd≤ₛsd' (r-unary uop s) = assign sd sd' β sd≤ₛsd' (r-unary uop s)
+use-temp {sd} {sd'} β sd≤ₛsd' (r-binary s₁ bop s₂) = assign sd sd' β sd≤ₛsd' (r-binary s₁ bop s₂)
 

### 2025-05-11 draft.tex
Evaluation almost done

@@
 \usepackage{mathabx}
+\usepackage{stmaryrd}
+\usepackage{upgreek}
 \usepackage{graphicx}
@@
 \usepackage{atbegshi}
+\usepackage{multirow, makecell}
+\usepackage{enumitem}
+\usepackage{hhline}
 
@@
 \newcommand{\bN}{\mathbb{N}}
+\newcommand{\bZ}{\mathbb{Z}}
 
@@
 \newcommand{\ang}[1]{\left\langle #1 \right\rangle}
+\newcommand{\intp}[1]{\left\llbracket #1 \right\rrbracket}
 
@@
 
+\renewcommand{\arraystretch}{1.5}
+
 \begin{document}
@@
         \textbf{Examination} & Computer Science Tripos - Part II - 2025 \\
-        \textbf{Word-Count:} & [wordcount] \\
-        \textbf{Code line count:} & [linecount] \\
+        \textbf{Word-count:} & [wordcount] \footnotemark \\
+        \textbf{Code line count:} & [linecount] \footnotemark \\
         \textbf{Project Originator:} & Yulong Huang \\
@@
     \vspace{1em}
+    \begingroup
+        \footnotetext[1]{This word-count was computed by \texttt{texcount -1 -sum -merge -q dissertation.tex}.}
+        \footnotetext[2]{This code line count was computed by \texttt{find . -name "*.agda" | xargs wc -l}.}
+    \endgroup
 \end{titlepage}
@@
     \minitoc
-    Programming languages act as a bridge between human thought and machine execution.
+    Programming languages act as a bridge between human thoughts and machine execution.
 They exist in two complementary realms: the human realm, where intent is expressed through abstractions like variables and functions, and the machine realm, where low-level instructions are executed on hardware.
@@
     This project explores how the two process can be deeply connected by demonstrating how denotational semantics can directly generate a compiler.
-Simple Typed Lambda Calculus (STLC) is a well-studied programming language that serves as a foundation for many modern languages.
+Simply typed lambda calculus (STLC)~\cite{stlc} is a well-studied programming language that serves as a foundation for many modern languages.
 It has denotational semantics in cartesian closed categories, shown by Lambek~\cite{lambek}.
@@
 
-    I implement this compiler for STLC with stores in a dependently typed programming language, Agda~\cite{Agda}.
+    In this dissertation, I implement this compiler for STLC with stores in a dependently typed programming language, Agda~\cite{Agda}.
 The compiler is a functor (structure-preserving map) from the source language's semantic domain to the target language's instruction set.
@@
 
-        % \motivation{Trend of verified compilers}
-        % The rise of verified compilers including CompCert~\cite{CompCert}, CakeML~\cite{CakeML} reflects a broader trend toward trustworthy systems, where correctness proofs replace testing for critical guarantees.
-Like Lean 4~\cite{Lean4}, we leverage dependent types to internalise the verification of correctness of terms.
-
     \section{Language choice: Agda's advantages}
@@
 
-        Agda also provides an interactive environment for writing and verifying programs, which will be further discussed in \secref{subsec: holes}.
+        Agda also provides an interactive environment for writing and verifying programs, which will be further discussed in~\secref{subsec: holes}.
 
     \section{Contributions}
-        Addressed the three motivations presented in \secref{sec: motivation} and contributed to the following:
+        Addressed the two motivations presented in~\secref{sec: motivation} and contributed to the following:
         \begin{quote}
@@
             \savedmotivationII
-            I formalised the terms in the source language and target language in Agda, and proved that the compiler is a functor from the source language to the target language.
-
-            % \savedmotivationIII
-            % This implementation follows the trend of verified compilers, and provides a practical example of how to use functor categories to generate intermediate code.
+            I formalised the terms in the source language and target language in Agda. I also refined some type definitions in the denotational semantics of the source language.
+
         \end{quote}
@@
 For example, $A, B, \dots$ are used to denote objects, sets, or types, and arrows are used to denote morphisms or functions (e.g.\ $A \to B$).
-There is a deeper connection between category theory and type theory, which will
-        be discussed in \secref{subsec: curry-howard-lambek}.
+There is a deeper connection between category theory and type theory, which will be discussed in~\secref{subsec: curry-howard-lambek}.
 
@@
         \begin{definition}[Category]
-            A \emph{category} $\mathcal{C}$ is specified by the following:
+            A \emph{category} $\mathcal{C}$ is specified by
             \begin{itemize}
@@
                     \textbf{(Unit Laws)}
-                    for all $X, Y \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$, we have:
+                    For all $X, Y \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$, we have
                     \begin{equation} \label{law: unit}
@@
                     \textbf{(Associativity Law)}
-                    for all $X, Y, Z, W \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$, $g \in \mathcal{C}{(Y,Z)}$, $h \in \mathcal{C}{(Z,W)}$, we have:
+                    For all $X, Y, Z, W \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$, $g \in \mathcal{C}{(Y,Z)}$, $h \in \mathcal{C}{(Z,W)}$, we have
                     \begin{equation} \label{law: associativity}
@@
         \begin{example}[$\mathcal{Set}$]
-            An example of category is the category of sets, denoted as $\mathcal{Set}$, specifed by:
-            \begin{itemize}
-                \item 
-                    the objects of $\mathcal{Set}$ are a fixed universe of sets;
-                \item
-                    for each $X, Y \in \textbf{obj}(\mathcal{Set})$, the morphisms from $X \to Y$ in $\mathcal{Set}$ are the functions $X \to Y$;
-                \item
-                    the identity morphism on $X$ in $\mathcal{Set}$ is the identity function on $X$;
-                \item
-                    the composition of morphisms in $\mathcal{Set}$ is defined as the composition of functions.
+            An example of category is the category of sets, denoted as $\mathcal{Set}$, specifed by the following:
+            \begin{itemize}
+                \item 
+                    The objects of $\mathcal{Set}$ are a fixed universe of sets;
+                \item
+                    For each $X, Y \in \textbf{obj}(\mathcal{Set})$, the morphisms from $X \to Y$ in $\mathcal{Set}$ are the functions $X \to Y$;
+                \item
+                    The identity morphism on $X$ in $\mathcal{Set}$ is the identity function on $X$;
+                \item
+                    The composition of morphisms in $\mathcal{Set}$ is defined as the composition of functions.
             \end{itemize}
@@
 
-        \begin{example}[$\mathcal{Poset}$]
-            Another example of category is the category of posets, denoted as $\mathcal{Poset}$, specified by:
-            \begin{itemize}
-                \item 
-                    the objects of $\mathcal{Poset}$ are a fixed universe of posets, which is a set $P$ with a binary relation $\subseteq$ that is 
-                    \begin{itemize}
-                        \item reflexive: $\forall x \in P, x \subseteq x$;
-                        \item transitive: $\forall x, y, z \in P, x \subseteq y \land y \subseteq z \implies x \subseteq z$;
-                        \item antisymmetric: $\forall x, y \in P, x \subseteq y \land y \subseteq x \implies x = y$.
-                    \end{itemize}
-                \item
-                    for each $X, Y \in \textbf{obj}(\mathcal{Poset})$, the morphisms from $X$ to $Y$ in $\mathcal{Poset}$ are the monotone (order-preserving) functions from $X$ to $Y$;
-                \item
-                    the identity morphism on $X$ in $\mathcal{Poset}$ is the identity function on $X$;
-                \item
-                    the composition of morphisms in $\mathcal{Poset}$ is defined as the composition of functions.
-            \end{itemize}
-            Associativity law and unit laws are satisfied in $\mathcal{Poset}$, since the set of monotone functions contains identity functions and is closed under composition.
-
-            $\mathcal{Poset}$ is used later for stack descriptors in the denotational semantics of the source language.
+        \begin{definition}[Preorder]
+            A \emph{preorder} $\underline{P} = (P, \sqsubseteq)$ is a set $P$ with a binary relation $\sqsubseteq$ that is
+            \begin{itemize}
+                \item reflexive: $\forall x \in P, x \sqsubseteq x$;
+                \item transitive: $\forall x, y, z \in P, x \sqsubseteq y \land y \sqsubseteq z \implies x \sqsubseteq z$.
+            \end{itemize}
+        \end{definition}
+
+        \begin{example}[Category determined by preorder] \label{ex: category_preorder}
+            Another example of category is a category $\mathcal{C}_{\underline{P}}$ determined by any preorder $\underline{P}$, which is specified by the following:
+            \begin{itemize}
+                \item 
+                    The objects of $\mathcal{C}_{\underline{P}}$ are the elements of $P$;
+                \item
+                    $\mathcal{C}_{\underline{P}}(x,y) = \begin{cases}
+                        \{(x,y)\} & \text{if $x \sqsubseteq y$} \\
+                        \emptyset & \text{otherwise}
+                    \end{cases}$
+                \item
+                    The identity morphism on $X$ in $\mathcal{C}_{\underline{P}}$ is the identity function on $X$;
+                \item
+                    The composition of morphisms in $\mathcal{C}_{\underline{P}}$ is defined as the composition of functions.
+            \end{itemize}
+            Associativity law and unit laws are satisfied in $\mathcal{C}_{\underline{P}}$.
+
+            $\mathcal{C}_{\underline{P}}$ is used later for stack descriptors in the denotational semantics of the source language.
         \end{example}
@@
             \begin{definition}[Opposite category]
-                Given a category $\mathcal{C}$, its \emph{opposite category} $\mathcal{C}^{\textbf{op}}$ is specified by:
-                \begin{itemize}
-                    \item 
-                        the objects of $\mathcal{C}^{\textbf{op}}$ are the same as those of $\mathcal{C}$;
-                    \item 
-                        for each $X, Y \in \textbf{obj}(\mathcal{C})$, the morphisms from $X$ to $Y$ in $\mathcal{C}^{\textbf{op}}$ are the morphisms from $Y$ to $X$ in $\mathcal{C}$;
-                    \item 
-                        the identity morphism on $X$ in $\mathcal{C}^{\textbf{op}}$ is the identity morphism on $X$ in $\mathcal{C}$;
-                    \item 
-                        the composition of morphisms in $\mathcal{C}^{\textbf{op}}$ is defined as the composition of morphisms in $\mathcal{C}$.
+                Given a category $\mathcal{C}$, its \emph{opposite category} $\mathcal{C}^{\textbf{op}}$ is specified by the following:
+                \begin{itemize}
+                    \item 
+                        The objects of $\mathcal{C}^{\textbf{op}}$ are the same as those of $\mathcal{C}$;
+                    \item 
+                        For each $X, Y \in \textbf{obj}(\mathcal{C})$, the morphisms from $X$ to $Y$ in $\mathcal{C}^{\textbf{op}}$ are the morphisms from $Y$ to $X$ in $\mathcal{C}$;
+                    \item 
+                        The identity morphism on $X$ in $\mathcal{C}^{\textbf{op}}$ is the identity morphism on $X$ in $\mathcal{C}$;
+                    \item 
+                        The composition of morphisms in $\mathcal{C}^{\textbf{op}}$ is defined as the composition of morphisms in $\mathcal{C}$.
                 \end{itemize}
@@
 
-            As examples of commutative diagrams, Figure \ref{fig: associativity_law} and Figure \ref{fig: unit_laws} are commutative diagrams for the unit laws and associativity law respectively.
+            As examples of commutative diagrams, Figure~\ref{fig: associativity_law} and Figure~\ref{fig: unit_laws} are commutative diagrams for the unit laws and associativity law respectively.
 
@@
             \end{definition}
-            Terminal objects are unique up to isomorphism. In other words, we have
-            \begin{itemize}
-                \item 
-                    if $T$ and $T'$ are both terminal objects in $\mathcal{C}$, then there exists a unique isomorphism $f : T \to T'$.
-                \item
-                    if $T$ is a terminal object in $\mathcal{C}$ and $T \cong T'$, then $T'$ is also a terminal object in $\mathcal{C}$.
+            Terminal objects are unique up to isomorphism. In other words, we have the following properties:
+            \begin{itemize}
+                \item 
+                    If $T$ and $T'$ are both terminal objects in $\mathcal{C}$, then there exists a unique isomorphism $f : T \to T'$.
+                \item
+                    If $T$ is a terminal object in $\mathcal{C}$ and $T \cong T'$, then $T'$ is also a terminal object in $\mathcal{C}$.
             \end{itemize}
@@
                 \end{equation}
-                The unique morphism $u$ is written as 
-                \[ \bracket{ f, g } : Z \to X \times Y \]
-                where $f = \pi_1 \circ u$ and $g = \pi_2 \circ u$.
+                The unique morphism $u$ is written as $\ang{ f, g } : Z \to X \times Y$ where $f = \pi_1 \circ u$ and $g = \pi_2 \circ u$.
             \end{definition}
@@
         \begin{definition}[Functor]
-            Given two categories $\mathcal{C}$ and $\mathcal{D}$, a \emph{functor} $F: \mathcal{C} \to \mathcal{D}$ is specified by:
+            Given two categories $\mathcal{C}$ and $\mathcal{D}$, a \emph{functor} $F: \mathcal{C} \to \mathcal{D}$ is specified by
             \begin{itemize}
@@
                 \item 
-                    for all $X, Y \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$, we have: $ F(\textbf{id}_X) = \textbf{id}_{F(X)}$
-                \item
-                    for all $X, Y, Z \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$, $g \in \mathcal{C}{(Y,Z)}$, we have: $F(g \circ f) = F(g) \circ F(f)$
+                    For all $X, Y \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$, we have: $ F(\textbf{id}_X) = \textbf{id}_{F(X)}$
+                \item
+                    For all $X, Y, Z \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$, $g \in \mathcal{C}{(Y,Z)}$, we have: $F(g \circ f) = F(g) \circ F(f)$
             \end{itemize}
@@
                 \item 
-                    the objects of $\mathcal{D}^{\mathcal{C}}$ are all functors $\mathcal{C} \to \mathcal{D}$;
-                \item 
-                    given two functors $F,G: \mathcal{C} \to \mathcal{D}$, the morphisms from $F$ to $G$ in $\mathcal{D}^{\mathcal{C}}$ are all natural transformations $\theta : F \to G$;
-                \item
-                    composition and identity morphisms in $\mathcal{D}^{\mathcal{C}}$ are defined as follows:
-                    \begin{itemize}
-                        \item 
-                            the identity morphism $\textbf{id}_F$ on $F$ is defined as $\theta_X = \textbf{id}_{F(X)}$ for all $X \in \textbf{obj}(\mathcal{C})$;
-                        \item
-                            the composition of two natural transformations $\theta : F \to G$ and $\phi : G \to H$ is defined as $(\phi \circ \theta)_X = \phi_X \circ \theta_X$ for all $X \in \textbf{obj}(\mathcal{C})$.
+                    The objects of $\mathcal{D}^{\mathcal{C}}$ are all functors $\mathcal{C} \to \mathcal{D}$;
+                \item 
+                    Given two functors $F,G: \mathcal{C} \to \mathcal{D}$, the morphisms from $F$ to $G$ in $\mathcal{D}^{\mathcal{C}}$ are all natural transformations $\theta : F \to G$;
+                \item
+                    Composition and identity morphisms in $\mathcal{D}^{\mathcal{C}}$ are defined as follows:
+                    \begin{itemize}
+                        \item 
+                            The identity morphism $\textbf{id}_F$ on $F$ is defined as $\theta_X = \textbf{id}_{F(X)}$ for all $X \in \textbf{obj}(\mathcal{C})$;
+                        \item
+                            The composition of two natural transformations $\theta : F \to G$ and $\phi : G \to H$ is defined as $(\phi \circ \theta)_X = \phi_X \circ \theta_X$ for all $X \in \textbf{obj}(\mathcal{C})$.
                     \end{itemize}
@@
         \begin{definition}[Presheaf]
-            Given a category $\mathcal{C}$, a \emph{presheaf} on $\mathcal{C}$ is a functor $F: \mathcal{C}^{\textbf{op}} \to \textbf{Set}$.
+            Given a category $\mathcal{C}$, a \emph{presheaf} on $\mathcal{C}$ is a functor $F: \mathcal{C}^{\textbf{op}} \to \mathcal{Set}$.
             A presheaf is a contravariant functor, which means that it reverses the direction of morphisms.
@@
                 \item 
-                    for each $X \in \textbf{obj}(\mathcal{C})$, $F(X)$ is a set;
-                \item
-                    for each $X, Y \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$, $F(f)$ is a function $F(Y) \to F(X)$.
+                    For each $X \in \textbf{obj}(\mathcal{C})$, $F(X)$ is a set;
+                \item
+                    For each $X, Y \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$, $F(f)$ is a function $F(Y) \to F(X)$.
             \end{itemize}
@@
         \begin{definition}[Presheaf category]
-            Given a category $\mathcal{C}$, the \emph{presheaf category} $\hat{\mathcal{C}}$ is the is the functor category $\mathcal{Set}^{\mathcal{C}^{\textbf{op}}}$, which explicitly contains the following:
-            \begin{itemize}
-                \item 
-                    the objects of $\hat{\mathcal{C}}$ are all presheaves on $\mathcal{C}$;
-                \item
-                    given two presheaves $F,G: \mathcal{C}^{\textbf{op}} \to \mathcal{Set}$, the morphisms from $F$ to $G$ in $\hat{\mathcal{C}}$ are all natural transformations $\theta : F \to G$.
+            Given a category $\mathcal{C}$, the \emph{presheaf category} $\hat{\mathcal{C}}$ is the functor category $\mathcal{Set}^{\mathcal{C}^{\textbf{op}}}$, which explicitly contains the following:
+            \begin{itemize}
+                \item 
+                    The objects of $\hat{\mathcal{C}}$ are all presheaves on $\mathcal{C}$;
+                \item
+                    Given two presheaves $F,G: \mathcal{C}^{\textbf{op}} \to \mathcal{Set}$, the morphisms from $F$ to $G$ in $\hat{\mathcal{C}}$ are all natural transformations $\theta : F \to G$.
             \end{itemize}
@@
                 \item 
-                    for each $X \in \textbf{obj}(\mathcal{C})$, $\yo(X)$ is the functor $\mathcal{C}^{\textbf{op}} \to \mathcal{Set}$ defined as:
+                    For each $X \in \textbf{obj}(\mathcal{C})$, $\yo(X)$ is the functor $\mathcal{C}^{\textbf{op}} \to \mathcal{Set}$ defined as:
                     \begin{equation} \label{eq: yoneda_element}
@@
                     \end{equation}
-                    for all $Y \in \textbf{obj}(\mathcal{C})$;
-                \item
-                    for each $X, Y \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$, $\yo(f)$ is the morphism $\yo(X) \to \yo(Y)$ defined a natural transformation whose component at any given $Z \in \mathcal{C}^{\textbf{op}}$ is given by:
+                    For all $Y \in \textbf{obj}(\mathcal{C})$;
+                \item
+                    For each $X, Y \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$, $\yo(f)$ is the morphism $\yo(X) \to \yo(Y)$ defined a natural transformation whose component at any given $Z \in \mathcal{C}^{\textbf{op}}$ is given by:
                     \begin{equation} \label{eq: yoneda_morphism}
@@
 
-        \subsection{Cartesian closed structure in presheaf categories}
+        \subsection{Cartesian closed structure in presheaf categories} \label{sec: ccc_presheaf}
         \begin{prf}[Cartesian closed structure in presheaf categories]
@@
 
-        Here we define a datatype $\mb{\mathsf{Vec}}$ for vectors.
-The type of vectors is dependent on the length of the vector.
-With dependent types, we can encode properties directly into types and ensure that they are satisfied at compile time.
+        Here we define a datatype $\mb{\mathsf{Vec}}$ for vectors. The type of vectors is dependent on the length of the vector. With dependent types, we can encode properties directly into types.
 
@@
                 \textbf{Logic} & \textbf{Type theory} & \textbf{Category theory} \\
-                \hline
+                \hhline{|=|=|=|}
                 Proposition & Type & Object \\
+                \hline
                 Proof & Term & Morphism \\
+                \hline
                 Falsity & Empty type & Initial object \\
+                \hline
                 Truth & Unit type & Terminal object \\
+                \hline
                 Implication & Function type & Exponential \\
+                \hline
                 Conjunction & Product type & Product \\
+                \hline
                 Disjunction & Sum type & Coproduct \\
@@
 
-        \subsection{Standard library}
+        \subsection{Standard library} \label{subsec: stdlib}
         The Agda standard library~\cite{agda_std} is a collection of modules that provide a wide range of useful functions and types.
 It includes modules for basic data types, such as natural numbers, lists, and vectors.
-In my implementation, however, I defined most of the basic data types and functions from scratch for the following two reasons:
-        \begin{itemize}
-            \item
-                I wanted to have a better understanding of the basic data types and functions, so I decided to implement them from scratch.
-            \item
-                I need a particular representation of minus operation that ensures the input is always valid. This is further explained in [to add]
+In my implementation, however, I defined the basic data types and functions from scratch for the following reasons:
+        \begin{itemize}
+            \item
+                \textbf{Specialised Requirements}: The standard library's definitions (e.g.
+subtraction as monus, `'$\dotdiv$') do not align with my project's need for a rigorously defined subtraction operation.
+My implementation, discussed in Section~\ref{subsec: subtraction}, ensures correctness and preserves the properties of natural numbers.
+            \item
+                \textbf{Verification Clarity}: By defining the basic data types and functions from scratch, I can tailor properties (e.g.
+the property `$n-[n-m] \equiv m$') to my specific requirements, and avoid unnecessary complexity (e.g.
+`$\leq$' being also defined as a boolean predicate in the standard library).
+            \item
+                \textbf{Minimal Dependencies}: Avoiding the standard library reduces external assumptions, making the project self-contained. 
         \end{itemize}
@@
 Agda provides a way to link self-defined functions to the standard library with a \og{\textsf{BUILTIN}} pragma.
-This allows me to use a convenient syntax for numbers, while still using the self-defined functions in the implementation.
+This allows me to use a convenient syntax for numbers, while still using the self-defined functions in the implementation without any import.
         \[\includegraphics[scale=1.2]{natural_pragma.pdf}\]
@@
     \end{itemize}
-    The success criteria of the project is that the compiler can compile a term in the source language to a term in the target language, and the output term is well-typed in the target language.
+    The success criteria of the project is that the file compiler.agda type checks, as the type checking process will reduce the source term to the target term.
 
@@
             .3 compiler.agda.
+            .3 test.agda.
             .2 proof.
@@
             .3 compiler.agda.
+            .3 test.agda.
         }
@@
             \centering
-            \begin{tabular}{l l l}
+            \begin{tabular}{|l|l|l|}
                 \hline
                 \textbf{File} & \textbf{Description}\\
-                \hline
-                lib.agda & Shared utilities (e.g. natural numbers and operations, equality, etc.) \\
-                source.agda & Source language syntax \\
-                target.agda & Target language (stack machine) instructions \\
-                compiler.agda & Compiler functor \\
+                \hhline{|=|=|}
+                lib.agda & shared utilities (e.g. natural numbers and operations, equality, etc.) \\
+                \hline
+                source.agda & source language syntax \\
+                \hline
+                target.agda & target language (stack machine) instructions \\
+                \hline
+                compiler.agda & compiler derived from denotational semantics \\
+                \hline
+                test.agda & test cases for the compiler \\
                 \hline
@@
     \section{Source Language}
-    A simply typed lambda calculus (STLC) is a typed lambda calculus with only one type constructor ($\to$) that builds function types.
+    A simply typed lambda calculus (STLC) is a typed lambda calculus with only one type constructor ($\Rightarrow$) \footnote{Normally we use $\to$ to denote the function type, but here we use $\Rightarrow$ to be consistent with the notation in Agda, as $\to$ is a primitive in Agda.} that builds function types.
 
@@
         and the set $\Theta$ of types is defined as follows: 
-        \[ \Theta := \textsf{comm} \mid \textsf{intexp} \mid \textsf{intacc} \mid \textsf{intvar} \mid \Theta \to \Theta \]
+        \[ \Theta := \textsf{comm} \mid \textsf{intexp} \mid \textsf{intacc} \mid \textsf{intvar} \mid \Theta \Rightarrow \Theta \] 
         which corresponds with the following agda implementation:
@@
 
-        \subsection{Terms and the typing judgement}
+        \subsection{Terms and the typing judgement} \label{subsec: terms}
         The terms and the typing judgement are described in the following rules:
@@
             \item For any variable we have 
-                \[\includegraphics{source_terms_var.pdf}\]
+                \begin{figure}[H]
+                    \centering
+                    \includegraphics{source_terms_var.pdf}
+                    \caption{Variable typing rule}
+                    \label{fig: rule_var}
+                \end{figure}
             \item For subtyping we have
-                \[\includegraphics{source_terms_subtype.pdf}\]
+                \begin{figure}[H]
+                    \centering
+                    \includegraphics{source_terms_subtype.pdf}
+                    \caption{Subtyping rule}
+                    \label{fig: rule_subtype}
+                \end{figure}
             \item For lambda abstraction we have
-                \[\includegraphics{source_terms_lambda.pdf}\]
+                \begin{figure}[H]
+                    \centering
+                    \includegraphics{source_terms_lambda.pdf}
+                    \caption{Lambda abstraction typing rules}
+                    \label{fig: rule_lambda}
+                \end{figure}
             \item For command we have
-                \[\includegraphics{source_terms_comm.pdf}\]
+                \begin{figure}[H]
+                    \centering
+                    \includegraphics{source_terms_comm.pdf}
+                    \caption{Command typing rules}
+                    \label{fig: rule_comm}
+                \end{figure}
             \item For integer expression we have
-                \[\includegraphics{source_terms_intexp.pdf}\]
+                \begin{figure}[H]
+                    \centering
+                    \includegraphics{source_terms_intexp.pdf}
+                    \caption{Integer expression typing rules}
+                    \label{fig: rule_intexp}
+                \end{figure}
         \end{itemize}
@@
 
-        Here the definition of the integers is defined in the customised library, which is defined in [section ref].
+        Here the definition of the integers is defined in the customised library, which is defined in~\secref{subsec: natural_numbers}.
 
@@
         The operational semantics of the source language is defined with renaming, substitution and reduction rules.
-However, since the compiler itself does not require the operational semantics, the implementation is included in the appendix [link to appendix].
+However, since the compiler itself does not require the operational semantics, the implementation is included in the appendix~\ref{app: operational_semantics}.
 Operational semantics can be used to verify the correctness of the compiler in the future, but it is beyond the scope of this dissertation.
@@
     \[\includegraphics[scale=1.2]{/target/stack_descriptor.pdf}\]
-    This requires the definition of natural numbers, which is defined in \secref{subsec: natural_numbers}.
+    This requires the definition of natural numbers, which is defined in~\secref{subsec: natural_numbers}.
 
@@
     \[\includegraphics[scale=1.2]{/target/stack_descriptor_order.pdf}\]
-    This requires the definition of the order of natural numbers, which is defined in \secref{subsec: order}.
+    This requires the definition of the order of natural numbers, which is defined in~\secref{subsec: order}.
 
@@
 the subtracted displacement is less than or equal to the displacement of the current stack descriptor.
-Here we need a rigorous definition of the subtraction of natural numbers, which is defined in \secref{subsec: subtraction}
+Here we need a rigorous definition of the subtraction of natural numbers, which is defined in~\secref{subsec: subtraction}
 
@@
 To make a rigorous definition, we define $\delta$ as a natural number, and treat the positive and negative displacements as two different instructions, using addition and subtraction of stack descriptors respectively.
-Since the definition of negative displacement involves the rigorous definition of subtraction, we will discuss the subtraction of natural numbers and correpsonding implementation in \secref{subsec: subtraction}.
+Since the definition of negative displacement involves the rigorous definition of subtraction, we will discuss the subtraction of natural numbers and correpsonding implementation in~\secref{subsec: subtraction}.
 The definition (except for the negative displacement) in Agda is as follows:
@@
     The customised library is a collection of types and functions centered around natural numbers, their operations and properties.
+The reason for creating a customised library is summarised in \secref{subsec: stdlib}.
 
@@
     \[\includegraphics[scale=1.2]{/lib/natural.pdf}\]
-    The use of \og{\textsf{BUILTIN}} is specifed in \secref{subsubsec: builtin_pragma}.
+    The use of \og{\textsf{BUILTIN}} is specifed in~\secref{subsubsec: builtin_pragma}.
 
     \subsection{Equality, congruence and substitution}
-    The definition of equality, congruence and substitution is similar to the one in \secref{subsec: equality}.\footnote{The definition of equality and related properties in the custom library differ slightly by using an indexed $\mb{\mathsf{Set}}$, which provides a more general formulation.
+    The definition of equality, congruence and substitution is similar to the one in~\secref{subsec: equality}.\footnote{The definition of equality and related properties in the custom library differ slightly by using an indexed $\mb{\mathsf{Set}}$, which provides a more general formulation.
 See Appendex [corresponding link].}
@@
     \subsubsection{Comparison of the two approaches}
-    The straightforward approach explicitly carries proofs in the type system, which is more transparent but verbose.
-The fin approach intially appears to be more elegant, as it encapsulates bounds check within a refined type.
+    The explicit approach carries proofs directly in the type system, which is more transparent but verbose.
+The $\textsf{Fin}$-based approach intially appears to be more elegant, as it encapsulates bounds check within a refined type.
 However, this elegance is superficial: constructing a term of type $\mb{\mathsf{Fin}}\ n$ still requires the same underlying proof of boundedness, shifting complexity to auxiliary conversions.
 
-    To prove a property with the fin approach, we need the following auxiliary function:
+    To prove a property with the $\textsf{Fin}$-based approach, we need the following auxiliary function:
     \[\includegraphics[scale=1.2]{/lib/fin/toFin.pdf}\]
@@
     \end{figure}
-    It is clear that the explicit proof-passing approach is more straightforward and easier to understand.
-The fin-based approach requires additional auxiliary functions and conversions, which makes the code more complex and harder to read.
-
-    Although the project completed both approaches, the following implementation of the compiler uses the explicit proof-passing approach due to its simplicity and clarity.
+    The explicit approach's verbosity pays off in readability when representing properties.
+the type of the term directly mirrors the mathematical statement with an explicit proof.
+In contrast, the $\textsf{Fin}$-based approach fractures this relationship, and reconstructing the original subtrahend requires tracing the type of the proof.
+This becomes cumbersome when the proofs are chained inequalities with transitivity, making the code harder to understand.
+
+    Although the project completed both approaches, the following implementation of the compiler uses the explicit proof-passing approach due to its clarity.
 
     \subsection{More properties of natural numbers}
+    The following are some properties of natural numbers that are useful for the implementation of the compiler with corresponding proofs.
+
+    The implementation of the properties of natural numbers in Agda is as follows:
+    \begin{figure}[H]
+        \centering
+        \includegraphics[scale=1.2]{/lib/proof/properties.pdf}
+        \caption{Properties of natural numbers related to subtraction}
+        \label{fig: properties_subtraction}
+    \end{figure}
 
     \section{Compiler}
+    \subsection{Presheaf semantics}
+    The denotation semantics interprets types as presheaves over a base category $\Upsigma$. 
+    \subsubsection{Base category}
+    The base category $\Upsigma$ is specified as follows:
+    \begin{itemize}
+        \item Objects are stack descriptors ($sd = \ang{f, d}$)
+        \item Morphisms are stack expansions ($\iota : sd \to sd'$ for $sd \leq_s sd'$) 
+    \end{itemize}
+    We define $\mathsf{SD}$ as the set of stack descriptors.
+Then the base category is the category determined by preorder $\underline{\mathsf{SD}} = \{\mathsf{SD}, \leq_s\}$ in Example~\ref{ex: category_preorder}.
+
+    \subsubsection{Semantic category}
+    Semantic category $\mathcal{K}$ is the functor category $\text{PDOM}^{\Upsigma^{\textbf{op}}}$, where $\text{PDOM}$ is the category of predomains.
+    \begin{itemize}
+        \item Objects are presheaves: $P = \Upsigma^{\textbf{op}} \to \text{PDOM}$.
+        \item Morphisms are natural transformations: $\eta : P \to Q$ for $P, Q \in \text{PDOM}^{\Upsigma^{\textbf{op}}}$.
+    \end{itemize}
+    The proof for semantic category is similar to the one in~\secref{sec: ccc_presheaf}, and the full proof is given by Oles in~\cite{Oles_1},\cite{Oles_2}.
+    \begin{itemize}
+        \item Products are given by pointwise product of presheaves: $P \times Q = \lambda sd.\ P\ sd \times Q\ sd$.
+        \item Exponentials $P \Rightarrow_s Q$ are given by the following equation:
+            \begin{equation}
+                \begin{aligned}
+                    P \Rightarrow_s Q &= \lambda sd.\ \mathcal{K}(\yo (sd) \times P, Q) \\
+                    &\cong \lambda sd.\{F \mid sd' \in \Upsigma, F : (\yo (sd) \times P)\ sd' \to Q\ sd'\} \\
+                    &\cong \lambda sd.\{F \mid sd' \in \Upsigma, F : (\Upsigma(sd, sd') \times P)\ sd' \to Q\ sd'\} \\
+                    &\cong \lambda sd.\{F \mid sd' \in \Upsigma, F : sd \leq_s sd' \to P\ sd' \to Q\ sd'\}
+                \end{aligned}
+                \label{eq: presheaf_exponential}
+            \end{equation}
+    \end{itemize}
+    [need support for each step of the proof]
+
+    The definition of products and exponentials in Agda is as follows:
+    \[\includegraphics[scale=1.2]{/compiler/product_exponentials.pdf}\]
+
+    We have a functor $\intp{-} : \Theta \to \mathcal{K}$, that interprets the type constructor $\to$ as the exponential functor $\Rightarrow_s$.
+
+    \subsection{Continuations}
+    In Reynolds' model, we use \textsf{Compl} and \textsf{Intcompl} to represent command and integer continuations. Mathematically we have
+    \[\textsf{Compl } sd : \mathsf{SD} \to O \qquad \textsf{IntCompl } sd : \bZ \to (\mathsf{SD} \to O)\]
+    where $O$ is an unspecified domain of outputs.
+
+    For code generation we define the continuation to be the instruction sequence in the target language:
+    \[\textsf{Compl } sd = \textsf{I}_{sd}\]
+
+    The definition of integer continuation is more complex, it is an exponential object in the presheaf category, which is defined as follows:
+    \[\textsf{IntCompl } = R \Rightarrow_s \textsf{Compl } \]
+    where $R$ is the functor corresponding to the righthand sides in the target language, $R\ sd = \textsf{R}_{sd}$.
+Thus we can directly use the definition of $R$ to define the integer continuation as follows:
+    \[\includegraphics[scale=1.2]{/compiler/continuations.pdf}\]
+
+    \subsection{Denotational semantics of types and contexts}
+    Given the definition of continuations, we can define the denotational semantics of types in Agda as follows:
+    \[\includegraphics[scale=1.2]{/compiler/type_interpretation.pdf}\]
+
+    The denotational semantics of contexts is essentially a list expressed by the product of the denotational semantics of the types in the context.
+The denotational semantics of contexts is defined as follows, where we use $\emptyset$ to denote the denotational semantics of the empty context:
+    \[\includegraphics[scale=1.2]{/compiler/context_interpretation.pdf}\]
+
+    \subsection{Morphisms: functorial mapping}
+    \[\includegraphics[scale=1.2]{/compiler/fmap_ctx.pdf}\]
+    Similarly, this functorial mapping also holds for \textsf{L} and \textsf{S} in the target language. The functorial mapping is defined as follows:
+    \[\includegraphics[scale=1.2]{/compiler/fmap_LS.pdf}\]
+
+    \subsection{Denotational semantics of terms}
+    The denotational semantics of terms is defined as a morphism from the denotational semantics of contexts to the denotational semantics of types.
+Similarly, it is a family of continuous functions indexed by the stack descriptor.
+The denotational semantics of terms has the following type in Agda:
+    \[\includegraphics[scale=1.2]{/compiler/term_interpretation_type.pdf}\]
+
+    We need to find out the denotational semantics of the terms correpsonding to all rules in the typing judgement mentioned in~\secref{subsec: terms}.
+
+        \subsubsection{Variables}
+        The denotational semantics of variables is defined as follows:
+        \[\includegraphics[scale=1.2]{/compiler/term_var.pdf}\]
+
+        \subsubsection{Subtyping}
+        The denotational semantics of subtyping is defined as follows:
+        \[\includegraphics[scale=1.2]{/compiler/term_subtype.pdf}\]
+
+        \subsubsection{Lambda abstraction}
+        The denotational semantics of lambda abstraction is defined as follows:
+        \[\includegraphics[scale=1.2]{/compiler/term_lambda.pdf}\]
+
+        \subsubsection{Commands}
+        The denotational semantics of commands is defined as follows:
+        \[\includegraphics[scale=1.2]{/compiler/term_comm.pdf}\]
+        The command \textsf{NewVar} is slightly more complicated, [To complete].
+
+        \subsubsection{Integer expressions}
+        The denotational semantics of integer expressions is defined as follows:
+        \[\includegraphics[scale=1.2]{/compiler/term_intexp.pdf}\]
+        The helper function \textsf{use-temp} is defined as follows:
+        \[\includegraphics[scale=1.2]{/compiler/assign_use-temp.pdf}\]
+
+    \subsection{Compilation} \label{subsec: compilation}
+    Compilation is a functor from the source language to the target language.
+To defrine the compilation functor, we use the denotational semantics of terms and fill in the initial stack descriptor ($\ang{0, 0}$), the empty context (\textsf{unit}), a trivial proof for stack descriptor being not less than itself (\textsf{$\leq_s$-refl}) and the continuation representing the last instruction (\textsf{stop}):
+    \[\includegraphics[scale=1.2]{/compiler/compilation.pdf}\]
 
@@
     Chapter~\chapref{chap: implementation} describes the implementation of the source language, the target language and the compiler in Agda.
-This chapter evaluates the implementation with a demonstrative example in Agda, and discusses the success criteria of the project.
-    \section{A demonstrative example in Agda}
+This chapter evaluates the implementation with integration tests and a feature checklist and then discusses the success criteria of the project.
+    \section{Tests}
+    \subsection{Test cases}
+    The correctness of the compiler is evaluated with a set of test cases. Each test is defined as follows
+    \begin{figure}[H]
+        \centering
+        \includegraphics[scale=1.2]{/test/example.pdf}
+        \caption{Test 0 as an example of test cases}
+        \label{fig: test_case_0}
+    \end{figure}
+    where definition of the \mb{\textsf{compile-closed}} function is specified in~\secref{subsec: compilation}.
+The program type checks only if both of the source term and the target term are correctly defined, and the target term is the result of the compilation of the source term.
+
+    There are special tests to check that some expressions in the source language compiles to the same expression in the target language. Such test is defined as follows:
+    \begin{figure}[H]
+        \centering
+        \includegraphics[scale=1.2]{/test/equivalence.pdf}
+        \caption{Test 3' as an example for checking equivalent compiled results}
+        \label{fig: test_case_3'}
+    \end{figure}
+
+    The full test cases are available in the appendix [insert link]. Here is a summary of the test cases written in a more readable format:
+    \begin{enumerate}[label=\textbf{Test \arabic*.}, leftmargin=*]
+        \setcounter{enumi}{-1}
+        \item $\mathsf{skip}$
+        \item $\mathsf{x := 2}$
+        \item $\mathsf{x := (\mathnormal{\lambda} a.\ a)\ 4}$
+        \item $\mathsf{x := (\mathnormal{\lambda} a.\ (\mathnormal{\lambda} b.\ a+b)\ 2)\ 3}$
+        \item[\textbf{Test 3'.}] $\mathsf{x := 3 + 2}$
+        \item $\mathsf{x := -3;\ y := (\mathnormal{\lambda} a. x)\ 2}$
+        \item $\mathsf{x := 2;\ x := x + 1}$
+        \item[\textbf{Test 5'.}] $\mathsf{x := 2;\ skip;\ x := x + 1}$
+        \item $\mathsf{x := 2;\ x := -x + 1}$
+        \item $\mathsf{x := (\mathnormal{\lambda} a.\ -a+1)\ 2}$
+    \end{enumerate}
+    where \textbf{Test 3} and \textbf{Test 3'}, \textbf{Test 5} and \textbf{Test 5'} compile to the same target term.
+
+    \textbf{Test 3} and \textbf{Test 3'} are equivalent in terms of compilation because the compilation directly substitutes the value in corresponding lambda terms.
+
+    \textbf{Test 5} and \textbf{Test 5'} are equivalent in terms of compilation because $\mathsf{skip}$ is a no-op in the source language.
+
+    \subsection{Feature checklist}
+    Traditional unit tests are not suitable for this project, as many typing judgement rules cannot be tested in isolation.
+For example, testing subtyping rule (Figure~\ref{fig: rule_subtype}) or any of the integer expression typing rules (Figure~\ref{fig: rule_intexp}) inherently requires embedding them in a well-typed command (\textsc{NewVar} in Figure~\ref{fig: rule_comm}), as the compiler only accepts complete commands.
+
+    Instead, I employed integration testing with a feature checklist, ensuring comprehensive coverage by validating all typing rules and targeting edge cases.
+    \begin{table}[H]
+        \centering
+        \begin{tabular}{| c | c | c | c |}
+            \hline
+            \textbf{Feature}  & \textbf{Typing judgement} & \textbf{Specification} & \textbf{Test cases number} \\
+            \hhline{|=|=|=|=|}
+            Variable & \textsc{Var} & - & 1, 2, 3, 3', 4, 5, 5', 6, 7 \\ \cline{3-4}
+            \hline
+            \multirow{2}{*}{Subtyping} 
+                & \multirow{2}{*}{\textsc{Sub}} 
+                    & \textsf{intvar} $\leq:$ \textsf{intacc} & 1, 2, 3, 3', 4, 5, 5', 6, 7  \\ \cline{3-4}
+                &   & \textsf{intvar} $\leq:$ \textsf{intexp} & 4, 5, 5', 6 \\
+            \hline
+            \multirowcell{4}{Lambda\\abstraction} 
+                & \multirow{3}{*}{\textsc{Lambda}} 
+                    & - & 2, 3, 4, 7 \\ \cline{3-4}
+                &   & Multiple variables\hyperlink{note1}{$^{\ast}$} & 3  \\ \cline{3-4}
+                &   & Free variables\hyperlink{note1}{$^{\ast}$} & 4 \\ \cline{2-4}
+                & \textsc{App} & - & 2, 3, 4, 7  \\
+            \hline
+            \multirow{7}{*}{Command} 
+                & \textsc{Skip} & - & 0, 5' \\ \cline{2-4}
+                & \multirow{2}{*}{\textsc{Seq}} 
+                    & - & 4, 5, 5', 6 \\ \cline{3-4}
+                &   & Multiple sequencing & 5' \\ \cline{2-4}
+                & \multirow{2}{*}{\textsc{NewVar}} 
+                    & - & 1, 2, 3, 3', 4, 5, 5', 6, 7 \\ \cline{3-4}
+                &   & Multiple variables\hyperlink{note1}{$^{\ast}$} & 4 \\ \cline{2-4}
+                & \multirow{2}{*}{\textsc{Assign}} 
+                    & -  & 1, 2, 3, 3', 4, 5, 5', 6, 7  \\ \cline{3-4}
+                &   & Self-referential assignments & 5, 5', 6 \\
+            \hline
+            \multirowcell{5}{Integer\\expression} 
+                & \multirow{2}{*}{\textsc{Lit}}  
+                    & Natural number  & 1, 3, 3', 4, 5, 6, 7 \\ \cline{3-4}
+                &   & Negative number & 2, 4 \\ \cline{2-4}
+                & \textsc{Neg} & - & 5, 5', 6, 7  \\ \cline{2-4}
+                & \textsc{Plus} & - & 3, 3', 6, 7  \\ \cline{2-4}
+                & -             & Multiple expressions\hyperlink{note2}{$^{\dagger}$} & 6, 7 \\
+            \hline
+        \end{tabular}
+
+        \caption{Feature checklist}
+        \label{tab: feature_checklist}
+    \end{table}
+
+    Here are some notes on the feature checklist:
+
+    \hypertarget{note1}{$^{\ast}$} These tests ensure that the translation of context as a whole is correct.
+
+    \hypertarget{note2}{$^{\dagger}$} This type of test is necessary because the target language does not support doing multiple operations in a single simple instructions.
+This is specified in [Implementation section].
+As a result, special tests are required to check that the compiler correctly translates multiple integer operations into a continuation of simple instructions defined in the target language.
+
+    \vspace{2.5em}
+
+    The feature checklist includes all the typing rules in the source language, including edge cases including multiple variables, free variables and self-referential assignments.
+Aditionally, I account for target-language-specific constraints, ensuring multiple operations are translated into simple instructions with continuation.
+The tests cover all the cases in the feature checklist, ensuring that the compiler is correct and complete.
 
     \section{Success criteria}
+    The project has met the success criteria as follows:
+    \begin{itemize}
+        \item
+            A formalisation of the source language has been given in Agda, which includes the syntax, typing rules and operational semantics.
+
+        \item
+            A formalisation of the target language has been given in Agda, which includes all instructions from the instruction set.
+Rigorous definitions of the operation of the stack descriptors are given, ensuring correctness and preserving the mathematical properties of the stack descriptors.
+
+        \item
+            A formalisation of the compiler has been given in Agda, which includes the denotational semantics of the source language and a term for compilation.
+
+        \item 
+            Integration tests have been given in Agda, which cover all the case in the feature checklist. The tests ensure that the compiler is correct and complete.
+    \end{itemize}
+
+    The following are the extension criteria that are met:
+    \begin{itemize}
+        \item 
+            A customised library have been developed, which includes rigorous definitions of subtraction of natural numbers and corresponding properties.
+Two approaches to rigorous definition of subtraction has been implemented and compared.
+        \item
+            Operational semantics of the source language has been defined with renaming, substitution and reduction rules.
+        \item
+            usetmp [to be completed]
+
+    \end{itemize}
 
@@
     \section{Lessons learned}
-
-    % \section{Future work}
-
+    \begin{itemize}
+        \item 
+        challenging in both theory and implementation
+
+        \item
+        struggle with different approaches
+        \item
+        struggle with inserting agda code into latex
+        \begin{itemize}
+            \item 
+                problem with unicode characters
+            \item 
+                alternative solution does not colour well due to dependent types
+        \end{itemize}
+    \end{itemize}
+
+    \section{Future work}
+    \begin{itemize}
+        \item subroutine and iteration
+        \item correctness of the compiler
+        \item exploring a reasonable equational theory that can be stated directly on the instruction sequences, under which the semantics actually becomes a true functor category model (i.e.
+naturality holds).
+    \end{itemize}
 \printbibliography
@@
 \appendix
+
+\chapter{Operational Semantics of the source language} \label{app: operational_semantics}
+    \minitoc
+    The operational semantics of the source language is defined with renaming, substitution and reduction rules. The implementation is as follows:
+    \begin{figure}[H]
+        \centering
+        \includegraphics[scale=1.2]{/source/operational_semantics_1.pdf}
+        \caption{Operational semantics of the source language (Part 1)}
+        \label{fig: operational_semantics_1}
+    \end{figure}
+    \begin{figure}[H]
+        \centering
+        \includegraphics[scale=1.2]{/source/operational_semantics_2.pdf}
+        \caption{Operational semantics of the source language (Part 2)}
+        \label{fig: operational_semantics_2}
+    \end{figure}
 

### 2025-05-11 src/compiler.lagda.tex
Evaluation almost done

--- 2025-05-01 src/compiler.lagda.tex
@@
 \newunicodechar{ℤ}{\ensuremath{\mathbb{Z}}}
+\newunicodechar{β}{\ensuremath{\beta}}
 \newunicodechar{δ}{\ensuremath{\delta}}
+\newunicodechar{γ}{\ensuremath{\gamma}}
+\newunicodechar{κ}{\ensuremath{\kappa}}
+\newunicodechar{λ}{\ensuremath{\lambda}}
+\newunicodechar{π}{\ensuremath{\pi}}
+\newunicodechar{ρ}{\ensuremath{\rho}}
+\newunicodechar{σ}{\ensuremath{\sigma}}
+\newunicodechar{θ}{\ensuremath{\theta}}
 \newunicodechar{∈}{\ensuremath{\in}}
@@
 \newunicodechar{ᵛ}{\ensuremath{\textsuperscript{v}}}
+\newunicodechar{ʳ}{\ensuremath{\textsuperscript{r}}}
+\newunicodechar{₁}{\ensuremath{\textsubscript{1}}}
+\newunicodechar{₂}{\ensuremath{\textsubscript{2}}}
+\newunicodechar{⟨}{\ensuremath{\langle}}
+\newunicodechar{⟩}{\ensuremath{\rangle}}
+\newunicodechar{–}{\ensuremath{-}}
+\newunicodechar{∅}{\ensuremath{\emptyset}}
 
@@
 
-get-var : ∀ {Γ A sd} → A ∈ Γ → ⟦ Γ ⟧ctx sd → ⟦ A ⟧ty sd
-get-var Zero     (_ , a) = a
-get-var (Suc x) (γ , _) = get-var x γ
+⟦_⟧var : ∀ {Γ A sd} → A ∈ Γ → ⟦ Γ ⟧ctx sd → ⟦ A ⟧ty sd
+⟦ Zero ⟧var (_ , a) = a
+⟦ Suc b ⟧var (γ , _) =  ⟦ b ⟧var γ
 
--- Functorality
-fmap-⇒ : ∀ {P Q sd sd'} → (P ⇒ₛ Q) sd → sd ≤ₛ sd' → (P ⇒ₛ Q) sd'
-fmap-⇒ θ p p' x = θ (≤ₛ-trans p p') x
+⟦_⟧sub : ∀ {A A' sd} → A ≤: A' → ⟦ A ⟧ty sd → ⟦ A' ⟧ty sd
+⟦ ≤:-refl ⟧sub a = a
+⟦ ≤:-trans A≤:A' A'≤:A'' ⟧sub a = ⟦ A'≤:A'' ⟧sub (⟦ A≤:A' ⟧sub a)
+⟦ ≤:-fn A≤:A' B'≤:B ⟧sub a = 
+    λ sd≤ₛsd' a' → ⟦ B'≤:B ⟧sub (a sd≤ₛsd' (⟦ A≤:A' ⟧sub a'))
+⟦ var-≤:-exp ⟧sub (exp , acc) = exp
+⟦ var-≤:-acc ⟧sub (exp , acc) = acc
 
-fmap-Compl : ∀ {sd sd'} → Compl sd → sd ≤ₛ sd' → Compl sd'
-fmap-Compl {sd} c (<-f f<f') = popto sd (<-f f<f') c
-fmap-Compl {⟨ f , d ⟩} {⟨ f , d' ⟩} c (≤-d d≤d') = 
-    adjustdisp-dec ((d' - d) d≤d') (-→≤ d≤d') 
-        (sub I (-ₛ≡ 
-            {n = (d' - d) d≤d'} 
-                (n-[n-m]≡m d≤d')) c)
+-- Functorial mapping
+
+fmap-I : ∀ {sd sd'} → I sd → sd ≤ₛ sd' → I sd'
+fmap-I {sd} c (<-f f<f') = popto sd (<-f f<f') c
+fmap-I {⟨ f , d ⟩} {⟨ f , d' ⟩} c (≤-d d≤d') = 
+    adjustdisp-dec ((d' – d) d≤d') (–→≤ d≤d') 
+        (I-sub {n = (d' – d) d≤d'} (n–[n–m]≡m d≤d') c)
 
@@
 
-fmap-A : ∀ {A sd sd'} → ⟦ A ⟧ty sd → sd ≤ₛ sd' → ⟦ A ⟧ty sd'
-fmap-A {comm}  = fmap-⇒ {Compl} {Compl}
-fmap-A {intexp} = fmap-⇒ {Intcompl} {Compl}
-fmap-A {intacc} = fmap-⇒ {Compl} {Intcompl}
-fmap-A {intvar} ( e , a ) sd≤ₛsd' = ( fmap-A {intexp} e sd≤ₛsd' , fmap-A {intacc} a sd≤ₛsd' )
-fmap-A {A ⇒ B} = fmap-⇒ {⟦ A ⟧ty} {⟦ B ⟧ty}
+fmap-⇒ : ∀ {P Q sd sd'} → (P ⇒ₛ Q) sd → sd ≤ₛ sd' → (P ⇒ₛ Q) sd'
+fmap-⇒ P⇒Q sd≤ₛsd' sd'≤ₛsd'' p = P⇒Q (≤ₛ-trans sd≤ₛsd' sd'≤ₛsd'') p
 
-fmap-Γ : ∀ {Γ sd sd'} → ⟦ Γ ⟧ctx sd → sd ≤ₛ sd' → ⟦ Γ ⟧ctx sd'
-fmap-Γ {·} unit _ = unit
-fmap-Γ {Γ , A} (γ , a) p = fmap-Γ γ p , fmap-A {A} a p
+fmap-ty : ∀ {A sd sd'} → ⟦ A ⟧ty sd → sd ≤ₛ sd' → ⟦ A ⟧ty sd'
+fmap-ty {comm}  = fmap-⇒ {Compl} {Compl}
+fmap-ty {intexp} = fmap-⇒ {Intcompl} {Compl}
+fmap-ty {intacc} = fmap-⇒ {Compl} {Intcompl}
+fmap-ty {intvar} ( exp , acc ) sd≤ₛsd' = 
+    ( fmap-ty {intexp} exp sd≤ₛsd' , fmap-ty {intacc} acc sd≤ₛsd' )
+fmap-ty {A ⇒ B} = fmap-⇒ {⟦ A ⟧ty} {⟦ B ⟧ty}
 
-sd≤ₛsd'→sd≤ₛsd'-ₛ[d'-[suc-d]] : ∀ {sd sd'} → sd ≤ₛ sd' → (δ₁≤δ₂ : suc (SD.d sd) ≤ SD.d sd') → sd ≤ₛ ((sd' -ₛ ((SD.d sd' - (suc (SD.d sd))) δ₁≤δ₂)) (-→≤ δ₁≤δ₂))
-sd≤ₛsd'→sd≤ₛsd'-ₛ[d'-[suc-d]] {⟨ f , _ ⟩} {⟨ f' , _ ⟩} (<-f f<f') _ = <-f f<f'
-sd≤ₛsd'→sd≤ₛsd'-ₛ[d'-[suc-d]] {⟨ f , d ⟩} {⟨ f , d' ⟩} (≤-d d≤d') δ₁≤δ₂ = ≤-d (suc-d≤d'→d≤d'-[d'-[suc-d]] δ₁≤δ₂)
+fmap-ctx : ∀ {Γ sd sd'} → ⟦ Γ ⟧ctx sd → sd ≤ₛ sd' → ⟦ Γ ⟧ctx sd'
+fmap-ctx {·} unit _ = unit
+fmap-ctx {Γ , A} (γ , a) p = fmap-ctx γ p , fmap-ty {A} a p
 
-assign : (sd : SD) → (sd' : SD) → (S ⇒ₛ Compl) sd → sd ≤ₛ sd' → R sd' → I sd'
+sd≤ₛsd'→sd≤ₛsd'–ₛ[d'–[suc-d]] : ∀ {sd sd'} → sd ≤ₛ sd' 
+    → (δ₁≤δ₂ : suc (SD.d sd) ≤ SD.d sd') 
+    → sd ≤ₛ ((sd' –ₛ ((SD.d sd' – (suc (SD.d sd))) δ₁≤δ₂)) (–→≤ δ₁≤δ₂))
+sd≤ₛsd'→sd≤ₛsd'–ₛ[d'–[suc-d]] {⟨ f , _ ⟩} {⟨ f' , _ ⟩} (<-f f<f') _ 
+    = <-f f<f'
+sd≤ₛsd'→sd≤ₛsd'–ₛ[d'–[suc-d]] {⟨ f , d ⟩} {⟨ f , d' ⟩} (≤-d d≤d') δ₁≤δ₂ 
+    = ≤-d (suc-d≤d'→d≤d'–[d'–[suc-d]] δ₁≤δ₂)
+
+new-intvar : ∀ sd → ⟦ intvar ⟧ty sd
+new-intvar sd = ( exp , acc )
+    where
+        exp : ⟦ intexp ⟧ty sd
+        exp sd≤ₛsd' β = β ≤ₛ-refl (r-s (s-l (l-var sd sd≤ₛsd')))
+        acc : ⟦ intacc ⟧ty sd
+        acc {sd' = sd'} sd≤ₛsd' κ (≤-d {d = d'} {d' = d''} d'≤d'') r
+            = assign-dec 
+                ((d'' – d') d'≤d'') (–→≤ d'≤d'') 
+                (l-var sd
+                   (sub-sd≤ₛ (–ₛ≡ {n≤d' = –→≤ d'≤d''} (n–[n–m]≡m d'≤d'')) sd≤ₛsd'))
+                r
+                (I-sub {n = (d'' – d') d'≤d''}(n–[n–m]≡m d'≤d'') κ)
+        acc {sd' = sd'} sd≤ₛsd' κ (<-f f<f') r 
+            = assign-inc 0 (l-var _ ≤ₛ-refl) r (fmap-I κ (<-f f<f'))
+
+assign : (sd : SD) → (sd' : SD) → (S ⇒ₛ Compl) sd 
+            → sd ≤ₛ sd' → R sd' → I sd'
 assign ⟨ f , d ⟩ ⟨ f' , d' ⟩ β sd≤ₛsd' r with (≤-compare {suc d} {d'})
-... | leq δ₁≤δ₂ = assign-dec ((d' - (suc d)) δ₁≤δ₂) 
-                    (-→≤ δ₁≤δ₂) (l-var ⟨ f , d ⟩ (sd≤ₛsd'→sd≤ₛsd'-ₛ[d'-[suc-d]] sd≤ₛsd' δ₁≤δ₂)) r 
-                    (β ((sd≤ₛsd'→sd≤ₛsd'-ₛ[d'-[suc-d]] sd≤ₛsd' δ₁≤δ₂)) 
-                        (s-l (l-var ⟨ f , d ⟩ ((sd≤ₛsd'→sd≤ₛsd'-ₛ[d'-[suc-d]] sd≤ₛsd' δ₁≤δ₂)))))
+... | leq δ₁≤δ₂ 
+        = assign-dec 
+            ((d' – (suc d)) δ₁≤δ₂) (–→≤ δ₁≤δ₂) 
+              (l-var ⟨ f , d ⟩ 
+                (sd≤ₛsd'→sd≤ₛsd'–ₛ[d'–[suc-d]] sd≤ₛsd' δ₁≤δ₂)) 
+              r 
+              (β ((sd≤ₛsd'→sd≤ₛsd'–ₛ[d'–[suc-d]] sd≤ₛsd' δ₁≤δ₂)) 
+                (s-l (l-var ⟨ f , d ⟩ 
+                  ((sd≤ₛsd'→sd≤ₛsd'–ₛ[d'–[suc-d]] sd≤ₛsd' δ₁≤δ₂)))))
 
-... | geq δ₂≤δ₁ = assign-inc (((suc d) - d') δ₂≤δ₁) 
+... | geq δ₂≤δ₁ = assign-inc (((suc d) – d') δ₂≤δ₁) 
                   (l-var ⟨ f , d ⟩ (≤ₛ-trans sd≤ₛsd' +ₛ→≤ₛ)) r 
@@
 
-⟦_⟧ : ∀ {Γ A} → (e : Γ ⊢ A) → (sd : SD) → ⟦ Γ ⟧ctx sd → ⟦ A ⟧ty sd
-⟦ Var x ⟧ _ γ = get-var x γ
-⟦ Lambda f ⟧ sd γ {sd' = sd'} p a = ⟦ f ⟧ sd' (fmap-Γ γ p , a) 
+⟦_⟧ : ∀ {Γ A} → Γ ⊢ A → (sd : SD) → ⟦ Γ ⟧ctx sd → ⟦ A ⟧ty sd
+⟦ Var a ⟧ sd γ = ⟦ a ⟧var γ
+
+⟦ Sub a A≤:B ⟧ sd γ = ⟦ A≤:B ⟧sub (⟦ a ⟧ sd γ)
+
+⟦ Lambda f ⟧ sd γ {sd' = sd'} sd≤ₛsd' a 
+    = ⟦ f ⟧ sd' (fmap-ctx γ sd≤ₛsd' , a)
+
 ⟦ App f e ⟧ sd γ = ⟦ f ⟧ sd γ (≤-d ≤-refl) (⟦ e ⟧ sd γ)
-⟦ Skip ⟧ _ _ _ γ = γ
-⟦ Seq c₁ c₂ ⟧ sd γ sd' p = ⟦ c₁ ⟧ sd γ sd' (⟦ c₂ ⟧ sd γ sd' p)
-⟦ Lit i ⟧ _ _ _ κ = κ ≤ₛ-refl (r-s (s-lit i))
-⟦ Neg e ⟧ sd γ p κ = ⟦ e ⟧ sd γ p (use-temp λ p s → κ p (r-unary UNeg s))    
-⟦ Plus e₁ e₂ ⟧ sd γ p κ = ⟦ e₁ ⟧ sd γ p (use-temp (λ p' s₁ → ⟦ e₂ ⟧ sd γ (≤ₛ-trans p p') (use-temp (λ p'' s₂ →  κ (≤ₛ-trans p' p'') (r-binary (fmap-S s₁ p'') BPlus s₂)))))
+
+⟦ Skip ⟧ sd γ sd≤ₛsd' κ = κ
+
+⟦ Seq c₁ c₂ ⟧ sd γ sd≤ₛsd' κ 
+    = ⟦ c₁ ⟧ sd γ sd≤ₛsd' (⟦ c₂ ⟧ sd γ sd≤ₛsd' κ)
+
+⟦ NewVar c ⟧ sd γ {sd' = sd'} sd≤ₛsd' κ = 
+    assign-inc 
+        1 
+        (l-var sd' (≤-d +→≤)) 
+        (r-s (s-lit (pos 0))) 
+        (⟦ c ⟧ 
+            (sd' +ₛ 1)
+            (fmap-ctx {Γ = _ , intvar} 
+                ((fmap-ctx γ sd≤ₛsd' , new-intvar sd')) 
+                (+ₛ→≤ₛ {sd'} {1}))
+            ≤ₛ-refl
+            (adjustdisp-dec 
+                1 
+                +→≤ʳ 
+                (I-sub {d' = SD.d sd' + 1} {n = 1} 
+                    (n+m–m≡n {m = 1}) κ)))
+
+⟦ Assign a e ⟧ sd γ sd≤ₛsd' κ = ⟦ e ⟧ sd γ sd≤ₛsd' (⟦ a ⟧ sd γ sd≤ₛsd' κ)
+
+⟦ Lit i ⟧ sd γ sd≤ₛsd' κ = κ ≤ₛ-refl (r-s (s-lit i))
+
+⟦ Neg e ⟧ sd γ sd≤ₛsd' κ = 
+    ⟦ e ⟧ sd γ sd≤ₛsd' 
+        (use-temp λ sd≤ₛsd' s → κ sd≤ₛsd' (r-unary UNeg s))
+
+⟦ Plus e₁ e₂ ⟧ sd γ p κ = 
+    ⟦ e₁ ⟧ sd γ p (use-temp (λ p' s₁ → ⟦ e₂ ⟧ sd γ (≤ₛ-trans p p') 
+                    (use-temp (λ p'' s₂ →  κ (≤ₛ-trans p' p'') 
+                        (r-binary (fmap-S s₁ p'') BPlus s₂)))))
+
+compile-closed : · ⊢ comm → I ⟨ 0 , 0 ⟩
+compile-closed t = ⟦ t ⟧ ⟨ 0 , 0 ⟩ unit ≤ₛ-refl stop
 \end{code}

### 2025-05-12 draft.tex
Evaluation and conclusion almost completed

@@
-\documentclass[12pt,twoside,a4paper]{report}
+\documentclass[12pt,a4paper]{report}
 \usepackage{amsmath}
@@
 
-\usepackage[backend=biber,style=ieee]{biblatex}
+\usepackage[backend=biber,bibstyle=ieee,citestyle=numeric-comp]{biblatex}
 \addbibresource{ref.bib}
@@
 \theoremstyle{definition}
-\newtheorem{definition}{Definition}
-
-\theoremstyle{definition}
-\newtheorem{theorem}{Theorem}
-
-\theoremstyle{definition}
-\newtheorem{example}{Example}
-
-\theoremstyle{definition}
-\newtheorem{prf}{Proof}
+\newtheorem{definition}{Definition}[chapter]
+
+\newtheorem{theorem}[definition]{Theorem}
+
+\newtheorem{example}[definition]{Example}
+
+\newtheorem{prf}[definition]{Proof Sketch}
 
@@
 It provides a theoretical framework for defining the meaning of programming languages by interpreting them into mathematical objects.
-By formalising the denotational semantics of a programming language, we ensure that its abstraction align with human intuition.
+By formalising the denotational semantics of a programming language, we ensure that its abstraction align with our intentions.
 
@@
     This project explores how the two process can be deeply connected by demonstrating how denotational semantics can directly generate a compiler.
-Simply typed lambda calculus (STLC)~\cite{stlc} is a well-studied programming language that serves as a foundation for many modern languages.
-It has denotational semantics in cartesian closed categories, shown by Lambek~\cite{lambek}.
-As a ccc, presheaf categories over store locations can be used to model STLC with stores, as shown by by Reynolds~\cite{essence} and Oles~\cite{Oles_1}~\cite{Oles_2}.
-Instead, Reynolds~\cite{Reynolds} presented a denotational semantics of STLC with stores in the form of a presheaf category over compiler states.
-By interpresting the source language into the presheaf category over stack descriptors, where objects of the category represent instruction sequences parameterised by stack layouts, the semantic model directly yields a compiler.
-
-    In this dissertation, I implement this compiler for STLC with stores in a dependently typed programming language, Agda~\cite{Agda}.
-The compiler is a functor (structure-preserving map) from the source language's semantic domain to the target language's instruction set.
-The implementation is verified with Agda's type system, which ensures that the generated code is well-typed and adheres to the semantics of both the source and target languages.
+Simply typed lambda calculus (STLC)~\autocite{stlc} is a well-studied programming language that serves as a foundation for many modern languages.
+It has denotational semantics in cartesian closed categories (CCC)~\autocite{lambek}.
+As a CCC, presheaf categories over store locations can be used to model STLC with stores, as shown by by Reynolds~\autocite{essence} and Oles~\autocite{Oles_1,Oles_2}.
+Later, Reynolds presented a denotational semantics of STLC with stores in the form of a presheaf category over compiler states~\autocite{Reynolds}.
+By interpreting the source language into the presheaf category over \emph{stack descriptors}, where objects of the category represent instruction sequences parametrised by stack layouts, the semantic model directly yields a compiler.
+
+    In this dissertation, I implement Reynolds' presheaf-based compiler for STLC with stores in a dependently typed programming language, Agda~\autocite{Agda}.
+The compiler is a \emph{functor} (structure-preserving map) from the source language to the target language.
+The implementation is verified with Agda, which ensures that the input source program, the compilation process, and the output target program are all well-typed.
 
@@
 
-        \motivation{Implementation of the compiler}
-        Reynolds concluded that he did not have a proper dependently typed programming language in hand, so his compiler remained a partial function.
-I aim to provide a computer implementation of this theoretical framework in a dependently typed programming language.
-
         \motivation{Formal verification of the compiler}
         Reynolds' work presented detailed definitions of denotational semantics of STLC with stores, which are complicated and error-prone.
-The rise of verified compilers including CompCert~\cite{CompCert}, CakeML~\cite{CakeML} reflects a broader trend toward trustworthy systems, where correctness proofs replace testing for critical guarantees.
+The rise of verified compilers including CompCert~\autocite{CompCert} and CakeML~\autocite{CakeML} reflects a broader trend toward trustworthy systems, where correctness proofs replace testing for critical guarantees.
 I aim to provide a formalisation of the definition in a proof assistant to verify the correctness of the given denotational semantics.
 
+        \motivation{Implementation of the compiler}
+        Reynolds concluded that he did not have a proper dependently typed programming language in hand, so his compiler remained a partial function~\autocite[Ch.6]{Reynolds}.
+I aim to provide a computer implementation of this theoretical framework in a dependently typed programming language.
+
     \section{Language choice: Agda's advantages}
-        Agda~\cite{Agda} is a dependently typed programming language and proof assistant.
-Agda captures the source language's intrinsic sytax with indexed families, which contains only well-typed terms.
+        Agda~\autocite{Agda} is a dependently typed programming language and proof assistant.
+Agda captures the source language's intrinsic syntax with indexed families, which contains only well-typed terms.
 Therefore, it focuses on the correct programs and rules out the ill-typed nonsensical inputs.
@@
         Dependently typed languages provide a natural framework for expressing functor categories is proven both theoretically and practically.
-There have been dependent-type-theoretic model of categories~\cite{Dybjer}, and it has been shown that functor categories arise naturally as dependent function types~\cite{Jacobs}.
-A formalisation of Category Theory, including cartesian closed categories, functors and presheaves has been developed in Agda by Hu and Caratte~\cite{Cat_Agda}.
+There have been dependent-type-theoretic model of categories~\autocite{Dybjer}, and it has been shown that functor categories arise naturally as dependent function types~\autocite{Jacobs}.
+A formalisation of Category Theory, including cartesian closed categories, functors and presheaves has been developed in Agda by Hu and Caratte~\autocite{Cat_Agda}.
 Other proof assistants, such as Isabelle/Hol, does not have a dependently typed language structure, and thus cannot express the functor categories as naturally as Agda.
@@
             \savedmotivationI
+            I formalised the terms in the source language and target language in Agda. I also refined some type definitions in the denotational semantics of the source language.
+
+            \savedmotivationII
             I implemented the compiler from the source language to the target language in Agda. 
-
-            \savedmotivationII
-            I formalised the terms in the source language and target language in Agda. I also refined some type definitions in the denotational semantics of the source language.
-
         \end{quote}
@@
     Prior to this project, I had no experience with Agda.
-Although I was aware of the open-source online tutorial \textit{Programming Language Foundations in Agda} (PLFA)~\cite{plfa}, my preparation was limited to setting up the Agda environment on my laptop by following the ``Front Matter'' section of the tutorial.
+Although I was aware of the open-source online tutorial \textit{Programming Language Foundations in Agda} (PLFA)~\autocite{plfa}, my preparation was limited to setting up the Agda environment on my laptop by following the ``Front Matter'' section of the tutorial.
 
@@
         Category theory provides a high-level abstraction from which we can reason about the structure of mathematical objects and their relationships.
-It provides us a ``bird's eye view'' of the mathematics which enable us to spot patterns that are difficult to see in the details~\cite{basic_cat}.
-More specifically, it provides a ``purer'' view of functions that is not derived from sets~\cite{scott-lambda}.
+It provides us a ``bird's eye view'' of the mathematics which enable us to spot patterns that are difficult to see in the details~\autocite{basic_cat}.
+More specifically, it provides a ``purer'' view of functions that is not derived from sets~\autocite{scott-lambda}.
 Compared to set theory which is ``element-oriented'', category theory is ``function-oriented'' and ``morphism-oriented''.
@@
 
-        The following is a brief introduction to the basic concepts of category theory, which is based on the work of Leinster~\cite{basic_cat}, 
-        Riehl~\cite{cat_context}, and the lecture notes of Part II Category Theory by Andrew Pitts and Marcelo Fiore~\cite{cat_lecture_notes}.
+        The following is a brief introduction to the basic concepts of category theory, which is based on the work of Leinster~\autocite{basic_cat}, 
+        Riehl~\autocite{cat_context}, and the lecture notes of Part II Category Theory by Andrew Pitts and Marcelo Fiore~\autocite{cat_lecture_notes}.
 
@@
         \begin{example}[$\mathcal{Set}$]
-            An example of category is the category of sets, denoted as $\mathcal{Set}$, specifed by the following:
+            An example of category is the category of sets, denoted as $\mathcal{Set}$, specified by the following:
             \begin{itemize}
@@
         \begin{definition}[Cartesian closed category]
-            A category $\mathcal{C}$ is called a \emph{Cartesian closed category} (ccc) if it has a terminal object, binary products and exponentials of any two objects.
+            A category $\mathcal{C}$ is called a \emph{Cartesian closed category} (CCC) if it has a terminal object, binary products and exponentials of any two objects.
         \end{definition}
@@
         \begin{theorem}[Yoneda lemma]
-            Given a category $\mathcal{C}$, the \emph{Yoneda lemma} states that for each object $X \in \textbf{obj}(\mathcal{C})$ and any functor $F: \mathcal{C} \to \textbf{Set}$, there is a natural isomorphism:
+            For each small\footnote{Here the smallness condition avoids foundational issues analogous to Russell's paradox.
+While we omit the formal definition of size due to the space limit here, all constructions in this work preserve smallness.} category $\mathcal{C}$, the \emph{Yoneda lemma} states that for each object $X \in \textbf{obj}(\mathcal{C})$ and each presheaf $F \in \hat{\mathcal{C}}$, there exists a natural isomorphism
             \begin{equation} \label{eq: yoneda_lemma}
@@
         \begin{prf}[Cartesian closed structure in presheaf categories]
-            Given a small category $\mathcal{C}$, the presheaf category $\hat{\mathcal{C}}$ is a Cartesian closed category.
+            Given a small\footnote{See footnote 1.} category $\mathcal{C}$, the presheaf category $\hat{\mathcal{C}}$ is a Cartesian closed category.
             \begin{itemize}
@@
     \section{Agda}
-        \subsection{Basic datatypes and pattern matching}
-        We will go through a simple example in PLFA~\cite{plfa} to illustrate the basic datatypes and pattern matching in Agda.
+        \subsection{Basic data types and pattern matching}
+        Here is a simple example selected from PLFA~\autocite{plfa} to illustrate the basic data types and pattern matching in Agda. The example is a definition of natural numbers and a plus function.
 
@@
 
-        Here we define a datatype $\mb{\bN}$ for natural numebers.
-$\mb{\bN}$ itself has a type $\mb{\mathsf{Set}}$, which is the type of all small types.
-The natural number is defined as a recursive datatype with two constructors: $\gn{\mathsf{zero}}$ and $\gn{\mathsf{suc}}$, where
-        $\gn{\mathsf{zero}}$ is the base case and $\gn{\mathsf{suc}}$ is the inductive case.
-The $\gn{\mathsf{zero}}$ constructor has type $\mb{\bN}$, and the $\gn{\mathsf{suc}}$ constructor has type $\mb{\bN \to \bN}$.
-
-        In order to define the plus function $\mb{\_+\_}$, we use pattern matching to match the input argument with the constructors of the datatype.
-The first case is the base case, where we match the input argument with $\gn{\mathsf{zero}}$.
-In this case, we return the second argument.
-The second case is the inductive case, where we match the input argument with $\gn{\mathsf{suc}}$.
-In this case, we return $\gn{\mathsf{suc}}$ applied to the result of adding one to the second argument.
+        In Agda we use the $\og{\mathsf{data}}$ keyword to define a type.
+Every type has a type, and we use $\mb{\mathsf{Set}}$ to denote the type of all small types.
+To define a type, we specify its type and its constructors.
+To define a function, we specify its type and pattern match the input according to the constructors of the type.
 
@@
 
-        Here we define a datatype $\mb{\mathsf{Vec}}$ for vectors. The type of vectors is dependent on the length of the vector. With dependent types, we can encode properties directly into types.
+        Here we define a data type $\mb{\mathsf{Vec}}$ for vectors. The type of vectors is dependent on the length of the vector. With dependent types, we can encode properties directly into types.
 
         \subsection{Curry-Howard-Lambek correspondence} \label{subsec: curry-howard-lambek}
-        Curry-Howard correspondence~\cite{curry-howard} establishes an isomorphism between logic and type theory, where propositions correspond to types and proofs correspond to terms.
+        Curry-Howard correspondence~\autocite{curry-howard} establishes an isomorphism between logic and type theory, where propositions correspond to types and proofs correspond to terms.
 This correspondence forms the foundation of functional programming languages that can be used to implement proofs.
-Building upon this, Joachim Lambek showed that cartesian closed categories provide a natural semantic setting for the simply typed lambda calculus (STLC)~\cite{lambek}.
+Building upon this, Joachim Lambek showed that cartesian closed categories provide a natural semantic setting for the simply typed lambda calculus (STLC)~\autocite{lambek}.
 The Curry-Howard-Lambek correspondence can be summarised as follows:
@@
         \subsection{Standard library} \label{subsec: stdlib}
-        The Agda standard library~\cite{agda_std} is a collection of modules that provide a wide range of useful functions and types.
+        The Agda standard library~\autocite{agda_std} is a collection of modules that provide a wide range of useful functions and types.
 It includes modules for basic data types, such as natural numbers, lists, and vectors.
-In my implementation, however, I defined the basic data types and functions from scratch for the following reasons:
-        \begin{itemize}
-            \item
-                \textbf{Specialised Requirements}: The standard library's definitions (e.g.
-subtraction as monus, `'$\dotdiv$') do not align with my project's need for a rigorously defined subtraction operation.
-My implementation, discussed in Section~\ref{subsec: subtraction}, ensures correctness and preserves the properties of natural numbers.
-            \item
-                \textbf{Verification Clarity}: By defining the basic data types and functions from scratch, I can tailor properties (e.g.
-the property `$n-[n-m] \equiv m$') to my specific requirements, and avoid unnecessary complexity (e.g.
-`$\leq$' being also defined as a boolean predicate in the standard library).
-            \item
-                \textbf{Minimal Dependencies}: Avoiding the standard library reduces external assumptions, making the project self-contained. 
-        \end{itemize}
+In my implementation, standard library is used as a reference for defining a customised library, which is specified in~\secref{sec: lib}.
 
@@
 This is a convenient feature for testing.
-Agda provides a way to link self-defined functions to the standard library with a \og{\textsf{BUILTIN}} pragma.
-This allows me to use a convenient syntax for numbers, while still using the self-defined functions in the implementation without any import.
+Self-defined functions can be used with the builtin numbers with a \og{\textsf{BUILTIN}} pragma.
+This allows me to use a convenient syntax of numbers for self-defined functions.
         \[\includegraphics[scale=1.2]{natural_pragma.pdf}\]
@@
         \subsection{Interactive programming with holes} \label{subsec: holes}
-        A feature of Agda is that it allows us to write programs with holes interatively.
-A hole is a placeholder for a term that we have not yet defined.
+        A feature of Agda is interactive programming with holes.
 By leaving holes in place of undefined terms, we can write programs that are incomplete but still type-check, and Agda's type checker will guide completion of the program: the context window displays inferred types of the holes, available variables and candidate terms with their types.
@@
         In my implementation, I used holes to write the terms in the compiler.
-The complex terms are incrementally filled and verified by interatively refining partial implementations, reducing post-hoc debugging and ensuring robustness.
+The complex terms are incrementally filled and verified by refining partial implementations, reducing post-hoc debugging and ensuring robustness.
 
     \section{Requirement Analysis}
-    To complete a compiler in Agda we need to implement the following components:
-    \begin{itemize}
-        \item 
-            A file source.agda that record the syntax of the source language.
-
-        \item
-            A file target.agda that record the syntax of the target language.
-
-        \item
-            A file compiler.agda that uses source.agda and target.agda as modules, and write functions whose input is a term in the source language and output is a term in the target language.
-    \end{itemize}
-    The success criteria of the project is that the file compiler.agda type checks, as the type checking process will reduce the source term to the target term.
+    To complete the compiler in Agda we need to implement the following components:
+    \begin{itemize}
+        \item 
+            A file \texttt{source.agda} that record the syntax of the source language, which include basic instructions in STLC.
+
+        \item
+            A file \texttt{target.agda} that record the syntax of the target language.
+
+        \item
+            A file \texttt{compiler.agda} that uses \texttt{source.agda} and \texttt{target.agda} as modules, and write functions whose input is a term in the source language and output is a term in the target language.
+        \item 
+            A file \texttt{test.agda} that contains test cases for the compiler. The test cases are written in the source language, and the expected output is written in the target language. 
+    \end{itemize}
+    The success criteria of the project is that all of the above files are implemented and type checked, which ensures that all the terms are well typed and the compilation is as expected.
 
@@
 
-    Completing the project is an iterative process. I used Git~\cite{git} for version control, and work had been synchronised with a GitHub~\cite{github} repository for backup.
-
-    For the development environment, I tried both Emacs~\cite{emacs} and Visual Studio Code~\cite{vscode} with an agda-mode extension~\cite{agda_mode} on Windows Subsystem for Linux with Ubuntu~\cite{wsl_ubuntu} 22.04 LTS.
+    Completing the project is an iterative process. I used Git~\autocite{git} for version control, and work had been synchronised with a GitHub~\autocite{github} repository for backup.
+
+    For the development environment, I tried both Emacs~\autocite{emacs} and Visual Studio Code~\autocite{vscode} with an agda-mode extension~\autocite{agda_mode} on Windows Subsystem for Linux with Ubuntu~\autocite{wsl_ubuntu} 22.04 LTS.
 I am more familiar with the snippet and syntax highlighting features of Visual Studio Code, so I used it for most of the development.
 
-    Code from the PLFA tutorial and Agda standard library~\cite{agda_std} were used as references for implementation of the source language and the customised library.
+    Code from the PLFA tutorial and Agda standard library~\autocite{agda_std} were used as references for implementation of the source language and the customised library.
 Apart from that, the code is written from scratch.
@@
                 \hhline{|=|=|}
-                lib.agda & shared utilities (e.g. natural numbers and operations, equality, etc.) \\
-                \hline
-                source.agda & source language syntax \\
-                \hline
-                target.agda & target language (stack machine) instructions \\
-                \hline
-                compiler.agda & compiler derived from denotational semantics \\
-                \hline
-                test.agda & test cases for the compiler \\
+                \texttt{lib.agda} & shared utilities (e.g. natural numbers and operations, equality, etc.) \\
+                \hline
+                \texttt{source.agda} & source language syntax \\
+                \hline
+                \texttt{target.agda} & target language (stack machine) instructions \\
+                \hline
+                \texttt{compiler.agda} & compiler derived from denotational semantics \\
+                \hline
+                \texttt{test.agda} & test cases for the compiler \\
                 \hline
@@
         \[ \textsf{intvar} \leq: \textsf{intexp} \qquad \textsf{intvar} \leq: \textsf{intacc} \]
-        and for function types we have the contravariant subtyping:
+        since a variable can be used as an expression (e.g. $\mathsf{x} + 1$) or an acceptor (e.g. $\mathsf{x} := 1$).
+
+        For function types we have the contravariant subtyping:
         \[ A' \leq: A \land B \leq: B' \Rightarrow A \to B \leq: A' \to B' \]
@@
         We define the context as a finite list of types.
-When we are looking up a variable, the type of the variable is either on the top of the context or in the tail of the context.
-The context and the lookup judgement are defined as follows:
+When we are looking up a variable, the type of the variable is either the head of the context or in the tail of the context.
+The definition in Agda is as follows:
         \[\includegraphics[scale=1.2]{/source/contexts.pdf}\]
+        where the $\gn{\mathsf{Zero}}$ case corresponds to the situation where the variable is the head of the context, and the $\gn{\mathsf{Suc}}$ case corresponds to the situation where the variable is in the tail of the context.
 
@@
 
-        The corresponding Agda implementation is as follows, note that the Agda implementation does not include the name of the terms, but the names are included in the latex implementation for clarity:
+        The corresponding Agda implementation is as follows, note that the Agda implementation only does not include the name of the terms, as a term can be specified by how it is constructed (i.e.
+the name of the typing rules and the corresponding types)
         \[\includegraphics[scale=1.2]{/source/terms.pdf}\]
 
-        Here the definition of the integers is defined in the customised library, which is defined in~\secref{subsec: natural_numbers}.
+        Here the definition of the integers $\bZ$ is in the customised library. Please refer to~\secref{sec: lib} for more details.
 
@@
         The operational semantics of the source language is defined with renaming, substitution and reduction rules.
-However, since the compiler itself does not require the operational semantics, the implementation is included in the appendix~\ref{app: operational_semantics}.
-Operational semantics can be used to verify the correctness of the compiler in the future, but it is beyond the scope of this dissertation.
+However, since the compiler itself does not require the operational semantics, the implementation is included in Appendix~\ref{app: operational_semantics}.
+Operational semantics can be used to verify the correctness of the compiler in the future, but it is beyond the scope of this project.
 
@@
         \item 
-            $\bracket{\textsf{L}_{sd}}$: lefthand sides
-        \item 
-            $\bracket{\textsf{S}_{sd}}$: simple righthand sides
-        \item
-            $\bracket{\textsf{R}_{sd}}$: righthand sides
+            $\bracket{\textsf{L}_{sd}}$: left-hand sides
+        \item 
+            $\bracket{\textsf{S}_{sd}}$: simple right-hand sides
+        \item
+            $\bracket{\textsf{R}_{sd}}$: right-hand sides
         \item
@@
     \[\includegraphics[scale=1.2]{/target/stack_descriptor.pdf}\]
-    This requires the definition of natural numbers, which is defined in~\secref{subsec: natural_numbers}.
+    Here definition of natural numbers is in the customised library. Please refer to~\secref{sec: lib} for more details.
 
@@
     \[\includegraphics[scale=1.2]{/target/stack_descriptor_order.pdf}\]
-    This requires the definition of the order of natural numbers, which is defined in~\secref{subsec: order}.
+    Here definition of the order of natural numbers is in the customised library. Please refer to~\secref{sec: lib} for more details.
 
@@
 the subtracted displacement is less than or equal to the displacement of the current stack descriptor.
-Here we need a rigorous definition of the subtraction of natural numbers, which is defined in~\secref{subsec: subtraction}
+This leads us to the problem of defining the subtraction of natural numbers, which is explained in detail in~\secref{subsec: subtraction}
 
@@
     We can use reflexivity and transitivity of the order $<$ and $\leq$ to prove that the order of stack descriptors $\leq_s$ is a preorder. The proof is as follows:
+    \begin{proof}
+        We need to show that $\leq_s$ is reflexive and transitive. 
         \begin{itemize}
@@
                     \item 
-                    if $f < f'$, $f' = f''$ and $d \leq d'$, then $f < f''$; 
-                \item 
-                    if $f < f'$ and $f' < f''$, then $f < f''$ by transitivity of $<$;
-                \item
-                    if $f = f'$, $d \leq d'$ and $f' < f''$, then $f < f''$;
-                \item
-                    if $f = f'$, $d \leq d'$, $f' = f''$ and $d' \leq d''$, then $f = f''$ and $d \leq d''$ by transitivity of $\leq$.
+                        If $f < f'$, $f' = f''$ and $d \leq d'$, then $f < f''$; 
+                    \item 
+                        If $f < f'$ and $f' < f''$, then $f < f''$ by transitivity of $<$;
+                    \item
+                        If $f = f'$, $d \leq d'$ and $f' < f''$, then $f < f''$;
+                    \item
+                        If $f = f'$, $d \leq d'$, $f' = f''$ and $d' \leq d''$, then $f = f''$ and $d \leq d''$ by transitivity of $\leq$.
 \footnote{Note that the properties of $=$ is not required in as in the Agda definition of $\leq_s$, we directly define $f'$ to be $f$ instead of defining a equivalence relation, thus equivalence can be checked directly via type checking.}
@@
         \end{itemize}
+    \end{proof}
+
     The proof is defined in Agda as follows:
@@
 
-    Proof above requires the proof of the properties of natural numbers, which is defined in [section ref].
+    Proof above requires the proof of the properties of natural numbers, which is defined in~\secref{subsec: natural_numbers}.
 
     \subsection{Grammar}
-    The grammar of the target language is defined as follows, given the current stack descriptor $sd = \ang{f, d}$, and new stack descriptor $sd' = \ang{f', d'}$:
+    The grammar of the target language is defined as follows, given the current stack descriptor $sd = \ang{f, d}$, and new stack descriptor $sd'$ and $sd^v$:
     \[\begin{aligned}
@@
                         \begin{aligned}
-                        &\mid \bracket{\textsf{L}_{sd+\delta}} \gets \bracket{\textsf{R}_{sd}}[\delta] \text{ ; } \bracket{\textsf{I}_{sd+\delta}} \\
-                        &\mid \texttt{if } \bracket{\textsf{S}_{sd}} \bracket{\text{relational operator}} \bracket{\textsf{S}_{sd}}[\delta] \\
+                        &|{\ } \bracket{\textsf{L}_{sd+\delta}} \gets \bracket{\textsf{R}_{sd}}[\delta] \text{ ; } \bracket{\textsf{I}_{sd+\delta}} \\
+                        &|{\ } \texttt{if } \bracket{\textsf{S}_{sd}} \bracket{\text{relational operator}} \bracket{\textsf{S}_{sd}}[\delta] \\
                         & \hphantom{\mid {}} \texttt{ then } \bracket{\textsf{I}_{sd+\delta}} \texttt{ else } \bracket{\textsf{I}_{sd+\delta}} \\
-                        &\mid \texttt{adjustdisp} [\delta] \text{ ; } \bracket{\textsf{I}_{sd+\delta}} \\
+                        &|{\ } \texttt{adjustdisp} [\delta] \text{ ; } \bracket{\textsf{I}_{sd+\delta}} \\
                         \end{aligned}
                         \quad \right\} \text{if } d + \delta \geq 0  \\
-                        &{}\mid \texttt{popto } sd' \text{ ; } \bracket{\textsf{I}_{sd'}} \quad \text{when } sd' \leq_s sd \\
+                        &{}\mid{} \texttt{popto } sd' \text{ ; } \bracket{\textsf{I}_{sd'}} \quad \text{when } sd' \leq_s sd \\
     \end{aligned}\]
@@
 
-    \subsubsection{Lefthand sides, simple righthand sides and righthand sides}
-    The lefthand sides, simple righthand sides and righthand sides are straightforward, and they are defined as follows in Agda:
+    \subsubsection{Left-hand sides, simple right-hand sides and right-hand sides}
+    The left-hand sides, simple right-hand sides and right-hand sides are straightforward, and they are defined as follows in Agda:
     \[\includegraphics[scale=1.2]{/target/leftrighthand_sides.pdf}\]
@@
 To make a rigorous definition, we define $\delta$ as a natural number, and treat the positive and negative displacements as two different instructions, using addition and subtraction of stack descriptors respectively.
-Since the definition of negative displacement involves the rigorous definition of subtraction, we will discuss the subtraction of natural numbers and correpsonding implementation in~\secref{subsec: subtraction}.
+Since the definition of negative displacement involves the rigorous definition of subtraction, we will discuss the subtraction of natural numbers and corresponding implementation in~\secref{subsec: subtraction}.
 The definition (except for the negative displacement) in Agda is as follows:
@@
 
-    \section{Customised Library}
-    The customised library is a collection of types and functions centered around natural numbers, their operations and properties.
-The reason for creating a customised library is summarised in \secref{subsec: stdlib}.
-
-    \subsection{Natural numbers, integers and addition} \label{subsec: natural_numbers}
-    The definition of natural numbers, integers and addition is standard, and it is defined as follows:
-    \[\includegraphics[scale=1.2]{/lib/natural.pdf}\]
-    The use of \og{\textsf{BUILTIN}} is specifed in~\secref{subsubsec: builtin_pragma}.
-
-    \subsection{Equality, congruence and substitution}
-    The definition of equality, congruence and substitution is similar to the one in~\secref{subsec: equality}.\footnote{The definition of equality and related properties in the custom library differ slightly by using an indexed $\mb{\mathsf{Set}}$, which provides a more general formulation.
-See Appendex [corresponding link].}
-
-    \subsection{Order of natural numbers} \label{subsec: order}
-    The order of natural numbers we defined include $\leq$ and $<$, which are defined standardly as follows:
-    \[\includegraphics[scale=1.2]{/lib/order.pdf}\]
-
-    \subsection{Properties of order and addition}
-    \subsubsection{Transitivity and reflexivity}
-    The transitivity and reflexivity of the order $<$ and $\leq$ are defined as follows:
-    \[\includegraphics[scale=1.2]{/lib/order_proof.pdf}\]
-
-    \subsubsection{Implication of order}
-    We know that $\forall m, n \in \bN$, if $m < n$, then we have $m + 1 \leq n$ and $m \leq n$. This is defined in Agda as follows:
-    \[\includegraphics[scale=1.2]{/lib/order_implication.pdf}\]
+    \section{Customised Library} \label{sec: lib}
+    The customised library is a collection of types and functions centred around natural numbers, their operations and properties.
+Instead of using the standard library~\autocite{agda_std}, I implemented a customised library for the following reasons:
+    \begin{itemize}
+        \item
+            \textbf{Specialised Requirements}: The standard library's definitions (e.g.
+subtraction as monus, `$\dotdiv$') do not align with my project's need for a rigorously defined subtraction operation.
+This is specified in~\secref{subsec: subtraction}.
+        \item
+            \textbf{Verification Clarity}: By defining the basic data types and functions from scratch, I can tailor properties (e.g.
+the property `$n-[n-m] \equiv m$') to my specific requirements, and avoid unnecessary complexity (e.g.
+`$\leq$' being also defined as a boolean predicate in the standard library).
+        \item
+            \textbf{Minimal Dependencies}: Avoiding the standard library reduces external assumptions, making the project self-contained. 
+    \end{itemize}
+
+    \subsection{Definition from standard library}
+    The following is a list of definitions (or their variants) from the standard library that are used in the customised library:
+    \begin{itemize}
+        \item 
+            Natural numbers, integers and addition.
+        \item
+            Equality, congruence and substitution.
+        \item
+            Order of natural numbers, including $\leq$ and $<$.
+        \item
+            Some properties of order and addition.
+    \end{itemize}
+
+    The properties of order and addition contains the following terms summarised in the table below:
+    \begin{table}[H]
+        \centering
+        \begin{tabular}{|l|l|}
+            \hline
+            \textbf{Agda term} & \textbf{Mathematical meaning} \\
+            \hhline{|=|=|}
+            $\mb{\mathsf{\mathord{\leq}\text{-}refl}}$ & $\forall n \in \bN, n \leq n$ \\
+            \hline
+            $\mb{\mathsf{\mathord{\leq}\text{-}trans}}$ & $\forall m, n, p \in \bN, m \leq n \land n \leq p \Rightarrow m \leq p$ \\
+            \hline
+            $\mb{\mathsf{\mathord{<}\text{-}trans}}$ & $\forall m, n, p \in \bN, m < n \land n < p \Rightarrow m < p$ \\
+            \hline
+            $\mb{\mathsf{\mathord{<}\mathord{\to}s\mathord{\leq}}}$ & $\forall m, n \in \bN, m < n \Rightarrow \textsf{suc } m \leq n$ \\
+            \hline
+            $\mb{\mathsf{< \to \leq}}$ & $\forall m, n \in \bN, m < n \Rightarrow m \leq n$ \\
+            \hline
+            $\mb{\mathsf{\mathord{\leq}\text{-}irrelevance}}$ & $\forall m, n \in \bN$, we consider all proofs of $m \leq n$ to be equal \\
+            \hline
+            $\mb{\mathsf{\mathord{+}\mathord{\to}\mathord{\leq}}}$ & $\forall m, n \in \bN, m \leq m + n$ \\
+            \hline
+            $\mb{\mathsf{\mathord{+}\mathord{\to}\mathord{\leq}^r}}$ & $\forall m, n \in \bN, m \leq n + m$ \\
+            \hline
+        \end{tabular}
+        \caption{Properties of order and addition}
+        \label{tab: properties}
+    \end{table}
+
+    The detailed definitions are included in Appendix~[ref needed].
+
+    % \subsection{Natural numbers, integers and addition} \label{subsec: natural_numbers}
+    % The definition of natural numbers, integers and addition is standard, and it is defined as follows:
+    % \[\includegraphics[scale=1.2]{/lib/natural.pdf}\]
+    % The use of \og{\textsf{BUILTIN}} is specified in~\secref{subsubsec: builtin_pragma}.
+
+    % \subsection{Equality, congruence and substitution}
+    % The definition of equality, congruence and substitution is similar to the one in~\secref{subsec: equality}.\footnote{The definition of equality and related properties in the custom library differ slightly by using an indexed $\mb{\mathsf{Set}}$, which provides a more general formulation.
+See Appendix [corresponding link].}
+
+    % \subsection{Order of natural numbers} \label{subsec: order}
+    % The order of natural numbers we defined include $\leq$ and $<$, we use a simplified definition compared to the one in the standard library as follows:
+    % \[\includegraphics[scale=1.2]{/lib/order.pdf}\]
+
+    % \subsection{Properties of order and addition}
+    % \subsubsection{Transitivity and reflexivity}
+    % The transitivity and reflexivity of the order $<$ and $\leq$ are defined as follows:
+    % \[\includegraphics[scale=1.2]{/lib/order_proof.pdf}\]
+
+    % \subsubsection{Implication of order}
+    % We know that $\forall m, n \in \bN$, if $m < n$, then we have $m + 1 \leq n$ and $m \leq n$. This is defined in Agda as follows:
+    % \[\includegraphics[scale=1.2]{/lib/order_implication.pdf}\]
 
@@
 
-    \subsubsection{Other properties}
-    We can show that when a number $n$ is added to a natural number $m$, the result is greater than or equal to $m$. This is defined in Agda as follows:
-    \[\includegraphics[scale=1.2]{/lib/order_add.pdf}\]
+    % \subsubsection{Other properties}
+    % We can show that when a number $n$ is added to a natural number $m$, the result is greater than or equal to $m$. This is defined in Agda as follows:
+    % \[\includegraphics[scale=1.2]{/lib/order_add.pdf}\]
 
     \subsection{Subtraction} \label{subsec: subtraction}
-    In the standard library~\cite{agda_std}, the subtraction of natural numbers is defined as follows:\footnote{The definition in the standard library directly uses symbol $\mathsf{-}$, but here for clarity we use $\mathsf{\dotdiv}$ instead.}
+    In the standard library~\autocite{agda_std}, the subtraction of natural numbers is defined as follows:\footnote{The definition in the standard library directly uses symbol $\mathsf{-}$, but here for clarity we use $\mathsf{\dotdiv}$ instead.}
     \[\includegraphics[scale=1.2]{minus.pdf}\]
@@
     \subsubsection{Semantic category}
-    Semantic category $\mathcal{K}$ is the functor category $\text{PDOM}^{\Upsigma^{\textbf{op}}}$, where $\text{PDOM}$ is the category of predomains.
+    Semantic category $\mathcal{K}$ is the functor category $\text{PDOM}^{\Upsigma^{\textbf{op}}}$, where $\text{PDOM}$ is the category of predomains and continuous functions.
     \begin{itemize}
@@
     \end{itemize}
-    The proof for semantic category is similar to the one in~\secref{sec: ccc_presheaf}, and the full proof is given by Oles in~\cite{Oles_1},\cite{Oles_2}.
+    The proof for semantic category is similar to the one in~\secref{sec: ccc_presheaf}, and the full proof is given by Oles in~\autocite{Oles_1, Oles_2}.
     \begin{itemize}
@@
     \subsection{Continuations}
-    In Reynolds' model, we use \textsf{Compl} and \textsf{Intcompl} to represent command and integer continuations. Mathematically we have
-    \[\textsf{Compl } sd : \mathsf{SD} \to O \qquad \textsf{IntCompl } sd : \bZ \to (\mathsf{SD} \to O)\]
+    In Reynolds' model, we use $\mathsf{Compl}$ and $\mathsf{Intcompl}$ to represent command and integer continuations. Mathematically we have
+    \[\mathsf{Compl } sd : \mathsf{SD} \to O \qquad \mathsf{Intcompl } sd : \bZ \to (\mathsf{SD} \to O)\]
     where $O$ is an unspecified domain of outputs.
@@
     For code generation we define the continuation to be the instruction sequence in the target language:
-    \[\textsf{Compl } sd = \textsf{I}_{sd}\]
+    \[\mathsf{Compl } sd = \textsf{I}_{sd}\]
 
     The definition of integer continuation is more complex, it is an exponential object in the presheaf category, which is defined as follows:
-    \[\textsf{IntCompl } = R \Rightarrow_s \textsf{Compl } \]
-    where $R$ is the functor corresponding to the righthand sides in the target language, $R\ sd = \textsf{R}_{sd}$.
+    \[\mathsf{Intcompl } = R \Rightarrow_s \mathsf{Compl } \]
+    where $R$ is the functor corresponding to the right-hand sides in the target language, $R\ sd = \textsf{R}_{sd}$.
 Thus we can directly use the definition of $R$ to define the integer continuation as follows:
@@
 
-    We need to find out the denotational semantics of the terms correpsonding to all rules in the typing judgement mentioned in~\secref{subsec: terms}.
+    We need to find out the denotational semantics of the terms corresponding to all rules in the typing judgement mentioned in~\secref{subsec: terms}.
 
@@
     Compilation is a functor from the source language to the target language.
-To defrine the compilation functor, we use the denotational semantics of terms and fill in the initial stack descriptor ($\ang{0, 0}$), the empty context (\textsf{unit}), a trivial proof for stack descriptor being not less than itself (\textsf{$\leq_s$-refl}) and the continuation representing the last instruction (\textsf{stop}):
+To define the compilation functor, we use the denotational semantics of terms and fill in the initial stack descriptor ($\ang{0, 0}$), the empty context (\textsf{unit}), a trivial proof for stack descriptor being not less than itself ($\mathsf{\leq_s-refl}$) and the continuation representing the last instruction (\textsf{stop}):
     \[\includegraphics[scale=1.2]{/compiler/compilation.pdf}\]
@@
     The feature checklist includes all the typing rules in the source language, including edge cases including multiple variables, free variables and self-referential assignments.
-Aditionally, I account for target-language-specific constraints, ensuring multiple operations are translated into simple instructions with continuation.
-The tests cover all the cases in the feature checklist, ensuring that the compiler is correct and complete.
+Additionally, I account for target-language-specific constraints, ensuring multiple operations are translated into simple instructions with continuation.
+The tests cover all the cases in the feature checklist, ensuring that the compiler generates expected target code under all circumstances.
+
+    \section{Extensibility}
+    This project is inherently extensible, as all of the components are defined as terms and types in Agda.
+The compiler can be extended to support more features by adding new terms in the form of type judgement rules in the source language, adding any new instructions in the target language if needed, and write corresponding compilation rules.
 
@@
         \item 
-            Integration tests have been given in Agda, which cover all the case in the feature checklist. The tests ensure that the compiler is correct and complete.
+            Integration tests have been given in Agda, which cover all the case in the feature checklist. The tests ensure that the compiler generates expected target code under all circumstances.
     \end{itemize}
@@
     \section{Results}
-
-    \section{Overview}
+    This project has successfully implemented a compiler from a source language (STLC with store) to a target language (stack machine) in Agda.
+The compiler is defined as a functor from the source language to the target language, which is directly generated from the denotational semantics of the source language.
+The compiler validates and refines Reynolds' theory~\autocite{Reynolds}, offers a concrete example of how category-theoretic semantics can generate intermediate code.
 
     \section{Lessons learned}
-    \begin{itemize}
-        \item 
-        challenging in both theory and implementation
-
-        \item
-        struggle with different approaches
-        \item
-        struggle with inserting agda code into latex
-        \begin{itemize}
-            \item 
-                problem with unicode characters
-            \item 
-                alternative solution does not colour well due to dependent types
-        \end{itemize}
-    \end{itemize}
+    The project has been quite challenging as I have to learn both category theory and Agda from scratch, and apply them to implementation.
+The implementation process revealed unexpected gaps between Reynolds' theoretical framework and the computational realisation: while his denotational semantics provided core definitions, actualising them in Agda required formalising numbers, their operations, and properties and diagnosing and resolving type mismatches and ambiguities in the original paper~\autocite{Reynolds}.
+These hurdles highlighted how even meticulously defined theories can be complicated when translated to working systems.
+
+    In terms of planning the project, the project has deviated slightly from the original timetable in the project proposal due to differences
+    between the anticipated structure of the project and its actual development process.
+When I was drafting the proposal, I expected the workflow to be similar to a standard compiler, so I divided the work into components including basic instructions, variable declarations and conditionals, allocating two weeks for each.
+In hindsight, these components are similar term definitions, while the core of the project can be more accurately divided into three main tasks: defining the source language, defining the target language, and defining the translation between the two.
+The most time-consuming aspect of each step has been understanding their formal definitions in the paper and addressing the missing details in the Agda implementation.
+
+    Overall, the project has been a valuable learning experience, and I have gained a deeper understanding of both Category Theory and Agda and an exciting glimpse of how the correspondences between logic, type theory and category theory can be used to implement a compiler.
 
     \section{Future work}
-    \begin{itemize}
-        \item subroutine and iteration
-        \item correctness of the compiler
-        \item exploring a reasonable equational theory that can be stated directly on the instruction sequences, under which the semantics actually becomes a true functor category model (i.e.
+    The project has successfully implemented the compiler, but there are still many areas for improvement and further research:
+    \begin{itemize}
+        \item 
+            The compiler can be extended to support more features, such as subroutines and iterations.
+        \item
+            The operational semantics of the target language can be defined, which can be used, along with the operational semantics of the source language, to prove the correctness of the compiler.
+        \item
+            Reynolds pointed out that the requirement of instructions being natural transformation must be relaxed to allow for instruction sequences that differ operationally but are equivalent in terms of denotational semantics~\autocite[Ch.
+6]{Reynolds}.
+Extra research can be done to develop a reasonable equational theory that can be stated directly on the instruction sequences, under which the semantics actually becomes a true functor category model (i.e.
 naturality holds).
     \end{itemize}
+
 \printbibliography

### 2025-05-12 fig/implementation/dependencies.tex
Evaluation almost done
Evaluation and conclusion almost completed

@@
 		% Nodes
-		\node (lib) {lib.agda};
-		\node[below left=of lib] (source) {source.agda};
-		\node[below right=of lib] (target) {target.agda};
-		\node[below left=of target] (compiler) {compiler.agda};
+		\node (lib) {\texttt{lib.agda}};
+		\node[below left=of lib] (source) {\texttt{source.agda}};
+		\node[below right=of lib] (target) {\texttt{target.agda}};
+		\node[below =of lib] (compiler) {\texttt{compiler.agda}};
+		\node[below =of compiler] (test) {\texttt{test.agda}};
 
 		% Arrows
-		\draw[arrow] (lib) -- (source);
-		\draw[arrow] (lib) -- (target);
-		\draw[arrow] (source) -- (compiler);
-		\draw[arrow] (target) -- (compiler);
-		\draw[arrow] (lib) -- (compiler);
+		\draw[arrow] (source) -- (lib);
+		\draw[arrow] (target) -- (lib);
+		\draw[arrow] (compiler) -- (source);
+		\draw[arrow] (compiler) -- (target);
+		\draw[arrow] (compiler) -- (lib);
+		\draw[arrow] (test) -- (source);
+		\draw[arrow] (test) -- (target);
+		\draw[arrow] (test) -- (compiler);
 

### 2025-05-13 draft.tex
draft completed

@@
 
-\newcommand{\bracket}[1]{\left\{ #1 \right\}}
+\newcommand{\bracket}[1]{\mathord{<} #1 \mathord{>}}
 \newcommand{\ang}[1]{\left\langle #1 \right\rangle}
@@
         \subsection{Category}
-        \begin{definition}[Category]
+        \begin{definition}[Category] \label{def: category}
             A \emph{category} $\mathcal{C}$ is specified by
@@
 
-            \begin{definition}[Opposite category]
+            \begin{definition}[Opposite category] \label{def: opposite}
                 Given a category $\mathcal{C}$, its \emph{opposite category} $\mathcal{C}^{\textbf{op}}$ is specified by the following:
@@
         \subsection{Functor}
-        \begin{definition}[Functor]
+        \begin{definition}[Functor] \label{def: functor}
             Given two categories $\mathcal{C}$ and $\mathcal{D}$, a \emph{functor} $F: \mathcal{C} \to \mathcal{D}$ is specified by
@@
                 \item 
-                    a function 
+                    a function referred to as object mapping
                     \[\begin{aligned}
@@
                 \item 
-                    for each $X, Y \in \textbf{obj}(\mathcal{C})$, a function 
+                    for each $X, Y \in \textbf{obj}(\mathcal{C})$, a function referred to as functorial mapping
                     \[\begin{aligned}
@@
         \subsection{Yoneda lemma}
-        \begin{definition}[Yoneda functor]
+        \begin{definition}[Yoneda functor] \label{def: yoneda}
             Given a category $\mathcal{C}$, the \emph{Yoneda functor} $\yo: \mathcal{C} \to \hat{\mathcal{C}}$ is defined as follows:
@@
 Then it discusses the specification of the source language, and the target language, which lead us to the problem of implementing a rigorous natural number subtraction and two different approaches.
-We will further see the difference between the two approaches and how they affect the implementation of the customised library and the implementation of the compiler.
+It further reveals the difference between the two approaches and how they affect the implementation of the customised library.
+Finally a detailed implementation of the compiler is presented.
 
@@
 
-        Here the definition of the integers $\bZ$ is in the customised library. Please refer to~\secref{sec: lib} for more details.
-
         \subsection{Operational Semantics}
@@
     \end{itemize}
+    The intent of the indexing here is any instructions with the form $\bracket{\textsf{I}_{sd}}$ is an instruction sequence that can be executed when the current stack descriptor is $sd$.
 
@@
     \[\includegraphics[scale=1.2]{/target/stack_descriptor.pdf}\]
-    Here definition of natural numbers is in the customised library. Please refer to~\secref{sec: lib} for more details.
 
@@
     \subsubsection{Order}
-    The stack descriptor is ordered lexicographically with $\leq_s$ as follows:
-    \[\ang{f, d} \leq_s \ang{f', d'} \Leftrightarrow f < f' \lor (f = f' \land d \leq d')\]
+    The stack descriptor is ordered lexicographically with $\leq_\mathsf{s}$ as follows:
+    \[\ang{f, d} \leq_\mathsf{s} \ang{f', d'} \Leftrightarrow f < f' \lor (f = f' \land d \leq d')\]
 
@@
     For subtraction, we need to make sure that the subtraction is valid, i.e.
-the subtracted displacement is less than or equal to the displacement of the current stack descriptor.
+the subtracted displacement adjustment is less than or equal to the displacement of the current stack descriptor.
 This leads us to the problem of defining the subtraction of natural numbers, which is explained in detail in~\secref{subsec: subtraction}
@@
     \subsubsection{Properties of order and addition}
-    We can use reflexivity and transitivity of the order $<$ and $\leq$ to prove that the order of stack descriptors $\leq_s$ is a preorder. The proof is as follows:
+    We can use reflexivity and transitivity of the order $<$ and $\leq$ to prove that the order of stack descriptors $\leq_\mathsf{s}$ is a preorder. The proof is as follows:
     \begin{proof}
-        We need to show that $\leq_s$ is reflexive and transitive. 
-        \begin{itemize}
-            \item 
-                Reflexivity: $sd \leq_s sd$ is trivially true since $f = f$ and $d \leq d$.
-            \item
-                Transitivity: if $\ang{f, d} \leq_s \ang{f', d'}$ and $\ang{f', d'} \leq_s \ang{f'', d''}$, we do the following case split:
+        We need to show that $\leq_\mathsf{s}$ is reflexive and transitive. 
+        \begin{itemize}
+            \item 
+                Reflexivity: $sd \leq_\mathsf{s} sd$ is trivially true since $f = f$ and $d \leq d$.
+            \item
+                Transitivity: if $\ang{f, d} \leq_\mathsf{s} \ang{f', d'}$ and $\ang{f', d'} \leq_\mathsf{s} \ang{f'', d''}$, we do the following case split:
                 \begin{itemize}
@@
                         If $f = f'$, $d \leq d'$, $f' = f''$ and $d' \leq d''$, then $f = f''$ and $d \leq d''$ by transitivity of $\leq$.
-\footnote{Note that the properties of $=$ is not required in as in the Agda definition of $\leq_s$, we directly define $f'$ to be $f$ instead of defining a equivalence relation, thus equivalence can be checked directly via type checking.}
+\footnote{Note that the properties of $=$ is not required in as in the Agda definition of $\leq_\mathsf{s}$, we directly define $f'$ to be $f$ instead of defining a equivalence relation, thus equivalence can be checked directly via type checking.}
                 \end{itemize}
@@
 
-    Proof above requires the proof of the properties of natural numbers, which is defined in~\secref{subsec: natural_numbers}.
+    Proofs here are based on the properties of natural numbers specified in the customised library. Please refer to~\secref{sec: lib} for more details.
 
@@
     The grammar of the target language is defined as follows, given the current stack descriptor $sd = \ang{f, d}$, and new stack descriptor $sd'$ and $sd^v$:
+    \begin{figure}[H]
+        \centering
         \[\begin{aligned}
-        \bracket{\textsf{L}_{sd}} ::={}& sd^v \quad \text{when } sd^v \leq_s sd \\
+            \bracket{\textsf{L}_{sd}} ::={}& sd^v \quad \text{when } sd^v \leq_\mathsf{s} sd \\
                             &\mid \texttt{sbrs}  \\
             \bracket{\textsf{S}_{sd}} ::={}& \bracket{\textsf{L}_{sd}} \\
-                        &\mid \texttt{lit} \bracket{\text{integer}} \\
+                            &\mid \texttt{lit } \bracket{\text{integer}} \\
             \bracket{\textsf{R}_{sd}} ::={}& \bracket{\textsf{S}_{sd}} \\
@@
                             \begin{aligned}
-                        &|{\ } \bracket{\textsf{L}_{sd+\delta}} \gets \bracket{\textsf{R}_{sd}}[\delta] \text{ ; } \bracket{\textsf{I}_{sd+\delta}} \\
+                            &|{\ } \bracket{\textsf{L}_{sd+\delta}} := \bracket{\textsf{R}_{sd}}[\delta] \text{ ; } \bracket{\textsf{I}_{sd+\delta}} \\
                             &|{\ } \texttt{if } \bracket{\textsf{S}_{sd}} \bracket{\text{relational operator}} \bracket{\textsf{S}_{sd}}[\delta] \\
@@
                             \quad \right\} \text{if } d + \delta \geq 0  \\
-                        &{}\mid{} \texttt{popto } sd' \text{ ; } \bracket{\textsf{I}_{sd'}} \quad \text{when } sd' \leq_s sd \\
+                            &{}\mid{} \texttt{popto } sd' \text{ ; } \bracket{\textsf{I}_{sd'}} \quad \text{when } sd' \leq_\mathsf{s} sd \\
         \end{aligned}\]
+        \caption{Target language grammar}
+        \label{fig: target_grammar}
+    \end{figure}
+    Some explanations of the grammar are as follows:
+    \begin{itemize}
+        \item 
+            $\texttt{sbrs}$: a register used to communicate the result of function procedures implemented by closed subroutines.
+        \item 
+            $\texttt{lit}$: a literal integer.
+        \item 
+            $\texttt{stop}$: stop the execution of the program.
+        \item 
+            $\delta$: a displacement adjustments, which can be any integer that satisfies the condition mentioned above.
+        \item 
+            $\texttt{adjustdisp}$: adjust the displacement of specified stack descriptor.
+        \item 
+            $\texttt{popto}$: pop to the specified stack descriptor, which is used to reduce the number of frames.
+    \end{itemize}
+    Note that the design of right-hand sides ensures that the right operand of the assignment contains at most one operator, which means that any instruction that involves multiple operators must be divided into multiple instructions.
+This feature of the target language significantly complicates the compilation of integer expressions, which we will analysis in detail in~\secref{subsubsec: compiler_intexp}.
 
@@
     \subsubsection{Instruction sequences}
-    In the instruction sequences, $\delta$ as a displacement can be either positive or negative.
+    In the instruction sequences, $\delta$ as a displacement adjustment can be positive, zero or negative.
 To make a rigorous definition, we define $\delta$ as a natural number, and treat the positive and negative displacements as two different instructions, using addition and subtraction of stack descriptors respectively.
@@
     \subsection{Definition from standard library}
-    The following is a list of definitions (or their variants) from the standard library that are used in the customised library:
-    \begin{itemize}
-        \item 
-            Natural numbers, integers and addition.
-        \item
-            Equality, congruence and substitution.
-        \item
-            Order of natural numbers, including $\leq$ and $<$.
+    The following is a list of definitions (or their variants) from the standard library and PLFA~\cite{plfa} that are used in the customised library:
+    \begin{itemize}
+        \item 
+            Natural numbers ($\mb{\bN}$), integers ($\mb{\bZ}$) and addition ($\mb{+}$).
+        \item
+            Equality ($\mb{\equiv}$), congruence ($\mb{\mathsf{cong}}$), substitution ($\mb{\mathsf{sub}}$) and transitivity of equality ($\mb{\mathsf{trans}}$).
+        \item
+            Order of natural numbers, including $\mb{\leq}$ and $\mb{<}$.
         \item
@@
             \hhline{|=|=|}
-            $\mb{\mathsf{\mathord{\leq}\text{-}refl}}$ & $\forall n \in \bN, n \leq n$ \\
-            \hline
-            $\mb{\mathsf{\mathord{\leq}\text{-}trans}}$ & $\forall m, n, p \in \bN, m \leq n \land n \leq p \Rightarrow m \leq p$ \\
-            \hline
-            $\mb{\mathsf{\mathord{<}\text{-}trans}}$ & $\forall m, n, p \in \bN, m < n \land n < p \Rightarrow m < p$ \\
-            \hline
-            $\mb{\mathsf{\mathord{<}\mathord{\to}s\mathord{\leq}}}$ & $\forall m, n \in \bN, m < n \Rightarrow \textsf{suc } m \leq n$ \\
-            \hline
-            $\mb{\mathsf{< \to \leq}}$ & $\forall m, n \in \bN, m < n \Rightarrow m \leq n$ \\
-            \hline
-            $\mb{\mathsf{\mathord{\leq}\text{-}irrelevance}}$ & $\forall m, n \in \bN$, we consider all proofs of $m \leq n$ to be equal \\
-            \hline
-            $\mb{\mathsf{\mathord{+}\mathord{\to}\mathord{\leq}}}$ & $\forall m, n \in \bN, m \leq m + n$ \\
-            \hline
-            $\mb{\mathsf{\mathord{+}\mathord{\to}\mathord{\leq}^r}}$ & $\forall m, n \in \bN, m \leq n + m$ \\
+            $\mb{+\text{-}\mathsf{identity^r}}$ & $\forall n \in \bN.\ n + 0 = n$ \\
+            \hline
+            $\mb{+\text{-}\mathsf{suc^r}}$ & $\forall m, n \in \bN.\ m + \textsf{suc } n = \textsf{suc } (m + n)$ \\
+            \hline
+            $\mb{+\text{-}\mathsf{comm}}$ & $\forall m, n \in \bN.\ m + n \equiv n + m$ \\
+            \hline
+            $\mb{\mathsf{\mathord{\leq}\text{-}irrelevant}}$ & For all $m, n \in \bN$, we consider all proofs of $m \leq n$ to be equal. \\
+            \hline
+            $\mb{\mathsf{\mathord{\leq}\text{-}refl}}$ & $\forall n \in \bN.\ n \leq n$ \\
+            \hline
+            $\mb{\mathsf{\mathord{\leq}\text{-}trans}}$ & $\forall m, n, p \in \bN.\ m \leq n \land n \leq p \Rightarrow m \leq p$ \\
+            \hline
+            $\mb{\mathsf{n\mathord{\leq}suc\text{-}n}}$ & $\forall n \in \bN.\ n \leq \textsf{suc } n$ \\
+            \hline
+            $\mb{\mathsf{m\mathord{\equiv}n,p\mathord{\leq}n\mathord{\to}p\mathord{\leq}m}}$ & $\forall p, m, n \in \bN.\ m \equiv n \land p \leq n \Rightarrow p \leq m$ \\
+            \hline
+            $\mb{\mathsf{\mathord{+}\mathord{\to}\mathord{\leq}}}$ & $\forall m, n \in \bN.\ m \leq m + n$ \\
+            \hline
+            $\mb{\mathsf{\mathord{+}\mathord{\to}\mathord{\leq}^r}}$ & $\forall m, n \in \bN.\ m \leq n + m$ \\
+            \hline
+            $\mb{\mathsf{\mathord{<}\text{-}trans}}$ & $\forall m, n, p \in \bN.\ m < n \land n < p \Rightarrow m < p$ \\
+            \hline
+            $\mb{\mathsf{\mathord{<}\mathord{\to}s\mathord{\leq}}}$ & $\forall m, n \in \bN.\ m < n \Rightarrow \textsf{suc } m \leq n$ \\
+            \hline
+            $\mb{\mathsf{< \to \leq}}$ & $\forall m, n \in \bN.\ m < n \Rightarrow m \leq n$ \\
             \hline
@@
 
-    The detailed definitions are included in Appendix~[ref needed].
+    The detailed definitions are included in Appendix~[TBD].
 
@@
 
-    \subsubsection{Totality of order}
+    \subsubsection{Totality of order} \label{subsubsec: order_totality}
     It is useful to case split the order of natural numbers, i.e.
@@
     \subsubsection{\textsf{Fin}-based approach}
-    Instead of include the proof directly, we can define the type of the subtrahend as a type that depends on the minuend, where the type encodes the proof.
+    Instead of include the proof directly, we can define the type of the subtrahend to be dependent on the minuend, where the dependence encodes the proof.
 There is a standard library in Agda on finite sets, where a type $\mb{\mathsf{Fin}}$ is defined as a type that depends on a natural number $n$, where $\mb{\mathsf{Fin}}\ n$ can be seen as the set of natural numbers less than $n$.
@@
     \begin{itemize}
-        \item Base case: when $n = 0$, there is no element less than $0$, so we do not have any constructor that gives us an element of type $\mb{\mathsf{Fin}}\ 0$. 
+        \item Base case: when $n = 0$, we do not have any constructor that gives us an element of type $\mb{\mathsf{Fin}}\ 0$, corresponding to the empty set. 
         \item Inductive case: 
@@
             \centering
-            \includegraphics[width=0.35\textwidth]{fin_inductive.pdf}
+            \includegraphics[width=0.5\textwidth]{fin_inductive.pdf}
             \caption{Inductive case of $\mb{\mathsf{Fin}}$}
@@
     The explicit approach carries proofs directly in the type system, which is more transparent but verbose.
-The $\textsf{Fin}$-based approach intially appears to be more elegant, as it encapsulates bounds check within a refined type.
+The $\textsf{Fin}$-based approach initially appears to be more elegant, as it encapsulates bounds check within a refined type.
 However, this elegance is superficial: constructing a term of type $\mb{\mathsf{Fin}}\ n$ still requires the same underlying proof of boundedness, shifting complexity to auxiliary conversions.
@@
 
-    \subsection{More properties of natural numbers}
-    The following are some properties of natural numbers that are useful for the implementation of the compiler with corresponding proofs.
-
-    The implementation of the properties of natural numbers in Agda is as follows:
-    \begin{figure}[H]
-        \centering
-        \includegraphics[scale=1.2]{/lib/proof/properties.pdf}
+    \subsection{More properties of natural numbers} \label{subsec: more_properties}
+    Given the definition of subtraction, the additional properties of natural numbers are summarised in the table below:
+    \begin{table}[H]
+        \centering
+        \begin{tabular}{|l|l|}
+            \hline
+            \textbf{Agda term} & \textbf{Mathematical meaning} \\
+            \hhline{|=|=|}
+            $\mb{\mathsf{-\text{-}irrelevant}}$ & \makecell{For all $m, n \in \bN$, we consider all terms of $n-m$ \\ with different proofs of $m \leq n$ to be equal.} \\
+            \hline
+            $\mb{\mathsf{\mathord{-}\mathord{\to}\mathord{\leq}}}$ & $\forall m, n \in \bN.\ m \leq n \Rightarrow m - n \leq m$ \\
+            \hline
+            $\mb{\mathsf{n\mathord{-}n\mathord{\equiv}0}}$ & $\forall n \in \bN.\ n - n \equiv 0$ \\
+            \hline
+            $\mb{\mathsf{\mathord{-}\text{-}suc}}$ & $\forall m, n \in \bN.\ \mathsf{suc}\ (n - m) \equiv \mathsf{suc}\ n - m$ \\
+            \hline
+            $\mb{\mathsf{n\mathord{-}[n\mathord{-}m]\mathord{\equiv}m}}$ & $\forall m, n \in \bN.\ m \leq n \Rightarrow n - (n - m) \equiv m$ \\
+            \hline
+            $\mb{\mathsf{n\mathord{+}m\mathord{-}m\mathord{\equiv}n}}$ & $\forall m, n \in \bN.\ n + m - m \equiv n$ \\
+            \hline
+            $\mb{\mathsf{suc\text{-}d\mathord{\leq}d'\mathord{\to}d'\mathord{-}[d'\mathord{-}[suc\text{-}d]]}}$ & $\forall d, d' \in \bN.\ \textsf{suc } d \leq d' \Rightarrow d \leq d' - (d' - \textsf{suc } d)$ \\
+            \hline
+        \end{tabular}
         \caption{Properties of natural numbers related to subtraction}
-        \label{fig: properties_subtraction}
-    \end{figure}
+        \label{tab: properties_subtraction}
+    \end{table}
+
+    The equations in the table above are used later in the implementation of the compiler to prove that for instructions with displacement, the given displacement is valid.
+Here is the mathematical proof of the property $\mb{\mathsf{n\mathord{-}[n\mathord{-}m]\mathord{\equiv}m}}$:
+    \begin{proof}
+        We need to show that $n - (n - m) \equiv m$ for all $m, n \in \bN$ such that $m \leq n$. We do the following case split:
+        \begin{itemize}
+            \item 
+                If $m = 0$, then the term reduces to $n - n \equiv 0$, which is a term we have already proved.
+            \item
+                Otherwise it is guaranteed that $m = \mathsf{suc}\ m'$ for some $m' \in \bN$, and $n = \mathsf{suc}\ n'$ for some $n' \in \bN$, because $m \leq n$.
+The term reduces to $\mathsf{suc}\ n' - (n' - m') \equiv \mathsf{suc}\ m'$.
+With congruence, we can reduce the term to $n' - (n' - m') \equiv m'$, which is the inductive hypothesis.
+        \end{itemize}
+    \end{proof}
+    The full implementation of the properties is included in Appendix~[TBD].
+
+    % The implementation of the properties of natural numbers in Agda is as follows:
+    % \begin{figure}[H]
+    %     \centering
+    %     \includegraphics[scale=1.2]{/lib/proof/properties.pdf}
+    %     \caption{Properties of natural numbers related to subtraction}
+    %     \label{fig: properties_subtraction}
+    % \end{figure}
 
@@
     \begin{itemize}
-        \item Objects are stack descriptors ($sd = \ang{f, d}$)
-        \item Morphisms are stack expansions ($\iota : sd \to sd'$ for $sd \leq_s sd'$) 
+        \item Objects are stack descriptors ($sd = \ang{f, d}$);
+        \item Morphisms are stack expansions ($\iota : sd \to sd'$ for $sd \leq_\mathsf{s} sd'$).
     \end{itemize}
     We define $\mathsf{SD}$ as the set of stack descriptors.
-Then the base category is the category determined by preorder $\underline{\mathsf{SD}} = \{\mathsf{SD}, \leq_s\}$ in Example~\ref{ex: category_preorder}.
+Then the base category is the category determined by preorder $\underline{\mathsf{SD}} = \{\mathsf{SD}, \leq_\mathsf{s}\}$ in Example~\ref{ex: category_preorder}.
 
@@
     \begin{itemize}
-        \item Objects are presheaves: $P = \Upsigma^{\textbf{op}} \to \text{PDOM}$.
+        \item Objects are presheaves: $P = \Upsigma^{\textbf{op}} \to \text{PDOM}$;
         \item Morphisms are natural transformations: $\eta : P \to Q$ for $P, Q \in \text{PDOM}^{\Upsigma^{\textbf{op}}}$.
@@
                     P \Rightarrow_s Q &= \lambda sd.\ \mathcal{K}(\yo (sd) \times P, Q) \\
-                    &\cong \lambda sd.\{F \mid sd' \in \Upsigma, F : (\yo (sd) \times P)\ sd' \to Q\ sd'\} \\
+                    &\cong \lambda sd.\{F \mid sd' \in \Upsigma^{\textbf{op}}, F : (\yo (sd) \times P)\ sd' \to Q\ sd'\} \\
+                    &\makebox[0.8\linewidth][r]{\text{by definition of morphisms in Definition~\ref{def: category}}}\\
+                    &\cong \lambda sd.\{F \mid sd' \in \Upsigma^{\textbf{op}}, F : (\Upsigma^{\textbf{op}}(sd', sd) \times P)\ sd' \to Q\ sd'\} \\
+                    &\makebox[0.8\linewidth][r]{\text{by definition of $\yo$ in Definition~\ref{def: yoneda}}}\\
                     &\cong \lambda sd.\{F \mid sd' \in \Upsigma, F : (\Upsigma(sd, sd') \times P)\ sd' \to Q\ sd'\} \\
-                    &\cong \lambda sd.\{F \mid sd' \in \Upsigma, F : sd \leq_s sd' \to P\ sd' \to Q\ sd'\}
+                    &\makebox[0.8\linewidth][r]{\text{by definition of opposite category in Definition~\ref{def: opposite}}}\\
+                    &\cong \lambda sd.\{F \mid sd' \in \Upsigma, F : sd \leq_\mathsf{s} sd' \to P\ sd' \to Q\ sd'\} \\
+                    &\makebox[0.8\linewidth][r]{\text{by definition of $\Upsigma$ above}}\\
                 \end{aligned}
@@
     \end{itemize}
-    [need support for each step of the proof]
 
@@
 
-    We have a functor $\intp{-} : \Theta \to \mathcal{K}$, that interprets the type constructor $\to$ as the exponential functor $\Rightarrow_s$.
+    The definition of exponentials captures the essence of stack-respecting computations in the compiler. 
+    \begin{itemize}
+        \item $sd \leq_\mathsf{s} sd'$ means the new stack descriptor $sd'$ is larger than the old stack descriptor $sd$, representing the dynamic expansion of the stack during execution.
+
+        \item $P$ and $Q$ are denotational semantics of types. 
+    \end{itemize}
+    The exponential $P \Rightarrow_\textsf{s} Q$ is a function that given a proof of stack growth, transforming a $P$-value at $sd'$ into a $Q$-value at $sd'$, and the $\forall{sd'}$ quantifier guarantees it works no matter how the stack grows.
+It is designed in this way so that a functor $\intp{-} : \Theta \to \mathcal{K}$ exists that interprets the type constructor $\Rightarrow$ as the exponential functor $\Rightarrow_s$.
 
     \subsection{Continuations}
-    In Reynolds' model, we use $\mathsf{Compl}$ and $\mathsf{Intcompl}$ to represent command and integer continuations. Mathematically we have
-    \[\mathsf{Compl } sd : \mathsf{SD} \to O \qquad \mathsf{Intcompl } sd : \bZ \to (\mathsf{SD} \to O)\]
+    In Reynolds' model, we construct $\mathsf{Compl}$ and $\mathsf{Intcompl}$\footnote{In the work of Reynolds, $\mathsf{compl}$ and $\mathsf{intcompl}$ are introduced as new types in the source language, and the definitions here are the denotational semantics of those types, respectively.
+Since these two introduced types are only used for the denotational semantics, I think directly defining them as denotational semantics constructs is natural and sufficient.} as tools in the denotational semantics to represent command continuations and integer continuations, respectively.
+We can think of integer continuations as a function that takes an integer and returns a command continuation.
+Mathematically we have
+    \[\mathsf{Compl}\ sd : \mathsf{SD} \to O \qquad \mathsf{Intcompl}\ sd : \bZ \to (\mathsf{SD} \to O)\]
     where $O$ is an unspecified domain of outputs.
@@
     For code generation we define the continuation to be the instruction sequence in the target language:
-    \[\mathsf{Compl } sd = \textsf{I}_{sd}\]
-
-    The definition of integer continuation is more complex, it is an exponential object in the presheaf category, which is defined as follows:
-    \[\mathsf{Intcompl } = R \Rightarrow_s \mathsf{Compl } \]
+    \[\mathsf{Compl}\ sd = \textsf{I}_{sd}\]
+
+    The definition of integer continuation is an exponential object in the presheaf category, which is defined as follows:
+    \[\mathsf{Intcompl} = R \Rightarrow_s \mathsf{Compl} \]
     where $R$ is the functor corresponding to the right-hand sides in the target language, $R\ sd = \textsf{R}_{sd}$.
-Thus we can directly use the definition of $R$ to define the integer continuation as follows:
+This works because the right-hand sides are all integer expressions we can use according to the grammar of the target language.
+
+    Thus we can directly use the definition of $R$ in the target language to define the integer continuation as follows:
     \[\includegraphics[scale=1.2]{/compiler/continuations.pdf}\]
 
-    \subsection{Denotational semantics of types and contexts}
-    Given the definition of continuations, we can define the denotational semantics of types in Agda as follows:
+    \subsection{Denotational semantics of types and contexts} \label{subsec: type_interpretation}
+    With the idea of continuation, the denotational semantics of types can be defined as follows:
+    \begin{itemize}
+        \item Command passes on command continuations;
+        \item Integer expressions takes an integer continuation and returns a command continuation;
+        \item Integer acceptors take a command continuation and returns an integer continuation;
+        \item Integer variables can be used both as an integer expression and an integer acceptor, so it has the denotational semantics of both, defined as a product of the two.
+    \end{itemize}
+
+    The denotational semantics of types in Agda as follows:
     \[\includegraphics[scale=1.2]{/compiler/type_interpretation.pdf}\]
@@
     The denotational semantics of contexts is essentially a list expressed by the product of the denotational semantics of the types in the context.
-The denotational semantics of contexts is defined as follows, where we use $\emptyset$ to denote the denotational semantics of the empty context:
+The denotational semantics of contexts is defined as follows, where we use $\mb{\varnothing}$ to denote the denotational semantics of the empty context:
     \[\includegraphics[scale=1.2]{/compiler/context_interpretation.pdf}\]
 
-    \subsection{Morphisms: functorial mapping}
+    \subsection{Functorial mapping}
+    The denotational semantics of terms is defined as a functor, defined in~\secref{def: functor}.
+Before we define its object mapping, we need to define the functorial mapping, which acts on the morphisms of the base category $\Upsigma$.
+
+    Since the morphisms of the base category $\Upsigma$ are stack expansions, the functorial mapping essentially lifts a semantic object indexed by a stack descriptor $sd$ to a semantic object indexed by a larger stack descriptor $sd'$.
+This ensures the denotational semantics of terms remains valid when the stack grows.
+
+    \subsubsection{Functorial mapping for exponentials, products, contexts and types}
+    Functorial mapping for exponentials is simple, as the original exponential can transforms a $P$-value at any $sd'$ greater than $sd''$ into a $Q$-value at $sd'$.
+To construct a new exponential, we simply take a new $P$-value at $ad''$ which is greater than $sd'$, and use the original exponential to transform it into a $Q$-value at $sd'$, as $sd''$ is guaranteed to be greater than $sd$ due to the transitivity of order of the stack descriptors.
+
+    Functorial mapping for products is defined pointwise.
+
+    Thus, functorial mapping of types can be defined simply use the definition of functorial mapping of products and exponentials, as denotational semantics of types is defined as either product or exponential.
+As a list of types, the functorial mapping of contexts is simply a map of the functorial mapping of types in the list.
+The definition of functorial mapping in Agda is as follows:
     \[\includegraphics[scale=1.2]{/compiler/fmap_ctx.pdf}\]
-    Similarly, this functorial mapping also holds for \textsf{L} and \textsf{S} in the target language. The functorial mapping is defined as follows:
+
+    \subsubsection{Functoral mapping for left-hand sides and simple right-hand sides}
+    Similarly, we can use transitivity of order to define the functorial mapping of the denotational semantics of left-hand sides, as the definition of left-hand sides requires a proof.
+Since simple right-hand sides are defined from left-hand sides and literals
     \[\includegraphics[scale=1.2]{/compiler/fmap_LS.pdf}\]
+
+    \subsubsection[Functorial mapping for instruction sequences]{Functorial mapping for instruction sequences\footnote{In the work of Reynolds, the functorial mapping of instruction sequences is presented as the functorial mapping of $\mathsf{Compl}$.
+The two definitions are equivalent as we define $\mathsf{Compl}\ sd = \textsf{I}_{sd}$.
+However, I think it is more natural to present it as the functorial mapping of instruction sequences, as the definition consists of instruction sequences.}}
+    The functorial mapping of the denotational semantics of instruction sequences is defined as follows, assuming the stack descriptor $sd' = \ang{f',d'}$ is greater than $sd = \ang{f,d}$:
+    \begin{itemize}
+        \item When $f < f'$, we use the $\mathsf{popto}$ instruction that directly pops the stack to $sd$;
+        \item When $f' = f$ and $d < d'$, we use $\mathsf{adjustdisp}$ to decrease the displacement by $d'-d$.
+    \end{itemize}
+    In the Agda implementation, we also need to show that after the the adjustment, the stack descriptor is now $sd$.
+This requires the term $\mb{\mathsf{n\mathord{-}[n\mathord{-}m]\mathord{\equiv}m}}$ proved in~\secref{subsec: more_properties}.
+The functorial mapping of the denotational semantics of instruction sequences is defined as follows:
+    \[\includegraphics[scale=1.2]{/compiler/fmap_instruction.pdf}\]
 
@@
         \subsubsection{Variables}
-        The denotational semantics of variables is defined as follows:
+        We define an auxiliary function that simply gets the variable from the list of variables (the context), and the denotational semantics of variables is given by applying this function:
         \[\includegraphics[scale=1.2]{/compiler/term_var.pdf}\]
@@
         \subsubsection{Subtyping}
-        The denotational semantics of subtyping is defined as follows:
+        The idea of subtyping is to use a term of type $A$ as a term of type $A'$, where $A$ is a subtype of $A'$.
+We define an auxiliary function that takes in the subtype relation $A\leq:A'$ and the denotational semantics of $A$, and returns the denotational semantics of $A'$.
+        \begin{itemize}
+            \item For integer variables as subtypes of integer expressions and integer acceptors, since we defined the denotational semantics of integer variable as product of the denotational semantics of integer expression and integer acceptor in~\secref{subsec: type_interpretation}, I can simply use the projection to get the denotational semantics of either side.
+            \item For reflexivity, we simply use the identity function.
+            \item For transitivity, we use the composition of the two functions.
+            \item For contravariant function subtyping, we use a contravariant function.
+        \end{itemize}
+        The denotational semantics of subtyping is given by applying the auxiliary function:
         \[\includegraphics[scale=1.2]{/compiler/term_subtype.pdf}\]
@@
         \subsubsection{Lambda abstraction}
+        \begin{itemize}
+            \item For lambda, we need to extend the context $\gamma$ with the extra variable in the lambda term. This is done by using the functorial mapping of the denotational semantics of contexts.
+            \item For application, we simply apply the denotational semantics of the lambda term to the denotational semantics of the argument, where the proof is simply the reflexivity of the order of stack descriptors.
+        \end{itemize}
         The denotational semantics of lambda abstraction is defined as follows:
@@
         \subsubsection{Commands}
+        \begin{itemize}
+            \item For skip, we simply return the continuation $\kappa$ without changing it.
+            \item For sequence, we need to prefix the continuation with the denotational semantics of the second command, and then prefix it with the denotational semantics of the first command, as the continuation $\kappa$ is to be performed after both commands.
+            \item For assignment, the definition is similar to sequence, as we need to prefix the continuation with the denotational semantics of the integer accepter and then prefix it with the denotational semantics of the integer expression.
+        \end{itemize}
         The denotational semantics of commands is defined as follows:
         \[\includegraphics[scale=1.2]{/compiler/term_comm.pdf}\]
-        The command \textsf{NewVar} is slightly more complicated, [To complete].
-
-        \subsubsection{Integer expressions}
+
+        The denotational semantics of new variable is more complicated.
+We first place a new variable in the stack with the current stack descriptor $sd'$ by assigning literal $0$ with the current stack descriptor $sd'$ and set the displacement adjustment to $1$, which corresponds to the place taken by this new variable.
+Then we do the command in \textsf{NewVar}, deallocate the new variable and do the rest of the commands in the continuation by applying the denotational semantics of the command in \textsf{NewVar} to an $\mathsf{adjustdisp}$ instruction that adjusts the displacement by $-1$, followed by the continuation $\kappa$.
+Here the new stack descriptor used is $sd' +_s 1$.
+The new environment (denotational semantics of context) $\gamma'$ is the old environment $\gamma$ with the denotational semantics of the new variable added.
+
+        The denotational semantics of the new variable is a product of the denotational semantics of an integer expression and the denotational semantics of an integer acceptor by definition in~\secref{subsec: type_interpretation}.
+        \begin{itemize}
+            \item The expression component fills the a given integer continuation $\beta$ with the stack descriptor for the new variable;
+            \item The acceptor component prefixes the continuation $\kappa$ with an assignment of the new variable.
+        \end{itemize}
+
+        Please see Appendix~[TBD] for the full implementation of the function \textsf{NewVar}.
+
+        \subsubsection{Integer expressions} \label{subsubsec: compiler_intexp}
+        \begin{itemize}
+            \item For integer literals, we simply fill in the integer literal (as an $\mathsf{R}$ term) to the integer continuation $\beta$.
+            \item For plus and negation, we wish to fill the negation of the given expression or the sum of the two given expressions to the integer continuation $\beta$.
+However, this is only possible when the given expression(s) are simple left-hand sides, as the grammar of the target language in Figure~\ref{fig: target_grammar} restricts right-hand sides to contain at most one operator.
+To solve this problem, we introduce an auxiliary function \textsf{use-temp}.
+        \end{itemize}
+        The auxiliary function \textsf{use-temp} checks if the given expression is a simple left-hand side,
+        \begin{itemize}
+            \item If it is, we simply fill the expression to the integer continuation $\beta$\footnote{The type of $\beta$ here is actually a bit different to integer continuation we defined, as it only accepts simple right-hand sides instead of right-hand sides.
+Reynolds gave a wrong definition of the type of this term.
+I have corrected it in my Agda implementation.}.
+            \item If it is not, we need to use a temporary variable to store the result of the expression, and then fill the temporary variable to the integer continuation $\beta$.
+        \end{itemize}
+        However, regarding the stack descriptor, according to Reynolds' model, we assume
+        \begin{itemize}
+            \item $sd$ is the stack descriptor passed along the environment $\gamma$, describing any program variables that may be accessed during the evaluation of the whole expression (plus/negation on the given expression).
+            \item $sd'$ is the current stack descriptor before the evaluation of the whole expression, which is guaranteed to be not less than $sd$.
+$sd'$ is also the position of the temporary variable in the stack.
+            \item $sd''$ is the current stack descriptor after the evaluation on the given expression and just before the assignment of the temporary variable.
+$sd''$ is guaranteed to be not less than $sd'$.
+            \item $sd''' = sd' +_s 1$ is the stack descriptor after the assignment of the temporary variable, as it is just large enough to hold the temporary variable.
+        \end{itemize}
+        In Reynolds' model, we simply adjust the stack descriptor from $sd''$ to $sd'''$ by the adjustment $\delta$ in the assignment instruction.
+However, in the Agda implementation, we need to know whether the adjustment is positive or negative, using \textsf{assign-inc} and \textsf{assign-dec} respectively.
+We also need to show that the adjustment is valid for each case.
+This is done by using the totality of order of natural numbers mentioned in~\secref{subsubsec: order_totality} and case split.
+Please refer to Appendix~[TBD] for the full implementation of the function \textsf{use-temp}.
+        % The auxiliary function \textsf{use-temp} is defined as follows:
+        % \[\includegraphics[scale=1.2]{/compiler/assign_use-temp.pdf}\]
+
+        Given the definition of \textsf{use-temp}, the denotational semantics of plus and negation is simply wrapping $\beta$ with a lambda function using \textsf{use-temp} to get the temporary variable, and directly fill the plus/negation of the variable to the integer continuation $\beta$.
+Note that in the denotational semantics of plus, we need to use the functorial mapping of simple right-hand sides for the first argument, as the stack may grow during the evaluation of the second argument.
 The denotational semantics of integer expressions is defined as follows:
         \[\includegraphics[scale=1.2]{/compiler/term_intexp.pdf}\]
-        The helper function \textsf{use-temp} is defined as follows:
-        \[\includegraphics[scale=1.2]{/compiler/assign_use-temp.pdf}\]
 
@@
     Compilation is a functor from the source language to the target language.
-To define the compilation functor, we use the denotational semantics of terms and fill in the initial stack descriptor ($\ang{0, 0}$), the empty context (\textsf{unit}), a trivial proof for stack descriptor being not less than itself ($\mathsf{\leq_s-refl}$) and the continuation representing the last instruction (\textsf{stop}):
+To define the compilation functor, we use the denotational semantics of terms and fill in the initial stack descriptor ($\ang{0, 0}$), the empty context (\textsf{unit}), a trivial proof for stack descriptor being not less than itself ($\mathsf{\mathord{\leq_s}\text{-}refl}$) and the continuation representing the last instruction (\textsf{stop}):
     \[\includegraphics[scale=1.2]{/compiler/compilation.pdf}\]
@@
 
-    \hypertarget{note2}{$^{\dagger}$} This type of test is necessary because the target language does not support doing multiple operations in a single simple instructions.
-This is specified in [Implementation section].
-As a result, special tests are required to check that the compiler correctly translates multiple integer operations into a continuation of simple instructions defined in the target language.
+    \hypertarget{note2}{$^{\dagger}$} This type of test is necessary because the target language does not support doing multiple integer operations in a single instruction, as specified in Figure~\ref{fig: target_grammar}.
+As a result, special tests are required to check that the compiler correctly translates integer expressions with multiple operations into a continuation of single operations defined in the target language.
 
@@
         \item
-            usetmp [to be completed]
+            Complicated functions defined for translating expressions with multiple operations in the source language to a continuation of simple instructions in the target language.
 

### 2025-05-17 draft.tex
draft-ver-2

@@
 \definecolor{darkpink}{HTML}{EE1289}
+\definecolor{purple}{HTML}{A020F0}
 
@@
 \newcommand{\dpink}[1]{\textcolor{darkpink}{#1}}
-
-\newcommand{\bN}{\mathbb{N}}
-\newcommand{\bZ}{\mathbb{Z}}
+\newcommand{\pp}[1]{\textcolor{purple}{#1}}
+
+\newcommand{\mbt}[1]{\mb{\textsf{#1}}}
+\newcommand{\gnt}[1]{\gn{\textsf{#1}}}
+\newcommand{\ogt}[1]{\og{\textsf{#1}}}
+\newcommand{\ppt}[1]{\pp{\textsf{#1}}}
+
+\newcommand{\bN}{\ensuremath{\mathbb{N}}}
+\newcommand{\bZ}{\ensuremath{\mathbb{Z}}}
 
@@
         Agda~\autocite{Agda} is a dependently typed programming language and proof assistant.
-Agda captures the source language's intrinsic syntax with indexed families, which contains only well-typed terms.
+As a dependently typed language, Agda captures the source language's intrinsic syntax with indexed families, which contains only well-typed terms.
 Therefore, it focuses on the correct programs and rules out the ill-typed nonsensical inputs.
@@
 
-    \section{Contributions}
-        Addressed the two motivations presented in~\secref{sec: motivation} and contributed to the following:
+    \section{Contributions} \label{sec: contributions}
+        The success criteria of the project are:
+        \begin{itemize}
+            \item 
+                Formalise the definitions of the source language in Agda
+            \item 
+                Formalise the definitions of the target language in Agda
+            \item
+                Implement a compiler from the source language to the target language in Agda
+            \item 
+                The compiler successfully turns well-typed closed programs in the source language to valid target language expressions
+        \end{itemize}
+
+        The project successfully met all of the above success criteria, addressed the two motivations presented in~\secref{sec: motivation} and contributed to the following:
         \begin{quote}            
@@
 
-    For implementing the compiler, I need to understand the theoretical background of presheaves and functor categories that are used as the denotational semantics of the source language, and I need to understand Agda's dependent types to correctly express the dependent function space of presheaf exponentials.
-This chapter begins with my starting point and an introduction to category theory, followed by a brief overview of the dependently typed programming language Agda, and requirements analysis of the compiler.
+    For implementing the compiler, I need to understand the theoretical background of presheaves and functor categories that are used as the denotational semantics of the source language, and I need to understand dependent types to correctly express the dependent function space of presheaf exponentials.
+
+    This chapter begins with my starting point and introducing core concepts of category theory.
+It then provides a brief overview of Agda as a dependently typed programming language, concluding with a requirements analysis for the compiler design.
 
@@
                 \item 
-                    for each $X, Y \in \textbf{obj}(\mathcal{C})$, a collection of morphisms $\mathcal{C}{(X,Y)}$, whose elements are called $\mathcal{C}$-morphisms from $X$ to $Y$ (e.g.\ $f : X \to Y$);
+                    for each $X, Y \in \textbf{obj}(\mathcal{C})$, a collection of morphisms $\mathcal{C}{(X,Y)}$, whose elements are called $\mathcal{C}$-morphisms from $X$ to $Y$ (e.g.\ $f : X \xrightarrow{\mathcal{C}} Y$);
                 \item 
@@
                 \item 
-                    \textbf{(Unit Laws)}
+                    \textbf{(Unit)}
                     For all $X, Y \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$, we have
@@
                 \item
-                    \textbf{(Associativity Law)}
+                    \textbf{(Associativity)}
                     For all $X, Y, Z, W \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$, $g \in \mathcal{C}{(Y,Z)}$, $h \in \mathcal{C}{(Z,W)}$, we have
@@
                 \item 
-                    The objects of $\mathcal{Set}$ are a fixed universe of sets;
+                    The objects of $\mathcal{Set}$ are small\footnote{Here the smallness condition avoids foundational issues analogous to Russell's paradox.
+While we omit the formal definition of size due to the space limit here, all constructions in this work preserve smallness.} sets;
                 \item
@@
 
-            \subsubsection{Opposite category}
         The idea of opposite category is that if we have a category $\mathcal{C}$, we can reverse the direction of all morphisms in $\mathcal{C}$ to obtain a new category $\mathcal{C}^{\textbf{op}}$.
@@
         \end{definition}
-
-                % \paragraph{The principle of duality}
-                % Whenever one defines a concept or proves a theorem in category theory $\mathcal{C}$, one can obtain another concept or theorem in the opposite category $\mathcal{C}^{\textbf{op}}$, called the \emph{dual} of the original concept or theorem, by reversing all arrows in the original concept or theorem.
 
@@
                 \centering
-                \begin{minipage}{0.3\textwidth}
-                    \centering
-                    \includegraphics[width=0.8\textwidth]{unit_laws.pdf}
+                \begin{minipage}{0.3\linewidth}
+                    \centering
+                    \includegraphics[width=0.6\linewidth]{unit_laws.pdf}
                     \caption{Commutative diagram for Unit Laws}
                     \label{fig: unit_laws}
-                \end{minipage} \hspace{0.2\textwidth}
-                \begin{minipage}{0.3\textwidth}
-                    \centering
-                    \includegraphics[width=0.8\textwidth]{associativity_law.pdf}
+                \end{minipage} \hspace{0.1\linewidth}
+                \begin{minipage}{0.3\linewidth}
+                    \centering
+                    \includegraphics[width=0.6\linewidth]{associativity_law.pdf}
                     \caption{Commutative diagram for Associativity Law}
@@
         \begin{definition}[Isomorphism]
-            Given a category $\mathcal{C}$, a $C$-morphism $f : X \to Y$ is called an \emph{isomorphism} if there exists a $C$-morphism $g : Y \to X$ such that the following diagram commutes:
+            Given a category $\mathcal{C}$, a $\mathcal{C}$-morphism $f : X \xrightarrow{\mathcal{C}} Y$ is called an \emph{isomorphism} if there exists a morphism $g : Y \xrightarrow{\mathcal{C}} X$ such that the following diagram commutes:
             \begin{equation}
@@
         \subsection{Cartesian closed category}
-            \subsubsection{Terminal object}
             \begin{definition}[Terminal object]
@@
 
-            \subsubsection{Binary product}
             \begin{definition}[Binary product]
@@
             \begin{example}[Binary product in $\mathcal{Set}$]
-                The binary product of two sets $X$ and $Y$ in $\mathcal{Set}$ is the Cartesian product $X \times Y = \{(x,y) \mid x \in X \land y \in Y\}$, where $(x,y)$ are ordered pairs.
+                The binary product of two sets $X$ and $Y$ in $\mathcal{Set}$ is the cartesian product $X \times Y = \{(x,y) \mid x \in X \land y \in Y\}$, where $(x,y)$ are ordered pairs.
 
@@
 
-            \subsubsection{Exponential}
             \begin{definition}[Exponential]
@@
                 The currying operation transform a function $f : Z \times X \to Y$ into a function $\textbf{cur} f : Z \to (X \Rightarrow Y)$, which is defined as $\textbf{cur} f(z) = \lambda x.f(z,x)$ for all $z \in Z$ and $x \in X$.
-
             \end{example}
@@
         \begin{definition}[Cartesian closed category]
-            A category $\mathcal{C}$ is called a \emph{Cartesian closed category} (CCC) if it has a terminal object, binary products and exponentials of any two objects.
+            A category $\mathcal{C}$ is called a \emph{cartesian closed category} (CCC) if it has a terminal object, binary products and exponentials of any two objects.
         \end{definition}
@@
         \subsection{Presheaf category}
+        A presheaf is a contravariant functor, which means that it reverses the direction of morphisms.
+In other words, a presheaf is a functor that takes objects in $\mathcal{C}$ and assigns them sets, and takes morphisms in $\mathcal{C}^{\textbf{op}}$ and assigns them functions between the corresponding sets.
         \begin{definition}[Presheaf]
             Given a category $\mathcal{C}$, a \emph{presheaf} on $\mathcal{C}$ is a functor $F: \mathcal{C}^{\textbf{op}} \to \mathcal{Set}$.
-            A presheaf is a contravariant functor, which means that it reverses the direction of morphisms.
-            In other words, a presheaf is a functor that takes objects in $\mathcal{C}$ and assigns them sets, and takes morphisms in $\mathcal{C}$ and assigns them functions between the corresponding sets.
             The presheaf $F$ is defined as follows:
@@
                     \end{equation}
-                    For all $Y \in \textbf{obj}(\mathcal{C})$;
+                    for all $Y \in \textbf{obj}(\mathcal{C})$;
                 \item
@@
         \begin{theorem}[Yoneda lemma]
-            For each small\footnote{Here the smallness condition avoids foundational issues analogous to Russell's paradox.
-While we omit the formal definition of size due to the space limit here, all constructions in this work preserve smallness.} category $\mathcal{C}$, the \emph{Yoneda lemma} states that for each object $X \in \textbf{obj}(\mathcal{C})$ and each presheaf $F \in \hat{\mathcal{C}}$, there exists a natural isomorphism
+            For each small\footnote{See footnote 1.} category $\mathcal{C}$, the \emph{Yoneda lemma} states that for each object $X \in \textbf{obj}(\mathcal{C})$ and each presheaf $F \in \hat{\mathcal{C}}$, there exists a natural isomorphism
             \begin{equation} \label{eq: yoneda_lemma}
@@
         \begin{prf}[Cartesian closed structure in presheaf categories]
-            Given a small\footnote{See footnote 1.} category $\mathcal{C}$, the presheaf category $\hat{\mathcal{C}}$ is a Cartesian closed category.
+            Given a small\footnote{See footnote 1.} category $\mathcal{C}$, the presheaf category $\hat{\mathcal{C}}$ is a cartesian closed category.
             \begin{itemize}
@@
 
+        \subsection{Curry-Howard-Lambek correspondence} \label{subsec: curry-howard-lambek}
+        Joachim Lambek showed that cartesian closed categories provide a natural semantic setting for the simply typed lambda calculus (STLC)~\autocite{lambek}.
+His work builds upon Curry-Howard correspondence~\autocite{curry-howard}, the isomorphism between logic and type theory, where propositions correspond to types and proofs correspond to terms.
+The Curry-Howard-Lambek correspondence can be summarised as follows:
+        \begin{table}[H]
+            \centering
+            \begin{tabular}{|c|c|c|}
+                \hline
+                \textbf{Logic} & \textbf{Type theory} & \textbf{Category theory} \\
+                \hhline{|=|=|=|}
+                Proposition & Type & Object \\
+                \hline
+                Proof & Term & Morphism \\
+                \hline
+                Falsity & Empty type & Initial object \\
+                \hline
+                Truth & Unit type & Terminal object \\
+                \hline
+                Implication & Function type & Exponential \\
+                \hline
+                Conjunction & Product type & Product \\
+                \hline
+                Disjunction & Sum type & Coproduct \\
+                % Universal quantification & Dependent product type &  \\
+                % Existential quantification & Dependent sum type &  \\
+                \hline
+            \end{tabular}
+            \caption{Curry-Howard-Lambek correspondence}
+            \label{tab: curry-howard-lambek}
+        \end{table}
+        This correspondence forms the foundation of functional programming languages that can be used to implement proofs.
+
     \section{Agda}
@@
 
-        Here we define a data type $\mb{\mathsf{Vec}}$ for vectors. The type of vectors is dependent on the length of the vector. With dependent types, we can encode properties directly into types.
-
-        \subsection{Curry-Howard-Lambek correspondence} \label{subsec: curry-howard-lambek}
-        Curry-Howard correspondence~\autocite{curry-howard} establishes an isomorphism between logic and type theory, where propositions correspond to types and proofs correspond to terms.
-This correspondence forms the foundation of functional programming languages that can be used to implement proofs.
-Building upon this, Joachim Lambek showed that cartesian closed categories provide a natural semantic setting for the simply typed lambda calculus (STLC)~\autocite{lambek}.
-The Curry-Howard-Lambek correspondence can be summarised as follows:
-        \begin{table}[H]
-            \centering
-            \begin{tabular}{|c|c|c|}
-                \hline
-                \textbf{Logic} & \textbf{Type theory} & \textbf{Category theory} \\
-                \hhline{|=|=|=|}
-                Proposition & Type & Object \\
-                \hline
-                Proof & Term & Morphism \\
-                \hline
-                Falsity & Empty type & Initial object \\
-                \hline
-                Truth & Unit type & Terminal object \\
-                \hline
-                Implication & Function type & Exponential \\
-                \hline
-                Conjunction & Product type & Product \\
-                \hline
-                Disjunction & Sum type & Coproduct \\
-                % Universal quantification & Dependent product type &  \\
-                % Existential quantification & Dependent sum type &  \\
-                \hline
-            \end{tabular}
-            \caption{Curry-Howard-Lambek correspondence}
-            \label{tab: curry-howard-lambek}
-        \end{table}
+        Here a data type $\mb{\mathsf{Vec}}$ is defined for vectors. The type of vectors is dependent on the length of the vector. With dependent types, we can encode properties directly into types.
 
@@
         With equality as a type, whenever we want to prove that two terms are equal, we need to provide a witness of the equality.
-For example if we want to prove $x \equiv y$, we write out a term of type $\mb{\mathsf{x = y}}$, and then give its definition, which constructs a proof of the equality.
-A simple proof that directly uses the definition of equality is as follows:
+For example if we want to prove $x \equiv y$, we write out a term of type \textit{x} \mb{\textsf{≡}} \textit{y}, and then give its definition, which constructs a proof of the equality.
+All of the examples here are type-checked by Agda, so they are all valid proofs.
+
+        Two simple proofs that directly use the definition of equality is as follows:
         \[\includegraphics[scale=1.2]{sym_trans.pdf}\]
-        Here we are able to prove the symmetry and transitivity of equality by using the definition of equality. Those two properties are very useful for later proofs.
-
-        We can also have more complex proof with congruence and substitution, which can also be directly derived from the definition of equality as follows:
+        Here \textit{y} and \textit{z} are reduced to \textit{x} by the definition of the constructor \gn{\textsf{refl}}.
+The properties are called \emph{symmetry} and \emph{transitivity} of equality, which are very useful for later proofs.
+
+        We can also have more complex proof with \emph{congruence} and \emph{substitution}, which can also be directly derived from the definition of equality as follows:
         \[\includegraphics[scale=1.2]{cong_subst.pdf}\]
-        Congruence is a property of equality that states that if two terms are equal, then they can be substituted for each other in any context.
-Substitution is a property where we can get a new proof by replacing a term in a proof with another term that is equal to it.
+        % \emph{Congruence} is a property of equality that states that if two terms are equal, then they can be substituted for each other in any context.
+\emph{Substitution} is a property where we can get a new proof by replacing a term in a proof with another term that is equal to it.
 
         Here is a simple example of how congruence can be used in a proof:
-        \[\includegraphics[scale=1.2]{cong_example.pdf}\]
-
-        In this example, we want to prove that $\gn{\mathsf{zero}}$ is the right identity of the plus function. We do an inductive proof by pattern matching on the first argument of the plus function.
-
-        In the base case, we have $\gn{\mathsf{zero}} \mb{{}+{}} \gn{\mathsf{zero}} \equiv \gn{\mathsf{zero}}$, which is trivially true by the definition of the plus function (zero is defined to be the left identity of the plus function).
-
-        In the inductive case, we need to show $\gn{\mathsf{suc}}\ n \mb{{}+{}} \gn{\mathsf{zero}} \equiv \gn{\mathsf{suc}}\ n$.
-We can use the definition of the plus function to rewrite the left-hand side as $\gn{\mathsf{suc}}\ (n \mb{{}+{}} \gn{\mathsf{zero}})$.
-By the inductive hypothesis, we know that $n \mb{{}+{}} \gn{\mathsf{zero}} \equiv n$, so we can substitute $n$ for $n \mb{{}+{}} \gn{\mathsf{zero}}$ in the right-hand side by congruence, and we are done.
+        \[\includegraphics[scale=1.2]{plus_right_identity.pdf}\]
+        In this example, we want to prove that \gnt{zero} is the right identity of the plus function.
+This property cannot be directly shown by using \gn{\textsf{refl}} because \gn{\textsf{refl}} only knows about definitional equality.
+In the definition of the plus function, only the first argument is pattern matched, so we can only show that \gnt{zero} is the left identity of the plus function by directly sing the \gn{\textsf{refl}}.
+To show that \gnt{zero} is the right identity of the plus function, we need to do an inductive proof by pattern matching on the first argument of the plus function.
+
+        In the base case, we have \gnt{zero} \mb{+} \gnt{zero} \mb{≡} \gnt{zero}, which is true by the definition of the plus function.
+
+        In the inductive case, we need to show \gnt{suc} \textit{n} \mb{+} \gnt{zero} \mb{≡} \gnt{suc} \textit{n}.
+The left hand side is definitionally equal to \gnt{suc} (\textit{n} \mb{+} \gnt{zero}).
+By the inductive hypothesis, we know that \textit{n} \mb{+} \gnt{zero} \mb{≡} \textit{n}, so we can substitute \textit{n} for \textit{n} \mb{+} \gnt{zero} in the right-hand side by congruence, and we are done.
 
@@
         \subsubsection{Builtin pragma} \label{subsubsec: builtin_pragma}
-        With standard library, we can use actual numbers $1, 2, 3, \dots$ instead of calling the constructor $\gn{\mathsf{suc}}$ multiple times.
-This is a convenient feature for testing.
-Self-defined functions can be used with the builtin numbers with a \og{\textsf{BUILTIN}} pragma.
-This allows me to use a convenient syntax of numbers for self-defined functions.
+        With standard library, we can use literal natural numbers \ppt{1}, \ppt{2}, \dots\ instead of calling the constructor \gnt{suc} multiple times.
+This feature can be extended to self-defined functions with a \og{\textsf{BUILTIN}} pragma.
+We simply add the following two lines after the definition of \mb{\bN} and \mb{\_+\_}:
         \[\includegraphics[scale=1.2]{natural_pragma.pdf}\]
-        Note that in agda we can use unicode characters for terms, which makes the code more readable. For example, here we simply name the term \mb{1+1$\equiv$2}.
+        Note that in agda we can use unicode characters for names of terms, which makes the code more readable. For example, here we simply name the term \mb{\textsf{1+1≡2}}.
 
@@
         A feature of Agda is interactive programming with holes.
-By leaving holes in place of undefined terms, we can write programs that are incomplete but still type-check, and Agda's type checker will guide completion of the program: the context window displays inferred types of the holes, available variables and candidate terms with their types.
+When users leave holes in place of undefined terms, Agda's type checker will infer the type of the hole, show available variables and candidate terms with their types.
 Holes also supports case split and refinement, which means we can fill in a hole partially and split it into smaller holes.
-
-        In my implementation, I used holes to write the terms in the compiler.
+This feature is used in my implementation.
 The complex terms are incrementally filled and verified by refining partial implementations, reducing post-hoc debugging and ensuring robustness.
@@
     \section{Requirement Analysis}
-    To complete the compiler in Agda we need to implement the following components:
-    \begin{itemize}
-        \item 
-            A file \texttt{source.agda} that record the syntax of the source language, which include basic instructions in STLC.
+    To complete the compiler in Agda I need to implement the following components:
+    \begin{itemize}
+        \item 
+            A file \texttt{source.agda} that record the syntax of the source language, which include basic instructions in STLC with store.
 
@@
         \item
-            A file \texttt{compiler.agda} that uses \texttt{source.agda} and \texttt{target.agda} as modules, and write functions whose input is a term in the source language and output is a term in the target language.
+            A file \texttt{compiler.agda} that uses \texttt{source.agda} and \texttt{target.agda}, and write functions whose input is a closed term in the source language and output is a term in the target language.
         \item 
@@
     \end{itemize}
-    The success criteria of the project is that all of the above files are implemented and type checked, which ensures that all the terms are well typed and the compilation is as expected.
+    The implementation and type-checking of all files specified above constitutes a necessary and sufficient condition for meeting the project's success criteria mentioned in~\secref{sec: contributions}.
 
@@
     This chapter details the implementation of the compiler in Agda.
-Starting with a brief overview of the tools used, it then describes the directory structure and file dependencies.
-Then it discusses the specification of the source language, and the target language, which lead us to the problem of implementing a rigorous natural number subtraction and two different approaches.
-It further reveals the difference between the two approaches and how they affect the implementation of the customised library.
-Finally a detailed implementation of the compiler is presented.
-
-    \section{Tools used}
-    The project is implemented in Agda 2.7.0.1, which is the latest stable version at the time of writing.
+Following a brief overview of the tools used~(\secref{sec: tools}), it provides a repository overview~(\secref{sec: repo_overview}).
+Then it discusses the intrinsic syntax of the source language~(\secref{sec: source}) and the grammar of target language~(\secref{sec: target}), leading to the problem of implementing a proof-relevant natural number subtraction.
+
+    To address this, it presents the customised library~(\secref{sec: lib}) with two different approaches for implementing subtraction: one using additional proof object and the other using Fin, a dependent type.
+It compares the two approaches and discusses the trade-offs between them.
+The chapter concludes with a detailed implementation of the compiler~(\secref{sec: compiler}).
+
+    \section{Tools used} \label{sec: tools}
+    The project is implemented in Agda 2.7.0.1, the latest stable version at the time of writing.
 
@@
 
-    \section{Repository Overview}
+    \section{Repository Overview} \label{sec: repo_overview}
         \subsection{Directory structure}
-        The repository contains two independent implementations of the compiler, organised as follows:
+        The repository contains two independent implementations of the compiler, organised in two directories: \texttt{fin} and \texttt{proof} as follows:
         \dirtree{%
@@
 
-    \section{Source Language}
-    A simply typed lambda calculus (STLC) is a typed lambda calculus with only one type constructor ($\Rightarrow$) \footnote{Normally we use $\to$ to denote the function type, but here we use $\Rightarrow$ to be consistent with the notation in Agda, as $\to$ is a primitive in Agda.} that builds function types.
-
+    \section{Source Language} \label{sec: source}
+    % A simply typed lambda calculus (STLC) is a typed lambda calculus with only one type constructor ($\Rightarrow$) \footnote{Normally we use $\to$ to denote the function type, but here we use $\Rightarrow$ to be consistent with the notation in Agda, as $\to$ is a primitive in Agda.} that builds function types.
+    The source language is a simply typed lambda calculus (STLC) with store, following the syntax in Reynolds' paper~\autocite{Reynolds}.
         \subsection{Types}
-        In this dissertation, the source language is an STLC with the following primitive types:
-        \begin{itemize}
-            \item 
-                \textsf{comm}: the commands
-            \item 
-                \textsf{intexp}: the integer expressions
-            \item 
-                \textsf{intacc}: the integer acceptors
-            \item 
-                \textsf{intvar}: the integer variables
-        \end{itemize}
-        and the set $\Theta$ of types is defined as follows: 
-        \[ \Theta := \textsf{comm} \mid \textsf{intexp} \mid \textsf{intacc} \mid \textsf{intvar} \mid \Theta \Rightarrow \Theta \] 
+        The source language has four primitive types:
+        \begin{itemize}
+            \item 
+                \textsf{comm}: commands, which is the type of programs
+            \item 
+                \textsf{intexp}: integer expressions, corresponding to \texttt{int} in most programming languages
+            \item 
+                \textsf{intacc}: integer acceptors, representing reference to integer values
+            \item 
+                \textsf{intvar}: integer variables, which are integer acceptors that can also be used as expressions with automatic dereferencing
+        \end{itemize}
+        and general types are defined as follows: 
+        \[ A, B := \textsf{comm} \mid \textsf{intexp} \mid \textsf{intacc} \mid \textsf{intvar} \mid A \Rightarrow B \] 
         which corresponds with the following agda implementation:
@@
         \subsubsection{Subtypes}
-        We use the preorder $A \leq: B$ to denote the subtype relation $A$ is a subtype of $B$, as it has the following properties:
-        \begin{itemize}
-            \item 
-                reflexivity: $A \leq: A$;
-            \item 
-                transitivity: if $A \leq: B$ and $B \leq: C$, then $A \leq: C$.
-        \end{itemize}
+        I use the preorder $A ≤: B$ to denote the subtype relation $A$ is a subtype of $B$, as it has the following properties:
+        \begin{figure}[H]
+            \centering
+            \includegraphics[width=0.5\textwidth]{subtype.pdf}
+            \caption{Preorder of subtypes}
+            \label{fig: subtype}
+        \end{figure}
 
@@
         For function types we have the contravariant subtyping:
-        \[ A' \leq: A \land B \leq: B' \Rightarrow A \to B \leq: A' \to B' \]
+        \begin{figure}[H]
+            \centering
+            \includegraphics[width=0.3\textwidth]{subtype_function.pdf}
+            \caption{Contravariant subtyping for function types}
+            \label{fig: subtype_fun}
+        \end{figure}
 
@@
 
-        \subsection{Contexts, variables and the lookup judgement}
-        We define the context as a finite list of types.
-When we are looking up a variable, the type of the variable is either the head of the context or in the tail of the context.
-The definition in Agda is as follows:
+        \subsection{Contexts and variables}
+        We define the context as a finite list of types as follows:
         \[\includegraphics[scale=1.2]{/source/contexts.pdf}\]
-        where the $\gn{\mathsf{Zero}}$ case corresponds to the situation where the variable is the head of the context, and the $\gn{\mathsf{Suc}}$ case corresponds to the situation where the variable is in the tail of the context.
+        When we are looking for a variable, \gnt{Zero} case corresponds to the situation where the variable is the head of the context, and the \gnt{Suc} case corresponds to the situation where the variable is in the tail of the context.
+The number formed by \gnt{Zero} and \gnt{Suc} is the index of the variable in the context, called the \emph{de Bruijn index}~\autocite{de_bruijn}.
 
         \subsection{Terms and the typing judgement} \label{subsec: terms}
-        The terms and the typing judgement are described in the following rules:
-        \begin{itemize}
-            \item For any variable we have 
+        The terms are defined as follows:
+        \[\begin{aligned}
+            c_1, c_2 &= \texttt{skip} \mid c_1; c_2 \mid a := e \mid \texttt{new } x \texttt{ in } c_1 \\
+            e_1, e_2 &= \texttt{lit } z \mid -e_1 \mid e_1 + e_2 \mid \lambda e_1.\ e_2 \mid e_1\ e_2 \mid x \\
+        \end{aligned}\]
+
+        and the typing judgement are described in the following rules:
         \begin{figure}[H]
+            \centering
+            \begin{minipage}{0.4\textwidth}
                 \centering
@@
                 \label{fig: rule_var}
-                \end{figure}
-            \item For subtyping we have
-                \begin{figure}[H]
+            \end{minipage} \hspace{0.1\textwidth}
+            \begin{minipage}{0.4\textwidth}
                 \centering
@@
                 \label{fig: rule_subtype}
+            \end{minipage}
         \end{figure}
-            \item For lambda abstraction we have
         \begin{figure}[H]
@@
         \end{figure}
-            \item For command we have
         \begin{figure}[H]
             \centering
-                    \includegraphics{source_terms_comm.pdf}
-                    \caption{Command typing rules}
-                    \label{fig: rule_comm}
+            \includegraphics{source_terms_comm_1.pdf}
+            \caption{Command typing rules (part 1)}
+            \label{fig: rule_comm_1}
         \end{figure}
-            \item For integer expression we have
+        \begin{figure}[H]
+            \centering
+            \includegraphics{source_terms_comm_2.pdf}
+            \caption{Command typing rules (part 2)}
+            \label{fig: rule_comm_2}
+        \end{figure}
         \begin{figure}[H]
@@
         \end{figure}
-        \end{itemize}
 
@@
 
-    \section{Target Language}
+    \section{Target Language} \label{sec: target}
     The target language is an assembly-style intermediate language for a stack machine. It is defined with four stack-descriptor-indexed families of non-terminals: 
@@
         \item 
-            $\bracket{\textsf{L}_{sd}}$: left-hand sides
-        \item 
-            $\bracket{\textsf{S}_{sd}}$: simple right-hand sides
-        \item
-            $\bracket{\textsf{R}_{sd}}$: right-hand sides
-        \item
-            $\bracket{\textsf{I}_{sd}}$: instruction sequences
-    \end{itemize}
-    The intent of the indexing here is any instructions with the form $\bracket{\textsf{I}_{sd}}$ is an instruction sequence that can be executed when the current stack descriptor is $sd$.
+            $\bracket{\textsf{L}_{\textit{sd}}}$: left-hand sides
+        \item 
+            $\bracket{\textsf{S}_{\textit{sd}}}$: simple right-hand sides
+        \item
+            $\bracket{\textsf{R}_{\textit{sd}}}$: right-hand sides
+        \item
+            $\bracket{\textsf{I}_{\textit{sd}}}$: instruction sequences
+    \end{itemize}
+    The intent of the indexing here is any instructions with the form $\bracket{\textsf{I}_{\textit{sd}}}$ is an instruction sequence that can be executed when the current stack descriptor is $\textit{sd}$.
+
+    The following subsections start with the definition of stack descriptors, then define the grammar of the target language, and finally discuss the problem of subtraction of natural numbers.
 
     \subsection{Stack descriptor}
-    The stack descriptor $sd$ is defined as a pair of natural numbers $\ang{f, d}$, where $f$ is the frame number and $d$ is the displacement.
+    Now, I define the stack descriptor in Agda, as well as their pre-order, operations (addition and subtraction), and properties about ordering.
+
+    The stack descriptor $\textit{sd}$ is defined as a pair of natural numbers $\ang{f, d}$, where $f$ is the frame number and $d$ is the displacement.
 
@@
 
-    For a stack descriptor $sd$, we can use \dpink{SD.f} $sd$ to access the frame number and \dpink{SD.d} $sd$ to access the displacement.
+    For a stack descriptor $\textit{sd}$, we can use \dpink{SD.f} $\textit{sd}$ to access the frame number and \dpink{SD.d} $\textit{sd}$ to access the displacement.
 
@@
     \[\includegraphics[scale=1.2]{/target/stack_descriptor_order.pdf}\]
-    Here definition of the order of natural numbers is in the customised library. Please refer to~\secref{sec: lib} for more details.
 
     \subsubsection{Addition and subtraction of stack descriptors}
-    We define addition and subtraction of stack descriptors as follows:
-    \[\ang{f, d} \pm_s n = \ang{f, d \pm n} \text{ for } n \in \mathbb{N}\]
+    The addition and subtraction of stack descriptors is defined as follows:
+    \[\ang{f, d} \pm_\mathsf{s} n = \ang{f, d \pm n} \text{ for } n \in \mathbb{N}\]
     Addition of stack displacement is defined in Agda as follows:
@@
     For subtraction, we need to make sure that the subtraction is valid, i.e.
-the subtracted displacement adjustment is less than or equal to the displacement of the current stack descriptor.
-This leads us to the problem of defining the subtraction of natural numbers, which is explained in detail in~\secref{subsec: subtraction}
-
-    \subsubsection{Properties of order and addition}
-    We can use reflexivity and transitivity of the order $<$ and $\leq$ to prove that the order of stack descriptors $\leq_\mathsf{s}$ is a preorder. The proof is as follows:
-    \begin{proof}
-        We need to show that $\leq_\mathsf{s}$ is reflexive and transitive. 
-        \begin{itemize}
-            \item 
-                Reflexivity: $sd \leq_\mathsf{s} sd$ is trivially true since $f = f$ and $d \leq d$.
-            \item
-                Transitivity: if $\ang{f, d} \leq_\mathsf{s} \ang{f', d'}$ and $\ang{f', d'} \leq_\mathsf{s} \ang{f'', d''}$, we do the following case split:
-                \begin{itemize}
-                    \item 
-                        If $f < f'$, $f' = f''$ and $d \leq d'$, then $f < f''$; 
-                    \item 
-                        If $f < f'$ and $f' < f''$, then $f < f''$ by transitivity of $<$;
-                    \item
-                        If $f = f'$, $d \leq d'$ and $f' < f''$, then $f < f''$;
-                    \item
-                        If $f = f'$, $d \leq d'$, $f' = f''$ and $d' \leq d''$, then $f = f''$ and $d \leq d''$ by transitivity of $\leq$.
+$\ang{f, d} -\mathsf{s} n$ is only defined for $n \leq d$.
+This leads us to the problem of defining the subtraction of natural numbers, which is explained in detail in~\secref{subsec: subtraction}.
+
+    \subsubsection{Properties}
+    The properties of stack descriptors can be summarised as follows:
+    \begin{table}[H]
+        \centering
+        \begin{tabular}{|c|c|}
+            \hline
+            \textbf{Agda term} & \textbf{Mathematical meaning} \\
+            \hhline{|=|=|}
+            \mbt{≤ₛ-refl} & $\forall sd.\ sd \leq_\mathsf{s} sd$ \\
+            \hline
+            \mbt{≤ₛ-trans} & $\forall sd, sd', sd''.\ sd \leq_\mathsf{s} sd' \land sd' \leq_\mathsf{s} sd'' \Rightarrow sd \leq_\mathsf{s} sd''$ \\
+            \hline
+            \mbt{+ₛ→≤ₛ} & $\forall sd, n.\ sd \leq_\mathsf{s} sd +_\mathsf{s} n$ \\
+            \hline
+            \mbt{sub-sd≤ₛ} & $\forall sd, sd', sd''. sd' \equiv sd'' \land sd \leq_\mathsf{s} sd' \Rightarrow sd \leq_\mathsf{s} sd''$ \\
+            \hline
+            \mbt{–ₛ≡} & $\forall f, d, d′, n.\ d′ - n \equiv d \Rightarrow \ang{f, d} \equiv \ang{f, d′} -_\mathsf{s} n$ \\
+            \hline
+        \end{tabular}
+        \caption{Properties of order and addition of stack descriptors}
+        \label{tab: stack_descriptor_properties}
+    \end{table}
+    % We can use reflexivity and transitivity of the order $<$ and $\leq$ to prove that the order of stack descriptors $\leq_\mathsf{s}$ is a preorder. The proof in Agda is as follows:
+    % \begin{proof}
+    %     We need to show that $\leq_\mathsf{s}$ is reflexive and transitive. 
+    %     \begin{itemize}
+    %         \item 
+    %             Reflexivity: $\textit{sd} \leq_\mathsf{s} \textit{sd}$ is trivially true since $f = f$ and $d \leq d$.
+    %         \item
+    %             Transitivity: if $\ang{f, d} \leq_\mathsf{s} \ang{f', d'}$ and $\ang{f', d'} \leq_\mathsf{s} \ang{f'', d''}$, we do the following case split:
+    %             \begin{enumerate}
+    %                 \item 
+    %                     If $f < f'$, $f' = f''$ and $d \leq d'$, then $f < f''$; 
+    %                 \item 
+    %                     If $f < f'$ and $f' < f''$, then $f < f''$ by transitivity of $<$;
+    %                 \item
+    %                     If $f = f'$, $d \leq d'$ and $f' < f''$, then $f < f''$;
+    %                 \item
+    %                     Otherwise $f = f''$ and $d \leq d''$ by transitivity of $\leq$.
 \footnote{Note that the properties of $=$ is not required in as in the Agda definition of $\leq_\mathsf{s}$, we directly define $f'$ to be $f$ instead of defining a equivalence relation, thus equivalence can be checked directly via type checking.}
-                \end{itemize}
-        \end{itemize}
-    \end{proof}
-
-    The proof is defined in Agda as follows:
-    \[\includegraphics[scale=1.2]{/target/stack_descriptor_order_proof.pdf}\]
-
-    When a natural number is added to a stack descriptor, it is guaranteed that the new stack descriptor is not less than the old stack descriptor.
+    %             \end{enumerate}
+    %     \end{itemize}
+    % \end{proof}
+
+    % The proof is defined in Agda as follows:
+    % \[\includegraphics[scale=1.2]{/target/stack_descriptor_order_proof.pdf}\]
+
+    % When a natural number is added to a stack descriptor, it is guaranteed that the new stack descriptor is not less than the old stack descriptor.
 This can be proved directly using the same properties of integer addition.
 The proof is defined in Agda as follows:
-    \[\includegraphics[scale=1.2]{/target/stack_descriptor_add_proof.pdf}\]
-
-    Proofs here are based on the properties of natural numbers specified in the customised library. Please refer to~\secref{sec: lib} for more details.
-
-    \subsection{Grammar}
-    The grammar of the target language is defined as follows, given the current stack descriptor $sd = \ang{f, d}$, and new stack descriptor $sd'$ and $sd^v$:
+    % \[\includegraphics[scale=1.2]{/target/stack_descriptor_add_proof.pdf}\]
+
+    \subsection{Grammar} \label{subsec: grammar}
+    The grammar of the target language\footnote{This grammar can be extended with subroutines as an \textsf{L} command, and conditionals as an \textsf{I} command} is defined as follows, given the current stack descriptor $\textit{sd} = \ang{f, d}$, and new stack descriptor $\textit{sd′}$ and $\textit{sd\textsuperscript{v}}$:
     \begin{figure}[H]
@@
         \[\begin{aligned}
-            \bracket{\textsf{L}_{sd}} ::={}& sd^v \quad \text{when } sd^v \leq_\mathsf{s} sd \\
-                            &\mid \texttt{sbrs}  \\
-            \bracket{\textsf{S}_{sd}} ::={}& \bracket{\textsf{L}_{sd}} \\
+            \bracket{\textsf{L}_{\textit{sd}}} ::={}& \textit{sd\textsuperscript{v}} \quad \text{when } \textit{sd\textsuperscript{v}} \leq_\mathsf{s} \textit{sd} \\
+                            % &\mid \texttt{sbrs}  \\
+            \bracket{\textsf{S}_{\textit{sd}}} ::={}& \bracket{\textsf{L}_{\textit{sd}}} \\
                             &\mid \texttt{lit } \bracket{\text{integer}} \\
-            \bracket{\textsf{R}_{sd}} ::={}& \bracket{\textsf{S}_{sd}} \\
-                            &\mid \bracket{ \text{unary operator} } \bracket{ \textsf{S}_{sd}}\\
-                            &\mid \bracket{\textsf{S}_{sd}} \bracket{\textsf{binary operator}} \bracket{ \textsf{S}_{sd} } \\
-            \bracket{\textsf{I}_{sd}} ::={}& \texttt{stop} \\
+            \bracket{\textsf{R}_{\textit{sd}}} ::={}& \bracket{\textsf{S}_{\textit{sd}}} \\
+                            &\mid \bracket{ \text{unary operator} } \bracket{ \textsf{S}_{\textit{sd}}}\\
+                            &\mid \bracket{\textsf{S}_{\textit{sd}}} \bracket{\textsf{binary operator}} \bracket{ \textsf{S}_{\textit{sd}} } \\
+            \bracket{\textsf{I}_{\textit{sd}}} ::={}& \texttt{stop} \\
                             &\left.
                             \begin{aligned}
-                            &|{\ } \bracket{\textsf{L}_{sd+\delta}} := \bracket{\textsf{R}_{sd}}[\delta] \text{ ; } \bracket{\textsf{I}_{sd+\delta}} \\
-                            &|{\ } \texttt{if } \bracket{\textsf{S}_{sd}} \bracket{\text{relational operator}} \bracket{\textsf{S}_{sd}}[\delta] \\
-                            & \hphantom{\mid {}} \texttt{ then } \bracket{\textsf{I}_{sd+\delta}} \texttt{ else } \bracket{\textsf{I}_{sd+\delta}} \\
-                            &|{\ } \texttt{adjustdisp} [\delta] \text{ ; } \bracket{\textsf{I}_{sd+\delta}} \\
+                            &|{\ } \bracket{\textsf{L}_{\textit{sd}+\delta}} := \bracket{\textsf{R}_{\textit{sd}}}[\delta] \text{ ; } \bracket{\textsf{I}_{\textit{sd}+\delta}} \\
+                            % &|{\ } \texttt{if } \bracket{\textsf{S}_{\textit{sd}}} \bracket{\text{relational operator}} \bracket{\textsf{S}_{\textit{sd}}}[\delta] \\
+                            % & \hphantom{\mid {}} \texttt{ then } \bracket{\textsf{I}_{\textit{sd}+\delta}} \texttt{ else } \bracket{\textsf{I}_{\textit{sd}+\delta}} \\
+                            &|{\ } \texttt{adjustdisp} [\delta] \text{ ; } \bracket{\textsf{I}_{\textit{sd}+\delta}} \\
                             \end{aligned}
                             \quad \right\} \text{if } d + \delta \geq 0  \\
-                            &{}\mid{} \texttt{popto } sd' \text{ ; } \bracket{\textsf{I}_{sd'}} \quad \text{when } sd' \leq_\mathsf{s} sd \\
+                            &{}\mid{} \texttt{popto } \textit{sd′} \text{ ; } \bracket{\textsf{I}_{\textit{sd′}}} \quad \text{when } \textit{sd′} \leq_\mathsf{s} \textit{sd} \\
         \end{aligned}\]
@@
     \begin{itemize}
-        \item 
-            $\texttt{sbrs}$: a register used to communicate the result of function procedures implemented by closed subroutines.
+        % \item 
+        %     $\texttt{sbrs}$: a register used to communicate the result of function procedures implemented by closed subroutines.
         \item 
@@
         \item 
-            $\texttt{stop}$: stop the execution of the program.
-        \item 
-            $\delta$: a displacement adjustments, which can be any integer that satisfies the condition mentioned above.
-        \item 
-            $\texttt{adjustdisp}$: adjust the displacement of specified stack descriptor.
-        \item 
-            $\texttt{popto}$: pop to the specified stack descriptor, which is used to reduce the number of frames.
+            $\texttt{stop}$: stops the execution of the program.
+        \item 
+            $\delta$: an integer representing the displacement adjustment.
+        \item 
+            $\texttt{adjustdisp}$: adjusts the displacement of specified stack descriptor.
+        \item 
+            $\texttt{popto}$: pops to the specified stack descriptor, which is used to reduce the number of frames.
     \end{itemize}
@@
 
-    \subsubsection{Operators}
+    A fundamental property of the target language is its order-preserving extension with respect to stack descriptors: any term operating on a smaller stack descriptor can be systematically lifted to operate on a larger one.
+As later formalised in~\secref{subsec: functorial_mapping}, this property exhibits a functorial nature, and is essential for the construction of the compiler.
+
+    % \subsubsection{Operators}
     The operators are defined as follows:
@@
         \textsf{binary operator} &\in \{\texttt{BPlus}, \texttt{BMinus}, \texttt{BTimes}\} \\
-        \textsf{relational operator} &\in \{\texttt{RLeq}, \texttt{RLt}\}
+        % \textsf{relational operator} &\in \{\texttt{RLeq}, \texttt{RLt}\}
     \end{aligned}\]
@@
 
-    \subsubsection{Left-hand sides, simple right-hand sides and right-hand sides}
+    % \subsubsection{Left-hand sides, simple right-hand sides and right-hand sides}
     The left-hand sides, simple right-hand sides and right-hand sides are straightforward, and they are defined as follows in Agda:
@@
 
-    \subsubsection{Instruction sequences}
+    % \subsubsection{Instruction sequences}
     In the instruction sequences, $\delta$ as a displacement adjustment can be positive, zero or negative.
-To make a rigorous definition, we define $\delta$ as a natural number, and treat the positive and negative displacements as two different instructions, using addition and subtraction of stack descriptors respectively.
-Since the definition of negative displacement involves the rigorous definition of subtraction, we will discuss the subtraction of natural numbers and corresponding implementation in~\secref{subsec: subtraction}.
-The definition (except for the negative displacement) in Agda is as follows:
+To make a rigorous definition, I define $\delta$ as a natural number, and treat the positive and negative displacements as two different instructions, using addition and subtraction of stack descriptors respectively.
+
+    The assignment with negative displacement is left to discuss in~\secref{subsec: subtraction}, since it involves proof objects to validate the subtraction. 
+    The remaining instruction sequences are defined in Agda as follows:
     \[\includegraphics[scale=1.2]{/target/instruction_inc.pdf}\]
@@
     \end{itemize}
-
-    \subsection{Definition from standard library}
-    The following is a list of definitions (or their variants) from the standard library and PLFA~\cite{plfa} that are used in the customised library:
-    \begin{itemize}
-        \item 
-            Natural numbers ($\mb{\bN}$), integers ($\mb{\bZ}$) and addition ($\mb{+}$).
-        \item
-            Equality ($\mb{\equiv}$), congruence ($\mb{\mathsf{cong}}$), substitution ($\mb{\mathsf{sub}}$) and transitivity of equality ($\mb{\mathsf{trans}}$).
-        \item
-            Order of natural numbers, including $\mb{\leq}$ and $\mb{<}$.
-        \item
-            Some properties of order and addition.
-    \end{itemize}
-
-    The properties of order and addition contains the following terms summarised in the table below:
+    All definitions and properties can be found in Appendix~[TBD].
+
+    \subsection{Definitions from standard library}
+    The following is a list of definitions (or their variants) from the standard library and PLFA~\cite{plfa} that are redefined in the customised library:
+    \begin{itemize}
+        \item 
+            Natural numbers ($\mb{\bN}$), integers ($\mb{\bZ}$) and addition (\mbt{+}).
+        \item
+            Equality (\mbt{≡}), congruence ($\mb{\mathsf{cong}}$), substitution ($\mb{\mathsf{sub}}$) and transitivity of equality ($\mb{\mathsf{trans}}$).
+        \item
+            Order of natural numbers, including \mbt{≤} and \mbt{<}.
+        \item
+            Properties of preorder and addition (summarised in Table~\ref{tab: properties}).
+    \end{itemize}
     \begin{table}[H]
@@
             \hhline{|=|=|}
-            $\mb{+\text{-}\mathsf{identity^r}}$ & $\forall n \in \bN.\ n + 0 = n$ \\
-            \hline
-            $\mb{+\text{-}\mathsf{suc^r}}$ & $\forall m, n \in \bN.\ m + \textsf{suc } n = \textsf{suc } (m + n)$ \\
-            \hline
-            $\mb{+\text{-}\mathsf{comm}}$ & $\forall m, n \in \bN.\ m + n \equiv n + m$ \\
-            \hline
-            $\mb{\mathsf{\mathord{\leq}\text{-}irrelevant}}$ & For all $m, n \in \bN$, we consider all proofs of $m \leq n$ to be equal. \\
-            \hline
-            $\mb{\mathsf{\mathord{\leq}\text{-}refl}}$ & $\forall n \in \bN.\ n \leq n$ \\
-            \hline
-            $\mb{\mathsf{\mathord{\leq}\text{-}trans}}$ & $\forall m, n, p \in \bN.\ m \leq n \land n \leq p \Rightarrow m \leq p$ \\
-            \hline
-            $\mb{\mathsf{n\mathord{\leq}suc\text{-}n}}$ & $\forall n \in \bN.\ n \leq \textsf{suc } n$ \\
-            \hline
-            $\mb{\mathsf{m\mathord{\equiv}n,p\mathord{\leq}n\mathord{\to}p\mathord{\leq}m}}$ & $\forall p, m, n \in \bN.\ m \equiv n \land p \leq n \Rightarrow p \leq m$ \\
-            \hline
-            $\mb{\mathsf{\mathord{+}\mathord{\to}\mathord{\leq}}}$ & $\forall m, n \in \bN.\ m \leq m + n$ \\
-            \hline
-            $\mb{\mathsf{\mathord{+}\mathord{\to}\mathord{\leq}^r}}$ & $\forall m, n \in \bN.\ m \leq n + m$ \\
-            \hline
-            $\mb{\mathsf{\mathord{<}\text{-}trans}}$ & $\forall m, n, p \in \bN.\ m < n \land n < p \Rightarrow m < p$ \\
-            \hline
-            $\mb{\mathsf{\mathord{<}\mathord{\to}s\mathord{\leq}}}$ & $\forall m, n \in \bN.\ m < n \Rightarrow \textsf{suc } m \leq n$ \\
-            \hline
-            $\mb{\mathsf{< \to \leq}}$ & $\forall m, n \in \bN.\ m < n \Rightarrow m \leq n$ \\
+            \mbt{+-identity\textsuperscript{r}} & $\forall n \in \bN.\ n + 0 = n$ \\
+            \hline
+            \mbt{+-suc\textsuperscript{r}}& $\forall m, n \in \bN.\ m + \textsf{suc } n = \textsf{suc } (m + n)$ \\
+            \hline
+            \mbt{+-comm\textsuperscript{r}} & $\forall m, n \in \bN.\ m + n \equiv n + m$ \\
+            \hline
+            \mbt{≤-irrelevant} & For all $m, n \in \bN$, we consider all proofs of $m \leq n$ to be equal. \\
+            \hline
+            \mbt{≤-refl} & $\forall n \in \bN.\ n \leq n$ \\
+            \hline
+            \mbt{≤-trans} & $\forall m, n, p \in \bN.\ m \leq n \land n \leq p \Rightarrow m \leq p$ \\
+            \hline
+            \mbt{n≤suc-n} & $\forall n \in \bN.\ n \leq \textsf{suc } n$ \\
+            \hline
+            \mbt{m≡n,p≤n}\mb{$\to$}\mbt{p≤m} & $\forall p, m, n \in \bN.\ m \equiv n \land p \leq n \Rightarrow p \leq m$ \\
+            \hline
+            \mbt{+}\mb{$\to$}\mbt{≤} & $\forall m, n \in \bN.\ m \leq m + n$ \\
+            \hline
+            \mbt{+}\mb{$\to$}\mb{≤\textsuperscript{r}} & $\forall m, n \in \bN.\ m \leq n + m$ \\
+            \hline
+            \mbt{<-trans} & $\forall m, n, p \in \bN.\ m < n \land n < p \Rightarrow m < p$ \\
+            \hline
+            \mbt{<}\mb{$\to$}\mbt{s≤} & $\forall m, n \in \bN.\ m < n \Rightarrow \textsf{suc } m \leq n$ \\
+            \hline
+            \mbt{<}\mb{$\to$}\mbt{≤} & $\forall m, n \in \bN.\ m < n \Rightarrow m \leq n$ \\
+            \hline
+            \mbt{≤-compare} & $\forall m, n \in \bN.\ m \leq n \lor n \leq m$ \\
             \hline
@@
 
-    The detailed definitions are included in Appendix~[TBD].
-
     % \subsection{Natural numbers, integers and addition} \label{subsec: natural_numbers}
@@
 
-    \subsubsection{Totality of order} \label{subsubsec: order_totality}
-    It is useful to case split the order of natural numbers, i.e.
+    % \subsubsection{Totality of order} \label{subsubsec: order_totality}
+    % It is useful to case split the order of natural numbers, i.e.
 for any $m, n \in \bN$, we have $m \leq n$ or $n \leq m$.
@@
 The proof is as follows:
-    \[\includegraphics[scale=1.2]{/lib/order_totality.pdf}\]
+    % \[\includegraphics[scale=1.2]{/lib/order_totality.pdf}\]
 
@@
         \item 
-            The definition of subtraction is not rigorous.
+            The definition of $\dotdiv$ is not suitable for this project.
 Input $n$ should be guaranteed not to be less than $m$, and at any point in the program if there is a subtraction where $n < m$, the program should fail to type check instead of making $0$ type check with it.
         \item
-            We lose many numerical properties of natural numbers.
+            We do not have many numerical properties of natural numbers that are required for the implementation of the compiler.
 For example, $n \dotdiv m + m = n$ or $n \dotdiv (n \dotdiv m) = m$ are not guaranteed to hold if we allow $n < m$.
-Those properties are very useful for the implementation of the compiler.
-    \end{itemize}
-    We need a more rigorous definition of subtraction that ensures the result is a natural number and preserves the numerical properties.
+    \end{itemize}
+    A definition of subtraction that ensures the result is a natural number and preserves the numerical properties is required for the implementation of the compiler.
 The key is to have a proof that the first argument is greater than or equal to the second argument.
-There are two approaches to achieve this:
+There are two approaches to achieve this: passing proofs explicitly or using \textsf{Fin}, a dependent type that encodes the proof of boundedness.
 
@@
 
-    Here is a comparison of the two approaches representing the property $\mathsf{suc}\ (n - m) \equiv \mathsf{suc}\ n - m$:
+    Here is a comparison of the two approaches representing  $\mathsf{suc}\ (n - m) \equiv \mathsf{suc}\ n - m$:
     \begin{figure}[H]
@@
 
-    Although the project completed both approaches, the following implementation of the compiler uses the explicit proof-passing approach due to its clarity.
-
-    \subsection{More properties of natural numbers} \label{subsec: more_properties}
+    Although the project completed both approaches, the following implementation of the compiler presents the explicit proof-passing approach due to its clarity.
+
+    \subsection{Properties with subtractions} \label{subsec: properties_sub}
     Given the definition of subtraction, the additional properties of natural numbers are summarised in the table below:
@@
             \hhline{|=|=|}
-            $\mb{\mathsf{-\text{-}irrelevant}}$ & \makecell{For all $m, n \in \bN$, we consider all terms of $n-m$ \\ with different proofs of $m \leq n$ to be equal.} \\
-            \hline
-            $\mb{\mathsf{\mathord{-}\mathord{\to}\mathord{\leq}}}$ & $\forall m, n \in \bN.\ m \leq n \Rightarrow m - n \leq m$ \\
-            \hline
-            $\mb{\mathsf{n\mathord{-}n\mathord{\equiv}0}}$ & $\forall n \in \bN.\ n - n \equiv 0$ \\
-            \hline
-            $\mb{\mathsf{\mathord{-}\text{-}suc}}$ & $\forall m, n \in \bN.\ \mathsf{suc}\ (n - m) \equiv \mathsf{suc}\ n - m$ \\
-            \hline
-            $\mb{\mathsf{n\mathord{-}[n\mathord{-}m]\mathord{\equiv}m}}$ & $\forall m, n \in \bN.\ m \leq n \Rightarrow n - (n - m) \equiv m$ \\
-            \hline
-            $\mb{\mathsf{n\mathord{+}m\mathord{-}m\mathord{\equiv}n}}$ & $\forall m, n \in \bN.\ n + m - m \equiv n$ \\
-            \hline
-            $\mb{\mathsf{suc\text{-}d\mathord{\leq}d'\mathord{\to}d'\mathord{-}[d'\mathord{-}[suc\text{-}d]]}}$ & $\forall d, d' \in \bN.\ \textsf{suc } d \leq d' \Rightarrow d \leq d' - (d' - \textsf{suc } d)$ \\
+            \mbt{–-irrelevant} & \makecell{For all $m, n \in \bN$, we consider all terms of $n-m$ \\ with different proofs of $m \leq n$ to be equal.} \\
+            \hline
+            \mbt{–}\mb{$\to$}\mbt{≤}& $\forall m, n \in \bN.\ m \leq n \Rightarrow m - n \leq m$ \\
+            \hline
+            \mbt{n–n≡0} & $\forall n \in \bN.\ n - n \equiv 0$ \\
+            \hline
+            \mbt{–-suc} & $\forall m, n \in \bN.\ \mathsf{suc}\ (n - m) \equiv \mathsf{suc}\ n - m$ \\
+            \hline
+            \mbt{n–[n–m]≡m} & $\forall m, n \in \bN.\ m \leq n \Rightarrow n - (n - m) \equiv m$ \\
+            \hline
+            \mbt{n+m–m≡n} & $\forall m, n \in \bN.\ n + m - m \equiv n$ \\
+            \hline
+            \mbt{suc-d≤d′}\mb{\to}\mbt{d≤d′–[d′–[suc-d]]} & $\forall d, d' \in \bN.\ \textsf{suc } d \leq d' \Rightarrow d \leq d' - (d' - \textsf{suc } d)$ \\
             \hline
@@
 
-    The equations in the table above are used later in the implementation of the compiler to prove that for instructions with displacement, the given displacement is valid.
+    % The equations in the table above are used later in the implementation of the compiler to prove that for instructions with displacement, the given displacement is valid.
 Here is the mathematical proof of the property $\mb{\mathsf{n\mathord{-}[n\mathord{-}m]\mathord{\equiv}m}}$:
-    \begin{proof}
-        We need to show that $n - (n - m) \equiv m$ for all $m, n \in \bN$ such that $m \leq n$. We do the following case split:
-        \begin{itemize}
-            \item 
-                If $m = 0$, then the term reduces to $n - n \equiv 0$, which is a term we have already proved.
-            \item
-                Otherwise it is guaranteed that $m = \mathsf{suc}\ m'$ for some $m' \in \bN$, and $n = \mathsf{suc}\ n'$ for some $n' \in \bN$, because $m \leq n$.
+    % \begin{proof}
+    %     We need to show that $n - (n - m) \equiv m$ for all $m, n \in \bN$ such that $m \leq n$. We do the following case split:
+    %     \begin{itemize}
+    %         \item 
+    %             If $m = 0$, then the term reduces to $n - n \equiv 0$, which is a term we have already proved.
+    %         \item
+    %             Otherwise it is guaranteed that $m = \mathsf{suc}\ m'$ for some $m' \in \bN$, and $n = \mathsf{suc}\ n'$ for some $n' \in \bN$, because $m \leq n$.
 The term reduces to $\mathsf{suc}\ n' - (n' - m') \equiv \mathsf{suc}\ m'$.
 With congruence, we can reduce the term to $n' - (n' - m') \equiv m'$, which is the inductive hypothesis.
-        \end{itemize}
-    \end{proof}
-    The full implementation of the properties is included in Appendix~[TBD].
+    %     \end{itemize}
+    % \end{proof}
 
@@
 
-    \section{Compiler}
+    \section{Compiler} \label{sec: compiler}
+    This section develops the semantic foundation of the compiler, starting with the presheaf semantics of the target language.
+Building on this framework, I introduce the continuation-passing constructs to model control flow, enabling a simplified denotational semantics of types and contexts.
+I then derive a functorial mapping of semantics terms and the target terms.
+This section concludes with the implementation of the compiler from the denotational semantics of terms in the source language.
     \subsection{Presheaf semantics}
@@
     \begin{itemize}
-        \item Objects are stack descriptors ($sd = \ang{f, d}$);
-        \item Morphisms are stack expansions ($\iota : sd \to sd'$ for $sd \leq_\mathsf{s} sd'$).
+        \item Objects are stack descriptors ($\textit{sd} = \ang{f, d}$);
+        \item Morphisms are stack expansions ($\iota : \textit{sd} \to \textit{sd′}$ for $\textit{sd} \leq_\mathsf{s} \textit{sd′}$).
     \end{itemize}
@@
     \begin{itemize}
-        \item Products are given by pointwise product of presheaves: $P \times Q = \lambda sd.\ P\ sd \times Q\ sd$.
+        \item Products are given by pointwise product of presheaves: $P \times Q = \lambda \textit{sd}.\ P\ \textit{sd} \times Q\ \textit{sd}$.
         \item Exponentials $P \Rightarrow_s Q$ are given by the following equation:
-            \begin{equation}
-                \begin{aligned}
-                    P \Rightarrow_s Q &= \lambda sd.\ \mathcal{K}(\yo (sd) \times P, Q) \\
-                    &\cong \lambda sd.\{F \mid sd' \in \Upsigma^{\textbf{op}}, F : (\yo (sd) \times P)\ sd' \to Q\ sd'\} \\
+                \[\begin{aligned}
+                    P \Rightarrow_s Q &= \lambda \textit{sd}.\ \mathcal{K}(\yo (\textit{sd}) \times P, Q) \\
+                    &\cong \lambda \textit{sd}.\{F \mid \textit{sd′} \in \Upsigma^{\textbf{op}}, F : (\yo (\textit{sd}) \times P)\ \textit{sd′} \to Q\ \textit{sd′}\} \\
                     &\makebox[0.8\linewidth][r]{\text{by definition of morphisms in Definition~\ref{def: category}}}\\
-                    &\cong \lambda sd.\{F \mid sd' \in \Upsigma^{\textbf{op}}, F : (\Upsigma^{\textbf{op}}(sd', sd) \times P)\ sd' \to Q\ sd'\} \\
+                    &\cong \lambda \textit{sd}.\{F \mid \textit{sd′} \in \Upsigma^{\textbf{op}}, F : (\Upsigma^{\textbf{op}}(\textit{sd′}, \textit{sd}) \times P)\ \textit{sd′} \to Q\ \textit{sd′}\} \\
                     &\makebox[0.8\linewidth][r]{\text{by definition of $\yo$ in Definition~\ref{def: yoneda}}}\\
-                    &\cong \lambda sd.\{F \mid sd' \in \Upsigma, F : (\Upsigma(sd, sd') \times P)\ sd' \to Q\ sd'\} \\
+                    &\cong \lambda \textit{sd}.\{F \mid \textit{sd′} \in \Upsigma, F : (\Upsigma(\textit{sd}, \textit{sd′}) \times P)\ \textit{sd′} \to Q\ \textit{sd′}\} \\
                     &\makebox[0.8\linewidth][r]{\text{by definition of opposite category in Definition~\ref{def: opposite}}}\\
-                    &\cong \lambda sd.\{F \mid sd' \in \Upsigma, F : sd \leq_\mathsf{s} sd' \to P\ sd' \to Q\ sd'\} \\
+                    &\cong \lambda \textit{sd}.\{F \mid \textit{sd′} \in \Upsigma, F : \textit{sd} \leq_\mathsf{s} \textit{sd′} \to P\ \textit{sd′} \to Q\ \textit{sd′}\} \\
                     &\makebox[0.8\linewidth][r]{\text{by definition of $\Upsigma$ above}}\\
-                \end{aligned}
-                \label{eq: presheaf_exponential}
-            \end{equation}
+                \end{aligned}\]
     \end{itemize}
@@
     \begin{itemize}
-        \item $sd \leq_\mathsf{s} sd'$ means the new stack descriptor $sd'$ is larger than the old stack descriptor $sd$, representing the dynamic expansion of the stack during execution.
+        \item $\textit{sd} \leq_\mathsf{s} \textit{sd′}$ means the new stack descriptor $\textit{sd′}$ is larger than the old stack descriptor $\textit{sd}$, representing the dynamic expansion of the stack during execution.
 
@@
     \end{itemize}
-    The exponential $P \Rightarrow_\textsf{s} Q$ is a function that given a proof of stack growth, transforming a $P$-value at $sd'$ into a $Q$-value at $sd'$, and the $\forall{sd'}$ quantifier guarantees it works no matter how the stack grows.
+    The exponential $P \Rightarrow_\textsf{s} Q$ is a function that given a proof of stack growth, transforming a $P$-value at $\textit{sd′}$ into a $Q$-value at $\textit{sd′}$, and the $\forall{\textit{sd′}}$ quantifier guarantees it works no matter how the stack grows.
 It is designed in this way so that a functor $\intp{-} : \Theta \to \mathcal{K}$ exists that interprets the type constructor $\Rightarrow$ as the exponential functor $\Rightarrow_s$.
@@
 Mathematically we have
-    \[\mathsf{Compl}\ sd : \mathsf{SD} \to O \qquad \mathsf{Intcompl}\ sd : \bZ \to (\mathsf{SD} \to O)\]
+    \[\mathsf{Compl}\ \textit{sd} : \mathsf{SD} \to O \qquad \mathsf{Intcompl}\ \textit{sd} : \bZ \to (\mathsf{SD} \to O)\]
     where $O$ is an unspecified domain of outputs.
 
-    For code generation we define the continuation to be the instruction sequence in the target language:
-    \[\mathsf{Compl}\ sd = \textsf{I}_{sd}\]
+    For code generation I define the continuation to be the instruction sequence in the target language:
+    \[\mathsf{Compl}\ \textit{sd} = \textsf{I}_{\textit{sd}}\]
 
@@
     \[\mathsf{Intcompl} = R \Rightarrow_s \mathsf{Compl} \]
-    where $R$ is the functor corresponding to the right-hand sides in the target language, $R\ sd = \textsf{R}_{sd}$.
+    where $R$ is the functor corresponding to the right-hand sides in the target language, $R\ \textit{sd} = \textsf{R}_{\textit{sd}}$.
 This works because the right-hand sides are all integer expressions we can use according to the grammar of the target language.
+The functorial mapping is defined later in~\secref{subsec: functorial_mapping}.
 
@@
     The denotational semantics of contexts is essentially a list expressed by the product of the denotational semantics of the types in the context.
-The denotational semantics of contexts is defined as follows, where we use $\mb{\varnothing}$ to denote the denotational semantics of the empty context:
+The denotational semantics of contexts is defined as follows, where we use \mb{∅} to denote the denotational semantics of the empty context:
     \[\includegraphics[scale=1.2]{/compiler/context_interpretation.pdf}\]
 
-    \subsection{Functorial mapping}
-    The denotational semantics of terms is defined as a functor, defined in~\secref{def: functor}.
+    \subsection{Functorial mapping} \label{subsec: functorial_mapping}
+    The denotational semantics of terms is defined as a functor.
 Before we define its object mapping, we need to define the functorial mapping, which acts on the morphisms of the base category $\Upsigma$.
 
-    Since the morphisms of the base category $\Upsigma$ are stack expansions, the functorial mapping essentially lifts a semantic object indexed by a stack descriptor $sd$ to a semantic object indexed by a larger stack descriptor $sd'$.
+    Since the morphisms of the base category $\Upsigma$ are stack expansions, the functorial mapping essentially lifts a semantic object indexed by a stack descriptor $\textit{sd}$ to a semantic object indexed by a larger stack descriptor $\textit{sd′}$.
 This ensures the denotational semantics of terms remains valid when the stack grows.
 
-    \subsubsection{Functorial mapping for exponentials, products, contexts and types}
-    Functorial mapping for exponentials is simple, as the original exponential can transforms a $P$-value at any $sd'$ greater than $sd''$ into a $Q$-value at $sd'$.
-To construct a new exponential, we simply take a new $P$-value at $ad''$ which is greater than $sd'$, and use the original exponential to transform it into a $Q$-value at $sd'$, as $sd''$ is guaranteed to be greater than $sd$ due to the transitivity of order of the stack descriptors.
-
-    Functorial mapping for products is defined pointwise.
-
-    Thus, functorial mapping of types can be defined simply use the definition of functorial mapping of products and exponentials, as denotational semantics of types is defined as either product or exponential.
+    Functorial mapping for exponentials is simple, as the exponential \textit{P} $\mathsf{\Rightarrow_\textsf{S}}$ \textit{Q} \textit{sd} can transforms a $P$-value at any $\textit{sd′}$ greater than $\textit{sd}$ into a $Q$-value at $\textit{sd′}$.
+To construct a new exponential of type $\mathsf{P \Rightarrow_\textsf{S} Q\ \textit{sd′}}$, we simply take a new $P$-value at $\textit{sd″}$ which is greater than $\textit{sd′}$, and use the original exponential to transform it into a $Q$-value at $\textit{sd′}$, as $\textit{sd″}$ is guaranteed to be greater than $\textit{sd}$ due to the transitivity of order of the stack descriptors.
+
+    Functorial mapping for types can be defined based on functorial mapping of exponentials and products (defined point-wise), as denotational semantics of types is defined as either product or exponential.
 As a list of types, the functorial mapping of contexts is simply a map of the functorial mapping of types in the list.
@@
 
-    \subsubsection{Functoral mapping for left-hand sides and simple right-hand sides}
     Similarly, we can use transitivity of order to define the functorial mapping of the denotational semantics of left-hand sides, as the definition of left-hand sides requires a proof.
-Since simple right-hand sides are defined from left-hand sides and literals
+Since simple right-hand sides are defined from left-hand sides and literals, we can use the functorial mapping of left-hand sides to define the functorial mapping of simple right-hand sides.
+The functorial mapping of the denotational semantics of left-hand sides and simple right-hand sides is defined as follows:
     \[\includegraphics[scale=1.2]{/compiler/fmap_LS.pdf}\]
-
-    \subsubsection[Functorial mapping for instruction sequences]{Functorial mapping for instruction sequences\footnote{In the work of Reynolds, the functorial mapping of instruction sequences is presented as the functorial mapping of $\mathsf{Compl}$.
-The two definitions are equivalent as we define $\mathsf{Compl}\ sd = \textsf{I}_{sd}$.
-However, I think it is more natural to present it as the functorial mapping of instruction sequences, as the definition consists of instruction sequences.}}
-    The functorial mapping of the denotational semantics of instruction sequences is defined as follows, assuming the stack descriptor $sd' = \ang{f',d'}$ is greater than $sd = \ang{f,d}$:
-    \begin{itemize}
-        \item When $f < f'$, we use the $\mathsf{popto}$ instruction that directly pops the stack to $sd$;
+    Similarly, the functorial mapping of right-hand sides can be defined based on the functorial mapping of simple right-hand sides.
+Since it is not used in the implementation of the compiler, the definition is omitted here.
+
+    \subsubsection[Functorial mapping for instruction sequences]{Functorial mapping for instruction sequences}
+    The functorial mapping of the denotational semantics of instruction sequences is defined as follows, assuming the stack descriptor $\textit{sd′} = \ang{f',d'}$ is greater than $\textit{sd} = \ang{f,d}$:
+    \begin{itemize}
+        \item When $f < f'$, we use the $\mathsf{popto}$ instruction that directly pops the stack to $\textit{sd}$;
         \item When $f' = f$ and $d < d'$, we use $\mathsf{adjustdisp}$ to decrease the displacement by $d'-d$.
     \end{itemize}
-    In the Agda implementation, we also need to show that after the the adjustment, the stack descriptor is now $sd$.
-This requires the term $\mb{\mathsf{n\mathord{-}[n\mathord{-}m]\mathord{\equiv}m}}$ proved in~\secref{subsec: more_properties}.
+    In the Agda implementation, we also need to show that after the the adjustment, the stack descriptor is now $\textit{sd}$.
+This requires the term $\mb{\mathsf{n\mathord{-}[n\mathord{-}m]\mathord{\equiv}m}}$ proved in~\secref{subsec: properties_sub}.
 The functorial mapping of the denotational semantics of instruction sequences is defined as follows:
@@
 
-    \subsection{Denotational semantics of terms}
+    \subsection{Compilation}
     The denotational semantics of terms is defined as a morphism from the denotational semantics of contexts to the denotational semantics of types.
+The denotational semantics of terms is a functor from the source language to the target language, which directly yields a compiler.
 Similarly, it is a family of continuous functions indexed by the stack descriptor.
@@
 
-    We need to find out the denotational semantics of the terms corresponding to all rules in the typing judgement mentioned in~\secref{subsec: terms}.
+    The denotational semantics of the terms corresponding to all rules in the typing judgement mentioned in~\secref{subsec: terms} is defined as follows:
 
@@
         \begin{itemize}
-            \item For integer variables as subtypes of integer expressions and integer acceptors, since we defined the denotational semantics of integer variable as product of the denotational semantics of integer expression and integer acceptor in~\secref{subsec: type_interpretation}, I can simply use the projection to get the denotational semantics of either side.
-            \item For reflexivity, we simply use the identity function.
-            \item For transitivity, we use the composition of the two functions.
-            \item For contravariant function subtyping, we use a contravariant function.
+            \item For \gnt{var-≤:-exp} and \gnt{⟦var-≤:-acc}, sincethe denotational semantics of integer variable is defined as product of the denotational semantics of integer expression and integer acceptor in~\secref{subsec: type_interpretation}, we can simply use the projection to get the denotational semantics of either side.
+            \item For \gnt{≤:-refl}, we can simply use the identity function.
+            \item For \gnt{≤:-trans}, we can use the composition of the two functions.
+            \item For \gnt{≤:-fn}, we can use a contravariant function.
         \end{itemize}
@@
 
-        \subsubsection{Commands}
+        \subsubsection{Command}
         \begin{itemize}
@@
 
-        The denotational semantics of new variable is more complicated.
-We first place a new variable in the stack with the current stack descriptor $sd'$ by assigning literal $0$ with the current stack descriptor $sd'$ and set the displacement adjustment to $1$, which corresponds to the place taken by this new variable.
-Then we do the command in \textsf{NewVar}, deallocate the new variable and do the rest of the commands in the continuation by applying the denotational semantics of the command in \textsf{NewVar} to an $\mathsf{adjustdisp}$ instruction that adjusts the displacement by $-1$, followed by the continuation $\kappa$.
-Here the new stack descriptor used is $sd' +_s 1$.
-The new environment (denotational semantics of context) $\gamma'$ is the old environment $\gamma$ with the denotational semantics of the new variable added.
-
+        \paragraph{New variable}
+        The denotational semantics of \gnt{NewVar} command is more complicated. We prefix the continuation with the following in order:
+        \begin{enumerate}
+            \item an assignment with displacement adjustment $1$, representing the new variable;
+            \item the denotational semantics of the command where this variable is used;
+            \item an adjustment of the stack descriptor by $-1$, which deallocates the new variable.
+        \end{enumerate}
+        In step 2, the denotational semantics of the command in \textsf{NewVar} needs to be applied to
+        \begin{itemize}
+            \item a stack descriptor increased by $1$ to include the new variable;
+            \item an extended denotational semantics of the context, which includes the new variable.
+        \end{itemize}
         The denotational semantics of the new variable is a product of the denotational semantics of an integer expression and the denotational semantics of an integer acceptor by definition in~\secref{subsec: type_interpretation}.
@@
 
-        \subsubsection{Integer expressions} \label{subsubsec: compiler_intexp}
-        \begin{itemize}
-            \item For integer literals, we simply fill in the integer literal (as an $\mathsf{R}$ term) to the integer continuation $\beta$.
-            \item For plus and negation, we wish to fill the negation of the given expression or the sum of the two given expressions to the integer continuation $\beta$.
+        \subsubsection{Integer expression} \label{subsubsec: compiler_intexp}
+        The denotational semantics of type $\mathsf{intexp}$ is an exponential from an integer continuation to a command continuation.
+We need to fill the integer continuation with appropriate $R$ terms to get the command continuation.
+        \begin{itemize}
+            \item For integer literals, we can simply fill in the integer literal (as an $\mathsf{R}$ term) to the integer continuation $\beta$.
+            \item For addition and negation, we wish to fill the negation or the sum of the given expression(s) to the integer continuation $\beta$.
 However, this is only possible when the given expression(s) are simple left-hand sides, as the grammar of the target language in Figure~\ref{fig: target_grammar} restricts right-hand sides to contain at most one operator.
-To solve this problem, we introduce an auxiliary function \textsf{use-temp}.
-        \end{itemize}
+An auxiliary function \textsf{use-temp} that stores the intermediate result of given expressions is introduced to solve this problem.
+        \end{itemize}
+        With \textsf{use-temp}, the denotational semantics of addition and negation is simply wrapping $\beta$ with a lambda function using \textsf{use-temp} to get temporary variable(s) of the given expression(s), and directly fill the negation or the sum of the variable(s) to the integer continuation $\beta$.
+Note that in the denotational semantics of addition, we need to use the functorial mapping of simple right-hand sides for the first argument, as the stack may grow during the evaluation of the second argument.
+The denotational semantics of integer expressions is defined as follows:
+        \[\includegraphics[scale=1.2]{/compiler/term_intexp.pdf}\]
         The auxiliary function \textsf{use-temp} checks if the given expression is a simple left-hand side,
         \begin{itemize}
-            \item If it is, we simply fill the expression to the integer continuation $\beta$\footnote{The type of $\beta$ here is actually a bit different to integer continuation we defined, as it only accepts simple right-hand sides instead of right-hand sides.
+            \item If it is, we simply fill the expression to the integer continuation $\beta$.\footnote{The type of $\beta$ here is actually a bit different to integer continuation I defined, as it only accepts simple right-hand sides instead of right-hand sides.
 Reynolds gave a wrong definition of the type of this term.
-I have corrected it in my Agda implementation.}.
+I have corrected it in my Agda implementation.}
             \item If it is not, we need to use a temporary variable to store the result of the expression, and then fill the temporary variable to the integer continuation $\beta$.
@@
         \begin{itemize}
-            \item $sd$ is the stack descriptor passed along the environment $\gamma$, describing any program variables that may be accessed during the evaluation of the whole expression (plus/negation on the given expression).
-            \item $sd'$ is the current stack descriptor before the evaluation of the whole expression, which is guaranteed to be not less than $sd$.
-$sd'$ is also the position of the temporary variable in the stack.
-            \item $sd''$ is the current stack descriptor after the evaluation on the given expression and just before the assignment of the temporary variable.
-$sd''$ is guaranteed to be not less than $sd'$.
-            \item $sd''' = sd' +_s 1$ is the stack descriptor after the assignment of the temporary variable, as it is just large enough to hold the temporary variable.
-        \end{itemize}
-        In Reynolds' model, we simply adjust the stack descriptor from $sd''$ to $sd'''$ by the adjustment $\delta$ in the assignment instruction.
-However, in the Agda implementation, we need to know whether the adjustment is positive or negative, using \textsf{assign-inc} and \textsf{assign-dec} respectively.
+            \item \textit{sd} is the stack descriptor before the evaluation of plus or negation, which is the position of the temporary variable in the stack.
+            \item \textit{sd′} is the stack descriptor after the evaluation on the given expression and just before the assignment of the temporary variable. \textit{sd} ≤ₛ \textit{sd′} is guaranteed.
+            \item \textit{sd″} = \textit{sd} +ₛ 1 is the stack descriptor after the assignment of the temporary variable, as it is just large enough to hold the temporary variable.
+        \end{itemize}
+        In Reynolds' model, the stack descriptor can be directly adjusted from \textit{sd′} to \textit{sd″}.
+However, in the Agda implementation, we need to know whether the adjustment is positive or negative and use \textsf{assign-inc} or \textsf{assign-dec} respectively.
+This is done by using \mbt{≤-compare} in Table~\ref{tab: properties}.
 We also need to show that the adjustment is valid for each case.
-This is done by using the totality of order of natural numbers mentioned in~\secref{subsubsec: order_totality} and case split.
 Please refer to Appendix~[TBD] for the full implementation of the function \textsf{use-temp}.
@@
 
-        Given the definition of \textsf{use-temp}, the denotational semantics of plus and negation is simply wrapping $\beta$ with a lambda function using \textsf{use-temp} to get the temporary variable, and directly fill the plus/negation of the variable to the integer continuation $\beta$.
-Note that in the denotational semantics of plus, we need to use the functorial mapping of simple right-hand sides for the first argument, as the stack may grow during the evaluation of the second argument.
-The denotational semantics of integer expressions is defined as follows:
-        \[\includegraphics[scale=1.2]{/compiler/term_intexp.pdf}\]
-
-    \subsection{Compilation} \label{subsec: compilation}
-    Compilation is a functor from the source language to the target language.
-To define the compilation functor, we use the denotational semantics of terms and fill in the initial stack descriptor ($\ang{0, 0}$), the empty context (\textsf{unit}), a trivial proof for stack descriptor being not less than itself ($\mathsf{\mathord{\leq_s}\text{-}refl}$) and the continuation representing the last instruction (\textsf{stop}):
+        \subsubsection{Compilation for closed program} \label{subsubsec: compilation}
+        To define a compilation function for closed programs in the source language, we use the denotational semantics of terms and fill in the initial stack descriptor ($\ang{0, 0}$), the empty context (\textsf{unit}), a trivial proof for stack descriptor being not less than itself (\textsf{≤ₛ-refl}) and the continuation representing the last instruction (\textsf{stop}):
         \[\includegraphics[scale=1.2]{/compiler/compilation.pdf}\]
@@
     \minitoc
-    Chapter~\chapref{chap: implementation} describes the implementation of the source language, the target language and the compiler in Agda.
     This chapter evaluates the implementation with integration tests and a feature checklist and then discusses the success criteria of the project.
     \section{Tests}
+    The best way to evaluate a formalised compiler project is to formalise compiler correctness, which requires the full definition of the operational semantics of the source language and the target language, and then prove that for any program $e$ in the source language and the program $e'$ it compiles to in the target language, the value $v'$ that $e'$ evaluates to is also the compilation of the value $v$ that $e$ evaluates to.
+Due to time limitations, this is beyond the scope of this project.
+Instead, I used a set of integration tests that covers all features of the source language and the target language to evaluate the correctness of the compiler.
+All of the test cases have been passed successfully.
+
     \subsection{Test cases}
-    The correctness of the compiler is evaluated with a set of test cases. Each test is defined as follows
+    Each test case is an Agda program defined with the follow syntax, where \gn{\textsf{Skip}} is replaced with any closed program in the source language and \gn{\textsf{stop}} is replaced with the expected compiled result in the target language:
     \begin{figure}[H]
@@
     \end{figure}
-    where definition of the \mb{\textsf{compile-closed}} function is specified in~\secref{subsec: compilation}.
-The program type checks only if both of the source term and the target term are correctly defined, and the target term is the result of the compilation of the source term.
+    where definition of the \mb{\textsf{compile-closed}} function is specified in~\secref{subsubsec: compilation}.
+Each test case type checks only if both the source term and target term are well-typed, and the compiled result of the source term is definitionally equal to the target term.
 
@@
         \includegraphics[scale=1.2]{/test/equivalence.pdf}
-        \caption{Test 3' as an example for checking equivalent compiled results}
-        \label{fig: test_case_3'}
+        \caption{Test 3′ as an example for checking equivalent compiled results}
+        \label{fig: test_case_3′}
     \end{figure}
 
-    The full test cases are available in the appendix [insert link]. Here is a summary of the test cases written in a more readable format:
-    \begin{enumerate}[label=\textbf{Test \arabic*.}, leftmargin=*]
-        \setcounter{enumi}{-1}
-        \item $\mathsf{skip}$
-        \item $\mathsf{x := 2}$
-        \item $\mathsf{x := (\mathnormal{\lambda} a.\ a)\ 4}$
-        \item $\mathsf{x := (\mathnormal{\lambda} a.\ (\mathnormal{\lambda} b.\ a+b)\ 2)\ 3}$
-        \item[\textbf{Test 3'.}] $\mathsf{x := 3 + 2}$
-        \item $\mathsf{x := -3;\ y := (\mathnormal{\lambda} a. x)\ 2}$
-        \item $\mathsf{x := 2;\ x := x + 1}$
-        \item[\textbf{Test 5'.}] $\mathsf{x := 2;\ skip;\ x := x + 1}$
-        \item $\mathsf{x := 2;\ x := -x + 1}$
-        \item $\mathsf{x := (\mathnormal{\lambda} a.\ -a+1)\ 2}$
-    \end{enumerate}
-    where \textbf{Test 3} and \textbf{Test 3'}, \textbf{Test 5} and \textbf{Test 5'} compile to the same target term.
-
-    \textbf{Test 3} and \textbf{Test 3'} are equivalent in terms of compilation because the compilation directly substitutes the value in corresponding lambda terms.
-
-    \textbf{Test 5} and \textbf{Test 5'} are equivalent in terms of compilation because $\mathsf{skip}$ is a no-op in the source language.
+    The full test cases are available in the appendix [TBD]. Here is a summary of the test cases:
+    % \begin{enumerate}[label=\textbf{Test \arabic*.}, leftmargin=*]
+    %     \setcounter{enumi}{-1}
+    %     \item $\mathsf{skip}$
+    %     \item $\mathsf{x := 2}$
+    %     \item $\mathsf{x := (\mathnormal{\lambda} a.\ a)\ 4}$
+    %     \item $\mathsf{x := (\mathnormal{\lambda} a.\ (\mathnormal{\lambda} b.\ a+b)\ 2)\ 3}$
+    %     \item[\textbf{Test 3′.}] $\mathsf{x := 3 + 2}$
+    %     \item $\mathsf{x := -3;\ y := (\mathnormal{\lambda} a. x)\ 2}$
+    %     \item $\mathsf{x := 2;\ x := x + 1}$
+    %     \item[\textbf{Test 5′.}] $\mathsf{x := 2;\ skip;\ x := x + 1}$
+    %     \item $\mathsf{x := 2;\ x := -x + 1}$
+    %     \item $\mathsf{x := (\mathnormal{\lambda} a.\ -a+1)\ 2}$
+    % \end{enumerate}
+    \begin{table}[H]
+        \centering
+        \begin{tabular}{| c | c |}
+            \hline
+            \textbf{Test case} & \textbf{Source term} \\
+            \hhline{|=|=|}
+            \textbf{Test 0} & $\mathsf{skip}$ \\
+            \hline
+            \textbf{Test 1} & $\mathsf{x := 2}$ \\
+            \hline
+            \textbf{Test 2} & $\mathsf{x := (\mathnormal{\lambda} a.\ a)\ 4}$ \\
+            \hline
+            \textbf{Test 3} & $\mathsf{x := (\mathnormal{\lambda} a.\ (\mathnormal{\lambda} b.\ a+b)\ 2)\ 3}$ \\
+            \hline
+            \textbf{Test 3′} & $\mathsf{x := 3 + 2}$ \\
+            \hline
+            \textbf{Test 4} & $\mathsf{x := -3;\ y := (\mathnormal{\lambda} a. x)\ 2}$ \\
+            \hline
+            \textbf{Test 5} & $\mathsf{x := 2;\ x := x + 1}$ \\
+            \hline
+            \textbf{Test 5′} & $\mathsf{x := 2;\ skip;\ x := x + 1}$ \\
+            \hline
+            \textbf{Test 6} & $\mathsf{x := 2;\ x := -x + 1}$ \\
+            \hline
+            \textbf{Test 7} & $\mathsf{x := (\mathnormal{\lambda} a.\ -a+1)\ 2}$ \\
+            \hline
+        \end{tabular}
+        \caption{Test cases}
+        \label{tab: test_cases}
+    \end{table}
+    where \textbf{Test 3} and \textbf{Test 3′}, \textbf{Test 5} and \textbf{Test 5′} compile to the same target term.
+
+    \textbf{Test 3} and \textbf{Test 3′} are equivalent in terms of compilation because the compilation directly substitutes the value in corresponding lambda terms.
+
+    \textbf{Test 5} and \textbf{Test 5′} are equivalent in terms of compilation because $\mathsf{skip}$ is a no-op in the source language.
 
@@
     Traditional unit tests are not suitable for this project, as many typing judgement rules cannot be tested in isolation.
-For example, testing subtyping rule (Figure~\ref{fig: rule_subtype}) or any of the integer expression typing rules (Figure~\ref{fig: rule_intexp}) inherently requires embedding them in a well-typed command (\textsc{NewVar} in Figure~\ref{fig: rule_comm}), as the compiler only accepts complete commands.
+For example, testing subtyping rule (Figure~\ref{fig: rule_subtype}) or any of the integer expression typing rules (Figure~\ref{fig: rule_intexp}) inherently requires embedding them in a well-typed command (\textsc{NewVar} in Figure~\ref{fig: rule_comm_2}), as the compiler only accepts complete commands.
 
@@
             \hline
-            \textbf{Feature}  & \textbf{Typing judgement} & \textbf{Specification} & \textbf{Test cases number} \\
+            \textbf{Feature}  & \textbf{Typing judgement} & \textbf{Specification} & \textbf{Test cases} \\
             \hhline{|=|=|=|=|}
-            Variable & \textsc{Var} & - & 1, 2, 3, 3', 4, 5, 5', 6, 7 \\ \cline{3-4}
+            Variable & \textsc{Var} & - & 1, 2, 3, 3′, 4, 5, 5′, 6, 7 \\ \cline{3-4}
             \hline
@@
                 & \multirow{2}{*}{\textsc{Sub}} 
-                    & \textsf{intvar} $\leq:$ \textsf{intacc} & 1, 2, 3, 3', 4, 5, 5', 6, 7  \\ \cline{3-4}
-                &   & \textsf{intvar} $\leq:$ \textsf{intexp} & 4, 5, 5', 6 \\
+                    & \textsf{intvar} $\leq:$ \textsf{intacc} & 1, 2, 3, 3′, 4, 5, 5′, 6, 7  \\ \cline{3-4}
+                &   & \textsf{intvar} $\leq:$ \textsf{intexp} & 4, 5, 5′, 6 \\
             \hline
@@
                     & - & 2, 3, 4, 7 \\ \cline{3-4}
-                &   & Multiple variables\hyperlink{note1}{$^{\ast}$} & 3  \\ \cline{3-4}
-                &   & Free variables\hyperlink{note1}{$^{\ast}$} & 4 \\ \cline{2-4}
+                &   & Multiple variables & 3  \\ \cline{3-4}
+                &   & Free variables & 4 \\ \cline{2-4}
                 & \textsc{App} & - & 2, 3, 4, 7  \\
@@
             \multirow{7}{*}{Command} 
-                & \textsc{Skip} & - & 0, 5' \\ \cline{2-4}
+                & \textsc{Skip} & - & 0, 5′ \\ \cline{2-4}
                 & \multirow{2}{*}{\textsc{Seq}} 
-                    & - & 4, 5, 5', 6 \\ \cline{3-4}
-                &   & Multiple sequencing & 5' \\ \cline{2-4}
+                    & - & 4, 5, 5′, 6 \\ \cline{3-4}
+                &   & Multiple sequencing & 5′ \\ \cline{2-4}
                 & \multirow{2}{*}{\textsc{NewVar}} 
-                    & - & 1, 2, 3, 3', 4, 5, 5', 6, 7 \\ \cline{3-4}
-                &   & Multiple variables\hyperlink{note1}{$^{\ast}$} & 4 \\ \cline{2-4}
+                    & - & 1, 2, 3, 3′, 4, 5, 5′, 6, 7 \\ \cline{3-4}
+                &   & Multiple variables & 4 \\ \cline{2-4}
                 & \multirow{2}{*}{\textsc{Assign}} 
-                    & -  & 1, 2, 3, 3', 4, 5, 5', 6, 7  \\ \cline{3-4}
-                &   & Self-referential assignments & 5, 5', 6 \\
+                    & -  & 1, 2, 3, 3′, 4, 5, 5′, 6, 7  \\ \cline{3-4}
+                &   & Self-referential assignments & 5, 5′, 6 \\
             \hline
@@
                 & \multirow{2}{*}{\textsc{Lit}}  
-                    & Natural number  & 1, 3, 3', 4, 5, 6, 7 \\ \cline{3-4}
+                    & Natural number  & 1, 3, 3′, 4, 5, 6, 7 \\ \cline{3-4}
                 &   & Negative number & 2, 4 \\ \cline{2-4}
-                & \textsc{Neg} & - & 5, 5', 6, 7  \\ \cline{2-4}
-                & \textsc{Plus} & - & 3, 3', 6, 7  \\ \cline{2-4}
-                & -             & Multiple expressions\hyperlink{note2}{$^{\dagger}$} & 6, 7 \\
+                & \textsc{Neg} & - & 5, 5′, 6, 7  \\ \cline{2-4}
+                & \textsc{Plus} & - & 3, 3′, 6, 7  \\ \cline{2-4}
+                & -             & Multiple expressions & 6, 7 \\
             \hline
@@
 
-    Here are some notes on the feature checklist:
-
-    \hypertarget{note1}{$^{\ast}$} These tests ensure that the translation of context as a whole is correct.
-
-    \hypertarget{note2}{$^{\dagger}$} This type of test is necessary because the target language does not support doing multiple integer operations in a single instruction, as specified in Figure~\ref{fig: target_grammar}.
+    The specifications that include multiple variables, free variables and self-referential assignments ensure that the translation of the Debrujin index of the context works correctly under edge cases.
+
+    The specification of multiple expressions in integer expression is necessary because the target language does not support doing multiple integer operations in a single instruction, as specified in Figure~\ref{fig: target_grammar}.
 As a result, special tests are required to check that the compiler correctly translates integer expressions with multiple operations into a continuation of single operations defined in the target language.
 
-    \vspace{2.5em}
-
-    The feature checklist includes all the typing rules in the source language, including edge cases including multiple variables, free variables and self-referential assignments.
+    The feature checklist covers all the typing rules in the source language, including edge cases including multiple variables, free variables and self-referential assignments.
 Additionally, I account for target-language-specific constraints, ensuring multiple operations are translated into simple instructions with continuation.
@@
         \item 
-            The compiler can be extended to support more features, such as subroutines and iterations.
+            The compiler can be extended to support more features from Reynolds' paper~\autocite{Reynolds}, such as subroutines and iterations.
         \item

### 2025-05-17 src/compiler.lagda.tex
draft-ver-2

--- 2025-05-01 src/compiler.lagda.tex
@@
 \usepackage{mathabx}
-
-\usepackage{unicode-math}
-\setmathfont{XITS Math}
+\usepackage{fontspec}
+\setmainfont{Linux Libertine O}
+\setsansfont{Linux Biolinum O}
 
 \usepackage{newunicodechar}
-\newunicodechar{≤}{\ensuremath{\leq}}
-\newunicodechar{≡}{\ensuremath{\equiv}}
-\newunicodechar{∸}{\ensuremath{\dotdiv}}
-\newunicodechar{∀}{\ensuremath{\forall}}
-\newunicodechar{→}{\ensuremath{\rightarrow}}
 \newunicodechar{ℕ}{\ensuremath{\mathbb{N}}}
 \newunicodechar{ℤ}{\ensuremath{\mathbb{Z}}}
-\newunicodechar{δ}{\ensuremath{\delta}}
-\newunicodechar{∈}{\ensuremath{\in}}
-\newunicodechar{⊢}{\ensuremath{\vdash}}
+\newunicodechar{λ}{\ensuremath{\lambda}}
+\newunicodechar{∸}{\ensuremath{\dotdiv}}
+\newunicodechar{→}{\ensuremath{\rightarrow}}
 \newunicodechar{⇒}{\ensuremath{\Rightarrow}}
 \newunicodechar{⟶}{\ensuremath{\longrightarrow}}
-\newunicodechar{ₛ}{\ensuremath{\textsubscript{s}}}
 \newunicodechar{ᵛ}{\ensuremath{\textsuperscript{v}}}
+\newunicodechar{ʳ}{\ensuremath{\textsuperscript{r}}}
+\newunicodechar{⟨}{\ensuremath{\langle}}
+\newunicodechar{⟩}{\ensuremath{\rangle}}
 
@@
 _⇒ₛ_ : (SD → Set) → (SD → Set) → SD → Set
-(P ⇒ₛ Q) sd = ∀{sd'} → (sd ≤ₛ sd') → P sd' → Q sd'
+(P ⇒ₛ Q) sd = ∀{sd′} → (sd ≤ₛ sd′) → P sd′ → Q sd′
 
@@
 
-get-var : ∀ {Γ A sd} → A ∈ Γ → ⟦ Γ ⟧ctx sd → ⟦ A ⟧ty sd
-get-var Zero     (_ , a) = a
-get-var (Suc x) (γ , _) = get-var x γ
+⟦_⟧var : ∀ {Γ A sd} → A ∈ Γ → ⟦ Γ ⟧ctx sd → ⟦ A ⟧ty sd
+⟦ Zero ⟧var (_ , a) = a
+⟦ Suc b ⟧var (γ , _) =  ⟦ b ⟧var γ
 
--- Functorality
-fmap-⇒ : ∀ {P Q sd sd'} → (P ⇒ₛ Q) sd → sd ≤ₛ sd' → (P ⇒ₛ Q) sd'
-fmap-⇒ θ p p' x = θ (≤ₛ-trans p p') x
+⟦_⟧sub : ∀ {A A′ sd} → A ≤: A′ → ⟦ A ⟧ty sd → ⟦ A′ ⟧ty sd
+⟦ ≤:-refl ⟧sub a = a
+⟦ ≤:-trans A≤:A′ A′≤:A″ ⟧sub a = ⟦ A′≤:A″ ⟧sub (⟦ A≤:A′ ⟧sub a)
+⟦ ≤:-fn A≤:A′ B′≤:B ⟧sub a = 
+    λ sd≤ₛsd′ a′ → ⟦ B′≤:B ⟧sub (a sd≤ₛsd′ (⟦ A≤:A′ ⟧sub a′))
+⟦ var-≤:-exp ⟧sub (exp , acc) = exp
+⟦ var-≤:-acc ⟧sub (exp , acc) = acc
 
-fmap-Compl : ∀ {sd sd'} → Compl sd → sd ≤ₛ sd' → Compl sd'
-fmap-Compl {sd} c (<-f f<f') = popto sd (<-f f<f') c
-fmap-Compl {⟨ f , d ⟩} {⟨ f , d' ⟩} c (≤-d d≤d') = 
-    adjustdisp-dec ((d' - d) d≤d') (-→≤ d≤d') 
-        (sub I (-ₛ≡ 
-            {n = (d' - d) d≤d'} 
-                (n-[n-m]≡m d≤d')) c)
+-- Functorial mapping
 
-fmap-L : ∀ {sd sd'} → L sd → sd ≤ₛ sd' → L sd'
-fmap-L (l-var sdᵛ sdᵛ≤ₛsd) sd≤ₛsd' = l-var sdᵛ (≤ₛ-trans sdᵛ≤ₛsd sd≤ₛsd')
+fmap-I : ∀ {sd sd′} → I sd → sd ≤ₛ sd′ → I sd′
+fmap-I {sd} c (<-f f<f′) = popto sd (<-f f<f′) c
+fmap-I {⟨ f , d ⟩} {⟨ f , d′ ⟩} c (≤-d d≤d′) = 
+    adjustdisp-dec ((d′ – d) d≤d′) (–→≤ d≤d′) 
+        (I-sub {n = (d′ – d) d≤d′} (n–[n–m]≡m d≤d′) c)
+
+fmap-L : ∀ {sd sd′} → L sd → sd ≤ₛ sd′ → L sd′
+fmap-L (l-var sdᵛ sdᵛ≤ₛsd) sd≤ₛsd′ = l-var sdᵛ (≤ₛ-trans sdᵛ≤ₛsd sd≤ₛsd′)
 fmap-L (l-sbrs) _ = l-sbrs
 
-fmap-S : ∀ {sd sd'} → S sd → sd ≤ₛ sd' → S sd'
-fmap-S (s-l l) sd≤ₛsd' = s-l (fmap-L l sd≤ₛsd')
+fmap-S : ∀ {sd sd′} → S sd → sd ≤ₛ sd′ → S sd′
+fmap-S (s-l l) sd≤ₛsd′ = s-l (fmap-L l sd≤ₛsd′)
 fmap-S (s-lit lit) _ = s-lit lit
 
-fmap-A : ∀ {A sd sd'} → ⟦ A ⟧ty sd → sd ≤ₛ sd' → ⟦ A ⟧ty sd'
-fmap-A {comm}  = fmap-⇒ {Compl} {Compl}
-fmap-A {intexp} = fmap-⇒ {Intcompl} {Compl}
-fmap-A {intacc} = fmap-⇒ {Compl} {Intcompl}
-fmap-A {intvar} ( e , a ) sd≤ₛsd' = ( fmap-A {intexp} e sd≤ₛsd' , fmap-A {intacc} a sd≤ₛsd' )
-fmap-A {A ⇒ B} = fmap-⇒ {⟦ A ⟧ty} {⟦ B ⟧ty}
+fmap-⇒ : ∀ {P Q sd sd′} → (P ⇒ₛ Q) sd → sd ≤ₛ sd′ → (P ⇒ₛ Q) sd′
+fmap-⇒ P⇒Q sd≤ₛsd′ sd′≤ₛsd″ p = P⇒Q (≤ₛ-trans sd≤ₛsd′ sd′≤ₛsd″) p
 
-fmap-Γ : ∀ {Γ sd sd'} → ⟦ Γ ⟧ctx sd → sd ≤ₛ sd' → ⟦ Γ ⟧ctx sd'
-fmap-Γ {·} unit _ = unit
-fmap-Γ {Γ , A} (γ , a) p = fmap-Γ γ p , fmap-A {A} a p
+fmap-ty : ∀ {A sd sd′} → ⟦ A ⟧ty sd → sd ≤ₛ sd′ → ⟦ A ⟧ty sd′
+fmap-ty {comm}  = fmap-⇒ {Compl} {Compl}
+fmap-ty {intexp} = fmap-⇒ {Intcompl} {Compl}
+fmap-ty {intacc} = fmap-⇒ {Compl} {Intcompl}
+fmap-ty {intvar} ( exp , acc ) sd≤ₛsd′ = 
+    ( fmap-ty {intexp} exp sd≤ₛsd′ , fmap-ty {intacc} acc sd≤ₛsd′ )
+fmap-ty {A ⇒ B} = fmap-⇒ {⟦ A ⟧ty} {⟦ B ⟧ty}
 
-sd≤ₛsd'→sd≤ₛsd'-ₛ[d'-[suc-d]] : ∀ {sd sd'} → sd ≤ₛ sd' → (δ₁≤δ₂ : suc (SD.d sd) ≤ SD.d sd') → sd ≤ₛ ((sd' -ₛ ((SD.d sd' - (suc (SD.d sd))) δ₁≤δ₂)) (-→≤ δ₁≤δ₂))
-sd≤ₛsd'→sd≤ₛsd'-ₛ[d'-[suc-d]] {⟨ f , _ ⟩} {⟨ f' , _ ⟩} (<-f f<f') _ = <-f f<f'
-sd≤ₛsd'→sd≤ₛsd'-ₛ[d'-[suc-d]] {⟨ f , d ⟩} {⟨ f , d' ⟩} (≤-d d≤d') δ₁≤δ₂ = ≤-d (suc-d≤d'→d≤d'-[d'-[suc-d]] δ₁≤δ₂)
+fmap-ctx : ∀ {Γ sd sd′} → ⟦ Γ ⟧ctx sd → sd ≤ₛ sd′ → ⟦ Γ ⟧ctx sd′
+fmap-ctx {·} unit _ = unit
+fmap-ctx {Γ , A} (γ , a) p = fmap-ctx γ p , fmap-ty {A} a p
 
-assign : (sd : SD) → (sd' : SD) → (S ⇒ₛ Compl) sd → sd ≤ₛ sd' → R sd' → I sd'
-assign ⟨ f , d ⟩ ⟨ f' , d' ⟩ β sd≤ₛsd' r with (≤-compare {suc d} {d'})
-... | leq δ₁≤δ₂ = assign-dec ((d' - (suc d)) δ₁≤δ₂) 
-                    (-→≤ δ₁≤δ₂) (l-var ⟨ f , d ⟩ (sd≤ₛsd'→sd≤ₛsd'-ₛ[d'-[suc-d]] sd≤ₛsd' δ₁≤δ₂)) r 
-                    (β ((sd≤ₛsd'→sd≤ₛsd'-ₛ[d'-[suc-d]] sd≤ₛsd' δ₁≤δ₂)) 
-                        (s-l (l-var ⟨ f , d ⟩ ((sd≤ₛsd'→sd≤ₛsd'-ₛ[d'-[suc-d]] sd≤ₛsd' δ₁≤δ₂)))))
+sd≤ₛsd′→sd≤ₛsd′–ₛ[d′–[suc-d]] : ∀ {sd sd′} → sd ≤ₛ sd′ 
+    → (δ₁≤δ₂ : suc (SD.d sd) ≤ SD.d sd′) 
+    → sd ≤ₛ ((sd′ –ₛ ((SD.d sd′ – (suc (SD.d sd))) δ₁≤δ₂)) (–→≤ δ₁≤δ₂))
+sd≤ₛsd′→sd≤ₛsd′–ₛ[d′–[suc-d]] {⟨ f , _ ⟩} {⟨ f′ , _ ⟩} (<-f f<f′) _ 
+    = <-f f<f′
+sd≤ₛsd′→sd≤ₛsd′–ₛ[d′–[suc-d]] {⟨ f , d ⟩} {⟨ f , d′ ⟩} (≤-d d≤d′) δ₁≤δ₂ 
+    = ≤-d (suc-d≤d′→d≤d′–[d′–[suc-d]] δ₁≤δ₂)
 
-... | geq δ₂≤δ₁ = assign-inc (((suc d) - d') δ₂≤δ₁) 
-                    (l-var ⟨ f , d ⟩ (≤ₛ-trans sd≤ₛsd' +ₛ→≤ₛ)) r 
-                    (β ((≤ₛ-trans sd≤ₛsd' +ₛ→≤ₛ)) 
-                        (s-l (l-var ⟨ f , d ⟩ ((≤ₛ-trans sd≤ₛsd' +ₛ→≤ₛ)))))
+new-intvar : ∀ sd → ⟦ intvar ⟧ty sd
+new-intvar sd = ( exp , acc )
+    where
+        exp : ⟦ intexp ⟧ty sd
+        exp sd≤ₛsd′ β = β ≤ₛ-refl (r-s (s-l (l-var sd sd≤ₛsd′)))
+        acc : ⟦ intacc ⟧ty sd
+        acc {sd′ = sd′} sd≤ₛsd′ κ (≤-d {d = d′} {d′ = d″} d′≤d″) r
+            = assign-dec 
+                ((d″ – d′) d′≤d″) (–→≤ d′≤d″) 
+                (l-var sd
+                   (sub-sd≤ₛ (–ₛ≡ {n≤d′ = –→≤ d′≤d″} (n–[n–m]≡m d′≤d″)) sd≤ₛsd′))
+                r
+                (I-sub {n = (d″ – d′) d′≤d″}(n–[n–m]≡m d′≤d″) κ)
+        acc {sd′ = sd′} sd≤ₛsd′ κ (<-f f<f′) r 
+            = assign-inc 0 (l-var _ ≤ₛ-refl) r (fmap-I κ (<-f f<f′))
 
-use-temp : ∀ {sd sd'} → (S ⇒ₛ Compl) sd → sd ≤ₛ sd' → R sd' → I sd'
-use-temp β sd≤ₛsd' (r-s s) = β sd≤ₛsd' s
-use-temp {sd} {sd'} β sd≤ₛsd' (r-unary uop s) = 
-    assign sd sd' β sd≤ₛsd' (r-unary uop s)
-use-temp {sd} {sd'} β sd≤ₛsd' (r-binary s₁ bop s₂) = 
-    assign sd sd' β sd≤ₛsd' (r-binary s₁ bop s₂)
+assign : (sd : SD) → (sd′ : SD) → (S ⇒ₛ Compl) sd 
+            → sd ≤ₛ sd′ → R sd′ → I sd′
+assign ⟨ f , d ⟩ ⟨ f′ , d′ ⟩ β sd≤ₛsd′ r with (≤-compare {suc d} {d′})
+... | leq δ₁≤δ₂ 
+        = assign-dec 
+            ((d′ – (suc d)) δ₁≤δ₂) (–→≤ δ₁≤δ₂) 
+              (l-var ⟨ f , d ⟩ 
+                (sd≤ₛsd′→sd≤ₛsd′–ₛ[d′–[suc-d]] sd≤ₛsd′ δ₁≤δ₂)) 
+              r 
+              (β ((sd≤ₛsd′→sd≤ₛsd′–ₛ[d′–[suc-d]] sd≤ₛsd′ δ₁≤δ₂)) 
+                (s-l (l-var ⟨ f , d ⟩ 
+                  ((sd≤ₛsd′→sd≤ₛsd′–ₛ[d′–[suc-d]] sd≤ₛsd′ δ₁≤δ₂)))))
 
-⟦_⟧ : ∀ {Γ A} → (e : Γ ⊢ A) → (sd : SD) → ⟦ Γ ⟧ctx sd → ⟦ A ⟧ty sd
-⟦ Var x ⟧ _ γ = get-var x γ
-⟦ Lambda f ⟧ sd γ {sd' = sd'} p a = ⟦ f ⟧ sd' (fmap-Γ γ p , a) 
+... | geq δ₂≤δ₁ = assign-inc (((suc d) – d′) δ₂≤δ₁) 
+                  (l-var ⟨ f , d ⟩ (≤ₛ-trans sd≤ₛsd′ +ₛ→≤ₛ)) r 
+                  (β ((≤ₛ-trans sd≤ₛsd′ +ₛ→≤ₛ)) 
+                    (s-l (l-var ⟨ f , d ⟩ ((≤ₛ-trans sd≤ₛsd′ +ₛ→≤ₛ)))))
+
+use-temp : ∀ {sd sd′} → (S ⇒ₛ Compl) sd → sd ≤ₛ sd′ → R sd′ → I sd′
+use-temp β sd≤ₛsd′ (r-s s) = β sd≤ₛsd′ s
+use-temp {sd} {sd′} β sd≤ₛsd′ (r-unary uop s) = 
+    assign sd sd′ β sd≤ₛsd′ (r-unary uop s)
+use-temp {sd} {sd′} β sd≤ₛsd′ (r-binary s₁ bop s₂) = 
+    assign sd sd′ β sd≤ₛsd′ (r-binary s₁ bop s₂)
+
+⟦_⟧ : ∀ {Γ A} → Γ ⊢ A → (sd : SD) → ⟦ Γ ⟧ctx sd → ⟦ A ⟧ty sd
+⟦ Var a ⟧ sd γ = ⟦ a ⟧var γ
+
+⟦ Sub a A≤:B ⟧ sd γ = ⟦ A≤:B ⟧sub (⟦ a ⟧ sd γ)
+
+⟦ Lambda f ⟧ sd γ {sd′ = sd′} sd≤ₛsd′ a = ⟦ f ⟧ sd′ (fmap-ctx γ sd≤ₛsd′ , a)
+
 ⟦ App f e ⟧ sd γ = ⟦ f ⟧ sd γ (≤-d ≤-refl) (⟦ e ⟧ sd γ)
-⟦ Skip ⟧ _ _ _ γ = γ
-⟦ Seq c₁ c₂ ⟧ sd γ sd' p = ⟦ c₁ ⟧ sd γ sd' (⟦ c₂ ⟧ sd γ sd' p)
-⟦ Lit i ⟧ _ _ _ κ = κ ≤ₛ-refl (r-s (s-lit i))
-⟦ Neg e ⟧ sd γ p κ = ⟦ e ⟧ sd γ p (use-temp λ p s → κ p (r-unary UNeg s))    
-⟦ Plus e₁ e₂ ⟧ sd γ p κ = ⟦ e₁ ⟧ sd γ p (use-temp (λ p' s₁ → ⟦ e₂ ⟧ sd γ (≤ₛ-trans p p') (use-temp (λ p'' s₂ →  κ (≤ₛ-trans p' p'') (r-binary (fmap-S s₁ p'') BPlus s₂)))))
+
+⟦ Skip ⟧ sd γ sd≤ₛsd′ κ = κ
+
+⟦ Seq c₁ c₂ ⟧ sd γ sd≤ₛsd′ κ = ⟦ c₁ ⟧ sd γ sd≤ₛsd′ (⟦ c₂ ⟧ sd γ sd≤ₛsd′ κ)
+
+⟦ NewVar c ⟧ sd γ {sd′ = sd′} sd≤ₛsd′ κ = 
+    assign-inc 1 
+        (l-var sd′ (≤-d +→≤))
+        (r-s (s-lit (pos 0)))
+        (⟦ c ⟧
+            (sd′ +ₛ 1)
+            (fmap-ctx {Γ = _ , intvar} 
+                ((fmap-ctx γ sd≤ₛsd′ , new-intvar sd′)) 
+                (+ₛ→≤ₛ {sd′} {1}))
+            ≤ₛ-refl
+            (adjustdisp-dec 1 +→≤ʳ
+                (I-sub {d′ = SD.d sd′ + 1} {n = 1} 
+                    (n+m–m≡n {m = 1}) κ)))
+
+⟦ Assign a e ⟧ sd γ sd≤ₛsd′ κ = ⟦ e ⟧ sd γ sd≤ₛsd′ (⟦ a ⟧ sd γ sd≤ₛsd′ κ)
+
+⟦ Lit i ⟧ sd γ sd≤ₛsd′ β = β ≤ₛ-refl (r-s (s-lit i))
+
+⟦ Neg e ⟧ sd γ sd≤ₛsd′ β = 
+    ⟦ e ⟧ sd γ sd≤ₛsd′ (use-temp λ sd≤ₛsd′ s → β sd≤ₛsd′ (r-unary UNeg s))
+
+⟦ Plus e₁ e₂ ⟧ sd γ sd≤ₛsd′ β = 
+    ⟦ e₁ ⟧ sd γ sd≤ₛsd′ 
+        (use-temp (λ sd′≤ₛsd″ s₁ → ⟦ e₂ ⟧ sd γ (≤ₛ-trans sd≤ₛsd′ sd′≤ₛsd″)
+            (use-temp (λ sd″≤ₛsd‴ s₂ → β (≤ₛ-trans sd′≤ₛsd″ sd″≤ₛsd‴)
+                (r-binary (fmap-S s₁ sd″≤ₛsd‴) BPlus s₂)))))
+
+compile-closed : · ⊢ comm → I ⟨ 0 , 0 ⟩
+compile-closed t = ⟦ t ⟧ ⟨ 0 , 0 ⟩ unit ≤ₛ-refl stop
 \end{code}

### 2025-05-18 content.tex
under 40 pages

--- 2025-05-17 draft.tex
@@
 \usepackage{hhline}
+\usepackage{afterpage}
 
@@
     \refstepcounter{motivation}%
-    \vspace{1.5em}%
+    \vspace{1em}%
     \noindent\textbf{Motivation \themotivation.  #1}
@@
 \renewcommand{\arraystretch}{1.5}
+
+\makeatletter
+\newcommand{\chapterminitoc}{%
+  \begingroup
+    \let\ps@plain\ps@empty % Force empty page style
+    \let\ps@headings\ps@empty
+    \minitoc
+    \thispagestyle{empty} % Double protection
+    \afterpage{\clearpage} % Force content to next page
+  \endgroup
+    \clearpage
+  \addtocounter{page}{-1} % Adjust page counter
+}
+\makeatother
 
@@
 \chapter{Introduction}
-    \minitoc
+    \chapterminitoc
     Programming languages act as a bridge between human thoughts and machine execution.
@@
 
-    Denotational semantics is related to the human realms.
+    Denotational semantics is related to the human realm.
 It provides a theoretical framework for defining the meaning of programming languages by interpreting them into mathematical objects.
@@
 
-    Compilers are related to the machine realms.
+    Compilers are related to the machine realm.
 They are programs that translate high-level code into executable instructions, resolving abstractions into concrete operations like memory allocation and register management.
@@
     \section{Language choice: Agda's advantages}
-        Agda~\autocite{Agda} is a dependently typed programming language and proof assistant.
-As a dependently typed language, Agda captures the source language's intrinsic syntax with indexed families, which contains only well-typed terms.
-Therefore, it focuses on the correct programs and rules out the ill-typed nonsensical inputs.
+        Agda~\autocite{Agda}, as a dependently typed proof assistant, captures source language's intrinsic syntax with indexed families.
+This automatically rules out the ill-typed nonsensical inputs, and only well-typed programs can be compiled.
 
@@
             \savedmotivationI
-            I formalised the terms in the source language and target language in Agda. I also refined some type definitions in the denotational semantics of the source language.
+            I formalised the terms in the source and target language in Agda. I also refined some type definitions in the denotational semantics of the source language.
 
             \savedmotivationII
-            I implemented the compiler from the source language to the target language in Agda. 
+            I implemented a compiler from the source language to the target language in Agda. 
         \end{quote}
@@
 \chapter{Preparation}
-    \minitoc
+    \chapterminitoc
 
@@
 \chapter{Implementation} \label{chap: implementation}
-    \minitoc
+    \chapterminitoc
     This chapter details the implementation of the compiler in Agda.
@@
 \chapter{Evaluation}
-    \minitoc
+    \chapterminitoc
     This chapter evaluates the implementation with integration tests and a feature checklist and then discusses the success criteria of the project.
@@
 \chapter{Conclusion}
-    \minitoc
+    \chapterminitoc
     \section{Results}
@@
     \section{Lessons learned}
-    The project has been quite challenging as I have to learn both category theory and Agda from scratch, and apply them to implementation.
+    The project has been quite challenging as I have to learn both category theory and Agda from scratch and apply them to implementation.
 The implementation process revealed unexpected gaps between Reynolds' theoretical framework and the computational realisation: while his denotational semantics provided core definitions, actualising them in Agda required formalising numbers, their operations, and properties and diagnosing and resolving type mismatches and ambiguities in the original paper~\autocite{Reynolds}.
@@
 When I was drafting the proposal, I expected the workflow to be similar to a standard compiler, so I divided the work into components including basic instructions, variable declarations and conditionals, allocating two weeks for each.
-In hindsight, these components are similar term definitions, while the core of the project can be more accurately divided into three main tasks: defining the source language, defining the target language, and defining the translation between the two.
-The most time-consuming aspect of each step has been understanding their formal definitions in the paper and addressing the missing details in the Agda implementation.
-
-    Overall, the project has been a valuable learning experience, and I have gained a deeper understanding of both Category Theory and Agda and an exciting glimpse of how the correspondences between logic, type theory and category theory can be used to implement a compiler.
+In hindsight, these components are similar term definitions, while the most difficult task was to spot problems with the original paper and to prove properties about customised subtraction of natural numbers.
+
+    Overall, the project has been a valuable learning experience, and I have gained a deeper understanding of both category theory and Agda and an exciting glimpse of how the correspondences between logic, type theory and category theory can be used to implement a compiler.
 
     \section{Future work}
-    The project has successfully implemented the compiler, but there are still many areas for improvement and further research:
+    The implementation of the compiler can be extended in the following ways:
     \begin{itemize}
@@
 \chapter{Operational Semantics of the source language} \label{app: operational_semantics}
-    \minitoc
+    \chapterminitoc
     The operational semantics of the source language is defined with renaming, substitution and reduction rules. The implementation is as follows:

### 2025-05-19 content.tex
Minitoc is back! Hooray!

@@
         \textbf{Examination} & Computer Science Tripos - Part II - 2025 \\
-        \textbf{Word-count:} & [wordcount] \footnotemark \\
-        \textbf{Code line count:} & [linecount] \footnotemark \\
+        \textbf{Word-count:} & 9574 \footnotemark \\
+        \textbf{Code line count:} & 1727 \footnotemark \\
         \textbf{Project Originator:} & Yulong Huang \\
@@
 
+    The original aims of the project were to implement a compiler originated from the denotational semantics, following the work of Reynolds~\autocite{Reynolds}.
+The compiler is a functor from the source language to the target language.
+Agda is chosen as the implementation language because it is a dependently typed proof assistant, which ensures that the input source program, the compilation process, and the output target program are all well-typed.
+
     \vspace{2em}
@@
 
+    I defined a compiler in Agda for the source language and target language as described in Reynolds' work~\autocite{Reynolds}.
+The compiler was guaranteed to generate expected code by tests in a separate Agda file.
+An additional customised library was defined to support the implementation of the compiler.
+More importantly, I spotted a mistake in Reynolds' definition of the denotational semantics of the source language and provided a corrected version.
+All success criteria were met, and the project was completed successfully.
+
     \vspace{2em}
@@
     \vspace{1em}
+
+    None.
+
     \begingroup
-        \footnotetext[1]{This word-count was computed by \texttt{texcount -1 -sum -merge -q dissertation.tex}.}
+        \footnotetext[1]{This word-count was computed by \texttt{texcount -sum -1 content.tex}.}
         \footnotetext[2]{This code line count was computed by \texttt{find . -name "*.agda" | xargs wc -l}.}
@@
         \subsection{Contexts and variables}
-        We define the context as a finite list of types as follows:
+        I define the context as a finite list of types as follows:
         \[\includegraphics[scale=1.2]{/source/contexts.pdf}\]
@@
     \end{table}
-    % We can use reflexivity and transitivity of the order $<$ and $\leq$ to prove that the order of stack descriptors $\leq_\mathsf{s}$ is a preorder. The proof in Agda is as follows:
-    % \begin{proof}
-    %     We need to show that $\leq_\mathsf{s}$ is reflexive and transitive. 
-    %     \begin{itemize}
-    %         \item 
-    %             Reflexivity: $\textit{sd} \leq_\mathsf{s} \textit{sd}$ is trivially true since $f = f$ and $d \leq d$.
-    %         \item
-    %             Transitivity: if $\ang{f, d} \leq_\mathsf{s} \ang{f', d'}$ and $\ang{f', d'} \leq_\mathsf{s} \ang{f'', d''}$, we do the following case split:
-    %             \begin{enumerate}
-    %                 \item 
-    %                     If $f < f'$, $f' = f''$ and $d \leq d'$, then $f < f''$; 
-    %                 \item 
-    %                     If $f < f'$ and $f' < f''$, then $f < f''$ by transitivity of $<$;
-    %                 \item
-    %                     If $f = f'$, $d \leq d'$ and $f' < f''$, then $f < f''$;
-    %                 \item
-    %                     Otherwise $f = f''$ and $d \leq d''$ by transitivity of $\leq$.
-\footnote{Note that the properties of $=$ is not required in as in the Agda definition of $\leq_\mathsf{s}$, we directly define $f'$ to be $f$ instead of defining a equivalence relation, thus equivalence can be checked directly via type checking.}
-    %             \end{enumerate}
-    %     \end{itemize}
-    % \end{proof}
-
-    % The proof is defined in Agda as follows:
-    % \[\includegraphics[scale=1.2]{/target/stack_descriptor_order_proof.pdf}\]
-
-    % When a natural number is added to a stack descriptor, it is guaranteed that the new stack descriptor is not less than the old stack descriptor.
-This can be proved directly using the same properties of integer addition.
-The proof is defined in Agda as follows:
-    % \[\includegraphics[scale=1.2]{/target/stack_descriptor_add_proof.pdf}\]
+    The definitions of the above properties can be found in Appendix~\ref{app: target_properties}.
 
@@
     \end{itemize}
-    All definitions and properties can be found in Appendix~[TBD].
+    All definitions and properties that are listed in this section can be fount in Appendix~\ref{app: lib_properties}.
 
@@
     \end{itemize}
+    The properties are defined in a minimalistic way and tailored to the requirements of the compiler.
+For example, \mbt{≤-compare} in Table~\ref{tab: properties} is a property that states that for all $m, n \in \bN$, either $m \leq n$ or $n \leq m$, which is used to case split in the implementation of the compiler.
+In the standard library, a similar property is defined to split the cases into $m < n$, $m \equiv n$ and $m > n$, which adds unnecessary complexity to the implementation, as all the proof required for compiler is in the form of $m \leq n$.
     \begin{table}[H]
@@
     \subsection{Subtraction} \label{subsec: subtraction}
-    In the standard library~\autocite{agda_std}, the subtraction of natural numbers is defined as follows:\footnote{The definition in the standard library directly uses symbol $\mathsf{-}$, but here for clarity we use $\mathsf{\dotdiv}$ instead.}
+    In the standard library~\autocite{agda_std}, the subtraction of natural numbers is defined as follows:\footnote{The definition in the standard library directly uses symbol $\mathsf{-}$, but here for clarity I use $\mathsf{\dotdiv}$ instead.}
     \[\includegraphics[scale=1.2]{minus.pdf}\]
@@
     \end{itemize}
-    We define $\mathsf{SD}$ as the set of stack descriptors.
+    I define $\mathsf{SD}$ as the set of stack descriptors.
 Then the base category is the category determined by preorder $\underline{\mathsf{SD}} = \{\mathsf{SD}, \leq_\mathsf{s}\}$ in Example~\ref{ex: category_preorder}.
@@
     \subsection{Continuations}
-    In Reynolds' model, we construct $\mathsf{Compl}$ and $\mathsf{Intcompl}$\footnote{In the work of Reynolds, $\mathsf{compl}$ and $\mathsf{intcompl}$ are introduced as new types in the source language, and the definitions here are the denotational semantics of those types, respectively.
-Since these two introduced types are only used for the denotational semantics, I think directly defining them as denotational semantics constructs is natural and sufficient.} as tools in the denotational semantics to represent command continuations and integer continuations, respectively.
+    In Reynolds' model, $\mathsf{Compl}$ and $\mathsf{Intcompl}$\footnote{In the work of Reynolds, $\mathsf{compl}$ and $\mathsf{intcompl}$ are introduced as new types in the source language, and the definitions here are the denotational semantics of those types, respectively.
+Since these two introduced types are only used for the denotational semantics, I think directly defining them as denotational semantics constructs is natural and sufficient.} are constructed as tools in the denotational semantics to represent command continuations and integer continuations, respectively.
 We can think of integer continuations as a function that takes an integer and returns a command continuation.
@@
     \begin{itemize}
-        \item Command passes on command continuations;
-        \item Integer expressions takes an integer continuation and returns a command continuation;
-        \item Integer acceptors take a command continuation and returns an integer continuation;
-        \item Integer variables can be used both as an integer expression and an integer acceptor, so it has the denotational semantics of both, defined as a product of the two.
-    \end{itemize}
-
-    The denotational semantics of types in Agda as follows:
+        \item Commands pass on command continuations;
+        \item Integer expressions take integer continuations and return command continuations;
+        \item Integer acceptors take command continuations and return integer continuations;
+        \item Integer variables can be used either as integer expressions or integer acceptors, so they have the denotational semantics of both, defined as a product of the two.
+    \end{itemize}
+
+    The denotational semantics of types in Agda is as follows:
     \[\includegraphics[scale=1.2]{/compiler/type_interpretation.pdf}\]
@@
     The denotational semantics of contexts is essentially a list expressed by the product of the denotational semantics of the types in the context.
-The denotational semantics of contexts is defined as follows, where we use \mb{∅} to denote the denotational semantics of the empty context:
+The denotational semantics of contexts is defined as follows, where I use \mb{∅} to denote the denotational semantics of the empty context:
     \[\includegraphics[scale=1.2]{/compiler/context_interpretation.pdf}\]
@@
     The denotational semantics of terms is defined as a functor.
-Before we define its object mapping, we need to define the functorial mapping, which acts on the morphisms of the base category $\Upsigma$.
+Before defining its object mapping, we need to define the functorial mapping, which acts on the morphisms of the base category $\Upsigma$.
 
@@
         \subsubsection{Variables}
-        We define an auxiliary function that simply gets the variable from the list of variables (the context), and the denotational semantics of variables is given by applying this function:
+        I define an auxiliary function that simply gets the variable from the list of variables (the context), and the denotational semantics of variables is given by applying this function:
         \[\includegraphics[scale=1.2]{/compiler/term_var.pdf}\]
@@
         The idea of subtyping is to use a term of type $A$ as a term of type $A'$, where $A$ is a subtype of $A'$.
-We define an auxiliary function that takes in the subtype relation $A\leq:A'$ and the denotational semantics of $A$, and returns the denotational semantics of $A'$.
-        \begin{itemize}
-            \item For \gnt{var-≤:-exp} and \gnt{⟦var-≤:-acc}, sincethe denotational semantics of integer variable is defined as product of the denotational semantics of integer expression and integer acceptor in~\secref{subsec: type_interpretation}, we can simply use the projection to get the denotational semantics of either side.
+I define an auxiliary function that takes in the subtype relation $A\leq:A'$ and the denotational semantics of $A$, and returns the denotational semantics of $A'$.
+        \begin{itemize}
+            \item For \gnt{var-≤:-exp} and \gnt{⟦var-≤:-acc}, since the denotational semantics of integer variable is defined as product of the denotational semantics of integer expression and integer acceptor in~\secref{subsec: type_interpretation}, we can simply use the projection to get the denotational semantics of either side.
             \item For \gnt{≤:-refl}, we can simply use the identity function.
@@
 
-        Please see Appendix~[TBD] for the full implementation of the function \textsf{NewVar}.
+        Please see Appendix~\ref{app: compiler_details} for the full implementation of the function \textsf{NewVar}.
 
@@
 We also need to show that the adjustment is valid for each case.
-Please refer to Appendix~[TBD] for the full implementation of the function \textsf{use-temp}.
+Please refer to Appendix~\ref{app: compiler_details} for the full implementation of the function \textsf{use-temp}.
         % The auxiliary function \textsf{use-temp} is defined as follows:
@@
 
-    The full test cases are available in the appendix [TBD]. Here is a summary of the test cases:
+    Here is a summary of the test cases:
     % \begin{enumerate}[label=\textbf{Test \arabic*.}, leftmargin=*]
@@
 
-    The specifications that include multiple variables, free variables and self-referential assignments ensure that the translation of the Debrujin index of the context works correctly under edge cases.
+    The specifications that include multiple variables, free variables and self-referential assignments ensure that the translation of the de Bruijn index of the context works correctly under edge cases.
 
@@
 \chapter{Operational Semantics of the source language} \label{app: operational_semantics}
-    \chapterminitoc
     The operational semantics of the source language is defined with renaming, substitution and reduction rules. The implementation is as follows:
@@
         \centering
-        \includegraphics[scale=1.2]{/source/operational_semantics_1.pdf}
+        \includegraphics[scale=1.2]{/appendix/source_operational_semantics_1.pdf}
         \caption{Operational semantics of the source language (Part 1)}
@@
         \centering
-        \includegraphics[scale=1.2]{/source/operational_semantics_2.pdf}
+        \includegraphics[scale=1.2]{/appendix/source_operational_semantics_2.pdf}
         \caption{Operational semantics of the source language (Part 2)}
@@
     \end{figure}
+
+\chapter{Properties of target language} \label{app: target_properties}
+    The properties of the target language are defined as follows:
+    \begin{figure}[H]
+        \centering
+        \includegraphics[scale=1.2]{/appendix/target_properties.pdf}
+        \caption{Properties of the target language}
+        \label{fig: target_properties}
+    \end{figure}
+
+\chapter{Properties of natural numbers} \label{app: lib_properties}
+    The properties of natural numbers are defined as follows:
+    \begin{figure}[H]
+        \centering
+        \includegraphics[scale=1.2]{/appendix/lib_properties_plus.pdf}
+        \caption{Properties related to addition of natural numbers}
+        \label{fig: lib_properties_plus}
+    \end{figure}
+    \begin{figure}
+        \centering
+        \includegraphics[scale=1.2]{/appendix/lib_properties_plus_order.pdf}
+        \caption{Properties related to addition and order of natural numbers}
+        \label{fig: lib_properties_plus_order}
+    \end{figure}
+    \begin{figure}[H]
+        \centering
+        \includegraphics[scale=1.2]{/appendix/lib_properties_order.pdf}
+        \caption{Properties related to order of natural numbers}
+        \label{fig: lib_properties_order}
+    \end{figure}
+
+\chapter{Compiler details} \label{app: compiler_details}
+    The denotational semantics of \gnt{NewVar} is defined as follows:
+    \begin{figure}[H]
+        \centering
+        \includegraphics[scale=1.2]{/appendix/new_var.pdf}
+        \caption{New variable}
+        \label{fig: new_var}
+    \end{figure}
+
+    The implementation of the function \textsf{use-temp} is as follows:
+    \begin{figure}[H]
+        \centering
+        \includegraphics[scale=1.2]{/appendix/use_temp.pdf}
+        \caption{Use temporary variable}
+        \label{fig: use_temp}
+    \end{figure}
+
+    The helper function \textsf{new-intvar} for the denotational semantics of the new variable is defined as follows:
+    \begin{figure}[H]
+        \centering
+        \includegraphics[scale=1.2]{/appendix/new-intvar.pdf}
+        \caption{New integer variable}
+        \label{fig: new_intvar}
+    \end{figure}
+    The helper function \textsf{assign} for case-split and assignment is defined as follows:
+    \begin{figure}[H]
+        \centering
+        \includegraphics[scale=1.2]{/appendix/assign.pdf}
+        \caption{Assignment}
+        \label{fig: assign}
+    \end{figure}
+
+% \chapter{Test cases} \label{app: test_cases}
+%     The test cases are defined as follows:
+%     \begin{figure}[H]
+%         \centering
+%         \includegraphics[scale=1.2]{/appendix/test_1.pdf}
+%         \caption{Test cases}
+%         \label{fig: test_cases}
+%     \end{figure}
 

### 2025-05-19 draft.tex
Minitoc is back! Hooray!

@@
 \usepackage{enumerate}
-\usepackage[vmargin=2.5cm, hmargin=2.5cm]{geometry}
+\usepackage[tmargin=2.3cm, hmargin=2.5cm, bmargin=2.3cm]{geometry}
 \usepackage{hyperref}
@@
 \usepackage{hhline}
+\usepackage{titlesec}
 
@@
 
+\titleformat{\chapter}[hang]
+  {\normalfont\huge\bfseries}
+  {\thechapter\quad }{0pt}{\huge}
+
+\titlespacing*{\chapter}{0pt}{-25pt}{15pt}
+
+\titlespacing*{\section}{0pt}{16pt}{8pt}
+
+\titlespacing*{\subsection}{0pt}{12pt}{6pt}
+
+\titlespacing*{\subsubsection}{0pt}{8pt}{4pt}
+
 \begin{document}
@@
 \begin{titlepage}
-    \vspace*{5em}
-    \textbf{\LARGE Declaration of Originality}
+    \textbf{\Large Declaration of Originality}
     \vspace{2em}
@@
 \begin{titlepage}
-    \vspace*{5em}
-    \textbf{\LARGE Proforma}
+    \textbf{\Huge Proforma}
     \vspace{2em}
@@
         \textbf{Examination} & Computer Science Tripos - Part II - 2025 \\
-        \textbf{Word-count:} & [wordcount] \footnotemark \\
-        \textbf{Code line count:} & [linecount] \footnotemark \\
+        \textbf{Word count:} & 9567 \footnotemark \\
+        \textbf{Code line count:} & 1727 \footnotemark \\
         \textbf{Project Originator:} & Yulong Huang \\
@@
 \chapter{Introduction}
-    \minitoc
     Programming languages act as a bridge between human thoughts and machine execution.
@@
         \motivation{Implementation of the compiler}
-        Reynolds concluded that he did not have a proper dependently typed programming language in hand, so his compiler remained a partial function~\autocite[Ch.6]{Reynolds}.
+        Reynolds concluded that he did not have a proper dependently typed programming language in hand, so his compiler remained a partial function~\autocite[Ch.~6]{Reynolds}.
 I aim to provide a computer implementation of this theoretical framework in a dependently typed programming language.
@@
 
-        The project successfully met all of the above success criteria, addressed the two motivations presented in~\secref{sec: motivation} and contributed to the following:
+        The project successfully met all of the above success criteria and contributed to the following:
         \begin{quote}            
             \savedmotivationI
-            I formalised the terms in the source language and target language in Agda. I also refined some type definitions in the denotational semantics of the source language.
+            I formalised the terms in the source and target language in Agda. I also refined some type definitions in the denotational semantics of the source language.
+            \vspace*{1em}
 
             \savedmotivationII
-            I implemented the compiler from the source language to the target language in Agda. 
+            I implemented a compiler from the source language to the target language in Agda. 
         \end{quote}
@@
     \minitoc
-
     For implementing the compiler, I need to understand the theoretical background of presheaves and functor categories that are used as the denotational semantics of the source language, and I need to understand dependent types to correctly express the dependent function space of presheaf exponentials.
 
-    This chapter begins with my starting point and introducing core concepts of category theory.
+    This chapter begins with my starting point and introduces core concepts of category theory which form theoretical foundation of the compiler.
 It then provides a brief overview of Agda as a dependently typed programming language, concluding with a requirements analysis for the compiler design.
@@
                 \begin{equation}
-                    \vcenter{\hbox{\includegraphics[width=0.4\textwidth]{exponential.pdf}}}
+                    \vcenter{\hbox{\includegraphics[width=0.3\textwidth]{exponential.pdf}}}
                     \label{cd: exponential}
@@
 The chapter concludes with a detailed implementation of the compiler~(\secref{sec: compiler}).
+
+    % \clearpage
 
@@
 
+        Each file in the repository is described in Table~\ref{tab: file_descriptions}. 
         \begin{table}[H]
@@
                             &\mid \bracket{ \text{unary operator} } \bracket{ \textsf{S}_{\textit{sd}}}\\
-                            &\mid \bracket{\textsf{S}_{\textit{sd}}} \bracket{\textsf{binary operator}} \bracket{ \textsf{S}_{\textit{sd}} } \\
+                            &\mid \bracket{\textsf{S}_{\textit{sd}}} \bracket{\textsf{binary operator}} \bracket{ \textsf{S}_{\textit{sd}} }
+        \end{aligned}\]
+        \caption{Target language grammar (part 1)}
+        \label{fig: target_grammar_1}
+    \end{figure}
+
+    \begin{figure}[H]
+        \centering
+        \[\begin{aligned}
             \bracket{\textsf{I}_{\textit{sd}}} ::={}& \texttt{stop} \\
@@
         \end{aligned}\]
-        \caption{Target language grammar}
-        \label{fig: target_grammar}
+        \caption{Target language grammar (part 2)}
+        \label{fig: target_grammar_2}
     \end{figure}
@@
     \end{table}
-
+    The properties are defined in a minimalistic way and tailored to the requirements of the compiler.
+For example, \mbt{≤-compare} in Table~\ref{tab: properties} is a property that states that for all $m, n \in \bN$, either $m \leq n$ or $n \leq m$, which is used to case split in the implementation of the compiler.
+In the standard library, a similar property is defined to split the cases into $m < n$, $m \equiv n$ and $m > n$, which adds unnecessary complexity to the implementation, as all the proof required for compiler is in the form of $m \leq n$.
     % \subsection{Natural numbers, integers and addition} \label{subsec: natural_numbers}
@@
             \item For addition and negation, we wish to fill the negation or the sum of the given expression(s) to the integer continuation $\beta$.
-However, this is only possible when the given expression(s) are simple left-hand sides, as the grammar of the target language in Figure~\ref{fig: target_grammar} restricts right-hand sides to contain at most one operator.
+However, this is only possible when the given expression(s) are simple left-hand sides, as the grammar of the target language in Figure~\ref{fig: target_grammar_1} restricts right-hand sides to contain at most one operator.
 An auxiliary function \textsf{use-temp} that stores the intermediate result of given expressions is introduced to solve this problem.
@@
 \chapter{Evaluation}
-    \minitoc
     This chapter evaluates the implementation with integration tests and a feature checklist and then discusses the success criteria of the project.
     \section{Tests}
-    The best way to evaluate a formalised compiler project is to formalise compiler correctness, which requires the full definition of the operational semantics of the source language and the target language, and then prove that for any program $e$ in the source language and the program $e'$ it compiles to in the target language, the value $v'$ that $e'$ evaluates to is also the compilation of the value $v$ that $e$ evaluates to.
-Due to time limitations, this is beyond the scope of this project.
-Instead, I used a set of integration tests that covers all features of the source language and the target language to evaluate the correctness of the compiler.
-All of the test cases have been passed successfully.
+    The best way to evaluate a formalised compiler project is to formalise compiler correctness, proving that for any program $e$ in the source language and $e'$ in target language where $e' \equiv \texttt{compile}(e)$, their corresponding evaluation results according to their operational semantics $v$ and $v'$ also satisfy $v' \equiv \texttt{compile}(v)$, where $\texttt{compile}$ is the compilation function.
+This requires full operational semantics defined for both languages and formal equivalence proof.
+
+    While such verification exceeds this project's scope due to time limitations, formal validation has been achieved through comprehensive integration testing that covers all features of the source language and the target language.
+All of the test cases have passed successfully, confirming the output of the compiler is as expected.
 
@@
 
-    The specifications that include multiple variables, free variables and self-referential assignments ensure that the translation of the Debrujin index of the context works correctly under edge cases.
-
-    The specification of multiple expressions in integer expression is necessary because the target language does not support doing multiple integer operations in a single instruction, as specified in Figure~\ref{fig: target_grammar}.
+    The specifications that include multiple variables, free variables and self-referential assignments ensure that the translation of the de Bruijn index of the context works correctly under edge cases.
+
+    The specification of multiple expressions in integer expression is necessary because the target language does not support doing multiple integer operations in a single instruction, as specified in Figure~\ref{fig: target_grammar_1}.
 As a result, special tests are required to check that the compiler correctly translates integer expressions with multiple operations into a continuation of single operations defined in the target language.
@@
 \chapter{Conclusion}
-    \minitoc
     \section{Results}
@@
 When I was drafting the proposal, I expected the workflow to be similar to a standard compiler, so I divided the work into components including basic instructions, variable declarations and conditionals, allocating two weeks for each.
-In hindsight, these components are similar term definitions, while the core of the project can be more accurately divided into three main tasks: defining the source language, defining the target language, and defining the translation between the two.
-The most time-consuming aspect of each step has been understanding their formal definitions in the paper and addressing the missing details in the Agda implementation.
-
-    Overall, the project has been a valuable learning experience, and I have gained a deeper understanding of both Category Theory and Agda and an exciting glimpse of how the correspondences between logic, type theory and category theory can be used to implement a compiler.
+In hindsight, these components are similar term definitions, while the most difficult task was to spot problems with the original paper and to prove properties of customised subtraction.
+
+    Overall, the project has been a valuable learning experience, and I have gained a deeper understanding of both category theory and Agda and an exciting glimpse of how the correspondences between logic, type theory and category theory can be used to implement a compiler.
 
     \section{Future work}
-    The project has successfully implemented the compiler, but there are still many areas for improvement and further research:
+    The implementation of the compiler can be extended in the following ways:
     \begin{itemize}
@@
         \item
-            Reynolds pointed out that the requirement of instructions being natural transformation must be relaxed to allow for instruction sequences that differ operationally but are equivalent in terms of denotational semantics~\autocite[Ch.
-6]{Reynolds}.
-Extra research can be done to develop a reasonable equational theory that can be stated directly on the instruction sequences, under which the semantics actually becomes a true functor category model (i.e.
+            Reynolds noted that the natural transformation requirement must be relaxed to permit operationally distinct but denotationally equivalent instruction sequences~\autocite[Ch.~6]{Reynolds}.
+Extra research can be done to develop a reasonable equational theory that can be stated directly on the instruction sequences, under which the semantics becomes a true functor category model (i.e.
 naturality holds).
@@
 \chapter{Operational Semantics of the source language} \label{app: operational_semantics}
-    \minitoc
     The operational semantics of the source language is defined with renaming, substitution and reduction rules. The implementation is as follows:

### 2025-05-19 temp.tex
Minitoc is back! Hooray!

--- 2025-05-18 content.tex
@@
 
+    I have met all my proposed success criteria and have implemented three extensions.
+A formalisation of source language and target language in Agda was provided.
+The compiler was implemented as an Agda file that takes a source program and produces a target program.
+The compiler was guaranteed to generate expected code by tests in a separate Agda file.
+An additional customised library was defined to support the implementation of the compiler.
+More importantly, I spotted a mistake in Reynolds' definition of the denotational semantics of the source language and provided a corrected version.
+
     \vspace{2em}
@@
     \vspace{1em}
+
+    The implementation depends on the theory provided by Reynolds~\autocite{Reynolds}. Some details in the theory were missing, and a type definition in the theory was incorrect.
+
     \begingroup
-        \footnotetext[1]{This word-count was computed by \texttt{texcount -1 -sum -merge -q dissertation.tex}.}
+        \footnotetext[1]{This word-count was computed via \texttt{texcount}.}
         \footnotetext[2]{This code line count was computed by \texttt{find . -name "*.agda" | xargs wc -l}.}
@@
         Notation in category theory is similar to that in set theory and type theory.
-For example, $A, B, \dots$ are used to denote objects, sets, or types, and arrows are used to denote morphisms or functions (e.g.\ $A \to B$).
+For example, \text{A, B, \dots} are used to denote objects, sets, or types, and arrows are used to denote morphisms or functions (e.g.\ \text{A \to B}).
 There is a deeper connection between category theory and type theory, which will be discussed in~\secref{subsec: curry-howard-lambek}.
@@
         \begin{definition}[Category] \label{def: category}
-            A \emph{category} $\mathcal{C}$ is specified by
-            \begin{itemize}
-                \item 
-                    a collection of objects $\textbf{obj}(\mathcal{C})$, whose elements are called $\mathcal{C}$-objects;
-                \item 
-                    for each $X, Y \in \textbf{obj}(\mathcal{C})$, a collection of morphisms $\mathcal{C}{(X,Y)}$, whose elements are called $\mathcal{C}$-morphisms from $X$ to $Y$ (e.g.\ $f : X \xrightarrow{\mathcal{C}} Y$);
-                \item 
-                    for each $X \in \textbf{obj}(\mathcal{C})$, an element $\textbf{id}_X \in \mathcal{C}{(X,X)}$ called the identity morphism on $X$;
-                \item 
-                    for each $X, Y, Z \in \textbf{obj}(\mathcal{C})$, a function 
+            A \emph{category} \text{\mathcal{C}} is specified by
+            \begin{itemize}
+                \item 
+                    a collection of objects \text{\textbf{obj}(\mathcal{C})}, whose elements are called \text{\mathcal{C}}-objects;
+                \item 
+                    for each \text{X, Y \in \textbf{obj}(\mathcal{C})}, a collection of morphisms \text{\mathcal{C}{(X,Y)}}, whose elements are called \text{\mathcal{C}}-morphisms from \text{X} to \text{Y} (e.g.\ \text{f : X \xrightarrow{\mathcal{C}} Y});
+                \item 
+                    for each \text{X \in \textbf{obj}(\mathcal{C})}, an element \text{\textbf{id}_X \in \mathcal{C}{(X,X)}} called the identity morphism on \text{X};
+                \item 
+                    for each \text{X, Y, Z \in \textbf{obj}(\mathcal{C})}, a function 
                     \[\begin{aligned}
@@
                     \textbf{(Unit)}
-                    For all $X, Y \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$, we have
+                    For all \text{X, Y \in \textbf{obj}(\mathcal{C})} and \text{f \in \mathcal{C}{(X,Y)}}, we have
                     \begin{equation} \label{law: unit}
@@
                     \textbf{(Associativity)}
-                    For all $X, Y, Z, W \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$, $g \in \mathcal{C}{(Y,Z)}$, $h \in \mathcal{C}{(Z,W)}$, we have
+                    For all \text{X, Y, Z, W \in \textbf{obj}(\mathcal{C})} and \text{f \in \mathcal{C}{(X,Y)}}, \text{g \in \mathcal{C}{(Y,Z)}}, \text{h \in \mathcal{C}{(Z,W)}}, we have
                     \begin{equation} \label{law: associativity}
@@
 
-        \begin{example}[$\mathcal{Set}$]
-            An example of category is the category of sets, denoted as $\mathcal{Set}$, specified by the following:
-            \begin{itemize}
-                \item 
-                    The objects of $\mathcal{Set}$ are small\footnote{Here the smallness condition avoids foundational issues analogous to Russell's paradox.
+        \begin{example}[\text{\mathcal{Set}}]
+            An example of category is the category of sets, denoted as \text{\mathcal{Set}}, specified by the following:
+            \begin{itemize}
+                \item 
+                    The objects of \text{\mathcal{Set}} are small\footnote{Here the smallness condition avoids foundational issues analogous to Russell's paradox.
 While we omit the formal definition of size due to the space limit here, all constructions in this work preserve smallness.} sets;
                 \item
-                    For each $X, Y \in \textbf{obj}(\mathcal{Set})$, the morphisms from $X \to Y$ in $\mathcal{Set}$ are the functions $X \to Y$;
-                \item
-                    The identity morphism on $X$ in $\mathcal{Set}$ is the identity function on $X$;
-                \item
-                    The composition of morphisms in $\mathcal{Set}$ is defined as the composition of functions.
-            \end{itemize}
-            Associativity law and unit laws are satisfied in $\mathcal{Set}$, since the composition of functions is associative and the identity function compose with any function is the function itself.
+                    For each \text{X, Y \in \textbf{obj}(\mathcal{Set})}, the morphisms from \text{X \to Y} in \text{\mathcal{Set}} are the functions \text{X \to Y};
+                \item
+                    The identity morphism on \text{X} in \text{\mathcal{Set}} is the identity function on \text{X};
+                \item
+                    The composition of morphisms in \text{\mathcal{Set}} is defined as the composition of functions.
+            \end{itemize}
+            Associativity law and unit laws are satisfied in \text{\mathcal{Set}}, since the composition of functions is associative and the identity function compose with any function is the function itself.
         \end{example}
@@
         \begin{definition}[Preorder]
-            A \emph{preorder} $\underline{P} = (P, \sqsubseteq)$ is a set $P$ with a binary relation $\sqsubseteq$ that is
-            \begin{itemize}
-                \item reflexive: $\forall x \in P, x \sqsubseteq x$;
-                \item transitive: $\forall x, y, z \in P, x \sqsubseteq y \land y \sqsubseteq z \implies x \sqsubseteq z$.
+            A \emph{preorder} \text{\underline{P} = (P, \sqsubseteq)} is a set \text{P} with a binary relation \text{\sqsubseteq} that is
+            \begin{itemize}
+                \item reflexive: \text{\forall x \in P, x \sqsubseteq x};
+                \item transitive: \text{\forall x, y, z \in P, x \sqsubseteq y \land y \sqsubseteq z \implies x \sqsubseteq z}.
             \end{itemize}
@@
         \begin{example}[Category determined by preorder] \label{ex: category_preorder}
-            Another example of category is a category $\mathcal{C}_{\underline{P}}$ determined by any preorder $\underline{P}$, which is specified by the following:
-            \begin{itemize}
-                \item 
-                    The objects of $\mathcal{C}_{\underline{P}}$ are the elements of $P$;
+            Another example of category is a category \text{\mathcal{C}_{\underline{P}}} determined by any preorder \text{\underline{P}}, which is specified by the following:
+            \begin{itemize}
+                \item 
+                    The objects of \text{\mathcal{C}_{\underline{P}}} are the elements of \text{P};
                 \item
                     $\mathcal{C}_{\underline{P}}(x,y) = \begin{cases}
-                        \{(x,y)\} & \text{if $x \sqsubseteq y$} \\
+                        \{(x,y)\} & \text{if \text{x \sqsubseteq y}} \\
                         \emptyset & \text{otherwise}
@@
                 \item
-                    The identity morphism on $X$ in $\mathcal{C}_{\underline{P}}$ is the identity function on $X$;
-                \item
-                    The composition of morphisms in $\mathcal{C}_{\underline{P}}$ is defined as the composition of functions.
-            \end{itemize}
-            Associativity law and unit laws are satisfied in $\mathcal{C}_{\underline{P}}$.
-
-            $\mathcal{C}_{\underline{P}}$ is used later for stack descriptors in the denotational semantics of the source language.
+                    The identity morphism on \text{X} in \text{\mathcal{C}_{\underline{P}}} is the identity function on \text{X};
+                \item
+                    The composition of morphisms in \text{\mathcal{C}_{\underline{P}}} is defined as the composition of functions.
+            \end{itemize}
+            Associativity law and unit laws are satisfied in \text{\mathcal{C}_{\underline{P}}}.
+
+            \text{\mathcal{C}_{\underline{P}}} is used later for stack descriptors in the denotational semantics of the source language.
         \end{example}
 
-        The idea of opposite category is that if we have a category $\mathcal{C}$, we can reverse the direction of all morphisms in $\mathcal{C}$ to obtain a new category $\mathcal{C}^{\textbf{op}}$.
+        The idea of opposite category is that if we have a category \text{\mathcal{C}}, we can reverse the direction of all morphisms in \text{\mathcal{C}} to obtain a new category \text{\mathcal{C}^{\textbf{op}}}.
 
         \begin{definition}[Opposite category] \label{def: opposite}
-            Given a category $\mathcal{C}$, its \emph{opposite category} $\mathcal{C}^{\textbf{op}}$ is specified by the following:
-            \begin{itemize}
-                \item 
-                    The objects of $\mathcal{C}^{\textbf{op}}$ are the same as those of $\mathcal{C}$;
-                \item 
-                    For each $X, Y \in \textbf{obj}(\mathcal{C})$, the morphisms from $X$ to $Y$ in $\mathcal{C}^{\textbf{op}}$ are the morphisms from $Y$ to $X$ in $\mathcal{C}$;
-                \item 
-                    The identity morphism on $X$ in $\mathcal{C}^{\textbf{op}}$ is the identity morphism on $X$ in $\mathcal{C}$;
-                \item 
-                    The composition of morphisms in $\mathcal{C}^{\textbf{op}}$ is defined as the composition of morphisms in $\mathcal{C}$.
+            Given a category \text{\mathcal{C}}, its \emph{opposite category} \text{\mathcal{C}^{\textbf{op}}} is specified by the following:
+            \begin{itemize}
+                \item 
+                    The objects of \text{\mathcal{C}^{\textbf{op}}} are the same as those of \text{\mathcal{C}};
+                \item 
+                    For each \text{X, Y \in \textbf{obj}(\mathcal{C})}, the morphisms from \text{X} to \text{Y} in \text{\mathcal{C}^{\textbf{op}}} are the morphisms from \text{Y} to \text{X} in \text{\mathcal{C}};
+                \item 
+                    The identity morphism on \text{X} in \text{\mathcal{C}^{\textbf{op}}} is the identity morphism on \text{X} in \text{\mathcal{C}};
+                \item 
+                    The composition of morphisms in \text{\mathcal{C}^{\textbf{op}}} is defined as the composition of morphisms in \text{\mathcal{C}}.
             \end{itemize}
@@
             \subsubsection{Commutative diagrams}
-            A \emph{diagram} in a category $\mathcal{C}$ is a directed graph whose vertices are $\mathcal{C}$-objects and whose edges are $\mathcal{C}$-morphisms.
-
-            A diagram is \emph{commutative} (or \emph{commutes}) if any two finite paths in the graph between any two vertices $X$ and $Y$ in the diagram determine the equal morphism $f \in \mathcal{C}{(X,Y)}$ under the composition of morphisms.
+            A \emph{diagram} in a category \text{\mathcal{C}} is a directed graph whose vertices are \text{\mathcal{C}}-objects and whose edges are \text{\mathcal{C}}-morphisms.
+
+            A diagram is \emph{commutative} (or \emph{commutes}) if any two finite paths in the graph between any two vertices \text{X} and \text{Y} in the diagram determine the equal morphism \text{f \in \mathcal{C}{(X,Y)}} under the composition of morphisms.
 
@@
         \begin{definition}[Isomorphism]
-            Given a category $\mathcal{C}$, a $\mathcal{C}$-morphism $f : X \xrightarrow{\mathcal{C}} Y$ is called an \emph{isomorphism} if there exists a morphism $g : Y \xrightarrow{\mathcal{C}} X$ such that the following diagram commutes:
+            Given a category \text{\mathcal{C}}, a \text{\mathcal{C}}-morphism \text{f : X \xrightarrow{\mathcal{C}} Y} is called an \emph{isomorphism} if there exists a morphism \text{g : Y \xrightarrow{\mathcal{C}} X} such that the following diagram commutes:
             \begin{equation}
@@
             \end{equation}
-            In other words, $f$ is an isomorphism if there exists a morphism $g$ such that $g \circ f = \textbf{id}_X$ and $f \circ g = \textbf{id}_Y$.
-
-            The morphism $g$ is uniquely determined by $f$ and is called the \emph{inverse} of $f$, denoted as $f^{-1}$.
-
-            Given two objects $X$ and $Y$ in a category $\mathcal{C}$, if there exists an isomorphism from $X$ to $Y$, we say that $X$ and $Y$ are \emph{isomorphic} in $\mathcal{C}$ and write $X \cong Y$.
+            In other words, \text{f} is an isomorphism if there exists a morphism \text{g} such that \text{g \circ f = \textbf{id}_X} and \text{f \circ g = \textbf{id}_Y}.
+
+            The morphism \text{g} is uniquely determined by \text{f} and is called the \emph{inverse} of \text{f}, denoted as \text{f^{-1}}.
+
+            Given two objects \text{X} and \text{Y} in a category \text{\mathcal{C}}, if there exists an isomorphism from \text{X} to \text{Y}, we say that \text{X} and \text{Y} are \emph{isomorphic} in \text{\mathcal{C}} and write \text{X \cong Y}.
 
@@
             \begin{definition}[Terminal object]
-                Given a category $\mathcal{C}$, an object $T \in \textbf{obj}(\mathcal{C})$ is called a \emph{terminal object} if for all $X \in \textbf{obj}(\mathcal{C})$, there exists a unique \textbf{C}-morphism $f : X \to T$.
+                Given a category \text{\mathcal{C}}, an object \text{T \in \textbf{obj}(\mathcal{C})} is called a \emph{terminal object} if for all \text{X \in \textbf{obj}(\mathcal{C})}, there exists a unique \textbf{C}-morphism \text{f : X \to T}.
             \end{definition}
@@
                 \item 
-                    If $T$ and $T'$ are both terminal objects in $\mathcal{C}$, then there exists a unique isomorphism $f : T \to T'$.
-                \item
-                    If $T$ is a terminal object in $\mathcal{C}$ and $T \cong T'$, then $T'$ is also a terminal object in $\mathcal{C}$.
-            \end{itemize}
-            \begin{example}[Terminal object in $\mathcal{Set}$]
-                $\mathcal{Set}$ has a terminal object $\{\ast\}$, which is an arbitrary singleton set containing a single element $\ast$.
-
-                For any set $X$, there exists a unique function $f : X \to \{\ast\}$ that maps every element of $X$ to the single element $\ast$ in $\{\ast\}$.
-
-                There is a unique isomorphism $f : \{\ast\} \to \{\cdot\}$ for any two singleton sets $\{\ast\}$ and $\{\cdot\}$, which is $f(\ast) = \cdot$.
+                    If \text{T} and \text{T'} are both terminal objects in \text{\mathcal{C}}, then there exists a unique isomorphism \text{f : T \to T'}.
+                \item
+                    If \text{T} is a terminal object in \text{\mathcal{C}} and \text{T \cong T'}, then \text{T'} is also a terminal object in \text{\mathcal{C}}.
+            \end{itemize}
+            \begin{example}[Terminal object in \text{\mathcal{Set}}]
+                \text{\mathcal{Set}} has a terminal object \text{\{\ast\}}, which is an arbitrary singleton set containing a single element \text{\ast}.
+
+                For any set \text{X}, there exists a unique function \text{f : X \to \{\ast\}} that maps every element of \text{X} to the single element \text{\ast} in \text{\{\ast\}}.
+
+                There is a unique isomorphism \text{f : \{\ast\} \to \{\cdot\}} for any two singleton sets \text{\{\ast\}} and \text{\{\cdot\}}, which is \text{f(\ast) = \cdot}.
             \end{example}
@@
             \begin{definition}[Binary product]
-                Given a category $\mathcal{C}$, the \emph{binary product} of two objects $X$ and $Y$ in $\mathcal{C}$ is specified by
-                \begin{itemize}
-                    \item a $\mathcal{C}$-object $X \times Y$;
-                    \item two $\mathcal{C}$-morphisms $\pi_1 : X \times Y \to X$ and $\pi_2 : X \times Y \to Y$ called the \emph{projections} of $X \times Y$;
-                \end{itemize}
-                such that for all $Z \in \textbf{obj}(\mathcal{C})$ and morphisms $f : Z \to X$ and $g : Z \to Y$, there exists a unique morphism $u : Z \to X \times Y$ such that the following diagram commutes in $\mathcal{C}$:
+                Given a category \text{\mathcal{C}}, the \emph{binary product} of two objects \text{X} and \text{Y} in \text{\mathcal{C}} is specified by
+                \begin{itemize}
+                    \item a \text{\mathcal{C}}-object \text{X \times Y};
+                    \item two \text{\mathcal{C}}-morphisms \text{\pi_1 : X \times Y \to X} and \text{\pi_2 : X \times Y \to Y} called the \emph{projections} of \text{X \times Y};
+                \end{itemize}
+                such that for all \text{Z \in \textbf{obj}(\mathcal{C})} and morphisms \text{f : Z \to X} and \text{g : Z \to Y}, there exists a unique morphism \text{u : Z \to X \times Y} such that the following diagram commutes in \text{\mathcal{C}}:
                 \begin{equation}
@@
                 \end{equation}
-                The unique morphism $u$ is written as $\ang{ f, g } : Z \to X \times Y$ where $f = \pi_1 \circ u$ and $g = \pi_2 \circ u$.
+                The unique morphism \text{u} is written as \text{\ang{ f, g } : Z \to X \times Y} where \text{f = \pi_1 \circ u} and \text{g = \pi_2 \circ u}.
             \end{definition}
@@
 
-            \begin{example}[Binary product in $\mathcal{Set}$]
-                The binary product of two sets $X$ and $Y$ in $\mathcal{Set}$ is the cartesian product $X \times Y = \{(x,y) \mid x \in X \land y \in Y\}$, where $(x,y)$ are ordered pairs.
+            \begin{example}[Binary product in \text{\mathcal{Set}}]
+                The binary product of two sets \text{X} and \text{Y} in \text{\mathcal{Set}} is the cartesian product \text{X \times Y = \{(x,y) \mid x \in X \land y \in Y\}}, where \text{(x,y)} are ordered pairs.
 
@@
                     \item 
-                        $\pi_1 : X \times Y \to X$ is defined as $\pi_1(x,y) = x$ for all $(x,y) \in X \times Y$;
-                    \item
-                        $\pi_2 : X \times Y \to Y$ is defined as $\pi_2(x,y) = y$ for all $(x,y) \in X \times Y$.
-                \end{itemize}
-
-                For any set $Z$, for any functions $f : Z \to X$ and $g : Z \to Y$, the unique morphism $u : Z \to X \times Y$ is defined as:
-                \[u(z) = (f(z), g(z)) \text{ for all $z \in Z$.}\]
+                        \text{\pi_1 : X \times Y \to X} is defined as \text{\pi_1(x,y) = x} for all \text{(x,y) \in X \times Y};
+                    \item
+                        \text{\pi_2 : X \times Y \to Y} is defined as \text{\pi_2(x,y) = y} for all \text{(x,y) \in X \times Y}.
+                \end{itemize}
+
+                For any set \text{Z}, for any functions \text{f : Z \to X} and \text{g : Z \to Y}, the unique morphism \text{u : Z \to X \times Y} is defined as:
+                \[u(z) = (f(z), g(z)) \text{ for all \text{z \in Z}.}\]
             \end{example}
@@
             \begin{definition}[Exponential]
-                Given a category $\mathcal{C}$ with binary products, the \emph{exponential} of two objects $X$ and $Y$ in $\mathcal{C}$ is specified by
-                \begin{itemize}
-                    \item a $\mathcal{C}$-object $X \Rightarrow Y$;
-                    \item a $\mathcal{C}$-morphism $\textbf{app} : (X \Rightarrow Y) \times X \to Y$ called the \emph{application} of $X \Rightarrow Y$;
-                \end{itemize}
-                such that for all $Z \in \textbf{obj}(\mathcal{C})$ and morphisms $f : Z \times X \to Y$, there exists a unique morphism $u : Z \to X \Rightarrow Y$ such that the following diagram commutes in $\mathcal{C}$:
+                Given a category \text{\mathcal{C}} with binary products, the \emph{exponential} of two objects \text{X} and \text{Y} in \text{\mathcal{C}} is specified by
+                \begin{itemize}
+                    \item a \text{\mathcal{C}}-object \text{X \Rightarrow Y};
+                    \item a \text{\mathcal{C}}-morphism \text{\textbf{app} : (X \Rightarrow Y) \times X \to Y} called the \emph{application} of \text{X \Rightarrow Y};
+                \end{itemize}
+                such that for all \text{Z \in \textbf{obj}(\mathcal{C})} and morphisms \text{f : Z \times X \to Y}, there exists a unique morphism \text{u : Z \to X \Rightarrow Y} such that the following diagram commutes in \text{\mathcal{C}}:
                 \begin{equation}
@@
                 \end{equation}
-                We write $\textbf{cur} f$ for the unique morphism $u$ such that $f = \textbf{app} \circ (\textbf{cur} f \times \textbf{id}_X)$, 
-                where $\textbf{cur} f$ is called the \emph{currying} of $f$.
+                We write \text{\textbf{cur} f} for the unique morphism \text{u} such that \text{f = \textbf{app} \circ (\textbf{cur} f \times \textbf{id}_X)}, 
+                where \text{\textbf{cur} f} is called the \emph{currying} of \text{f}.
             \end{definition}
@@
 
-            \begin{example}[Exponential in $\mathcal{Set}$]
-                The exponential of two sets $X$ and $Y$ in $\mathcal{Set}$ is the set of all functions from $X$ to $Y$.
-
-                Function application gives the morphism $\textbf{app} : (X \Rightarrow Y) \times X \to Y$ as $\textbf{app}(f,x) = f(x)$ for all $f \in X \Rightarrow Y$ and $x \in X$.
-
-                The currying operation transform a function $f : Z \times X \to Y$ into a function $\textbf{cur} f : Z \to (X \Rightarrow Y)$, which is defined as $\textbf{cur} f(z) = \lambda x.f(z,x)$ for all $z \in Z$ and $x \in X$.
+            \begin{example}[Exponential in \text{\mathcal{Set}}]
+                The exponential of two sets \text{X} and \text{Y} in \text{\mathcal{Set}} is the set of all functions from \text{X} to \text{Y}.
+
+                Function application gives the morphism \text{\textbf{app} : (X \Rightarrow Y) \times X \to Y} as \text{\textbf{app}(f,x) = f(x)} for all \text{f \in X \Rightarrow Y} and \text{x \in X}.
+
+                The currying operation transform a function \text{f : Z \times X \to Y} into a function \text{\textbf{cur} f : Z \to (X \Rightarrow Y)}, which is defined as \text{\textbf{cur} f(z) = \lambda x.f(z,x)} for all \text{z \in Z} and \text{x \in X}.
             \end{example}
@@
         \begin{definition}[Cartesian closed category]
-            A category $\mathcal{C}$ is called a \emph{cartesian closed category} (CCC) if it has a terminal object, binary products and exponentials of any two objects.
+            A category \text{\mathcal{C}} is called a \emph{cartesian closed category} (CCC) if it has a terminal object, binary products and exponentials of any two objects.
         \end{definition}
@@
         \begin{definition}[Functor] \label{def: functor}
-            Given two categories $\mathcal{C}$ and $\mathcal{D}$, a \emph{functor} $F: \mathcal{C} \to \mathcal{D}$ is specified by
+            Given two categories \text{\mathcal{C}} and \text{\mathcal{D}}, a \emph{functor} \text{F: \mathcal{C} \to \mathcal{D}} is specified by
             \begin{itemize}
@@
                 \item 
-                    for each $X, Y \in \textbf{obj}(\mathcal{C})$, a function referred to as functorial mapping
+                    for each \text{X, Y \in \textbf{obj}(\mathcal{C})}, a function referred to as functorial mapping
                     \[\begin{aligned}
@@
                 \item 
-                    For all $X, Y \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$, we have: $ F(\textbf{id}_X) = \textbf{id}_{F(X)}$
-                \item
-                    For all $X, Y, Z \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$, $g \in \mathcal{C}{(Y,Z)}$, we have: $F(g \circ f) = F(g) \circ F(f)$
+                    For all \text{X, Y \in \textbf{obj}(\mathcal{C})} and \text{f \in \mathcal{C}{(X,Y)}}, we have: \text{ F(\textbf{id}_X) = \textbf{id}_{F(X)}}
+                \item
+                    For all \text{X, Y, Z \in \textbf{obj}(\mathcal{C})} and \text{f \in \mathcal{C}{(X,Y)}}, \text{g \in \mathcal{C}{(Y,Z)}}, we have: \text{F(g \circ f) = F(g) \circ F(f)}
             \end{itemize}
@@
 
-            Given two categories $\mathcal{C}$ and $\mathcal{D}$, and two functors $F,G: \mathcal{C} \to \mathcal{D}$, a \emph{natural transformation} $\theta : F \to G$ is a family of morphisms $\theta_X \in \mathcal{D}{(F(X),G(X))}$ for each $X \in \textbf{obj}(\mathcal{C})$ such that for all $X, Y \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$, the following diagram
+            Given two categories \text{\mathcal{C}} and \text{\mathcal{D}}, and two functors \text{F,G: \mathcal{C} \to \mathcal{D}}, a \emph{natural transformation} \text{\theta : F \to G} is a family of morphisms \text{\theta_X \in \mathcal{D}{(F(X),G(X))}} for each \text{X \in \textbf{obj}(\mathcal{C})} such that for all \text{X, Y \in \textbf{obj}(\mathcal{C})} and \text{f \in \mathcal{C}{(X,Y)}}, the following diagram
             \begin{equation}
@@
 
-            commutes in $\mathcal{D}$, i.e. $G(f) \circ \theta_X = \theta_Y \circ F(f)$
+            commutes in \text{\mathcal{D}}, i.e. \text{G(f) \circ \theta_X = \theta_Y \circ F(f)}
 
@@
         \begin{definition}[Functor category]
-            Given two categories $\mathcal{C}$ and $\mathcal{D}$, the \emph{functor category} $\mathcal{D}^{\mathcal{C}}$ is the category satisfying the following:
-            \begin{itemize}
-                \item 
-                    The objects of $\mathcal{D}^{\mathcal{C}}$ are all functors $\mathcal{C} \to \mathcal{D}$;
-                \item 
-                    Given two functors $F,G: \mathcal{C} \to \mathcal{D}$, the morphisms from $F$ to $G$ in $\mathcal{D}^{\mathcal{C}}$ are all natural transformations $\theta : F \to G$;
-                \item
-                    Composition and identity morphisms in $\mathcal{D}^{\mathcal{C}}$ are defined as follows:
-                    \begin{itemize}
-                        \item 
-                            The identity morphism $\textbf{id}_F$ on $F$ is defined as $\theta_X = \textbf{id}_{F(X)}$ for all $X \in \textbf{obj}(\mathcal{C})$;
-                        \item
-                            The composition of two natural transformations $\theta : F \to G$ and $\phi : G \to H$ is defined as $(\phi \circ \theta)_X = \phi_X \circ \theta_X$ for all $X \in \textbf{obj}(\mathcal{C})$.
+            Given two categories \text{\mathcal{C}} and \text{\mathcal{D}}, the \emph{functor category} \text{\mathcal{D}^{\mathcal{C}}} is the category satisfying the following:
+            \begin{itemize}
+                \item 
+                    The objects of \text{\mathcal{D}^{\mathcal{C}}} are all functors \text{\mathcal{C} \to \mathcal{D}};
+                \item 
+                    Given two functors \text{F,G: \mathcal{C} \to \mathcal{D}}, the morphisms from \text{F} to \text{G} in \text{\mathcal{D}^{\mathcal{C}}} are all natural transformations \text{\theta : F \to G};
+                \item
+                    Composition and identity morphisms in \text{\mathcal{D}^{\mathcal{C}}} are defined as follows:
+                    \begin{itemize}
+                        \item 
+                            The identity morphism \text{\textbf{id}_F} on \text{F} is defined as \text{\theta_X = \textbf{id}_{F(X)}} for all \text{X \in \textbf{obj}(\mathcal{C})};
+                        \item
+                            The composition of two natural transformations \text{\theta : F \to G} and \text{\phi : G \to H} is defined as \text{(\phi \circ \theta)_X = \phi_X \circ \theta_X} for all \text{X \in \textbf{obj}(\mathcal{C})}.
                     \end{itemize}
@@
         A presheaf is a contravariant functor, which means that it reverses the direction of morphisms.
-In other words, a presheaf is a functor that takes objects in $\mathcal{C}$ and assigns them sets, and takes morphisms in $\mathcal{C}^{\textbf{op}}$ and assigns them functions between the corresponding sets.
+In other words, a presheaf is a functor that takes objects in \text{\mathcal{C}} and assigns them sets, and takes morphisms in \text{\mathcal{C}^{\textbf{op}}} and assigns them functions between the corresponding sets.
         \begin{definition}[Presheaf]
-            Given a category $\mathcal{C}$, a \emph{presheaf} on $\mathcal{C}$ is a functor $F: \mathcal{C}^{\textbf{op}} \to \mathcal{Set}$.
-            The presheaf $F$ is defined as follows:
-            \begin{itemize}
-                \item 
-                    For each $X \in \textbf{obj}(\mathcal{C})$, $F(X)$ is a set;
-                \item
-                    For each $X, Y \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$, $F(f)$ is a function $F(Y) \to F(X)$.
+            Given a category \text{\mathcal{C}}, a \emph{presheaf} on \text{\mathcal{C}} is a functor \text{F: \mathcal{C}^{\textbf{op}} \to \mathcal{Set}}.
+            The presheaf \text{F} is defined as follows:
+            \begin{itemize}
+                \item 
+                    For each \text{X \in \textbf{obj}(\mathcal{C})}, \text{F(X)} is a set;
+                \item
+                    For each \text{X, Y \in \textbf{obj}(\mathcal{C})} and \text{f \in \mathcal{C}{(X,Y)}}, \text{F(f)} is a function \text{F(Y) \to F(X)}.
             \end{itemize}
@@
         \begin{definition}[Presheaf category]
-            Given a category $\mathcal{C}$, the \emph{presheaf category} $\hat{\mathcal{C}}$ is the functor category $\mathcal{Set}^{\mathcal{C}^{\textbf{op}}}$, which explicitly contains the following:
-            \begin{itemize}
-                \item 
-                    The objects of $\hat{\mathcal{C}}$ are all presheaves on $\mathcal{C}$;
-                \item
-                    Given two presheaves $F,G: \mathcal{C}^{\textbf{op}} \to \mathcal{Set}$, the morphisms from $F$ to $G$ in $\hat{\mathcal{C}}$ are all natural transformations $\theta : F \to G$.
+            Given a category \text{\mathcal{C}}, the \emph{presheaf category} \text{\hat{\mathcal{C}}} is the functor category \text{\mathcal{Set}^{\mathcal{C}^{\textbf{op}}}}, which explicitly contains the following:
+            \begin{itemize}
+                \item 
+                    The objects of \text{\hat{\mathcal{C}}} are all presheaves on \text{\mathcal{C}};
+                \item
+                    Given two presheaves \text{F,G: \mathcal{C}^{\textbf{op}} \to \mathcal{Set}}, the morphisms from \text{F} to \text{G} in \text{\hat{\mathcal{C}}} are all natural transformations \text{\theta : F \to G}.
             \end{itemize}
@@
         \begin{definition}[Yoneda functor] \label{def: yoneda}
-            Given a category $\mathcal{C}$, the \emph{Yoneda functor} $\yo: \mathcal{C} \to \hat{\mathcal{C}}$ is defined as follows:
-            \begin{itemize}
-                \item 
-                    For each $X \in \textbf{obj}(\mathcal{C})$, $\yo(X)$ is the functor $\mathcal{C}^{\textbf{op}} \to \mathcal{Set}$ defined as:
+            Given a category \text{\mathcal{C}}, the \emph{Yoneda functor} \text{\yo: \mathcal{C} \to \hat{\mathcal{C}}} is defined as follows:
+            \begin{itemize}
+                \item 
+                    For each \text{X \in \textbf{obj}(\mathcal{C})}, \text{\yo(X)} is the functor \text{\mathcal{C}^{\textbf{op}} \to \mathcal{Set}} defined as:
                     \begin{equation} \label{eq: yoneda_element}
@@
                     \end{equation}
-                    for all $Y \in \textbf{obj}(\mathcal{C})$;
-                \item
-                    For each $X, Y \in \textbf{obj}(\mathcal{C})$ and $f \in \mathcal{C}{(X,Y)}$, $\yo(f)$ is the morphism $\yo(X) \to \yo(Y)$ defined a natural transformation whose component at any given $Z \in \mathcal{C}^{\textbf{op}}$ is given by:
+                    for all \text{Y \in \textbf{obj}(\mathcal{C})};
+                \item
+                    For each \text{X, Y \in \textbf{obj}(\mathcal{C})} and \text{f \in \mathcal{C}{(X,Y)}}, \text{\yo(f)} is the morphism \text{\yo(X) \to \yo(Y)} defined a natural transformation whose component at any given \text{Z \in \mathcal{C}^{\textbf{op}}} is given by:
                     \begin{equation} \label{eq: yoneda_morphism}
@@
                     \end{equation}
-                    for all $Z \in \textbf{obj}(\mathcal{C})$.
+                    for all \text{Z \in \textbf{obj}(\mathcal{C})}.
                 \end{itemize}
@@
         \begin{theorem}[Yoneda lemma]
-            For each small\footnote{See footnote 1.} category $\mathcal{C}$, the \emph{Yoneda lemma} states that for each object $X \in \textbf{obj}(\mathcal{C})$ and each presheaf $F \in \hat{\mathcal{C}}$, there exists a natural isomorphism
+            For each small\footnote{See footnote 1.} category \text{\mathcal{C}}, the \emph{Yoneda lemma} states that for each object \text{X \in \textbf{obj}(\mathcal{C})} and each presheaf \text{F \in \hat{\mathcal{C}}}, there exists a natural isomorphism
             \begin{equation} \label{eq: yoneda_lemma}
@@
         \begin{prf}[Cartesian closed structure in presheaf categories]
-            Given a small\footnote{See footnote 1.} category $\mathcal{C}$, the presheaf category $\hat{\mathcal{C}}$ is a cartesian closed category.
-            \begin{itemize}
-                \item 
-                    The terminal object in $\hat{\mathcal{C}}$ is the constant functor $\mathbf{1} : \mathcal{C}^{\textbf{op}} \to \mathcal{Set}$, given by 
+            Given a small\footnote{See footnote 1.} category \text{\mathcal{C}}, the presheaf category \text{\hat{\mathcal{C}}} is a cartesian closed category.
+            \begin{itemize}
+                \item 
+                    The terminal object in \text{\hat{\mathcal{C}}} is the constant functor \text{\mathbf{1} : \mathcal{C}^{\textbf{op}} \to \mathcal{Set}}, given by 
                     \begin{equation}
@@
                 \item
-                    The binary product in $\hat{\mathcal{C}}$ is given by the product of functors, which is defined as follows:
+                    The binary product in \text{\hat{\mathcal{C}}} is given by the product of functors, which is defined as follows:
                     \begin{equation}
@@
                 \item
-                    The exponential in $\hat{\mathcal{C}}$ is derived from the Yoneda lemma,
+                    The exponential in \text{\hat{\mathcal{C}}} is derived from the Yoneda lemma,
                     \begin{equation}
@@
 
-        In Agda we use the $\og{\mathsf{data}}$ keyword to define a type.
-Every type has a type, and we use $\mb{\mathsf{Set}}$ to denote the type of all small types.
+        In Agda we use the \text{\og{\mathsf{data}}} keyword to define a type.
+Every type has a type, and we use \text{\mb{\mathsf{Set}}} to denote the type of all small types.
 To define a type, we specify its type and its constructors.
@@
 
-        Here a data type $\mb{\mathsf{Vec}}$ is defined for vectors. The type of vectors is dependent on the length of the vector. With dependent types, we can encode properties directly into types.
+        Here a data type \text{\mb{\mathsf{Vec}}} is defined for vectors.
+The type of vectors is dependent on the length of the vector.
+With dependent types, we can encode properties directly into types.
 
@@
         With equality as a type, whenever we want to prove that two terms are equal, we need to provide a witness of the equality.
-For example if we want to prove $x \equiv y$, we write out a term of type \textit{x} \mb{\textsf{≡}} \textit{y}, and then give its definition, which constructs a proof of the equality.
+For example if we want to prove \text{x \equiv y}, we write out a term of type \textit{x} \mb{\textsf{≡}} \textit{y}, and then give its definition, which constructs a proof of the equality.
 All of the examples here are type-checked by Agda, so they are all valid proofs.
@@
     \section{Source Language} \label{sec: source}
-    % A simply typed lambda calculus (STLC) is a typed lambda calculus with only one type constructor ($\Rightarrow$) \footnote{Normally we use $\to$ to denote the function type, but here we use $\Rightarrow$ to be consistent with the notation in Agda, as $\to$ is a primitive in Agda.} that builds function types.
+    % A simply typed lambda calculus (STLC) is a typed lambda calculus with only one type constructor (\text{\Rightarrow}) \footnote{Normally we use \text{\to} to denote the function type, but here we use \text{\Rightarrow} to be consistent with the notation in Agda, as \text{\to} is a primitive in Agda.} that builds function types.
     The source language is a simply typed lambda calculus (STLC) with store, following the syntax in Reynolds' paper~\autocite{Reynolds}.
@@
         \subsubsection{Subtypes}
-        I use the preorder $A ≤: B$ to denote the subtype relation $A$ is a subtype of $B$, as it has the following properties:
+        I use the preorder \text{A ≤: B} to denote the subtype relation \text{A} is a subtype of \text{B}, as it has the following properties:
         \begin{figure}[H]
@@
         \[ \textsf{intvar} \leq: \textsf{intexp} \qquad \textsf{intvar} \leq: \textsf{intacc} \]
-        since a variable can be used as an expression (e.g. $\mathsf{x} + 1$) or an acceptor (e.g. $\mathsf{x} := 1$).
+        since a variable can be used as an expression (e.g. \text{\mathsf{x} + 1}) or an acceptor (e.g. \text{\mathsf{x} := 1}).
 
@@
         \item 
-            $\bracket{\textsf{L}_{\textit{sd}}}$: left-hand sides
-        \item 
-            $\bracket{\textsf{S}_{\textit{sd}}}$: simple right-hand sides
-        \item
-            $\bracket{\textsf{R}_{\textit{sd}}}$: right-hand sides
-        \item
-            $\bracket{\textsf{I}_{\textit{sd}}}$: instruction sequences
-    \end{itemize}
-    The intent of the indexing here is any instructions with the form $\bracket{\textsf{I}_{\textit{sd}}}$ is an instruction sequence that can be executed when the current stack descriptor is $\textit{sd}$.
+            \text{\bracket{\textsf{L}_{\textit{sd}}}}: left-hand sides
+        \item 
+            \text{\bracket{\textsf{S}_{\textit{sd}}}}: simple right-hand sides
+        \item
+            \text{\bracket{\textsf{R}_{\textit{sd}}}}: right-hand sides
+        \item
+            \text{\bracket{\textsf{I}_{\textit{sd}}}}: instruction sequences
+    \end{itemize}
+    The intent of the indexing here is any instructions with the form \text{\bracket{\textsf{I}_{\textit{sd}}}} is an instruction sequence that can be executed when the current stack descriptor is \text{\textit{sd}}.
 
@@
 
-    The stack descriptor $\textit{sd}$ is defined as a pair of natural numbers $\ang{f, d}$, where $f$ is the frame number and $d$ is the displacement.
+    The stack descriptor \text{\textit{sd}} is defined as a pair of natural numbers \text{\ang{f, d}}, where \text{f} is the frame number and \text{d} is the displacement.
 
@@
 
-    For a stack descriptor $\textit{sd}$, we can use \dpink{SD.f} $\textit{sd}$ to access the frame number and \dpink{SD.d} $\textit{sd}$ to access the displacement.
+    For a stack descriptor \text{\textit{sd}}, we can use \dpink{SD.f} \text{\textit{sd}} to access the frame number and \dpink{SD.d} \text{\textit{sd}} to access the displacement.
 
     \subsubsection{Order}
-    The stack descriptor is ordered lexicographically with $\leq_\mathsf{s}$ as follows:
+    The stack descriptor is ordered lexicographically with \text{\leq_\mathsf{s}} as follows:
     \[\ang{f, d} \leq_\mathsf{s} \ang{f', d'} \Leftrightarrow f < f' \lor (f = f' \land d \leq d')\]
@@
     For subtraction, we need to make sure that the subtraction is valid, i.e.
-$\ang{f, d} -\mathsf{s} n$ is only defined for $n \leq d$.
+\text{\ang{f, d} -\mathsf{s} n} is only defined for \text{n \leq d}.
 This leads us to the problem of defining the subtraction of natural numbers, which is explained in detail in~\secref{subsec: subtraction}.
@@
             \hhline{|=|=|}
-            \mbt{≤ₛ-refl} & $\forall sd.\ sd \leq_\mathsf{s} sd$ \\
-            \hline
-            \mbt{≤ₛ-trans} & $\forall sd, sd', sd''.\ sd \leq_\mathsf{s} sd' \land sd' \leq_\mathsf{s} sd'' \Rightarrow sd \leq_\mathsf{s} sd''$ \\
-            \hline
-            \mbt{+ₛ→≤ₛ} & $\forall sd, n.\ sd \leq_\mathsf{s} sd +_\mathsf{s} n$ \\
-            \hline
-            \mbt{sub-sd≤ₛ} & $\forall sd, sd', sd''. sd' \equiv sd'' \land sd \leq_\mathsf{s} sd' \Rightarrow sd \leq_\mathsf{s} sd''$ \\
-            \hline
-            \mbt{–ₛ≡} & $\forall f, d, d′, n.\ d′ - n \equiv d \Rightarrow \ang{f, d} \equiv \ang{f, d′} -_\mathsf{s} n$ \\
+            \mbt{≤ₛ-refl} & \text{\forall sd.\ sd \leq_\mathsf{s} sd} \\
+            \hline
+            \mbt{≤ₛ-trans} & \text{\forall sd, sd', sd''.\ sd \leq_\mathsf{s} sd' \land sd' \leq_\mathsf{s} sd'' \Rightarrow sd \leq_\mathsf{s} sd''} \\
+            \hline
+            \mbt{+ₛ→≤ₛ} & \text{\forall sd, n.\ sd \leq_\mathsf{s} sd +_\mathsf{s} n} \\
+            \hline
+            \mbt{sub-sd≤ₛ} & \text{\forall sd, sd', sd''. sd' \equiv sd'' \land sd \leq_\mathsf{s} sd' \Rightarrow sd \leq_\mathsf{s} sd''} \\
+            \hline
+            \mbt{–ₛ≡} & \text{\forall f, d, d′, n.\ d′ - n \equiv d \Rightarrow \ang{f, d} \equiv \ang{f, d′} -_\mathsf{s} n} \\
             \hline
@@
     \end{table}
-    % We can use reflexivity and transitivity of the order $<$ and $\leq$ to prove that the order of stack descriptors $\leq_\mathsf{s}$ is a preorder. The proof in Agda is as follows:
+    % We can use reflexivity and transitivity of the order \text{<} and \text{\leq} to prove that the order of stack descriptors \text{\leq_\mathsf{s}} is a preorder. The proof in Agda is as follows:
     % \begin{proof}
-    %     We need to show that $\leq_\mathsf{s}$ is reflexive and transitive. 
+    %     We need to show that \text{\leq_\mathsf{s}} is reflexive and transitive. 
     %     \begin{itemize}
     %         \item 
-    %             Reflexivity: $\textit{sd} \leq_\mathsf{s} \textit{sd}$ is trivially true since $f = f$ and $d \leq d$.
+    %             Reflexivity: \text{\textit{sd} \leq_\mathsf{s} \textit{sd}} is trivially true since \text{f = f} and \text{d \leq d}.
     %         \item
-    %             Transitivity: if $\ang{f, d} \leq_\mathsf{s} \ang{f', d'}$ and $\ang{f', d'} \leq_\mathsf{s} \ang{f'', d''}$, we do the following case split:
+    %             Transitivity: if \text{\ang{f, d} \leq_\mathsf{s} \ang{f', d'}} and \text{\ang{f', d'} \leq_\mathsf{s} \ang{f'', d''}}, we do the following case split:
     %             \begin{enumerate}
     %                 \item 
-    %                     If $f < f'$, $f' = f''$ and $d \leq d'$, then $f < f''$; 
+    %                     If \text{f < f'}, \text{f' = f''} and \text{d \leq d'}, then \text{f < f''}; 
     %                 \item 
-    %                     If $f < f'$ and $f' < f''$, then $f < f''$ by transitivity of $<$;
+    %                     If \text{f < f'} and \text{f' < f''}, then \text{f < f''} by transitivity of \text{<};
     %                 \item
-    %                     If $f = f'$, $d \leq d'$ and $f' < f''$, then $f < f''$;
+    %                     If \text{f = f'}, \text{d \leq d'} and \text{f' < f''}, then \text{f < f''};
     %                 \item
-    %                     Otherwise $f = f''$ and $d \leq d''$ by transitivity of $\leq$.
-\footnote{Note that the properties of $=$ is not required in as in the Agda definition of $\leq_\mathsf{s}$, we directly define $f'$ to be $f$ instead of defining a equivalence relation, thus equivalence can be checked directly via type checking.}
+    %                     Otherwise \text{f = f''} and \text{d \leq d''} by transitivity of \text{\leq}.
+\footnote{Note that the properties of \text{=} is not required in as in the Agda definition of \text{\leq_\mathsf{s}}, we directly define \text{f'} to be \text{f} instead of defining a equivalence relation, thus equivalence can be checked directly via type checking.}
     %             \end{enumerate}
@@
     \subsection{Grammar} \label{subsec: grammar}
-    The grammar of the target language\footnote{This grammar can be extended with subroutines as an \textsf{L} command, and conditionals as an \textsf{I} command} is defined as follows, given the current stack descriptor $\textit{sd} = \ang{f, d}$, and new stack descriptor $\textit{sd′}$ and $\textit{sd\textsuperscript{v}}$:
+    The grammar of the target language\footnote{This grammar can be extended with subroutines as an \textsf{L} command, and conditionals as an \textsf{I} command} is defined as follows, given the current stack descriptor \text{\textit{sd} = \ang{f, d}}, and new stack descriptor \text{\textit{sd′}} and \text{\textit{sd\textsuperscript{v}}}:
     \begin{figure}[H]
@@
         % \item 
-        %     $\texttt{sbrs}$: a register used to communicate the result of function procedures implemented by closed subroutines.
-        \item 
-            $\texttt{lit}$: a literal integer.
-        \item 
-            $\texttt{stop}$: stops the execution of the program.
-        \item 
-            $\delta$: an integer representing the displacement adjustment.
-        \item 
-            $\texttt{adjustdisp}$: adjusts the displacement of specified stack descriptor.
-        \item 
-            $\texttt{popto}$: pops to the specified stack descriptor, which is used to reduce the number of frames.
+        %     \text{\texttt{sbrs}}: a register used to communicate the result of function procedures implemented by closed subroutines.
+        \item 
+            \text{\texttt{lit}}: a literal integer.
+        \item 
+            \text{\texttt{stop}}: stops the execution of the program.
+        \item 
+            \text{\delta}: an integer representing the displacement adjustment.
+        \item 
+            \text{\texttt{adjustdisp}}: adjusts the displacement of specified stack descriptor.
+        \item 
+            \text{\texttt{popto}}: pops to the specified stack descriptor, which is used to reduce the number of frames.
     \end{itemize}
@@
     % \subsubsection{Instruction sequences}
-    In the instruction sequences, $\delta$ as a displacement adjustment can be positive, zero or negative.
-To make a rigorous definition, I define $\delta$ as a natural number, and treat the positive and negative displacements as two different instructions, using addition and subtraction of stack descriptors respectively.
+    In the instruction sequences, \text{\delta} as a displacement adjustment can be positive, zero or negative.
+To make a rigorous definition, I define \text{\delta} as a natural number, and treat the positive and negative displacements as two different instructions, using addition and subtraction of stack descriptors respectively.
 
@@
             \textbf{Specialised Requirements}: The standard library's definitions (e.g.
-subtraction as monus, `$\dotdiv$') do not align with my project's need for a rigorously defined subtraction operation.
+subtraction as monus, `\text{\dotdiv}') do not align with my project's need for a rigorously defined subtraction operation.
 This is specified in~\secref{subsec: subtraction}.
@@
             \textbf{Verification Clarity}: By defining the basic data types and functions from scratch, I can tailor properties (e.g.
-the property `$n-[n-m] \equiv m$') to my specific requirements, and avoid unnecessary complexity (e.g.
-`$\leq$' being also defined as a boolean predicate in the standard library).
+the property `\text{n-[n-m] \equiv m}') to my specific requirements, and avoid unnecessary complexity (e.g.
+`\text{\leq}' being also defined as a boolean predicate in the standard library).
         \item
@@
         \item 
-            Natural numbers ($\mb{\bN}$), integers ($\mb{\bZ}$) and addition (\mbt{+}).
-        \item
-            Equality (\mbt{≡}), congruence ($\mb{\mathsf{cong}}$), substitution ($\mb{\mathsf{sub}}$) and transitivity of equality ($\mb{\mathsf{trans}}$).
+            Natural numbers (\text{\mb{\bN}}), integers (\text{\mb{\bZ}}) and addition (\mbt{+}).
+        \item
+            Equality (\mbt{≡}), congruence (\text{\mb{\mathsf{cong}}}), substitution (\text{\mb{\mathsf{sub}}}) and transitivity of equality (\text{\mb{\mathsf{trans}}}).
         \item
@@
             \hhline{|=|=|}
-            \mbt{+-identity\textsuperscript{r}} & $\forall n \in \bN.\ n + 0 = n$ \\
-            \hline
-            \mbt{+-suc\textsuperscript{r}}& $\forall m, n \in \bN.\ m + \textsf{suc } n = \textsf{suc } (m + n)$ \\
-            \hline
-            \mbt{+-comm\textsuperscript{r}} & $\forall m, n \in \bN.\ m + n \equiv n + m$ \\
-            \hline
-            \mbt{≤-irrelevant} & For all $m, n \in \bN$, we consider all proofs of $m \leq n$ to be equal. \\
-            \hline
-            \mbt{≤-refl} & $\forall n \in \bN.\ n \leq n$ \\
-            \hline
-            \mbt{≤-trans} & $\forall m, n, p \in \bN.\ m \leq n \land n \leq p \Rightarrow m \leq p$ \\
-            \hline
-            \mbt{n≤suc-n} & $\forall n \in \bN.\ n \leq \textsf{suc } n$ \\
-            \hline
-            \mbt{m≡n,p≤n}\mb{$\to$}\mbt{p≤m} & $\forall p, m, n \in \bN.\ m \equiv n \land p \leq n \Rightarrow p \leq m$ \\
-            \hline
-            \mbt{+}\mb{$\to$}\mbt{≤} & $\forall m, n \in \bN.\ m \leq m + n$ \\
-            \hline
-            \mbt{+}\mb{$\to$}\mb{≤\textsuperscript{r}} & $\forall m, n \in \bN.\ m \leq n + m$ \\
-            \hline
-            \mbt{<-trans} & $\forall m, n, p \in \bN.\ m < n \land n < p \Rightarrow m < p$ \\
-            \hline
-            \mbt{<}\mb{$\to$}\mbt{s≤} & $\forall m, n \in \bN.\ m < n \Rightarrow \textsf{suc } m \leq n$ \\
-            \hline
-            \mbt{<}\mb{$\to$}\mbt{≤} & $\forall m, n \in \bN.\ m < n \Rightarrow m \leq n$ \\
-            \hline
-            \mbt{≤-compare} & $\forall m, n \in \bN.\ m \leq n \lor n \leq m$ \\
+            \mbt{+-identity\textsuperscript{r}} & \text{\forall n \in \bN.\ n + 0 = n} \\
+            \hline
+            \mbt{+-suc\textsuperscript{r}}& \text{\forall m, n \in \bN.\ m + \textsf{suc } n = \textsf{suc } (m + n)} \\
+            \hline
+            \mbt{+-comm\textsuperscript{r}} & \text{\forall m, n \in \bN.\ m + n \equiv n + m} \\
+            \hline
+            \mbt{≤-irrelevant} & For all \text{m, n \in \bN}, we consider all proofs of \text{m \leq n} to be equal. \\
+            \hline
+            \mbt{≤-refl} & \text{\forall n \in \bN.\ n \leq n} \\
+            \hline
+            \mbt{≤-trans} & \text{\forall m, n, p \in \bN.\ m \leq n \land n \leq p \Rightarrow m \leq p} \\
+            \hline
+            \mbt{n≤suc-n} & \text{\forall n \in \bN.\ n \leq \textsf{suc } n} \\
+            \hline
+            \mbt{m≡n,p≤n}\mb{\text{\to}}\mbt{p≤m} & \text{\forall p, m, n \in \bN.\ m \equiv n \land p \leq n \Rightarrow p \leq m} \\
+            \hline
+            \mbt{+}\mb{\text{\to}}\mbt{≤} & \text{\forall m, n \in \bN.\ m \leq m + n} \\
+            \hline
+            \mbt{+}\mb{\text{\to}}\mb{≤\textsuperscript{r}} & \text{\forall m, n \in \bN.\ m \leq n + m} \\
+            \hline
+            \mbt{<-trans} & \text{\forall m, n, p \in \bN.\ m < n \land n < p \Rightarrow m < p} \\
+            \hline
+            \mbt{<}\mb{\text{\to}}\mbt{s≤} & \text{\forall m, n \in \bN.\ m < n \Rightarrow \textsf{suc } m \leq n} \\
+            \hline
+            \mbt{<}\mb{\text{\to}}\mbt{≤} & \text{\forall m, n \in \bN.\ m < n \Rightarrow m \leq n} \\
+            \hline
+            \mbt{≤-compare} & \text{\forall m, n \in \bN.\ m \leq n \lor n \leq m} \\
             \hline
@@
     % \subsection{Equality, congruence and substitution}
-    % The definition of equality, congruence and substitution is similar to the one in~\secref{subsec: equality}.\footnote{The definition of equality and related properties in the custom library differ slightly by using an indexed $\mb{\mathsf{Set}}$, which provides a more general formulation.
+    % The definition of equality, congruence and substitution is similar to the one in~\secref{subsec: equality}.\footnote{The definition of equality and related properties in the custom library differ slightly by using an indexed \text{\mb{\mathsf{Set}}}, which provides a more general formulation.
 See Appendix [corresponding link].}
@@
     % \subsection{Order of natural numbers} \label{subsec: order}
-    % The order of natural numbers we defined include $\leq$ and $<$, we use a simplified definition compared to the one in the standard library as follows:
+    % The order of natural numbers we defined include \text{\leq} and \text{<}, we use a simplified definition compared to the one in the standard library as follows:
     % \[\includegraphics[scale=1.2]{/lib/order.pdf}\]
@@
     % \subsubsection{Transitivity and reflexivity}
-    % The transitivity and reflexivity of the order $<$ and $\leq$ are defined as follows:
+    % The transitivity and reflexivity of the order \text{<} and \text{\leq} are defined as follows:
     % \[\includegraphics[scale=1.2]{/lib/order_proof.pdf}\]
@@
     % \subsubsection{Implication of order}
-    % We know that $\forall m, n \in \bN$, if $m < n$, then we have $m + 1 \leq n$ and $m \leq n$. This is defined in Agda as follows:
+    % We know that \text{\forall m, n \in \bN}, if \text{m < n}, then we have \text{m + 1 \leq n} and \text{m \leq n}. This is defined in Agda as follows:
     % \[\includegraphics[scale=1.2]{/lib/order_implication.pdf}\]
@@
     % It is useful to case split the order of natural numbers, i.e.
-for any $m, n \in \bN$, we have $m \leq n$ or $n \leq m$.
-This is defined in Agda by defining either case as an instance of the \mb{\textsf{Total}} type, and then showing that for any $m, n \in \bN$, we can construct a \mb{\textsf{Total}} type by case-split and \og{\textsf{with}}-construct.
+for any \text{m, n \in \bN}, we have \text{m \leq n} or \text{n \leq m}.
+This is defined in Agda by defining either case as an instance of the \mb{\textsf{Total}} type, and then showing that for any \text{m, n \in \bN}, we can construct a \mb{\textsf{Total}} type by case-split and \og{\textsf{with}}-construct.
 The proof is as follows:
@@
     % \subsubsection{Other properties}
-    % We can show that when a number $n$ is added to a natural number $m$, the result is greater than or equal to $m$. This is defined in Agda as follows:
+    % We can show that when a number \text{n} is added to a natural number \text{m}, the result is greater than or equal to \text{m}. This is defined in Agda as follows:
     % \[\includegraphics[scale=1.2]{/lib/order_add.pdf}\]
@@
     \subsection{Subtraction} \label{subsec: subtraction}
-    In the standard library~\autocite{agda_std}, the subtraction of natural numbers is defined as follows:\footnote{The definition in the standard library directly uses symbol $\mathsf{-}$, but here for clarity we use $\mathsf{\dotdiv}$ instead.}
+    In the standard library~\autocite{agda_std}, the subtraction of natural numbers is defined as follows:\footnote{The definition in the standard library directly uses symbol \text{\mathsf{-}}, but here for clarity we use \text{\mathsf{\dotdiv}} instead.}
     \[\includegraphics[scale=1.2]{minus.pdf}\]
-    Mathematically we have $ n \dotdiv m = \max(0, n - m)$.
+    Mathematically we have \text{ n \dotdiv m = \max(0, n - m)}.
 This definition is valid and ensures that the result is a natural number.
@@
         \item 
-            The definition of $\dotdiv$ is not suitable for this project.
-Input $n$ should be guaranteed not to be less than $m$, and at any point in the program if there is a subtraction where $n < m$, the program should fail to type check instead of making $0$ type check with it.
+            The definition of \text{\dotdiv} is not suitable for this project.
+Input \text{n} should be guaranteed not to be less than \text{m}, and at any point in the program if there is a subtraction where \text{n < m}, the program should fail to type check instead of making \text{0} type check with it.
         \item
             We do not have many numerical properties of natural numbers that are required for the implementation of the compiler.
-For example, $n \dotdiv m + m = n$ or $n \dotdiv (n \dotdiv m) = m$ are not guaranteed to hold if we allow $n < m$.
+For example, \text{n \dotdiv m + m = n} or \text{n \dotdiv (n \dotdiv m) = m} are not guaranteed to hold if we allow \text{n < m}.
     \end{itemize}
@@
     Instead of include the proof directly, we can define the type of the subtrahend to be dependent on the minuend, where the dependence encodes the proof.
-There is a standard library in Agda on finite sets, where a type $\mb{\mathsf{Fin}}$ is defined as a type that depends on a natural number $n$, where $\mb{\mathsf{Fin}}\ n$ can be seen as the set of natural numbers less than $n$.
+There is a standard library in Agda on finite sets, where a type \text{\mb{\mathsf{Fin}}} is defined as a type that depends on a natural number \text{n}, where \text{\mb{\mathsf{Fin}}\ n} can be seen as the set of natural numbers less than \text{n}.
 The definition is as follows:
@@
 
-    An intuitive explanation of the definition of $\mb{\mathsf{Fin}}$ is as follows:
-    \begin{itemize}
-        \item Base case: when $n = 0$, we do not have any constructor that gives us an element of type $\mb{\mathsf{Fin}}\ 0$, corresponding to the empty set. 
+    An intuitive explanation of the definition of \text{\mb{\mathsf{Fin}}} is as follows:
+    \begin{itemize}
+        \item Base case: when \text{n = 0}, we do not have any constructor that gives us an element of type \text{\mb{\mathsf{Fin}}\ 0}, corresponding to the empty set. 
         \item Inductive case: 
@@
             \includegraphics[width=0.5\textwidth]{fin_inductive.pdf}
-            \caption{Inductive case of $\mb{\mathsf{Fin}}$}
+            \caption{Inductive case of \text{\mb{\mathsf{Fin}}}}
             \label{fig: fin_inductive}
@@
 
-    For subtraction, we only need to change the type of the subtrahend to $\mb{\mathsf{Fin}}\ (\gn{\mathsf{suc}}\ n)$ compared to the implementation of addition. The definition in Agda is as follows:
+    For subtraction, we only need to change the type of the subtrahend to \text{\mb{\mathsf{Fin}}\ (\gn{\mathsf{suc}}\ n)} compared to the implementation of addition.
+The definition in Agda is as follows:
     \[\includegraphics[scale=1.2]{/lib/fin/minus.pdf}\]
@@
     The explicit approach carries proofs directly in the type system, which is more transparent but verbose.
-The $\textsf{Fin}$-based approach initially appears to be more elegant, as it encapsulates bounds check within a refined type.
-However, this elegance is superficial: constructing a term of type $\mb{\mathsf{Fin}}\ n$ still requires the same underlying proof of boundedness, shifting complexity to auxiliary conversions.
-
-    To prove a property with the $\textsf{Fin}$-based approach, we need the following auxiliary function:
+The \text{\textsf{Fin}}-based approach initially appears to be more elegant, as it encapsulates bounds check within a refined type.
+However, this elegance is superficial: constructing a term of type \text{\mb{\mathsf{Fin}}\ n} still requires the same underlying proof of boundedness, shifting complexity to auxiliary conversions.
+
+    To prove a property with the \text{\textsf{Fin}}-based approach, we need the following auxiliary function:
     \[\includegraphics[scale=1.2]{/lib/fin/toFin.pdf}\]
 
-    Here is a comparison of the two approaches representing  $\mathsf{suc}\ (n - m) \equiv \mathsf{suc}\ n - m$:
+    Here is a comparison of the two approaches representing  \text{\mathsf{suc}\ (n - m) \equiv \mathsf{suc}\ n - m}:
     \begin{figure}[H]
@@
 the type of the term directly mirrors the mathematical statement with an explicit proof.
-In contrast, the $\textsf{Fin}$-based approach fractures this relationship, and reconstructing the original subtrahend requires tracing the type of the proof.
+In contrast, the \text{\textsf{Fin}}-based approach fractures this relationship, and reconstructing the original subtrahend requires tracing the type of the proof.
 This becomes cumbersome when the proofs are chained inequalities with transitivity, making the code harder to understand.
@@
             \hhline{|=|=|}
-            \mbt{–-irrelevant} & \makecell{For all $m, n \in \bN$, we consider all terms of $n-m$ \\ with different proofs of $m \leq n$ to be equal.} \\
-            \hline
-            \mbt{–}\mb{$\to$}\mbt{≤}& $\forall m, n \in \bN.\ m \leq n \Rightarrow m - n \leq m$ \\
-            \hline
-            \mbt{n–n≡0} & $\forall n \in \bN.\ n - n \equiv 0$ \\
-            \hline
-            \mbt{–-suc} & $\forall m, n \in \bN.\ \mathsf{suc}\ (n - m) \equiv \mathsf{suc}\ n - m$ \\
-            \hline
-            \mbt{n–[n–m]≡m} & $\forall m, n \in \bN.\ m \leq n \Rightarrow n - (n - m) \equiv m$ \\
-            \hline
-            \mbt{n+m–m≡n} & $\forall m, n \in \bN.\ n + m - m \equiv n$ \\
-            \hline
-            \mbt{suc-d≤d′}\mb{\to}\mbt{d≤d′–[d′–[suc-d]]} & $\forall d, d' \in \bN.\ \textsf{suc } d \leq d' \Rightarrow d \leq d' - (d' - \textsf{suc } d)$ \\
+            \mbt{–-irrelevant} & \makecell{For all \text{m, n \in \bN}, we consider all terms of \text{n-m} \\ with different proofs of \text{m \leq n} to be equal.} \\
+            \hline
+            \mbt{–}\mb{\text{\to}}\mbt{≤}& \text{\forall m, n \in \bN.\ m \leq n \Rightarrow m - n \leq m} \\
+            \hline
+            \mbt{n–n≡0} & \text{\forall n \in \bN.\ n - n \equiv 0} \\
+            \hline
+            \mbt{–-suc} & \text{\forall m, n \in \bN.\ \mathsf{suc}\ (n - m) \equiv \mathsf{suc}\ n - m} \\
+            \hline
+            \mbt{n–[n–m]≡m} & \text{\forall m, n \in \bN.\ m \leq n \Rightarrow n - (n - m) \equiv m} \\
+            \hline
+            \mbt{n+m–m≡n} & \text{\forall m, n \in \bN.\ n + m - m \equiv n} \\
+            \hline
+            \mbt{suc-d≤d′}\mb{\to}\mbt{d≤d′–[d′–[suc-d]]} & \text{\forall d, d' \in \bN.\ \textsf{suc } d \leq d' \Rightarrow d \leq d' - (d' - \textsf{suc } d)} \\
             \hline
@@
     % The equations in the table above are used later in the implementation of the compiler to prove that for instructions with displacement, the given displacement is valid.
-Here is the mathematical proof of the property $\mb{\mathsf{n\mathord{-}[n\mathord{-}m]\mathord{\equiv}m}}$:
+Here is the mathematical proof of the property \text{\mb{\mathsf{n\mathord{-}[n\mathord{-}m]\mathord{\equiv}m}}}:
     % \begin{proof}
-    %     We need to show that $n - (n - m) \equiv m$ for all $m, n \in \bN$ such that $m \leq n$. We do the following case split:
+    %     We need to show that \text{n - (n - m) \equiv m} for all \text{m, n \in \bN} such that \text{m \leq n}. We do the following case split:
     %     \begin{itemize}
     %         \item 
-    %             If $m = 0$, then the term reduces to $n - n \equiv 0$, which is a term we have already proved.
+    %             If \text{m = 0}, then the term reduces to \text{n - n \equiv 0}, which is a term we have already proved.
     %         \item
-    %             Otherwise it is guaranteed that $m = \mathsf{suc}\ m'$ for some $m' \in \bN$, and $n = \mathsf{suc}\ n'$ for some $n' \in \bN$, because $m \leq n$.
-The term reduces to $\mathsf{suc}\ n' - (n' - m') \equiv \mathsf{suc}\ m'$.
-With congruence, we can reduce the term to $n' - (n' - m') \equiv m'$, which is the inductive hypothesis.
+    %             Otherwise it is guaranteed that \text{m = \mathsf{suc}\ m'} for some \text{m' \in \bN}, and \text{n = \mathsf{suc}\ n'} for some \text{n' \in \bN}, because \text{m \leq n}.
+The term reduces to \text{\mathsf{suc}\ n' - (n' - m') \equiv \mathsf{suc}\ m'}.
+With congruence, we can reduce the term to \text{n' - (n' - m') \equiv m'}, which is the inductive hypothesis.
     %     \end{itemize}
@@
     \subsection{Presheaf semantics}
-    The denotation semantics interprets types as presheaves over a base category $\Upsigma$. 
+    The denotation semantics interprets types as presheaves over a base category \text{\Upsigma}. 
     \subsubsection{Base category}
-    The base category $\Upsigma$ is specified as follows:
-    \begin{itemize}
-        \item Objects are stack descriptors ($\textit{sd} = \ang{f, d}$);
-        \item Morphisms are stack expansions ($\iota : \textit{sd} \to \textit{sd′}$ for $\textit{sd} \leq_\mathsf{s} \textit{sd′}$).
-    \end{itemize}
-    We define $\mathsf{SD}$ as the set of stack descriptors.
-Then the base category is the category determined by preorder $\underline{\mathsf{SD}} = \{\mathsf{SD}, \leq_\mathsf{s}\}$ in Example~\ref{ex: category_preorder}.
+    The base category \text{\Upsigma} is specified as follows:
+    \begin{itemize}
+        \item Objects are stack descriptors (\text{\textit{sd} = \ang{f, d}});
+        \item Morphisms are stack expansions (\text{\iota : \textit{sd} \to \textit{sd′}} for \text{\textit{sd} \leq_\mathsf{s} \textit{sd′}}).
+    \end{itemize}
+    We define \text{\mathsf{SD}} as the set of stack descriptors.
+Then the base category is the category determined by preorder \text{\underline{\mathsf{SD}} = \{\mathsf{SD}, \leq_\mathsf{s}\}} in Example~\ref{ex: category_preorder}.
 
     \subsubsection{Semantic category}
-    Semantic category $\mathcal{K}$ is the functor category $\text{PDOM}^{\Upsigma^{\textbf{op}}}$, where $\text{PDOM}$ is the category of predomains and continuous functions.
-    \begin{itemize}
-        \item Objects are presheaves: $P = \Upsigma^{\textbf{op}} \to \text{PDOM}$;
-        \item Morphisms are natural transformations: $\eta : P \to Q$ for $P, Q \in \text{PDOM}^{\Upsigma^{\textbf{op}}}$.
+    Semantic category \text{\mathcal{K}} is the functor category \text{\text{PDOM}^{\Upsigma^{\textbf{op}}}}, where \text{\text{PDOM}} is the category of predomains and continuous functions.
+    \begin{itemize}
+        \item Objects are presheaves: \text{P = \Upsigma^{\textbf{op}} \to \text{PDOM}};
+        \item Morphisms are natural transformations: \text{\eta : P \to Q} for \text{P, Q \in \text{PDOM}^{\Upsigma^{\textbf{op}}}}.
     \end{itemize}
@@
     \begin{itemize}
-        \item Products are given by pointwise product of presheaves: $P \times Q = \lambda \textit{sd}.\ P\ \textit{sd} \times Q\ \textit{sd}$.
-        \item Exponentials $P \Rightarrow_s Q$ are given by the following equation:
+        \item Products are given by pointwise product of presheaves: \text{P \times Q = \lambda \textit{sd}.\ P\ \textit{sd} \times Q\ \textit{sd}}.
+        \item Exponentials \text{P \Rightarrow_s Q} are given by the following equation:
                 \[\begin{aligned}
@@
                     &\cong \lambda \textit{sd}.\{F \mid \textit{sd′} \in \Upsigma^{\textbf{op}}, F : (\Upsigma^{\textbf{op}}(\textit{sd′}, \textit{sd}) \times P)\ \textit{sd′} \to Q\ \textit{sd′}\} \\
-                    &\makebox[0.8\linewidth][r]{\text{by definition of $\yo$ in Definition~\ref{def: yoneda}}}\\
+                    &\makebox[0.8\linewidth][r]{\text{by definition of \text{\yo} in Definition~\ref{def: yoneda}}}\\
                     &\cong \lambda \textit{sd}.\{F \mid \textit{sd′} \in \Upsigma, F : (\Upsigma(\textit{sd}, \textit{sd′}) \times P)\ \textit{sd′} \to Q\ \textit{sd′}\} \\
@@
                     &\cong \lambda \textit{sd}.\{F \mid \textit{sd′} \in \Upsigma, F : \textit{sd} \leq_\mathsf{s} \textit{sd′} \to P\ \textit{sd′} \to Q\ \textit{sd′}\} \\
-                    &\makebox[0.8\linewidth][r]{\text{by definition of $\Upsigma$ above}}\\
+                    &\makebox[0.8\linewidth][r]{\text{by definition of \text{\Upsigma} above}}\\
                 \end{aligned}\]
@@
     \begin{itemize}
-        \item $\textit{sd} \leq_\mathsf{s} \textit{sd′}$ means the new stack descriptor $\textit{sd′}$ is larger than the old stack descriptor $\textit{sd}$, representing the dynamic expansion of the stack during execution.
-
-        \item $P$ and $Q$ are denotational semantics of types. 
-    \end{itemize}
-    The exponential $P \Rightarrow_\textsf{s} Q$ is a function that given a proof of stack growth, transforming a $P$-value at $\textit{sd′}$ into a $Q$-value at $\textit{sd′}$, and the $\forall{\textit{sd′}}$ quantifier guarantees it works no matter how the stack grows.
-It is designed in this way so that a functor $\intp{-} : \Theta \to \mathcal{K}$ exists that interprets the type constructor $\Rightarrow$ as the exponential functor $\Rightarrow_s$.
+        \item \text{\textit{sd} \leq_\mathsf{s} \textit{sd′}} means the new stack descriptor \text{\textit{sd′}} is larger than the old stack descriptor \text{\textit{sd}}, representing the dynamic expansion of the stack during execution.
+
+        \item \text{P} and \text{Q} are denotational semantics of types. 
+    \end{itemize}
+    The exponential \text{P \Rightarrow_\textsf{s} Q} is a function that given a proof of stack growth, transforming a \text{P}-value at \text{\textit{sd′}} into a \text{Q}-value at \text{\textit{sd′}}, and the \text{\forall{\textit{sd′}}} quantifier guarantees it works no matter how the stack grows.
+It is designed in this way so that a functor \text{\intp{-} : \Theta \to \mathcal{K}} exists that interprets the type constructor \text{\Rightarrow} as the exponential functor \text{\Rightarrow_s}.
 
     \subsection{Continuations}
-    In Reynolds' model, we construct $\mathsf{Compl}$ and $\mathsf{Intcompl}$\footnote{In the work of Reynolds, $\mathsf{compl}$ and $\mathsf{intcompl}$ are introduced as new types in the source language, and the definitions here are the denotational semantics of those types, respectively.
+    In Reynolds' model, we construct \text{\mathsf{Compl}} and \text{\mathsf{Intcompl}}\footnote{In the work of Reynolds, \text{\mathsf{compl}} and \text{\mathsf{intcompl}} are introduced as new types in the source language, and the definitions here are the denotational semantics of those types, respectively.
 Since these two introduced types are only used for the denotational semantics, I think directly defining them as denotational semantics constructs is natural and sufficient.} as tools in the denotational semantics to represent command continuations and integer continuations, respectively.
@@
     \[\mathsf{Compl}\ \textit{sd} : \mathsf{SD} \to O \qquad \mathsf{Intcompl}\ \textit{sd} : \bZ \to (\mathsf{SD} \to O)\]
-    where $O$ is an unspecified domain of outputs.
+    where \text{O} is an unspecified domain of outputs.
 
@@
     \[\mathsf{Intcompl} = R \Rightarrow_s \mathsf{Compl} \]
-    where $R$ is the functor corresponding to the right-hand sides in the target language, $R\ \textit{sd} = \textsf{R}_{\textit{sd}}$.
+    where \text{R} is the functor corresponding to the right-hand sides in the target language, \text{R\ \textit{sd} = \textsf{R}_{\textit{sd}}}.
 This works because the right-hand sides are all integer expressions we can use according to the grammar of the target language.
@@
 
-    Thus we can directly use the definition of $R$ in the target language to define the integer continuation as follows:
+    Thus we can directly use the definition of \text{R} in the target language to define the integer continuation as follows:
     \[\includegraphics[scale=1.2]{/compiler/continuations.pdf}\]
@@
     The denotational semantics of terms is defined as a functor.
-Before we define its object mapping, we need to define the functorial mapping, which acts on the morphisms of the base category $\Upsigma$.
-
-    Since the morphisms of the base category $\Upsigma$ are stack expansions, the functorial mapping essentially lifts a semantic object indexed by a stack descriptor $\textit{sd}$ to a semantic object indexed by a larger stack descriptor $\textit{sd′}$.
+Before we define its object mapping, we need to define the functorial mapping, which acts on the morphisms of the base category \text{\Upsigma}.
+
+    Since the morphisms of the base category \text{\Upsigma} are stack expansions, the functorial mapping essentially lifts a semantic object indexed by a stack descriptor \text{\textit{sd}} to a semantic object indexed by a larger stack descriptor \text{\textit{sd′}}.
 This ensures the denotational semantics of terms remains valid when the stack grows.
 
-    Functorial mapping for exponentials is simple, as the exponential \textit{P} $\mathsf{\Rightarrow_\textsf{S}}$ \textit{Q} \textit{sd} can transforms a $P$-value at any $\textit{sd′}$ greater than $\textit{sd}$ into a $Q$-value at $\textit{sd′}$.
-To construct a new exponential of type $\mathsf{P \Rightarrow_\textsf{S} Q\ \textit{sd′}}$, we simply take a new $P$-value at $\textit{sd″}$ which is greater than $\textit{sd′}$, and use the original exponential to transform it into a $Q$-value at $\textit{sd′}$, as $\textit{sd″}$ is guaranteed to be greater than $\textit{sd}$ due to the transitivity of order of the stack descriptors.
+    Functorial mapping for exponentials is simple, as the exponential \textit{P} \text{\mathsf{\Rightarrow_\textsf{S}}} \textit{Q} \textit{sd} can transforms a \text{P}-value at any \text{\textit{sd′}} greater than \text{\textit{sd}} into a \text{Q}-value at \text{\textit{sd′}}.
+To construct a new exponential of type \text{\mathsf{P \Rightarrow_\textsf{S} Q\ \textit{sd′}}}, we simply take a new \text{P}-value at \text{\textit{sd″}} which is greater than \text{\textit{sd′}}, and use the original exponential to transform it into a \text{Q}-value at \text{\textit{sd′}}, as \text{\textit{sd″}} is guaranteed to be greater than \text{\textit{sd}} due to the transitivity of order of the stack descriptors.
 
@@
     \subsubsection[Functorial mapping for instruction sequences]{Functorial mapping for instruction sequences}
-    The functorial mapping of the denotational semantics of instruction sequences is defined as follows, assuming the stack descriptor $\textit{sd′} = \ang{f',d'}$ is greater than $\textit{sd} = \ang{f,d}$:
-    \begin{itemize}
-        \item When $f < f'$, we use the $\mathsf{popto}$ instruction that directly pops the stack to $\textit{sd}$;
-        \item When $f' = f$ and $d < d'$, we use $\mathsf{adjustdisp}$ to decrease the displacement by $d'-d$.
-    \end{itemize}
-    In the Agda implementation, we also need to show that after the the adjustment, the stack descriptor is now $\textit{sd}$.
-This requires the term $\mb{\mathsf{n\mathord{-}[n\mathord{-}m]\mathord{\equiv}m}}$ proved in~\secref{subsec: properties_sub}.
+    The functorial mapping of the denotational semantics of instruction sequences is defined as follows, assuming the stack descriptor \text{\textit{sd′} = \ang{f',d'}} is greater than \text{\textit{sd} = \ang{f,d}}:
+    \begin{itemize}
+        \item When \text{f < f'}, we use the \text{\mathsf{popto}} instruction that directly pops the stack to \text{\textit{sd}};
+        \item When \text{f' = f} and \text{d < d'}, we use \text{\mathsf{adjustdisp}} to decrease the displacement by \text{d'-d}.
+    \end{itemize}
+    In the Agda implementation, we also need to show that after the the adjustment, the stack descriptor is now \text{\textit{sd}}.
+This requires the term \text{\mb{\mathsf{n\mathord{-}[n\mathord{-}m]\mathord{\equiv}m}}} proved in~\secref{subsec: properties_sub}.
 The functorial mapping of the denotational semantics of instruction sequences is defined as follows:
@@
         \subsubsection{Subtyping}
-        The idea of subtyping is to use a term of type $A$ as a term of type $A'$, where $A$ is a subtype of $A'$.
-We define an auxiliary function that takes in the subtype relation $A\leq:A'$ and the denotational semantics of $A$, and returns the denotational semantics of $A'$.
+        The idea of subtyping is to use a term of type \text{A} as a term of type \text{A'}, where \text{A} is a subtype of \text{A'}.
+We define an auxiliary function that takes in the subtype relation \text{A\leq:A'} and the denotational semantics of \text{A}, and returns the denotational semantics of \text{A'}.
         \begin{itemize}
@@
         \begin{itemize}
-            \item For lambda, we need to extend the context $\gamma$ with the extra variable in the lambda term. This is done by using the functorial mapping of the denotational semantics of contexts.
+            \item For lambda, we need to extend the context \text{\gamma} with the extra variable in the lambda term.
+This is done by using the functorial mapping of the denotational semantics of contexts.
             \item For application, we simply apply the denotational semantics of the lambda term to the denotational semantics of the argument, where the proof is simply the reflexivity of the order of stack descriptors.
@@
         \begin{itemize}
-            \item For skip, we simply return the continuation $\kappa$ without changing it.
-            \item For sequence, we need to prefix the continuation with the denotational semantics of the second command, and then prefix it with the denotational semantics of the first command, as the continuation $\kappa$ is to be performed after both commands.
+            \item For skip, we simply return the continuation \text{\kappa} without changing it.
+            \item For sequence, we need to prefix the continuation with the denotational semantics of the second command, and then prefix it with the denotational semantics of the first command, as the continuation \text{\kappa} is to be performed after both commands.
             \item For assignment, the definition is similar to sequence, as we need to prefix the continuation with the denotational semantics of the integer accepter and then prefix it with the denotational semantics of the integer expression.
@@
         \begin{enumerate}
-            \item an assignment with displacement adjustment $1$, representing the new variable;
+            \item an assignment with displacement adjustment \text{1}, representing the new variable;
             \item the denotational semantics of the command where this variable is used;
-            \item an adjustment of the stack descriptor by $-1$, which deallocates the new variable.
+            \item an adjustment of the stack descriptor by \text{-1}, which deallocates the new variable.
         \end{enumerate}
@@
         \begin{itemize}
-            \item a stack descriptor increased by $1$ to include the new variable;
+            \item a stack descriptor increased by \text{1} to include the new variable;
             \item an extended denotational semantics of the context, which includes the new variable.
@@
         \begin{itemize}
-            \item The expression component fills the a given integer continuation $\beta$ with the stack descriptor for the new variable;
-            \item The acceptor component prefixes the continuation $\kappa$ with an assignment of the new variable.
+            \item The expression component fills the a given integer continuation \text{\beta} with the stack descriptor for the new variable;
+            \item The acceptor component prefixes the continuation \text{\kappa} with an assignment of the new variable.
         \end{itemize}
@@
         \subsubsection{Integer expression} \label{subsubsec: compiler_intexp}
-        The denotational semantics of type $\mathsf{intexp}$ is an exponential from an integer continuation to a command continuation.
-We need to fill the integer continuation with appropriate $R$ terms to get the command continuation.
-        \begin{itemize}
-            \item For integer literals, we can simply fill in the integer literal (as an $\mathsf{R}$ term) to the integer continuation $\beta$.
-            \item For addition and negation, we wish to fill the negation or the sum of the given expression(s) to the integer continuation $\beta$.
+        The denotational semantics of type \text{\mathsf{intexp}} is an exponential from an integer continuation to a command continuation.
+We need to fill the integer continuation with appropriate \text{R} terms to get the command continuation.
+        \begin{itemize}
+            \item For integer literals, we can simply fill in the integer literal (as an \text{\mathsf{R}} term) to the integer continuation \text{\beta}.
+            \item For addition and negation, we wish to fill the negation or the sum of the given expression(s) to the integer continuation \text{\beta}.
 However, this is only possible when the given expression(s) are simple left-hand sides, as the grammar of the target language in Figure~\ref{fig: target_grammar} restricts right-hand sides to contain at most one operator.
@@
         \end{itemize}
-        With \textsf{use-temp}, the denotational semantics of addition and negation is simply wrapping $\beta$ with a lambda function using \textsf{use-temp} to get temporary variable(s) of the given expression(s), and directly fill the negation or the sum of the variable(s) to the integer continuation $\beta$.
+        With \textsf{use-temp}, the denotational semantics of addition and negation is simply wrapping \text{\beta} with a lambda function using \textsf{use-temp} to get temporary variable(s) of the given expression(s), and directly fill the negation or the sum of the variable(s) to the integer continuation \text{\beta}.
 Note that in the denotational semantics of addition, we need to use the functorial mapping of simple right-hand sides for the first argument, as the stack may grow during the evaluation of the second argument.
@@
         \begin{itemize}
-            \item If it is, we simply fill the expression to the integer continuation $\beta$.\footnote{The type of $\beta$ here is actually a bit different to integer continuation I defined, as it only accepts simple right-hand sides instead of right-hand sides.
+            \item If it is, we simply fill the expression to the integer continuation \text{\beta}.\footnote{The type of \text{\beta} here is actually a bit different to integer continuation I defined, as it only accepts simple right-hand sides instead of right-hand sides.
 Reynolds gave a wrong definition of the type of this term.
 I have corrected it in my Agda implementation.}
-            \item If it is not, we need to use a temporary variable to store the result of the expression, and then fill the temporary variable to the integer continuation $\beta$.
+            \item If it is not, we need to use a temporary variable to store the result of the expression, and then fill the temporary variable to the integer continuation \text{\beta}.
         \end{itemize}
@@
         \subsubsection{Compilation for closed program} \label{subsubsec: compilation}
-        To define a compilation function for closed programs in the source language, we use the denotational semantics of terms and fill in the initial stack descriptor ($\ang{0, 0}$), the empty context (\textsf{unit}), a trivial proof for stack descriptor being not less than itself (\textsf{≤ₛ-refl}) and the continuation representing the last instruction (\textsf{stop}):
+        To define a compilation function for closed programs in the source language, we use the denotational semantics of terms and fill in the initial stack descriptor (\text{\ang{0, 0}}), the empty context (\textsf{unit}), a trivial proof for stack descriptor being not less than itself (\textsf{≤ₛ-refl}) and the continuation representing the last instruction (\textsf{stop}):
         \[\includegraphics[scale=1.2]{/compiler/compilation.pdf}\]
@@
     \section{Tests}
-    The best way to evaluate a formalised compiler project is to formalise compiler correctness, which requires the full definition of the operational semantics of the source language and the target language, and then prove that for any program $e$ in the source language and the program $e'$ it compiles to in the target language, the value $v'$ that $e'$ evaluates to is also the compilation of the value $v$ that $e$ evaluates to.
+    The best way to evaluate a formalised compiler project is to formalise compiler correctness, which requires the full definition of the operational semantics of the source language and the target language, and then prove that for any program \text{e} in the source language and the program \text{e'} it compiles to in the target language, the value \text{v'} that \text{e'} evaluates to is also the compilation of the value \text{v} that \text{e} evaluates to.
 Due to time limitations, this is beyond the scope of this project.
@@
     %     \setcounter{enumi}{-1}
-    %     \item $\mathsf{skip}$
-    %     \item $\mathsf{x := 2}$
-    %     \item $\mathsf{x := (\mathnormal{\lambda} a.\ a)\ 4}$
-    %     \item $\mathsf{x := (\mathnormal{\lambda} a.\ (\mathnormal{\lambda} b.\ a+b)\ 2)\ 3}$
-    %     \item[\textbf{Test 3′.}] $\mathsf{x := 3 + 2}$
-    %     \item $\mathsf{x := -3;\ y := (\mathnormal{\lambda} a. x)\ 2}$
-    %     \item $\mathsf{x := 2;\ x := x + 1}$
-    %     \item[\textbf{Test 5′.}] $\mathsf{x := 2;\ skip;\ x := x + 1}$
-    %     \item $\mathsf{x := 2;\ x := -x + 1}$
-    %     \item $\mathsf{x := (\mathnormal{\lambda} a.\ -a+1)\ 2}$
+    %     \item \text{\mathsf{skip}}
+    %     \item \text{\mathsf{x := 2}}
+    %     \item \text{\mathsf{x := (\mathnormal{\lambda} a.\ a)\ 4}}
+    %     \item \text{\mathsf{x := (\mathnormal{\lambda} a.\ (\mathnormal{\lambda} b.\ a+b)\ 2)\ 3}}
+    %     \item[\textbf{Test 3′.}] \text{\mathsf{x := 3 + 2}}
+    %     \item \text{\mathsf{x := -3;\ y := (\mathnormal{\lambda} a. x)\ 2}}
+    %     \item \text{\mathsf{x := 2;\ x := x + 1}}
+    %     \item[\textbf{Test 5′.}] \text{\mathsf{x := 2;\ skip;\ x := x + 1}}
+    %     \item \text{\mathsf{x := 2;\ x := -x + 1}}
+    %     \item \text{\mathsf{x := (\mathnormal{\lambda} a.\ -a+1)\ 2}}
     % \end{enumerate}
@@
             \hhline{|=|=|}
-            \textbf{Test 0} & $\mathsf{skip}$ \\
-            \hline
-            \textbf{Test 1} & $\mathsf{x := 2}$ \\
-            \hline
-            \textbf{Test 2} & $\mathsf{x := (\mathnormal{\lambda} a.\ a)\ 4}$ \\
-            \hline
-            \textbf{Test 3} & $\mathsf{x := (\mathnormal{\lambda} a.\ (\mathnormal{\lambda} b.\ a+b)\ 2)\ 3}$ \\
-            \hline
-            \textbf{Test 3′} & $\mathsf{x := 3 + 2}$ \\
-            \hline
-            \textbf{Test 4} & $\mathsf{x := -3;\ y := (\mathnormal{\lambda} a. x)\ 2}$ \\
-            \hline
-            \textbf{Test 5} & $\mathsf{x := 2;\ x := x + 1}$ \\
-            \hline
-            \textbf{Test 5′} & $\mathsf{x := 2;\ skip;\ x := x + 1}$ \\
-            \hline
-            \textbf{Test 6} & $\mathsf{x := 2;\ x := -x + 1}$ \\
-            \hline
-            \textbf{Test 7} & $\mathsf{x := (\mathnormal{\lambda} a.\ -a+1)\ 2}$ \\
+            \textbf{Test 0} & \text{\mathsf{skip}} \\
+            \hline
+            \textbf{Test 1} & \text{\mathsf{x := 2}} \\
+            \hline
+            \textbf{Test 2} & \text{\mathsf{x := (\mathnormal{\lambda} a.\ a)\ 4}} \\
+            \hline
+            \textbf{Test 3} & \text{\mathsf{x := (\mathnormal{\lambda} a.\ (\mathnormal{\lambda} b.\ a+b)\ 2)\ 3}} \\
+            \hline
+            \textbf{Test 3′} & \text{\mathsf{x := 3 + 2}} \\
+            \hline
+            \textbf{Test 4} & \text{\mathsf{x := -3;\ y := (\mathnormal{\lambda} a. x)\ 2}} \\
+            \hline
+            \textbf{Test 5} & \text{\mathsf{x := 2;\ x := x + 1}} \\
+            \hline
+            \textbf{Test 5′} & \text{\mathsf{x := 2;\ skip;\ x := x + 1}} \\
+            \hline
+            \textbf{Test 6} & \text{\mathsf{x := 2;\ x := -x + 1}} \\
+            \hline
+            \textbf{Test 7} & \text{\mathsf{x := (\mathnormal{\lambda} a.\ -a+1)\ 2}} \\
             \hline
@@
 
-    \textbf{Test 5} and \textbf{Test 5′} are equivalent in terms of compilation because $\mathsf{skip}$ is a no-op in the source language.
+    \textbf{Test 5} and \textbf{Test 5′} are equivalent in terms of compilation because \text{\mathsf{skip}} is a no-op in the source language.
 
@@
                 & \multirow{2}{*}{\textsc{Sub}} 
-                    & \textsf{intvar} $\leq:$ \textsf{intacc} & 1, 2, 3, 3′, 4, 5, 5′, 6, 7  \\ \cline{3-4}
-                &   & \textsf{intvar} $\leq:$ \textsf{intexp} & 4, 5, 5′, 6 \\
+                    & \textsf{intvar} \text{\leq:} \textsf{intacc} & 1, 2, 3, 3′, 4, 5, 5′, 6, 7  \\ \cline{3-4}
+                &   & \textsf{intvar} \text{\leq:} \textsf{intexp} & 4, 5, 5′, 6 \\
             \hline
